### 2013-09-07 Disseration/article.tex
Disseration

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}

%opening
\title{Bag of Words 3D object categorization based on scale-invariant features}
\author{Adam Kosiorek}
\bibliographystyle{abbrv}
\begin{document}

\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}

  Mobile robotics has already begun its entrance into our households. It is conceivable that numerous tasks from our daily routines will be no
  longer of our interest, for personal robotic assistanst will take care of them. Among their most obvious duties are now or will be:
  cleaning, cooking  and elderly care. A robot aspiring to become a personal assistant has a number of requirements to fullfil. These 
  requirements might consist of, but are not limited to: an ability of simultaneous localization and mapping or SLAM, a clever human-machine 
  interface and a capability of interaction with its enviornment. As for the last part, a capacity of object categorization is essential. One 
  has to bear in mind that the categorization is very different from: recognition, content based image retrieval or CBIR and detection as outlined
  in \cite{csurka2004visual}.

  An intermediate image representation that seems to yield the best results in scene classification, 2D object categorization and 3D shape retrieval
  over the past decade as seen in \cite{fei2005bayesian}, \cite{csurka2004visual}, \cite{li2010investigating} and \cite{tsai2012bag}
  is a Bag of Words model. It seems that it has not been used for 3D object categorization so far.

  Bag of Words model has numerous advantages over raw images. Firstly, with appropriate features used for word formation the resulting 
  representation can be invariant to affine transforms and lighting conditions. Moreover, it addresses the issue of a semantic gap. It is 
  challanging to determine whether certain low level visual features (or their description) are characteristic for any higher-level object.
  On the other hand, clustering thousands of such described features yields a relatively low number of intermediate level features - the visual words.

  A typicial pipeline for Bag of Words scene or object categorization is as follows:
  \begin{itemize}
  \item Points or regions of interest have to be detected.
  \item Each keypoint have to be described, thus resulting in a point in multi-dimensional space (or a vector)
  \item Every vector have to be assigned to a corresponding term from a pre-constructed visual vocabulary by a vector 
  quantization algorithm.
  \item The obtained histograms of visual words has to be fed into a multi-class classification algorithm.
  \end{itemize}

  Csurka \textit{et al} \cite{csurka2004visual} has presented a bag of words framework for 2D object categorization. They have employed the
  Harris affine detector for keypoint detection and SIFT for keypoint description. Even tough the training set has produced circa. 640 000 
  keypoints the visual vocabulary has been constructed by clustering with kmeans algorithm only 5 000 keypoints per category or 35 000 in 
  total. Then, histograms of visual words were processed by multi-class classificators - namely the Na\"{i}ve Bayes and the Support Vector Machine.
  As expected, the SVM proved superior yielding 85\% accuracy as opposed to Na\"{i}ve Bayes' 72\%. While being efficient and quite effective, this
  approach considers only two dimensional data. Mobile robots are usually equipped with a device capable of capturing three dimensional point clouds
  such as laser scanners or rgbd cameras. Utilization of the enriched spatial information might result in a higher accuracy.

  Recelty Zhang \textit{et al} \cite{zhangcategory} has employed a semi-supervised graphical model object categorization approach. 
  A structure-based graphical model is trained using the spatial-information from the RGBD images. It is believed that the spatial
  information can help overcome intra-category texture variations and various rigid transformations, thus enabling the user to provide
  just one annotated image of an object from every category to initialize the training. The model can then be refined with not annotated images.
  Furthermore, object is divided into several parts and a separate codebooks are constructed for each of them. The matching can be performed 
  on 2D or 3D images. Their average accuracy is above 85\% on 5 categories. Even though Zhang's method is easy to use for an end-user and 
  delievers state-of-the-art result it is very complex and difficult to implement.

  Therefore, in this paper I present a Bag of Words framework for object categorization based on a Microsoft Kinect sensor and a Scale-Invariant 
  Feature Transform as proposed by \cite{lowe1999object}. It is intended to utilize additional spatial information from RGBD images while
  remaining easy to implement.

  In section 2 I explain the categorization algorithm and justify the use of its components. In section 3 I present results
  of the algorithm applied to a modified B3D0 dataset. Section 4 discusses the performance of the system and potentiall improvements.
  Section 5 summarizes the results.

\section{Literature review}

\subsection{3D content based shape retrieval}

  Textual annotation and text-based search engines might provide statisfactory results when text documents are concerned. This method fails
  \cite{tangelder2008survey}, however, as soon as 2d images or 3d shapes are examined. One possible explanation is that human-annotations
  of visual (either 2d or 3d) objects is strongly dependant on the annotator's backgroud i.e. language, ethnicity. Content Based Image
  Retrieval, introduced in 1990s, lacks this disadvantage \cite{tangelder2008survey}. CBIR was first adapted to 2D images as a method of 
  extracting low-level visual features \cite{tsai2012bag}. A hypothesis is that the extracted features can be described, thus creating an 
  intermediate represenatation of an image. Such representations can be a subject to comparison with respect to some dissimilarity measure.
  Visual features are usually described as (key)points in a high-dimensional space \cite{tsai2012bag}. The dissimilarity measure can take a 
  form of a metric in this space. Therefore, distinct features can be compared in terms of a distance between them.

  A shape retrieval framework can be divided into two phases. Firstly, a database has to be built offline. A pre-annotated dataset is a
  prerequisite. Such a database should not contain images, nor shapes, but rather extracted and described keypoints of those. Secondly, 
  queries can be processed online by matching them against database's entries. A searching algorithm should be available. For a better 
  performance, the offline database should be organized in a structure that would reduce computational effort of finding the best match.
  A query can be formed in several ways: One can browse a database and select an entry as a query, feature description can be provided 
  or a query-by-example can be made. In the last case, feature descriptors has to be computed before the process of finding the best 
  match can begin.

  Shape matching techniques can be divided into three broad categories \cite{tangelder2008survey}, namely (1) feature based methods, (2) 
  graph based methods and (3) other methods.

\subsubsection{Feature based methods}

  Feature based methods focus on geometric features and their spatial distribution. This category can be further divided into (1) global features, 
  (2) global features distribution, (3) spatial features and (4) local features. The sub-category is very different, for it employs several 
  descriptors, one for each sub-region of an object. The first three method make use of just one descriptor per object. The descriptors are 
  \textit{d}-dimensional, with a \textit{d} being a fixed number of dimensions for all shapes. Only the local features approach provide satisfactory 
  results in partial matching.

\subsubsection{Graph based methods}

  Graph based methods try to utilize more information than feature based methods mentioned above. The latter base predominantly on the
  geometrical properties of an object. The former, on the other hand, build a graph reflecting relationships  between the geometrical
  properties.

\subsubsection{Other methods}

\subsection{A bag of words approach}

  Even though the process of feature extraction and description is automatic, the CBIR has a major drawback commonly referred to
  as a semantic gap. Acording to \cite{tsai2012bag}, a semantic gap is „the gap between th extracted and indexed low-level features
  by computers and the high-level concepts (or semantics) of users' queries”. That is, for visual features extracted and concepts
  operated by humans are on very different levels of abstraction, a formulation of users' queries in terms of low-level features is
  highly problematic.

\subsection{A bag of words approach for 3D object categorization}

\section{Knowledge base}

\subsection{Detection}

    The purpose of the detection process is to find interest points that would be distinctive to the given object and yet
    invariant to affine transforms as well as enviornmental conditions. The Scale-Invariant Feature Transform as described
    in \cite{lowe1999object} has been used extensively for the past decade and can boast of all the required characteristics.

    In order to compute the keypoints' locations the processed image is rescaled into multiple scales. To identify keypoints 
    locations the minima and maxima of a difference of Gaussian in the scale space are found. Each point is sampled relative to 
    its scale. Candidate object models are defined. Afterwards, a scale-space Hoguh transform hash-table is formed and then through
    a least-squares fit the final model estimation is carried out.

\subsection{Description}
\subsection{Vector Quantization}
\subsection{Prediction}

\subsection{OpenCV}
\subsection{PointCloud Library}

\section{Tagger3D}

\subsection{Design basis}
\subsection{Processing pipeline}
\subsection{System architecture}
\subsection{Implementation details}

\section{Testing enviornment}

\subsection{Dataset}
\subsection{Workstation}

\section{Results}

\section{Conclusions}

\bibliography{article}

\end{document}

### 2013-09-21 Disseration/article.tex
thesis

@@
 \usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
 
 %opening
-\title{Bag of Words 3D object categorization based on scale-invariant features}
+\title{Rozpoznawanie obiektów trójwymiarowych na podstawie danych RGBD wykorzystując podejście Bag of Words}
 \author{Adam Kosiorek}
@@
 
+Abstrakt
+
 \end{abstract}
 
-\section{Introduction}
+\section{Wstęp}
+\subsection{Motywacja}
 
-  Mobile robotics has already begun its entrance into our households. It is conceivable that numerous tasks from our daily routines will be no
-  longer of our interest, for personal robotic assistanst will take care of them. Among their most obvious duties are now or will be:
-  cleaning, cooking  and elderly care. A robot aspiring to become a personal assistant has a number of requirements to fullfil. These 
-  requirements might consist of, but are not limited to: an ability of simultaneous localization and mapping or SLAM, a clever human-machine 
-  interface and a capability of interaction with its enviornment. As for the last part, a capacity of object categorization is essential. One 
-  has to bear in mind that the categorization is very different from: recognition, content based image retrieval or CBIR and detection as outlined
-  in \cite{csurka2004visual}.
+  Rozwój nowych technologii pozwala na gromadzenie oraz przetwarzanie bardzo dużych ilości danych.
+Aparaty i kamery cyfrowe przyczyniają się do powstawania milionów gigabajtów informacji każdego dnia.
+Co więcej, dobrej jakości urządzenia służące do obrazowania trójwymiarowego osiągnęły tak niskie ceny, że można je znaleźć w wielu gospodarstwach domowych.
+Jednym z nich jest \textit{Microsoft Kinect} -- korzystający z technologii \textit{PrimeSense} --- oparty o światło strukturalne sensor rejestrujący dane RGBD.
 
-  An intermediate image representation that seems to yield the best results in scene classification, 2D object categorization and 3D shape retrieval
-  over the past decade as seen in \cite{fei2005bayesian}, \cite{csurka2004visual}, \cite{li2010investigating} and \cite{tsai2012bag}
-  is a Bag of Words model. It seems that it has not been used for 3D object categorization so far.
+  Nowe technologie przyczyniają się też do spadku cen robotów mobilnych.
+Można sobie wyobrazić, że w niedalekiej przyszłości zrobotyzowani asystenci zawitają w domach.
+Roboty takie będą musiały spełniać szereg wymagań związanych z wymogami bezpieczeństwa oraz wygodą użytkowania.
+W szczególności będą musiały być wyposażone w mechanizmy pozwalające na bezpieczną, a zarazem efektywną interakcję z otoczeniem --- w tym z ludźmi.
 
-  Bag of Words model has numerous advantages over raw images. Firstly, with appropriate features used for word formation the resulting 
-  representation can be invariant to affine transforms and lighting conditions. Moreover, it addresses the issue of a semantic gap. It is 
-  challanging to determine whether certain low level visual features (or their description) are characteristic for any higher-level object.
-  On the other hand, clustering thousands of such described features yields a relatively low number of intermediate level features - the visual words.
-
-  A typicial pipeline for Bag of Words scene or object categorization is as follows:
+  Zapewnienie poprawnej interakcji z otoczeniem wymaga spełnienia wielu warunków. Między innymi są to: 
   \begin{itemize}
-  \item Points or regions of interest have to be detected.
-  \item Each keypoint have to be described, thus resulting in a point in multi-dimensional space (or a vector)
-  \item Every vector have to be assigned to a corresponding term from a pre-constructed visual vocabulary by a vector 
-  quantization algorithm.
-  \item The obtained histograms of visual words has to be fed into a multi-class classification algorithm.
+   \item Interfejs człowiek-maszyna powinien pozwalać na swobodną komunikację z robotem.
+   \item Posiadanie wiedzy na temat aktualnego położenia oraz dysponowanie mapą otoczenia - problem opisywany w literaturze jako \textit{SLAM --- Simultaneous Localization And Mapping}
+   \item Zdolność semantycznej klasyfikacji miejsca, w którym robot się znajduje
+   \item Zdolnośc semantycznej klasyfikacji pojedyńczych obiektów   
   \end{itemize}
 
-  Csurka \textit{et al} \cite{csurka2004visual} has presented a bag of words framework for 2D object categorization. They have employed the
-  Harris affine detector for keypoint detection and SIFT for keypoint description. Even tough the training set has produced circa. 640 000 
-  keypoints the visual vocabulary has been constructed by clustering with kmeans algorithm only 5 000 keypoints per category or 35 000 in 
-  total. Then, histograms of visual words were processed by multi-class classificators - namely the Na\"{i}ve Bayes and the Support Vector Machine.
-  As expected, the SVM proved superior yielding 85\% accuracy as opposed to Na\"{i}ve Bayes' 72\%. While being efficient and quite effective, this
-  approach considers only two dimensional data. Mobile robots are usually equipped with a device capable of capturing three dimensional point clouds
-  such as laser scanners or rgbd cameras. Utilization of the enriched spatial information might result in a higher accuracy.
+  Wykorzystanie informacji przestrzennej mogłoby być problematyczne w przypadku semantycznej kategoryzacjii scen.
+W przypadku, gdy robot nie przebywa w budynku próba rejestracji chmury punktów z otoczenia może zakończyć się tylko częściowym powodzeniem --- jeśli nie będą występowały żadne obiekty w zasięgu np.
+skanera laserowego, to punkty nie zostaną zarejestrowane.
+Sytuacja przedstawia się zupełnie inaczej w przypadku kategoryzacji obiektów.
+Sam fakt wystąpienia problemu kategoryzacji obiektu oznacza, że obiekt ten jest w zasięgu sensorów rejestrujących otoczenie robota, a więc możliwe jest zebranie chmury punktów z tego przedmiotu.
 
-  Recelty Zhang \textit{et al} \cite{zhangcategory} has employed a semi-supervised graphical model object categorization approach. 
-  A structure-based graphical model is trained using the spatial-information from the RGBD images. It is believed that the spatial
-  information can help overcome intra-category texture variations and various rigid transformations, thus enabling the user to provide
-  just one annotated image of an object from every category to initialize the training. The model can then be refined with not annotated images.
-  Furthermore, object is divided into several parts and a separate codebooks are constructed for each of them. The matching can be performed 
-  on 2D or 3D images. Their average accuracy is above 85\% on 5 categories. Even though Zhang's method is easy to use for an end-user and 
-  delievers state-of-the-art result it is very complex and difficult to implement.
+\subsection{Cel pracy}
 
-  Therefore, in this paper I present a Bag of Words framework for object categorization based on a Microsoft Kinect sensor and a Scale-Invariant 
-  Feature Transform as proposed by \cite{lowe1999object}. It is intended to utilize additional spatial information from RGBD images while
-  remaining easy to implement.
+  Celem niniejszej pracy jest napisanie aplikacji służącej do semantycznej kategoryzacji obiektów trójwymiarowych.
+Kategoryzacja powinna odbywać się w oparciu o dane RGBD oraz wykorzystywać reprezentację Bag of Words.
+Aplikacja powinna działać w czasie rzeczywistym, a jej skuteczność powinna pozwalać na wykorzystanie jej w rzeczywistych robotach mobilnych.
 
-  In section 2 I explain the categorization algorithm and justify the use of its components. In section 3 I present results
-  of the algorithm applied to a modified B3D0 dataset. Section 4 discusses the performance of the system and potentiall improvements.
-  Section 5 summarizes the results.
+\subsection{Zakres pracy}
 
-\section{Literature review}
+  W pracy zostały przyjęte następujące założenia projektowe:
+  \begin{itemize}
+   \item System operuje na danych RGBD
+   \item Analizowane obrazy powinny zostać przygotowane w ten sposób, że rozpoznawany obiekt powinien wypełniać ponad połowę powierzchni zdjęcia
+   \item Kategoryzacja obiektów odbywa się z pominięciem segmentacji obrazu.
+  \end{itemize}
 
-\subsection{3D content based shape retrieval}
+  Do realizacji projektu wykorzystano biblioteki: \emph{OpenCV, PointCloudLibrary, Boost}.
+Wszystkie wykorzystywane algorytmy przetwarzania obrazu oraz uczenia maszynowego zostały zaimplementowane przez osoby trzecie, a w większości pochodzą z wymienionych bibliotek.
 
-  Textual annotation and text-based search engines might provide statisfactory results when text documents are concerned. This method fails
-  \cite{tangelder2008survey}, however, as soon as 2d images or 3d shapes are examined. One possible explanation is that human-annotations
-  of visual (either 2d or 3d) objects is strongly dependant on the annotator's backgroud i.e. language, ethnicity. Content Based Image
-  Retrieval, introduced in 1990s, lacks this disadvantage \cite{tangelder2008survey}. CBIR was first adapted to 2D images as a method of 
-  extracting low-level visual features \cite{tsai2012bag}. A hypothesis is that the extracted features can be described, thus creating an 
-  intermediate represenatation of an image. Such representations can be a subject to comparison with respect to some dissimilarity measure.
-  Visual features are usually described as (key)points in a high-dimensional space \cite{tsai2012bag}. The dissimilarity measure can take a 
-  form of a metric in this space. Therefore, distinct features can be compared in terms of a distance between them.
+  Zakłada się, że zostaną wykorzystane implementacje algorytmów uwzględniające wielowątkowość, w celu przyśpieszenia działania programu.
+Ponadto możliwe jest wykorzystanie platformy CUDA w celu porównania wydajności i dalszego przyśpieszenia obliczeń.
 
-  A shape retrieval framework can be divided into two phases. Firstly, a database has to be built offline. A pre-annotated dataset is a
-  prerequisite. Such a database should not contain images, nor shapes, but rather extracted and described keypoints of those. Secondly, 
-  queries can be processed online by matching them against database's entries. A searching algorithm should be available. For a better 
-  performance, the offline database should be organized in a structure that would reduce computational effort of finding the best match.
-  A query can be formed in several ways: One can browse a database and select an entry as a query, feature description can be provided 
-  or a query-by-example can be made. In the last case, feature descriptors has to be computed before the process of finding the best 
-  match can begin.
+\section{Przegląd literatury}
 
-  Shape matching techniques can be divided into three broad categories \cite{tangelder2008survey}, namely (1) feature based methods, (2) 
-  graph based methods and (3) other methods.
+\section{Proponowane podejście}
 
-\subsubsection{Feature based methods}
+	W poniższej pracy wykorzystuje się podejście Bag of Words (BoW) połączone z algorytmami uczenia nadzorowanego.
+Model BoW ma tę zaletę w stosunku do surowych zdjęć lub chmur punktów, iż zmniejsza tzw.
+semantic gap - lukę znaczeniową pomiędzy zdjęciem lub niskopoziomowymi cechami charakteryzującymi obraz a wysokopoziomowy koncepcjami, nadającymi zdjęciu znaczenie semantyczne np.
+zachód słońca, człowiek.
 
-  Feature based methods focus on geometric features and their spatial distribution. This category can be further divided into (1) global features, 
-  (2) global features distribution, (3) spatial features and (4) local features. The sub-category is very different, for it employs several 
-  descriptors, one for each sub-region of an object. The first three method make use of just one descriptor per object. The descriptors are 
-  \textit{d}-dimensional, with a \textit{d} being a fixed number of dimensions for all shapes. Only the local features approach provide satisfactory 
-  results in partial matching.
+\section{Opis zastosowanych rozwiązań}
 
-\subsubsection{Graph based methods}
+\section{Eksperymenty}
 
-  Graph based methods try to utilize more information than feature based methods mentioned above. The latter base predominantly on the
-  geometrical properties of an object. The former, on the other hand, build a graph reflecting relationships  between the geometrical
-  properties.
-
-\subsubsection{Other methods}
-
-\subsection{A bag of words approach}
-
-  Even though the process of feature extraction and description is automatic, the CBIR has a major drawback commonly referred to
-  as a semantic gap. Acording to \cite{tsai2012bag}, a semantic gap is „the gap between th extracted and indexed low-level features
-  by computers and the high-level concepts (or semantics) of users' queries”. That is, for visual features extracted and concepts
-  operated by humans are on very different levels of abstraction, a formulation of users' queries in terms of low-level features is
-  highly problematic.
-
-\subsection{A bag of words approach for 3D object categorization}
-
-\section{Knowledge base}
-
-\subsection{Detection}
-
-    The purpose of the detection process is to find interest points that would be distinctive to the given object and yet
-    invariant to affine transforms as well as enviornmental conditions. The Scale-Invariant Feature Transform as described
-    in \cite{lowe1999object} has been used extensively for the past decade and can boast of all the required characteristics.
-
-    In order to compute the keypoints' locations the processed image is rescaled into multiple scales. To identify keypoints 
-    locations the minima and maxima of a difference of Gaussian in the scale space are found. Each point is sampled relative to 
-    its scale. Candidate object models are defined. Afterwards, a scale-space Hoguh transform hash-table is formed and then through
-    a least-squares fit the final model estimation is carried out.
-
-\subsection{Description}
-\subsection{Vector Quantization}
-\subsection{Prediction}
-
-\subsection{OpenCV}
-\subsection{PointCloud Library}
-
-\section{Tagger3D}
-
-\subsection{Design basis}
-\subsection{Processing pipeline}
-\subsection{System architecture}
-\subsection{Implementation details}
-
-\section{Testing enviornment}
-
-\subsection{Dataset}
-\subsection{Workstation}
-
-\section{Results}
-
-\section{Conclusions}
+\section{Podsumowanie}
 

### 2013-09-22 Disseration/article.tex
layoyt strony

@@
-\documentclass[a4paper,10pt]{article}
+\documentclass[a4paper,10pt,twocolumn]{article}
 \usepackage[utf8]{inputenc}
 \usepackage[T1]{fontenc}
+\usepackage[top=2cm, bottom=2cm, left=3cm, right=2cm]{geometry}
 
 %opening
-\title{Rozpoznawanie obiektów trójwymiarowych na podstawie danych RGBD wykorzystując podejście Bag of Words}
+\title{Rozpoznawanie obiektów trójwymiarowych na podstawie danych RGBD}
 \author{Adam Kosiorek}
@@
 \section{Wstęp}
-\subsection{Motywacja}
 
@@
    \item Zdolność semantycznej klasyfikacji miejsca, w którym robot się znajduje
-   \item Zdolnośc semantycznej klasyfikacji pojedyńczych obiektów   
+   \item Zdolność semantycznej klasyfikacji pojedyńczych obiektów   
   \end{itemize}
 
-  Wykorzystanie informacji przestrzennej mogłoby być problematyczne w przypadku semantycznej kategoryzacjii scen.
-W przypadku, gdy robot nie przebywa w budynku próba rejestracji chmury punktów z otoczenia może zakończyć się tylko częściowym powodzeniem --- jeśli nie będą występowały żadne obiekty w zasięgu np.
-skanera laserowego, to punkty nie zostaną zarejestrowane.
-Sytuacja przedstawia się zupełnie inaczej w przypadku kategoryzacji obiektów.
-Sam fakt wystąpienia problemu kategoryzacji obiektu oznacza, że obiekt ten jest w zasięgu sensorów rejestrujących otoczenie robota, a więc możliwe jest zebranie chmury punktów z tego przedmiotu.
+  Trzy ostatnie spośród wymienionych punktów są zupełnie naturalne dla ludzi.
+Od dnia narodzin stajemy przed zadaniem rozpoznawanie swojego otoczenia, miejsca w którym się znajdujemy i przedmiotów, z którymi mamy do czynienia.
+Czynności te wydają się nam bardzo łatwe --- od samego początku dysponujemy bardzo dużą ilością danych dotyczących naszego otoczenia, których źródłem są nasze zmysły.
+Ponadto uczymy się od starszych jak zachowywać się w określonych miejscach, jak obchodzić się z konkretnymi przedmiotami.
+Maszyny zazwyczaj nie mają tak bogatych danych opisujących geometrię, kolor czy fakturę otaczających przedmiotów, nie mają też wiedzy nt.
+semantycznego znaczenia tych przedmiotów.
+Z tego powodu powstaje wiele algorytmów służacych do opisania otaczającego nas świata oraz takich, które uczą się rozpoznawać obiekty.
+
+  W przypadku semantycznej klasyfikacji otoczenia robota można zauważyć, że rejestracja wszystkich elementów otoczenia wykorzystując np.
+skaner laserowy będzie niemożliwa.
+Skanery takie mają ograniczony zasięg, a w przypadku przebywania w otwartej przestrzeni większość obiektów może znaleźć się poza zasięgiem skanera.
+Prowadzi to do utrudnienia bądź uniemożliwienia wykorzystania informacji przestrznnej do rozpoznawania otoczenia robota.
+W przypadku semanycznej klasyfikacji obiektów sytuacja przedstawia się inaczej --- sam fakt wystąpienia problemu dowodzi, że obiekt znalazł się w zasiegu sensorów.
+Możliwa jest więc rejestracja chmury punktów opisująca badany przedmiot oraz wykorzystanie informacji przestrzennej w celu klasyfikacji.
 

### 2013-09-22 Disseration/article.tex
1

@@
-\documentclass[a4paper,10pt,twocolumn]{article}
+\documentclass[a4paper,10pt]{article}
 \usepackage[utf8]{inputenc}
 \usepackage[T1]{fontenc}
-\usepackage[top=2cm, bottom=2cm, left=3cm, right=2cm]{geometry}
+\usepackage[top=3cm, bottom=3cm, left=4cm, right=3cm]{geometry}
 
@@
 
-\section{Przegląd literatury}
+\section{Bag of Words image representation}
 
-\section{Proponowane podejście}
+  As portreyed in \cite{tsai2012bag} the Bag of Words or BoW model has originated from the text retrieval domain.
+The original use enabled a vector-like representation of a text document.
+One of the most simple cases would be to, given a dictionary, construct a histogram depicting the incidence of words in a particular text document.
+Such an approach obliterates any grammatical dependencies in order to retain only the statistical information associated with each word.
+It is believed that the words' frequencies are connceted to the semantic meaning of the document.
 
-	W poniższej pracy wykorzystuje się podejście Bag of Words (BoW) połączone z algorytmami uczenia nadzorowanego.
-Model BoW ma tę zaletę w stosunku do surowych zdjęć lub chmur punktów, iż zmniejsza tzw.
-semantic gap - lukę znaczeniową pomiędzy zdjęciem lub niskopoziomowymi cechami charakteryzującymi obraz a wysokopoziomowy koncepcjami, nadającymi zdjęciu znaczenie semantyczne np.
-zachód słońca, człowiek.
+  The following questions emerge: 
+  \begin{itemize}
+    \item How does this apply to computer vision?
+    \item How can one convert an image to a text document? 
+  \end{itemize}
 
-\section{Opis zastosowanych rozwiązań}
+  In order to answer the first question one has to consider how computers process data.
+Digital images are nothing but streams of binary code.
+A simple conversion to an RGB format makes the data structured and is enough for people to understand their contents.
+Unforunately, such image representation is extrmelly vulnerable to translation and rotation as well as changing lighting conditions.
+One way to address these disadvantages would be to compute locations of some characteristic points (keypoints) and describe them somehow.
+Even then, however, the resulting represenation is low level and incomprehensible for humans.
+Defining robot's behaviour basing on such data might prove cumbersome, for there are too many details to consider.
+All of the above is reffered to as a semantic gap.
+It is defined by Tsai, with respect to the Content Based Image Retrieval or \textit{CBIR}, as \emph{`the gap between the extracted and indexed low-level features by computers and the high-level concepts (or semantics) of user’s queries'}.
+Suppose a text document can be created from an image.
+If this is the case, then the document can be converted into a BoW model.
+Since the latter contains information about the semantic significance of the image an impact of the semantic gap can be reduced.
 
-\section{Eksperymenty}
+  As for the second question, there is a quite well established pipeline that enables creation of text documents from images. The steps of the BoW methodology are as follows:
+  \begin{itemize}
+   \item Keypoint detection --- keypoints are local interest points or regions.
+They are usually computed in such a way so as to provide scale and location invariance.
+Rigid transformation and illumination invariance would be desired but it somewhat harder to achieve
+   \item Keypoint description --- each keypoint have to be described in a manner that distinguish the particular keypoint in some way.
+   \item Vector quantization --- clustering algorithms are used to find regions in the high dimensional space of keypoint descriptors.
+When the clusters are found, each described keypoint can be assigned to a corresponding cluster.
+Then, an image can be represented by the number of clusters, to which the image's keypoints were assigned.
+The clusters' numbers are called visual words.
+  \end{itemize}
 
-\section{Podsumowanie}
+\section{BoW in Scene and Object Categorization}
+
+\section{Image BoW model construction methods}
+
+\subsection{Detection}
+\subsection{Description}
+\subsection{Vector Quantization}
+
+\section{Classifiers}
+
+\section{Literature review}
 

### 2013-09-23 Disseration/article.tex
akapit o bow w cv

@@
 \usepackage[top=3cm, bottom=3cm, left=4cm, right=3cm]{geometry}
+\usepackage{cite}
 
@@
   As portreyed in \cite{tsai2012bag} the Bag of Words or BoW model has originated from the text retrieval domain.
-The original use enabled a vector-like representation of a text document.
-One of the most simple cases would be to, given a dictionary, construct a histogram depicting the incidence of words in a particular text document.
+In the original domain the model enabled a vector-like representation of a text document.
+One of the most simple cases would be to, given a dictionary, construct a histogram depicting the incidence of words in a particular document.
 Such an approach obliterates any grammatical dependencies in order to retain only the statistical information associated with each word.
@@
   \begin{itemize}
-    \item How does this apply to computer vision?
+    \item How does this apply to the area of computer vision?
     \item How can one convert an image to a text document? 
@@
 Digital images are nothing but streams of binary code.
-A simple conversion to an RGB format makes the data structured and is enough for people to understand their contents.
+A simple conversion to an RGB format makes the data structured and is enough for people to understand pictures' content.
 Unforunately, such image representation is extrmelly vulnerable to translation and rotation as well as changing lighting conditions.
 One way to address these disadvantages would be to compute locations of some characteristic points (keypoints) and describe them somehow.
-Even then, however, the resulting represenation is low level and incomprehensible for humans.
+Even then, however, the resulting represenation is a low level one and still incomprehensible for humans.
 Defining robot's behaviour basing on such data might prove cumbersome, for there are too many details to consider.
 All of the above is reffered to as a semantic gap.
-It is defined by Tsai, with respect to the Content Based Image Retrieval or \textit{CBIR}, as \emph{`the gap between the extracted and indexed low-level features by computers and the high-level concepts (or semantics) of user’s queries'}.
+It is defined by Tsai, with respect to the Content Based Image Retrieval or \textit{CBIR}, as \emph{``the gap between the extracted and indexed low-level features by computers and the high-level concepts (or semantics) of user’s queries''}.
 Suppose a text document can be created from an image.
@@
 
-\section{BoW in Scene and Object Categorization}
+\section{BoW in Scene in Computer Vision}
+
+  The Bag of Words image representation has been extensively used in the areas of scene \cite{csurka2004visual,fei2005bayesian, tsai2012bag} and object categorization \cite{zhangcategory} as well as CBIR \cite{li2010investigating,toldo2009bag} yielding state-of-the-art results.
+Advantages of this model are simplicity, computational efficiency and at least partial invariance to affine transformation, occlusion and lighting conditions.
+
+  The Bag of Words is a type of intermediate representation.
+Therefore it is not sufficient to compute a BoW model of an image in order to predict its category.
+Additional operations are essential if the model is to be used in one of the enumerated fields.
+
+  \subsection{Content Based Image Retrieval}
+
+    One of the most notorious use-case of \emph{CBIR} is to search a database in order to find an object fulfilling certain conditions.
+As \cite{li2010investigating} outlines, several criteria have to be met, for the task to be performed efficiently.
+Firstly, all entries should be indexed in a concise way.
+Secondly, some similarity measure should be provided.
+Finally, an efficient search algorithm should be employed.
+
+    As for the indexing method, the Bag of Words paradigm can be and is often used.
+Several modifications of the bag of words in different domains have been examined.
+In \cite{toldo2009bag} the BoW is used for retrieval of CAD-like meshes of articulated mesh models.
+The focus of this paper is on the codebook construction stage.
+Object segmentation by spectral clustering is used.
+Then, sub-parts of each objects are described separately and a codebook of visual words in constructed from a set of region descriptors.
+\cite{li2010investigating} introduced a Concentric Bag of Words approach.
+The main idea behind this concept is to make use of spatial information and multiple histograms instead of a single global histogram.
+Auhors partition each mesh model in concentric shapes, thus the name.
+As shown in this paper, both global-to-global and partial-to-global content based retrieval is possible.
 

### 2013-09-26 Disseration/article.tex
up

@@
-\documentclass[a4paper,10pt]{article}
+\documentclass[a4paper,12pt]{article}
 \usepackage[utf8]{inputenc}
 \usepackage[T1]{fontenc}
-\usepackage[top=3cm, bottom=3cm, left=4cm, right=3cm]{geometry}
+\usepackage[top=3cm, bottom=6cm, left=4cm, right=3cm]{geometry}
 \usepackage{cite}
 
+\linespread{1.5}
+
 %opening
-\title{Rozpoznawanie obiektów trójwymiarowych na podstawie danych RGBD}
+\title{Object Categorization based on RGBD data}
 \author{Adam Kosiorek}
@@
 
-\section{Wstęp}
-
-  Rozwój nowych technologii pozwala na gromadzenie oraz przetwarzanie bardzo dużych ilości danych.
-Aparaty i kamery cyfrowe przyczyniają się do powstawania milionów gigabajtów informacji każdego dnia.
-Co więcej, dobrej jakości urządzenia służące do obrazowania trójwymiarowego osiągnęły tak niskie ceny, że można je znaleźć w wielu gospodarstwach domowych.
-Jednym z nich jest \textit{Microsoft Kinect} -- korzystający z technologii \textit{PrimeSense} --- oparty o światło strukturalne sensor rejestrujący dane RGBD.
-
-  Nowe technologie przyczyniają się też do spadku cen robotów mobilnych.
-Można sobie wyobrazić, że w niedalekiej przyszłości zrobotyzowani asystenci zawitają w domach.
-Roboty takie będą musiały spełniać szereg wymagań związanych z wymogami bezpieczeństwa oraz wygodą użytkowania.
-W szczególności będą musiały być wyposażone w mechanizmy pozwalające na bezpieczną, a zarazem efektywną interakcję z otoczeniem --- w tym z ludźmi.
-
-  Zapewnienie poprawnej interakcji z otoczeniem wymaga spełnienia wielu warunków. Między innymi są to: 
-  \begin{itemize}
-   \item Interfejs człowiek-maszyna powinien pozwalać na swobodną komunikację z robotem.
-   \item Posiadanie wiedzy na temat aktualnego położenia oraz dysponowanie mapą otoczenia - problem opisywany w literaturze jako \textit{SLAM --- Simultaneous Localization And Mapping}
-   \item Zdolność semantycznej klasyfikacji miejsca, w którym robot się znajduje
-   \item Zdolność semantycznej klasyfikacji pojedyńczych obiektów   
-  \end{itemize}
-
-  Trzy ostatnie spośród wymienionych punktów są zupełnie naturalne dla ludzi.
-Od dnia narodzin stajemy przed zadaniem rozpoznawanie swojego otoczenia, miejsca w którym się znajdujemy i przedmiotów, z którymi mamy do czynienia.
-Czynności te wydają się nam bardzo łatwe --- od samego początku dysponujemy bardzo dużą ilością danych dotyczących naszego otoczenia, których źródłem są nasze zmysły.
-Ponadto uczymy się od starszych jak zachowywać się w określonych miejscach, jak obchodzić się z konkretnymi przedmiotami.
-Maszyny zazwyczaj nie mają tak bogatych danych opisujących geometrię, kolor czy fakturę otaczających przedmiotów, nie mają też wiedzy nt.
-semantycznego znaczenia tych przedmiotów.
-Z tego powodu powstaje wiele algorytmów służacych do opisania otaczającego nas świata oraz takich, które uczą się rozpoznawać obiekty.
-
-  W przypadku semantycznej klasyfikacji otoczenia robota można zauważyć, że rejestracja wszystkich elementów otoczenia wykorzystując np.
-skaner laserowy będzie niemożliwa.
-Skanery takie mają ograniczony zasięg, a w przypadku przebywania w otwartej przestrzeni większość obiektów może znaleźć się poza zasięgiem skanera.
-Prowadzi to do utrudnienia bądź uniemożliwienia wykorzystania informacji przestrznnej do rozpoznawania otoczenia robota.
-W przypadku semanycznej klasyfikacji obiektów sytuacja przedstawia się inaczej --- sam fakt wystąpienia problemu dowodzi, że obiekt znalazł się w zasiegu sensorów.
-Możliwa jest więc rejestracja chmury punktów opisująca badany przedmiot oraz wykorzystanie informacji przestrzennej w celu klasyfikacji.
-
-\subsection{Cel pracy}
-
-  Celem niniejszej pracy jest napisanie aplikacji służącej do semantycznej kategoryzacji obiektów trójwymiarowych.
-Kategoryzacja powinna odbywać się w oparciu o dane RGBD oraz wykorzystywać reprezentację Bag of Words.
-Aplikacja powinna działać w czasie rzeczywistym, a jej skuteczność powinna pozwalać na wykorzystanie jej w rzeczywistych robotach mobilnych.
-
-\subsection{Zakres pracy}
-
-  W pracy zostały przyjęte następujące założenia projektowe:
-  \begin{itemize}
-   \item System operuje na danych RGBD
-   \item Analizowane obrazy powinny zostać przygotowane w ten sposób, że rozpoznawany obiekt powinien wypełniać ponad połowę powierzchni zdjęcia
-   \item Kategoryzacja obiektów odbywa się z pominięciem segmentacji obrazu.
-  \end{itemize}
-
-  Do realizacji projektu wykorzystano biblioteki: \emph{OpenCV, PointCloudLibrary, Boost}.
-Wszystkie wykorzystywane algorytmy przetwarzania obrazu oraz uczenia maszynowego zostały zaimplementowane przez osoby trzecie, a w większości pochodzą z wymienionych bibliotek.
-
-  Zakłada się, że zostaną wykorzystane implementacje algorytmów uwzględniające wielowątkowość, w celu przyśpieszenia działania programu.
-Ponadto możliwe jest wykorzystanie platformy CUDA w celu porównania wydajności i dalszego przyśpieszenia obliczeń.
+%\include{introduction}
 
@@
   As portreyed in \cite{tsai2012bag} the Bag of Words or BoW model has originated from the text retrieval domain.
-In the original domain the model enabled a vector-like representation of a text document.
+Originally the model enabled a vector-like representation of a text document.
 One of the most simple cases would be to, given a dictionary, construct a histogram depicting the incidence of words in a particular document.
@@
 It is believed that the words' frequencies are connceted to the semantic meaning of the document.
+The following questions emerge:
 
-  The following questions emerge: 
   \begin{itemize}
@@
 They are usually computed in such a way so as to provide scale and location invariance.
-Rigid transformation and illumination invariance would be desired but it somewhat harder to achieve
+Rigid transformation and illumination invariance would be desired but it is somewhat harder to achieve
    \item Keypoint description --- each keypoint have to be described in a manner that distinguish the particular keypoint in some way.
@@
 When the clusters are found, each described keypoint can be assigned to a corresponding cluster.
-Then, an image can be represented by the number of clusters, to which the image's keypoints were assigned.
-The clusters' numbers are called visual words.
+Then, an image can be represented by the numbers of clusters, to which the image's keypoints were assigned.
+The numbers themselves are called \emph{`visual words'}.
   \end{itemize}
 
-\section{BoW in Scene in Computer Vision}
+\section{BoW in Computer Vision}
 
@@
   One of the most notorious use-case of \emph{CBIR} is to search a database in order to find an object fulfilling certain conditions.
-As \cite{li2010investigating} outlines, several criteria have to be met, for the task to be performed efficiently.
+As \cite{toldo2009bag} outlines, several criteria have to be met for the task to be performed efficiently.
 Firstly, all entries should be indexed in a concise way.
-Secondly, some similarity measure should be provided.
-Finally, an efficient search algorithm should be employed.
+Secondly, some (dis)similarity measure should be provided.
+Finally, an efficient search algorithm should be available.
 
-    As for the indexing method, the Bag of Words paradigm can be and is often used.
-Several modifications of the bag of words in different domains have been examined.
-In \cite{toldo2009bag} the BoW is used for retrieval of CAD-like meshes of articulated mesh models.
-The focus of this paper is on the codebook construction stage.
-Object segmentation by spectral clustering is used.
-Then, sub-parts of each objects are described separately and a codebook of visual words in constructed from a set of region descriptors.
-\cite{li2010investigating} introduced a Concentric Bag of Words approach.
-The main idea behind this concept is to make use of spatial information and multiple histograms instead of a single global histogram.
-Auhors partition each mesh model in concentric shapes, thus the name.
-As shown in this paper, both global-to-global and partial-to-global content based retrieval is possible.
+  There are numerous methods suitable for computation of objetcs' signatures.
+Many of them can be used in the indexing step.
+All the methods were divided into three general categories in \cite{toldo2009bag}, specifically: feature based methods, graph based methods and other methods.
 
-\section{Image BoW model construction methods}
+  Feature based methods can be either global or local.
+The former takes the form of a single vector or a point in a $d$ dimensional space --- the similarity measure resulting in computing point-wise distance in that space.
+The latter gives multiple such points for each object, rendering the computation of a similarity measure slightly more complicated.
+The global features takes forms of the models' volume, their volume or mass distribution.
+Others might incorporate the global features' distribtution --- one conceivable approach would be to compute global feature's distribution and summarize them into a histogram.
+These features have the advantage of being easy to compute and straightforward to implement.
+However, they are insensitive to any local shape variations, thus being ill suited for details comparisions.
+On the other hand, they might be exploited in the preprocessing of the data with more sophisticated methods being used afterwards.
+Partial matching is not possible, since the global features do not encode any relations between the parts of the objects.
+
+  As for the local features, \cite{toldo2009bag} describes only the features that describe neighbourhood of the points being on the boundary of a shape.
+While that might generally be true, different points might be considered as well.
+Moreover, the authors state that the local features based methods are inefficien and indexing is rather complex.
+A Bag of Words based approach, described in \cite{li2010investigating} has no such drawbacks.
+
+  Even tough BoW is a local features based method, it can be regarded as a feature distribution method.
+It is based on visual words, clearly being local features.
+When all the image's visual words are summarized into a histogram a distribution is created.
+Being similar to a point in a multi-dimensional space, it is similar to a global feature.
+Consequently, similar methods apply, with the distinction being that the histogram is rather a vector then a point.
+Thus metrics well-suited to vector comparision, such as a cosine distance, can be used.
+
+  \subsection{Scene Categorization}
+
+  One of the first works employing the BoW for the purpouse of scene categorization is \cite{csurka2004visual}.
+The authors suggested a general framework.
+What is more, algorthims performing each main pipeline's step were proposed and evaluated as well as a codebook construction method was developed.
+A \emph{Harris Affine Detector} was used for feature extraction and \emph{SIFT} for the feature descripton.
+The visual vocabulary has been generated by clustering only a limited number of keypoints from each category.
+After summarizing each image in the traning set with a histogram of visual words, supervised learning was used to train two classifiers: Na\`ive Bayes and a Support Vector Machine.
+As expected the Na\`ive Bayes resulted in lower accuracy than SVM (72 vs.
+85\% on 7 categories).
+An analysis on the number of centroids in the clustering step depicts that the greater size of the visual vocabulary migh increase accuracy.
+
+  Li \emph{et al} further refined the above approach by examining several keypoint detectors and descriptors.
+The main contribution of this work is, however, the development of a genuine classification algorithm based on probabilistic graphical models.
+Accuracy of 76\% on a large 13 category dataset was achieved.
+
+  \subsection{Object Categorization}
+
+  In many cases object categorization might be addressed as a scene categorization problem.
+There are following differences: (1) an object should be localized on an image (i.e.
+its bounding box has to be found) and (2) in object categorization information about the scene type might be used.
+The second case is symmetric, for in the scene categorization information about the objects present in the scene can be utilized as well.
+Having said that, it is possible to consider an object categorization problem where images of singled-out objects are provided --- e.g.
+a single object covers the majority of an image's area.
+Such an approach was exploited a recent work by Zhang \emph{et al} \cite{zhangcategory}.
+
+\section{BoW based image classification}
 
@@
 \subsection{Vector Quantization}
-
-\section{Classifiers}
-
-\section{Literature review}
+\subsection{Classification}
 

### 2013-09-28 Disseration/article.tex
a

@@
 
-\section{BoW based image classification}
+\section{BoW based classification}
+
+	The Bag of Words intermediate image represenation provides a concise way of summarizing images.
+It is invariant to affaine transformations, partial occlusion and, in some extent, to changing lighting conditions.
+What is more, it is easy to implement and computationally efficient.
+The efficiency can be enhanced even further with gpu based implementations as shown in \cite{van2011empowering}.
+In order to incorporate BoW into an object classification framework one has to feed the resulting histograms into a classification algorithms.
+Either generative or discriminative methods can be used.
+Below the main steps of BoW classification processing pipeline will be disscussed.
 
 \subsection{Detection}
+
+	Numerous keypoint detectors have been developed.
+
 \subsection{Description}

### 2013-09-29 Disseration/article.tex
description

@@
 
-\linespread{1.5}
+\linespread{1.15}
 
@@
 
-	Numerous keypoint detectors have been developed.
+	Characteristic point detection is the first step in any Bag of Words framework.
+Numerous detection methods have been developed, but choosing the right one for the particular case might prove tricky.
+A good overview of various mechanisms is available in \cite{tsai2012bag}.
+The most common detectors make use of a Harris corner detector or image's first or second derivatives.
+A technique taking advantage of the Harris corner detector is for example a Harris-Laplace detector --- the Harris function is scale adapted and its outcome is a subject to a Laplacian-of-Gaussian operator, which selects relevant points in the scale space.
+Images' regions' 2\textsuperscript{nd} derviatives --- namely the regions' Hessians --- can be combined with a LoG operator.
+This combination allows selection of points significant in the two spaces: the scale space and the Hessian's determinant space.
+The latter entails the speed at which pixel intensities change in the neighbourhood of a point.
+
+	A number of more complicated recipes for salient region localization have been developed and implemented.
+These include include Scale Invariant Feature Transform \cite{sift_keypoint}, SUSAN \cite{susan_keypoint} and Intrinistic Shapes Siganutes \cite{iss_keypoint}.
+The majority of keypoint detection formulas is being develoepd for the 2d domain.
+A number of them have been adapted to 3D, however.
+A comparative evaluation of detection algorithm available in PCL can be find in \cite{pcl_keypoint_comparision}.
+Another comprehensive study is \cite{3d_keypoint_eval}.
+
+	All these formulas, called sparse feature detectors, resort to selection of maxima in specific state spaces.
+An entierly different scheme is to use a dense feature detector.
+This particular form requires users to specify a uniformly sampled grid from which points are taken.
+Dense detectors have an advantage of taking points from slow changing regions.
+A sparse detector might be unable to summarize a slow changing region such as clouds, sky or ocean.
+Li \emph{et al} showed that the dense detectors outperforms the sparse ones.
 
 \subsection{Description}
+
+	Localization of a salient point is not enough.
+If a keypoint is to be affaine transform invariant, it has to be described in more general terms then it's coordinates.
+Such description, usually coordinates in a multi-dimensional space, is provided by specialized algorithms.
+128-dimensional SIFT \cite{sift_features} is a 3D histogram of gradient locations and orientetions.
+It is the most often extracted and well as the most effective descriptors \cite{tsai2012bag}.
+Other methods include various color descriptors, binary 512-dimensional GIST \cite{ponce2011cv}.
+There are techniques designed for 3D exclusively.
+Among them one can find Persistent Point Features Histogram \cite{pfh_rusu2008} and its faster alternative Fast Point Feature Histogram \cite{fpfh_rusu2009}, both implemented in PCL.
+
 \subsection{Vector Quantization}

### 2013-09-29 Disseration/article.tex
classification

@@
 %\include{introduction}
+
+\section{Introduction}
+
+introduction
 
@@
 
-	Localization of a salient point is not enough.
-If a keypoint is to be affaine transform invariant, it has to be described in more general terms then it's coordinates.
-Such description, usually coordinates in a multi-dimensional space, is provided by specialized algorithms.
+	Computing localization of a salient point is not enough.
+If a keypoint is to be affaine transform invariant, it has to be described in more general terms.
+Such description, usually in a form of coordinates in a multi-dimensional space, is provided by specialized algorithms.
 128-dimensional SIFT \cite{sift_features} is a 3D histogram of gradient locations and orientetions.
-It is the most often extracted and well as the most effective descriptors \cite{tsai2012bag}.
-Other methods include various color descriptors, binary 512-dimensional GIST \cite{ponce2011cv}.
+It is the most often extracted as well as one of the most effective descriptors \cite{tsai2012bag}.
+Other methods include various color descriptors, binary descriptors such as 512-dimensional GIST \cite{ponce2011cv}.
 There are techniques designed for 3D exclusively.
@@
 \subsection{Vector Quantization}
+
+	The final step of extracting Bag of Words features i vector quantization.
+Generally clustering with the kMeans algorithm is used \cite{tsai2012bag}.
+The kMeans algorithm was developed in the 50's and a variety of modifications have been developed since \cite{kmeans_jain2010data}.
+Some of them are: faster than the original \emph{approximate kmeans}, \emph{hierarchical kmeans}, which automatically chooses the resulting number of clusters and a  \emph{soft kmeans} --- a variation of the algorithm that allows a fuzzy alignment (\textit{i.e.} each point can belong to several clusters with different weights.
+The soft kMeans is a compromise between kMeans' (relative to GMM) low computational cost and GMM's precision.
+The number of resulting visual words depends on the number of clusters.
+
+	In order to improve performance multitude of pre- or postprocessing techniques can be resorted to.
+A weighting scheme such as Term Frequency (TF) or Term Frequency - Inverse Document Frequency (TF-IDF) can be used.
+Spatial information might be encoded so as to capture spatial reletions of the extracted features.
+
+	It has been shown that the vector quantization steps is the computationally most expensive step in any Bag of Words framework.
+Fortunately, the majority of the cost is associated with the training part of the computation.
+When all the models are trained the only operation required in case of vector quantization is keypoint -- visual vocabulary matching.
+Even so, diverse algorithms have been used in order to minimize the impact of clustering on the overall efficiency.
+The \emph{approximate kMeans} is faster but insufficiently so as to solve the problem.
+Random Forests algorithm is considerably less expensive and can provide bettern Mean Average Precision (MAP) score.
+
+	Quite a different approach is using a Gaussian Mixture Model (GMM) algorithm.
+It is many times more expensive than kMeans, the tradeoff being higher precision.
+The GMM finds not only clusters' centroids but the gaussian distribiutions of points in each cluster.
+Therfore, in the keypoint-centroid matching stage a set of probabilities is obtained instead of a simple single-cluster assignment.
+These probabilities encode likelihoods of the keypoint belonging to each cluster.
+It is up to the user how to utilize this additional information.
+
 \subsection{Classification}
+
+	Predicting a class associated with an image requires feeding the visual words histograms into a classifiers.
+A simple example of a classifier would be a K-nearest neighbours algorithms.
+In this manner every histogram is treated as a point in a multi-dimensional space.
+In this setting, a class of an image is determined by classes of the nearest neighbours.
+Manifold of distinct metrics can be used: L1, L2  and others.
+The number of nearest neighbours (K) has to be determined.
+More advanced classifiers can be divided into the two main classes --- namely generative models and discriminative models.
+
+	Construction of a discriminative model requires a supervised learning approach.
+It can be seen as a learning by example method.
+The general aim is to compute an approximate mapping between representations of examples (the train set) and their labels and correctly labels a set of examples with unknown labels (the test set) with some level of accuracy.
+The model computation stage is called \emph{training} of a model.
+After the model has been trained previously unseen examples can be fed into the classifier.
+The clasifier calculates some similarity measure between the unlabled input example and all the modeled classes.
+The resulting label is a label of which class had the highest score in terms of the similarity measure.
+The previously discussed KNN is an example of a discriminative model.
+The most widely used discriminative classificator is a Support Vector Machine.
+
+	The generative models are usually Baysian text-based models. Many of them heavily depends on the Probabilistic Graphical Models concept.
 

### 2013-09-30 Disseration/article.tex
aa

@@
 One of the most simple cases would be to, given a dictionary, construct a histogram depicting the incidence of words in a particular document.
-Such an approach obliterates any grammatical dependencies in order to retain only the statistical information associated with each word.
+Such an approach obliterates any grammatical dependencies in order to retain only statistical information associated with each word.
 It is believed that the words' frequencies are connceted to the semantic meaning of the document.
@@
 All of the above is reffered to as a semantic gap.
-It is defined by Tsai, with respect to the Content Based Image Retrieval or \textit{CBIR}, as \emph{``the gap between the extracted and indexed low-level features by computers and the high-level concepts (or semantics) of user’s queries''}.
+It is defined by Tsai \cite{tsai2012bag}, with respect to the Content Based Image Retrieval or \textit{CBIR}, as \emph{``the gap between the extracted and indexed low-level features by computers and the high-level concepts (or semantics) of user’s queries''}.
 Suppose a text document can be created from an image.
@@
 Rigid transformation and illumination invariance would be desired but it is somewhat harder to achieve
-   \item Keypoint description --- each keypoint have to be described in a manner that distinguish the particular keypoint in some way.
+   \item Keypoint description --- each keypoint have to be described in a manner that distinguishes the particular keypoint in some way.
    \item Vector quantization --- clustering algorithms are used to find regions in the high dimensional space of keypoint descriptors.
-When the clusters are found, each described keypoint can be assigned to a corresponding cluster.
+When clusters are found, each described keypoint can be assigned to a corresponding cluster.
 Then, an image can be represented by the numbers of clusters, to which the image's keypoints were assigned.
@@
   Feature based methods can be either global or local.
-The former takes the form of a single vector or a point in a $d$ dimensional space --- the similarity measure resulting in computing point-wise distance in that space.
+The former takes the form of a single vector or a point in a $d$ dimensional space --- the similarity measure being a point-wise distance in that space.
 The latter gives multiple such points for each object, rendering the computation of a similarity measure slightly more complicated.
-The global features takes forms of the models' volume, their volume or mass distribution.
-Others might incorporate the global features' distribtution --- one conceivable approach would be to compute global feature's distribution and summarize them into a histogram.
+The global features takes forms of the models' volume, their mass or mass distributions.
+Others might incorporate the global features' distribtution --- one conceivable approach would be to compute global features' distributions and summarize them into a histogram.
 These features have the advantage of being easy to compute and straightforward to implement.
-However, they are insensitive to any local shape variations, thus being ill suited for details comparisions.
+However, they are insensitive to any local shape variations, thus being ill-suited for detailed comparisions.
 On the other hand, they might be exploited in the preprocessing of the data with more sophisticated methods being used afterwards.
-Partial matching is not possible, since the global features do not encode any relations between the parts of the objects.
+Partial matching is not possible, since the global features do not encode any relations between parts of the objects.
 
-  As for the local features, \cite{toldo2009bag} describes only the features that describe neighbourhood of the points being on the boundary of a shape.
-While that might generally be true, different points might be considered as well.
-Moreover, the authors state that the local features based methods are inefficien and indexing is rather complex.
+  As for the local features, \cite{toldo2009bag} discusses only features describing neighbourhood of the points on boundaries of objects.
+Any settings that does not match this criteria are neglected.
+Moreover, the authors state that the local feature based methods are inefficient and indexing is rather complex.
 A Bag of Words based approach, described in \cite{li2010investigating} has no such drawbacks.
 
-  Even tough BoW is a local features based method, it can be regarded as a feature distribution method.
-It is based on visual words, clearly being local features.
+	Bag of Words techniques can be regarded as feature distributions, even though they are local feature based --- the local features being visual words.
 When all the image's visual words are summarized into a histogram a distribution is created.
@@
 What is more, algorthims performing each main pipeline's step were proposed and evaluated as well as a codebook construction method was developed.
-A \emph{Harris Affine Detector} was used for feature extraction and \emph{SIFT} for the feature descripton.
+The \emph{Harris Affine Detector} was used for feature extraction and the \emph{SIFT} for the feature descripton step.
 The visual vocabulary has been generated by clustering only a limited number of keypoints from each category.
-After summarizing each image in the traning set with a histogram of visual words, supervised learning was used to train two classifiers: Na\`ive Bayes and a Support Vector Machine.
-As expected the Na\`ive Bayes resulted in lower accuracy than SVM (72 vs.
+After summarizing every image in the traning set with a histogram of visual words, supervised learning was used to train two classifiers: Na\`ive Bayes and a Support Vector Machine.
+As expected the Na\`ive Bayes resulted in a lower accuracy than SVM (72 vs.
 85\% on 7 categories).
-An analysis on the number of centroids in the clustering step depicts that the greater size of the visual vocabulary migh increase accuracy.
+An analysis on the number of centroids in the clustering step depicts that the greater the size of the visual vocabulary the greater the accuracy.
 
   Li \emph{et al} further refined the above approach by examining several keypoint detectors and descriptors.
-The main contribution of this work is, however, the development of a genuine classification algorithm based on probabilistic graphical models.
+The main contribution of their work is, however, the development of a genuine classification algorithm based on a probabilistic graphical model.
 Accuracy of 76\% on a large 13 category dataset was achieved.
@@
 There are following differences: (1) an object should be localized on an image (i.e.
-its bounding box has to be found) and (2) in object categorization information about the scene type might be used.
-The second case is symmetric, for in the scene categorization information about the objects present in the scene can be utilized as well.
+its bounding box has to be found) and (2) in object categorization task information about a scene type might be used.
+The second case is symmetric, for in the scene categorization problem information about objects present in the scene can be utilized as well.
 Having said that, it is possible to consider an object categorization problem where images of singled-out objects are provided --- e.g.
 a single object covers the majority of an image's area.
-Such an approach was exploited a recent work by Zhang \emph{et al} \cite{zhangcategory}.
+Such an approach was exploited in a recent work by Zhang \emph{et al} \cite{zhangcategory}.
 
@@
 	A number of more complicated recipes for salient region localization have been developed and implemented.
-These include include Scale Invariant Feature Transform \cite{sift_keypoint}, SUSAN \cite{susan_keypoint} and Intrinistic Shapes Siganutes \cite{iss_keypoint}.
-The majority of keypoint detection formulas is being develoepd for the 2d domain.
+These include Scale Invariant Feature Transform \cite{sift_keypoint}, SUSAN \cite{susan_keypoint} and Intrinistic Shape Siganutes \cite{iss_keypoint}.
+The majority of keypoint detection formulas is being develoepd for the 2D domain.
 A number of them have been adapted to 3D, however.
-A comparative evaluation of detection algorithm available in PCL can be find in \cite{pcl_keypoint_comparision}.
+A comparative evaluation of detection algorithms available in PCL can be find in \cite{pcl_keypoint_comparision}.
 Another comprehensive study is \cite{3d_keypoint_eval}.
@@
 A sparse detector might be unable to summarize a slow changing region such as clouds, sky or ocean.
-Li \emph{et al} showed that the dense detectors outperforms the sparse ones.
+Li \emph{et al} showed that dense detectors outperforms the sparse ones.
 
@@
 There are techniques designed for 3D exclusively.
-Among them one can find Persistent Point Features Histogram \cite{pfh_rusu2008} and its faster alternative Fast Point Feature Histogram \cite{fpfh_rusu2009}, both implemented in PCL.
+Among them one can find Persistent Point Feature Histogram \cite{pfh_rusu2008} and its faster alternative Fast Point Feature Histogram \cite{fpfh_rusu2009}, both implemented in PCL.
 
@@
 
-	The final step of extracting Bag of Words features i vector quantization.
+	The final step of extracting Bag of Words features is vector quantization.
 Generally clustering with the kMeans algorithm is used \cite{tsai2012bag}.
@@
 Some of them are: faster than the original \emph{approximate kmeans}, \emph{hierarchical kmeans}, which automatically chooses the resulting number of clusters and a  \emph{soft kmeans} --- a variation of the algorithm that allows a fuzzy alignment (\textit{i.e.} each point can belong to several clusters with different weights.
-The soft kMeans is a compromise between kMeans' (relative to GMM) low computational cost and GMM's precision.
+The soft kMeans is a compromise between kMeans' (relative to GMM, discussed below) low computational cost and GMM's precision.
 The number of resulting visual words depends on the number of clusters.
@@
 
-	It has been shown that the vector quantization steps is the computationally most expensive step in any Bag of Words framework.
+	It has been shown that the vector quantization step is the computationally most expensive step in any Bag of Words framework.
 Fortunately, the majority of the cost is associated with the training part of the computation.
@@
 	Predicting a class associated with an image requires feeding the visual words histograms into a classifiers.
-A simple example of a classifier would be a K-nearest neighbours algorithms.
-In this manner every histogram is treated as a point in a multi-dimensional space.
-In this setting, a class of an image is determined by classes of the nearest neighbours.
+A simple example of a classifier would be a K-nearest neighbours algorithm.
+In this setting every histogram is treated as a point in a multi-dimensional space.
+A class of an image is determined by classes of the nearest neighbours.
 Manifold of distinct metrics can be used: L1, L2  and others.
 The number of nearest neighbours (K) has to be determined.
-More advanced classifiers can be divided into the two main classes --- namely generative models and discriminative models.
+More advanced classifiers can be divided into the two main classes: generative models and discriminative models.
 
@@
 It can be seen as a learning by example method.
-The general aim is to compute an approximate mapping between representations of examples (the train set) and their labels and correctly labels a set of examples with unknown labels (the test set) with some level of accuracy.
+The general aim is to compute an approximate mapping between representations of examples (the train set).
+The purpouse of this mapping is correct (e.g.
+with some success rate) prediction of labels for inputs which label is unknown.
 The model computation stage is called \emph{training} of a model.
@@
 The resulting label is a label of which class had the highest score in terms of the similarity measure.
-The previously discussed KNN is an example of a discriminative model.
+The KNN is an example of a discriminative model.
 The most widely used discriminative classificator is a Support Vector Machine.
 
-	The generative models are usually Baysian text-based models. Many of them heavily depends on the Probabilistic Graphical Models concept.
+	The generative models are usually Baysian text-based models.
+Many of them heavily depends on the Probabilistic Graphical Models concept.
+They include \emph{Latent Semantic Analysis} with \emph{probabilistic Latent Semantic Analysis}, \emph{Latent Dirichlet Allocation} and others.
+These models allow discovery of topic distrubution in documents.
+In the image domain an image can be though of as a document and an object category as a topic.
+Under this conditions an image (and its category) can be modeled as a mixture of topics.
+Learning consists of finding topics distributions for each specific category.
 

### 2013-10-01 Disseration/article.tex
refactoring in progress

@@
 
-  As portreyed in \cite{tsai2012bag} the Bag of Words or BoW model has originated from the text retrieval domain.
+  As portrayed in \cite{tsai2012bag} the Bag of Words or BoW model has originated from the text retrieval domain.
 Originally the model enabled a vector-like representation of a text document.
@@
 Such an approach obliterates any grammatical dependencies in order to retain only statistical information associated with each word.
-It is believed that the words' frequencies are connceted to the semantic meaning of the document.
+It is believed that the words' frequencies are connected to the semantic meaning of the document.
 The following questions emerge:
@@
 A simple conversion to an RGB format makes the data structured and is enough for people to understand pictures' content.
-Unforunately, such image representation is extrmelly vulnerable to translation and rotation as well as changing lighting conditions.
+Unfortunately, such image representation is extremely vulnerable to translation and rotation as well as changing lighting conditions.
 One way to address these disadvantages would be to compute locations of some characteristic points (keypoints) and describe them somehow.
-Even then, however, the resulting represenation is a low level one and still incomprehensible for humans.
+Even then, however, the resulting representation is a low level one and still incomprehensible for humans.
 Defining robot's behaviour basing on such data might prove cumbersome, for there are too many details to consider.
-All of the above is reffered to as a semantic gap.
+All of the above is refereed to as a semantic gap.
 It is defined by Tsai \cite{tsai2012bag}, with respect to the Content Based Image Retrieval or \textit{CBIR}, as \emph{``the gap between the extracted and indexed low-level features by computers and the high-level concepts (or semantics) of user’s queries''}.
@@
 
-  The Bag of Words image representation has been extensively used in the areas of scene \cite{csurka2004visual,fei2005bayesian, tsai2012bag} and object categorization \cite{zhangcategory} as well as CBIR \cite{li2010investigating,toldo2009bag} yielding state-of-the-art results.
+  The Bag of Words image representation has been extensively used in the areas of scene \cite{csurka2004visual,fei2005bayesian, tsai2012bag} and object categorisation \cite{zhangcategory} as well as CBIR \cite{li2010investigating,toldo2009bag} yielding state-of-the-art results.
 Advantages of this model are simplicity, computational efficiency and at least partial invariance to affine transformation, occlusion and lighting conditions.
@@
 
-  There are numerous methods suitable for computation of objetcs' signatures.
+  There are numerous methods suitable for computation of objects' signatures.
 Many of them can be used in the indexing step.
@@
 The global features takes forms of the models' volume, their mass or mass distributions.
-Others might incorporate the global features' distribtution --- one conceivable approach would be to compute global features' distributions and summarize them into a histogram.
+Others might incorporate the global features' distribution --- one conceivable approach would be to compute global features' distributions and summarise them into a histogram.
 These features have the advantage of being easy to compute and straightforward to implement.
-However, they are insensitive to any local shape variations, thus being ill-suited for detailed comparisions.
+However, they are insensitive to any local shape variations, thus being ill-suited for detailed comparisons.
 On the other hand, they might be exploited in the preprocessing of the data with more sophisticated methods being used afterwards.
@@
 	Bag of Words techniques can be regarded as feature distributions, even though they are local feature based --- the local features being visual words.
-When all the image's visual words are summarized into a histogram a distribution is created.
+When all the image's visual words are summarised into a histogram a distribution is created.
 Being similar to a point in a multi-dimensional space, it is similar to a global feature.
 Consequently, similar methods apply, with the distinction being that the histogram is rather a vector then a point.
-Thus metrics well-suited to vector comparision, such as a cosine distance, can be used.
+Thus metrics well-suited to vector comparison, such as a cosine distance, can be used.
 
-  \subsection{Scene Categorization}
+  \subsection{Scene Categorisation}
 
-  One of the first works employing the BoW for the purpouse of scene categorization is \cite{csurka2004visual}.
+  One of the first works employing the BoW for the purpose of scene categorisation is \cite{csurka2004visual}.
 The authors suggested a general framework.
-What is more, algorthims performing each main pipeline's step were proposed and evaluated as well as a codebook construction method was developed.
-The \emph{Harris Affine Detector} was used for feature extraction and the \emph{SIFT} for the feature descripton step.
+What is more, algorithms performing each main pipeline's step were proposed and evaluated as well as a codebook construction method was developed.
+The \emph{Harris Affine Detector} was used for feature extraction and the \emph{SIFT} for the feature description step.
 The visual vocabulary has been generated by clustering only a limited number of keypoints from each category.
-After summarizing every image in the traning set with a histogram of visual words, supervised learning was used to train two classifiers: Na\`ive Bayes and a Support Vector Machine.
+After summarising every image in the training set with a histogram of visual words, supervised learning was used to train two classifiers: Na\`ive Bayes and a Support Vector Machine.
 As expected the Na\`ive Bayes resulted in a lower accuracy than SVM (72 vs.
@@
 
-  \subsection{Object Categorization}
+  \subsection{Object Categorisation}
 
-  In many cases object categorization might be addressed as a scene categorization problem.
-There are following differences: (1) an object should be localized on an image (i.e.
-its bounding box has to be found) and (2) in object categorization task information about a scene type might be used.
-The second case is symmetric, for in the scene categorization problem information about objects present in the scene can be utilized as well.
-Having said that, it is possible to consider an object categorization problem where images of singled-out objects are provided --- e.g.
+  In many cases object categorisation might be addressed as a scene categorisation problem.
+There are following differences: (1) an object should be localised on an image (i.e.
+its bounding box has to be found) and (2) in object categorisation task information about a scene type might be used.
+The second case is symmetric, for in the scene categorisation problem information about objects present in the scene can be utilised as well.
+Having said that, it is possible to consider an object categorisation problem where images of singled-out objects are provided --- e.g.
 a single object covers the majority of an image's area.
@@
 
-	The Bag of Words intermediate image represenation provides a concise way of summarizing images.
-It is invariant to affaine transformations, partial occlusion and, in some extent, to changing lighting conditions.
+	The Bag of Words intermediate image representation provides a concise way of summarising images.
+It is invariant to affine transformations, partial occlusion and, in some extent, to changing lighting conditions.
 What is more, it is easy to implement and computationally efficient.
@@
 Either generative or discriminative methods can be used.
-Below the main steps of BoW classification processing pipeline will be disscussed.
+Below the main steps of BoW classification processing pipeline will be discussed.
 
@@
 A technique taking advantage of the Harris corner detector is for example a Harris-Laplace detector --- the Harris function is scale adapted and its outcome is a subject to a Laplacian-of-Gaussian operator, which selects relevant points in the scale space.
-Images' regions' 2\textsuperscript{nd} derviatives --- namely the regions' Hessians --- can be combined with a LoG operator.
+Images' regions' 2\textsuperscript{nd} derivatives --- namely the regions' Hessians --- can be combined with a LoG operator.
 This combination allows selection of points significant in the two spaces: the scale space and the Hessian's determinant space.
@@
 
-	A number of more complicated recipes for salient region localization have been developed and implemented.
-These include Scale Invariant Feature Transform \cite{sift_keypoint}, SUSAN \cite{susan_keypoint} and Intrinistic Shape Siganutes \cite{iss_keypoint}.
-The majority of keypoint detection formulas is being develoepd for the 2D domain.
+	A number of more complicated recipes for salient region localisation have been developed and implemented.
+These include Scale Invariant Feature Transform \cite{sift_keypoint}, SUSAN \cite{susan_keypoint} and Intrinistic Shape Signatures \cite{iss_keypoint}.
+The majority of keypoint detection formulas is being developed for the 2D domain.
 A number of them have been adapted to 3D, however.
@@
 	All these formulas, called sparse feature detectors, resort to selection of maxima in specific state spaces.
-An entierly different scheme is to use a dense feature detector.
+An entirely different scheme is to use a dense feature detector.
 This particular form requires users to specify a uniformly sampled grid from which points are taken.
 Dense detectors have an advantage of taking points from slow changing regions.
-A sparse detector might be unable to summarize a slow changing region such as clouds, sky or ocean.
+A sparse detector might be unable to summarise a slow changing region such as clouds, sky or ocean.
 Li \emph{et al} showed that dense detectors outperforms the sparse ones.
@@
 
-	Computing localization of a salient point is not enough.
-If a keypoint is to be affaine transform invariant, it has to be described in more general terms.
-Such description, usually in a form of coordinates in a multi-dimensional space, is provided by specialized algorithms.
-128-dimensional SIFT \cite{sift_features} is a 3D histogram of gradient locations and orientetions.
+	Computing localisation of a salient point is not enough.
+If a keypoint is to be affine transform invariant, it has to be described in more general terms.
+Such description, usually in a form of coordinates in a multi-dimensional space, is provided by specialised algorithms.
+128-dimensional SIFT \cite{sift_features} is a 3D histogram of gradient locations and orientations.
 It is the most often extracted as well as one of the most effective descriptors \cite{tsai2012bag}.
-Other methods include various color descriptors, binary descriptors such as 512-dimensional GIST \cite{ponce2011cv}.
+Other methods include various colour descriptors, binary descriptors such as 512-dimensional GIST \cite{ponce2011cv}.
 There are techniques designed for 3D exclusively.
@@
 A weighting scheme such as Term Frequency (TF) or Term Frequency - Inverse Document Frequency (TF-IDF) can be used.
-Spatial information might be encoded so as to capture spatial reletions of the extracted features.
+Spatial information might be encoded so as to capture spatial relations of the extracted features.
 
@@
 When all the models are trained the only operation required in case of vector quantization is keypoint -- visual vocabulary matching.
-Even so, diverse algorithms have been used in order to minimize the impact of clustering on the overall efficiency.
+Even so, diverse algorithms have been used in order to minimise the impact of clustering on the overall efficiency.
 The \emph{approximate kMeans} is faster but insufficiently so as to solve the problem.
-Random Forests algorithm is considerably less expensive and can provide bettern Mean Average Precision (MAP) score.
+Random Forests algorithm is considerably less expensive and can provide better Mean Average Precision (MAP) score.
 
@@
 It is many times more expensive than kMeans, the tradeoff being higher precision.
-The GMM finds not only clusters' centroids but the gaussian distribiutions of points in each cluster.
-Therfore, in the keypoint-centroid matching stage a set of probabilities is obtained instead of a simple single-cluster assignment.
+The GMM finds not only clusters' centroids but the Gaussian distributions of points in each cluster.
+Therefore, in the keypoint-centroid matching stage a set of probabilities is obtained instead of a simple single-cluster assignment.
 These probabilities encode likelihoods of the keypoint belonging to each cluster.
-It is up to the user how to utilize this additional information.
+It is up to the user how to utilise this additional information.
 
@@
 The general aim is to compute an approximate mapping between representations of examples (the train set).
-The purpouse of this mapping is correct (e.g.
+The purpose of this mapping is correct (e.g.
 with some success rate) prediction of labels for inputs which label is unknown.
@@
 After the model has been trained previously unseen examples can be fed into the classifier.
-The clasifier calculates some similarity measure between the unlabled input example and all the modeled classes.
+The classifier calculates some similarity measure between the unlabelled input example and all the modeled classes.
 The resulting label is a label of which class had the highest score in terms of the similarity measure.
@@
 
-	The generative models are usually Baysian text-based models.
+	The generative models are usually Bayesian text-based models.
 Many of them heavily depends on the Probabilistic Graphical Models concept.
 They include \emph{Latent Semantic Analysis} with \emph{probabilistic Latent Semantic Analysis}, \emph{Latent Dirichlet Allocation} and others.
-These models allow discovery of topic distrubution in documents.
+These models allow discovery of topic distribution in documents.
 In the image domain an image can be though of as a document and an object category as a topic.

### 2013-10-01 src/Common/ProcessObject.h

@@ -37,7 +37,7 @@ protected:
 	const std::string separator = ".";
 	lgr::LoggerPtr logger;
 	std::string directory;
-	const std::string directoryKey = "directory";
+
 
 private:
 	ProcessObject();
@@ -47,6 +47,9 @@ private:
 	T stringToNumber(const std::string &s, T def = T() );
 
 	std::map<std::string, std::string> configMap;
+
+	const std::string mode = "mode";
+	const std::string directoryKey = "directory";
 };
 
 template<typename T>

### 2013-10-01 src/Common/Tagger3D.cpp

@@ -19,6 +19,7 @@
 #include "../Predictor/SVMPredictor.h"
 
 #include <assert.h>
+#include <fstream>
 
 namespace Tagger3D {
 
@@ -73,6 +74,7 @@ Tagger3D::Tagger3D(const std::map<std::string, std::string> &configMap) : Proces
 	assert( descriptor != nullptr );
 	assert( cluster != nullptr );
 	assert( predictor != nullptr );
+
 }
 
 Tagger3D::~Tagger3D() {
@@ -86,45 +88,22 @@ int Tagger3D::trainTest() {
 	return 1;
 }
 void Tagger3D::train() {
-
 	INFO(logger, "Train");
-	std::vector<int> labels;
-	ColorVec colorClouds;
-	NormalVec normalClouds;
-	ScaleVec keypointClouds;
-	std::vector<cv::Mat> descriptors;
+
+	std::vector<int> labels = imgReader->readLabels();
+	std::vector<cv::Mat> descriptors = prepareDescriptors();
 	std::vector<std::vector<int>> wordDescriptors;
 
-	INFO(logger, "Reading images");
 
-	colorClouds = imgReader->readImgs();
-	labels = imgReader->readLabels();
-
-	if(colorClouds.size() != labels.size()) {
-
+	if(descriptors.size() != labels.size()) {
 		std::runtime_error e("Number of point clouds and labels differ: " +
 				std::to_string(colorClouds.size()) + ", " + std::to_string(labels.size()));
 		ERROR(logger, "train: " << e.what());
 		throw e;
 	}
 
-	INFO(logger, "Read " << colorClouds.size() << " point clouds");
-	INFO(logger, "Computing normals");
 
-	for(auto &cloud : colorClouds) {
-
-		normalClouds.emplace_back(pointNormal->computeNormals( cloud ));
-		pointNormal->cleanupInputCloud( cloud );
-	}
-
-	INFO(logger, "Detecting keypoints");
-	keypointClouds = detector->detect( colorClouds );
-
-	INFO(logger, "Describing keypoints");
-	descriptors = descriptor->describe( colorClouds, keypointClouds, normalClouds );
-
-
-
+	//prepareCluster;
 
 	switch( getParam<int>(trainCluster) ) {
 	case 1:
@@ -228,6 +207,131 @@ int Tagger3D::run() {
 	}
 }
 
+const std::string info = ".info";
 
[…]

### 2013-10-01 src/Common/Tagger3D.h

@@ -28,6 +28,9 @@ class Tagger3D: public ProcessObject {
 	 * Tagger3D is an object categorization.
 	 * Provided an RGB-D input it predicts a category of an object.
 	 */
+
+	//	-------------------------------------------------------------------------
+	//	Methods	------------------------------------------------------------------
 public:
 	Tagger3D(const std::map<std::string, std::string> &configMap);
 	virtual ~Tagger3D();
@@ -66,6 +69,19 @@ public:
 private:
 	Tagger3D();
 
+	void saveDescriptors(const std::vector<cv::Mat> &descriptors, const std::string &path);
+	std::vector<cv::Mat> loadDescriptors(const std::string &path);
+
+	std::vector<cv::Mat> getDescriptors(const std::string &path);
+
+	std::vector<cv::Mat> computeDescriptors();
+
+
+	//	-----------------------------------------------------------------------
+	// Fields	----------------------------------------------------------------
+public:
+private:
+	// Pointers	----------------------------------------------------------------
 	std::unique_ptr<ImgReader> imgReader;
 	std::unique_ptr<PointNormal> pointNormal;
 	std::unique_ptr<Detector> detector;
@@ -73,22 +89,35 @@ private:
 	std::unique_ptr<Cluster> cluster;
 	std::unique_ptr<Predictor> predictor;
 
-	enum { TRAIN, TEST, TRAINTEST, PREDICT };
-	enum { RANGEIMG_READER, PCD_READER };
-	enum { SIFT, ISS3D };
-	enum { PFH_DESC, FPFH_DESC };
-	enum { SLDA, SVM };
 
+	//	Parameters	------------------------------------------------------------
+
+
+
+
+	// Constants	----------------------------------------------------------------
 	const std::string loggerName = "Tagger3D";
 	const std::string moduleName = "Tagger3D" + separator;
 
-	// Config keys
-	const std::string mode = moduleName + "mode";
+	// Config keys	---------------------------------------------------------------
 	const std::string readerType = moduleName + "readerType";
 	const std::string detectorType = moduleName + "detectorType";
 	const std::string descType = moduleName + "descType";
 	const std::string predictorType = moduleName + "predictorType";
 	const std::string trainCluster = moduleName + "trainCluster";
+
+	const std::string trainDescriptors = "trainDescriptors";
+	const std::string testDescriptors = "testDescriptors";
[…]

### 2013-10-01 src/ImgReader/ImgReader.h

@@ -32,6 +32,12 @@ public:
 	 */
 	virtual ColorVec readImgs() = 0;
 
+
+	/**
+	 * Returns a label for a previously read image
+	 */
+	virtual int readLabel() = 0;
+
 	/**
 	 * Reads labels for a batch of images
 	 * @return a vector of labels
@@ -43,7 +49,7 @@ protected:
 	std::vector<std::string> getLineList(const std::string &path);
 	std::string moduleName = "ImgReader" + separator;
 	std::vector<std::string> labelVec;
-	const std::string mode = "Tagger3D.mode";
+
 	enum { TRAIN, TEST };
 
 private:

### 2013-10-01 src/ImgReader/PcdReader.cpp

@@ -76,4 +76,9 @@ ColorCloud::Ptr PcdReader::readImg() {
 	return readImg( pcdVec[count++] );
 }
 
+int PcdReader::readLabel() {
+
+	return 0;
+}
+
 } /* namespace Tagger3D */

### 2013-10-01 src/ImgReader/RangeImgReader.h

@@ -23,6 +23,8 @@ public:
 	ColorCloud::Ptr readImg();
 	ColorVec readImgs();
 
+	int readLabel();
+
 protected:
 	void readImg(const std::string &colorPath, const std::string &depthPath, cv::Mat &colorImg, cv::Mat &depthImg);
 	ColorCloud::Ptr readImg(const std::string &colorPath, const std::string &depthPath);

### 2013-10-01 src/Predictor/SVMPredictor.cpp

@@ -32,8 +32,8 @@ SVMPredictor::SVMPredictor(const std::map<std::string, std::string> &configMap) 
     svmType = getParam<int>( svmTypeKey );
     kernelType = getParam<int>( kernelTypeKey );
     termCrit  = getParam<int>( termCritKey );
-    svmPath = const_cast<char*>(getParam<std::string>( svmPathKey ).c_str() );
-    histogramPath = const_cast<char*>(getParam<std::string>( histogramPathKey ).c_str());
+    svmPath = directory + "/" + getParam<std::string>( svmPathKey );
+    histogramPath = directory + "/" + getParam<std::string>( histogramPathKey );
     storeHistogram = getParam<bool>(storeHistogramKey);
     dictionarySize = getParam<int>( dictionarySizeKey );
     epsilon = getParam<double>( epsilonKey );
@@ -41,7 +41,6 @@ SVMPredictor::SVMPredictor(const std::map<std::string, std::string> &configMap) 
     gamma = getParam<double>( gammaKey );
     C = getParam<double>( CKey );
     degree = getParam<int>( epsilonKey );
-
 
     if (storeHistogram) {//if store, than delete old-file
         if( remove( histogramPath.c_str() ) != 0 ){

### 2013-10-09 Disseration/article.tex
a

@@
 \usepackage[T1]{fontenc}
-\usepackage[top=3cm, bottom=6cm, left=4cm, right=3cm]{geometry}
+\usepackage[top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
 \usepackage{cite}
 
-\linespread{1.15}
+%\setlength{\parskip}{6pt}%
+\linespread{1.5}
+
+\newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}
+\newcommand{\subscript}[1]{\ensuremath{_{\textrm{#1}}}}
 
@@
 
-  As portrayed in \cite{tsai2012bag} the Bag of Words or BoW model has originated from the text retrieval domain.
-Originally the model enabled a vector-like representation of a text document.
-One of the most simple cases would be to, given a dictionary, construct a histogram depicting the incidence of words in a particular document.
-Such an approach obliterates any grammatical dependencies in order to retain only statistical information associated with each word.
-It is believed that the words' frequencies are connected to the semantic meaning of the document.
+  As portrayed by Tsai in \cite{tsai2012bag} the Bag of Words (BoW) model has originated from the text retrieval domain.
+The model enables text document represenation in a form of a vector.
+Suppose we have a corpus of documents.
+A dictionary over the corpus is a set of words such that every word from the corpus can be matched to exactly one word in the dictionary and every two words in a dictionary are different.
+Given a dictionary, a histogram of incidence of words can be build.
+This histogram has the following form: for every entry in the dictionary there isa number of words in the document matching the entry.
+Such an approach obliterates any grammatical dependencies in order to retain only statistical information associated with words.
+It is believed that the words' frequencies enconde enough data for further processing.
 The following questions emerge:
@@
 
-  In order to answer the first question one has to consider how computers process data.
-Digital images are nothing but streams of binary code.
-A simple conversion to an RGB format makes the data structured and is enough for people to understand pictures' content.
-Unfortunately, such image representation is extremely vulnerable to translation and rotation as well as changing lighting conditions.
-One way to address these disadvantages would be to compute locations of some characteristic points (keypoints) and describe them somehow.
-Even then, however, the resulting representation is a low level one and still incomprehensible for humans.
-Defining robot's behaviour basing on such data might prove cumbersome, for there are too many details to consider.
-All of the above is refereed to as a semantic gap.
-It is defined by Tsai \cite{tsai2012bag}, with respect to the Content Based Image Retrieval or \textit{CBIR}, as \emph{``the gap between the extracted and indexed low-level features by computers and the high-level concepts (or semantics) of user’s queries''}.
+  In order to answer the first question one has to consider what digital images are --- they are nothing but strings of binary code.
+Translated to i.e.
+RGB colour space, they can be displayed and understood by humans, but there are no direct methods that would let computers `understand' what does a picture contain.
+Suppose two images of the same object were taken from different viewing angles.
+Being easy for a human,  it is impossible for any computer to compare those two pictures (or objects they depict) in any simple manner.
+This example shows a need for an intermediate representation that would enable image processing.
+Advanced algorithms for characteristic region detection and description exist (SIFT, SURF, FAST among many others).
+Even then, however, the resulting representation is a low level one.
+Consider a scenerio in which a robot is to adjust its behaviour depending on where it currently is (a type of a location, i.e.
+house, factory, mine).
+It order to define required adjustments a programmer would have to encode the low level representation of possibly many robot's destination enviornments.
+It is a variation of a problem described by Tsai \cite{tsai2012bag}, with respect to the Content Based Image Retrieval (\textit{CBIR}), as \emph{``the gap between the extracted and indexed low-level features by computers and the high-level concepts (or semantics) of user’s queries''}.
 Suppose a text document can be created from an image.
-If this is the case, then the document can be converted into a BoW model.
-Since the latter contains information about the semantic significance of the image an impact of the semantic gap can be reduced.
+In this case, then the document can be converted into a BoW model.
+Since it preserve semantic information that can be extracted  from it, an impact of the semantic gap can be reduced.
 

### 2013-10-11 Disseration/article.tex
added figures, class diagrams

--- 2013-09-30 Disseration/article.tex
@@
 
-\begin{abstract}
-
-Abstrakt
-
-\end{abstract}
-
-%\include{introduction}
-
-\section{Introduction}
-
-introduction
-
-\section{Bag of Words image representation}
-
-  As portreyed in \cite{tsai2012bag} the Bag of Words or BoW model has originated from the text retrieval domain.
-Originally the model enabled a vector-like representation of a text document.
-One of the most simple cases would be to, given a dictionary, construct a histogram depicting the incidence of words in a particular document.
-Such an approach obliterates any grammatical dependencies in order to retain only statistical information associated with each word.
-It is believed that the words' frequencies are connceted to the semantic meaning of the document.
-The following questions emerge:
-
-  \begin{itemize}
-    \item How does this apply to the area of computer vision?
-    \item How can one convert an image to a text document? 
-  \end{itemize}
-
-  In order to answer the first question one has to consider how computers process data.
-Digital images are nothing but streams of binary code.
-A simple conversion to an RGB format makes the data structured and is enough for people to understand pictures' content.
-Unforunately, such image representation is extrmelly vulnerable to translation and rotation as well as changing lighting conditions.
-One way to address these disadvantages would be to compute locations of some characteristic points (keypoints) and describe them somehow.
-Even then, however, the resulting represenation is a low level one and still incomprehensible for humans.
-Defining robot's behaviour basing on such data might prove cumbersome, for there are too many details to consider.
-All of the above is reffered to as a semantic gap.
-It is defined by Tsai \cite{tsai2012bag}, with respect to the Content Based Image Retrieval or \textit{CBIR}, as \emph{``the gap between the extracted and indexed low-level features by computers and the high-level concepts (or semantics) of user’s queries''}.
-Suppose a text document can be created from an image.
-If this is the case, then the document can be converted into a BoW model.
-Since the latter contains information about the semantic significance of the image an impact of the semantic gap can be reduced.
-
-  As for the second question, there is a quite well established pipeline that enables creation of text documents from images. The steps of the BoW methodology are as follows:
-  \begin{itemize}
-   \item Keypoint detection --- keypoints are local interest points or regions.
-They are usually computed in such a way so as to provide scale and location invariance.
-Rigid transformation and illumination invariance would be desired but it is somewhat harder to achieve
-   \item Keypoint description --- each keypoint have to be described in a manner that distinguishes the particular keypoint in some way.
-   \item Vector quantization --- clustering algorithms are used to find regions in the high dimensional space of keypoint descriptors.
-When clusters are found, each described keypoint can be assigned to a corresponding cluster.
-Then, an image can be represented by the numbers of clusters, to which the image's keypoints were assigned.
-The numbers themselves are called \emph{`visual words'}.
-  \end{itemize}
-
-\section{BoW in Computer Vision}
-
-  The Bag of Words image representation has been extensively used in the areas of scene \cite{csurka2004visual,fei2005bayesian, tsai2012bag} and object categorization \cite{zhangcategory} as well as CBIR \cite{li2010investigating,toldo2009bag} yielding state-of-the-art results.
-Advantages of this model are simplicity, computational efficiency and at least partial invariance to affine transformation, occlusion and lighting conditions.
-
-  The Bag of Words is a type of intermediate representation.
-Therefore it is not sufficient to compute a BoW model of an image in order to predict its category.
-Additional operations are essential if the model is to be used in one of the enumerated fields.
-
-  \subsection{Content Based Image Retrieval}
-
-  One of the most notorious use-case of \emph{CBIR} is to search a database in order to find an object fulfilling certain conditions.
-As \cite{toldo2009bag} outlines, several criteria have to be met for the task to be performed efficiently.
-Firstly, all entries should be indexed in a concise way.
-Secondly, some (dis)similarity measure should be provided.
-Finally, an efficient search algorithm should be available.
-
-  There are numerous methods suitable for computation of objetcs' signatures.
-Many of them can be used in the indexing step.
-All the methods were divided into three general categories in \cite{toldo2009bag}, specifically: feature based methods, graph based methods and other methods.
-
-  Feature based methods can be either global or local.
-The former takes the form of a single vector or a point in a $d$ dimensional space --- the similarity measure being a point-wise distance in that space.
-The latter gives multiple such points for each object, rendering the computation of a similarity measure slightly more complicated.
-The global features takes forms of the models' volume, their mass or mass distributions.
-Others might incorporate the global features' distribtution --- one conceivable approach would be to compute global features' distributions and summarize them into a histogram.
-These features have the advantage of being easy to compute and straightforward to implement.
-However, they are insensitive to any local shape variations, thus being ill-suited for detailed comparisions.
-On the other hand, they might be exploited in the preprocessing of the data with more sophisticated methods being used afterwards.
-Partial matching is not possible, since the global features do not encode any relations between parts of the objects.
-
-  As for the local features, \cite{toldo2009bag} discusses only features describing neighbourhood of the points on boundaries of objects.
-Any settings that does not match this criteria are neglected.
-Moreover, the authors state that the local feature based methods are inefficient and indexing is rather complex.
-A Bag of Words based approach, described in \cite{li2010investigating} has no such drawbacks.
-
-	Bag of Words techniques can be regarded as feature distributions, even though they are local feature based --- the local features being visual words.
-When all the image's visual words are summarized into a histogram a distribution is created.
-Being similar to a point in a multi-dimensional space, it is similar to a global feature.
-Consequently, similar methods apply, with the distinction being that the histogram is rather a vector then a point.
-Thus metrics well-suited to vector comparision, such as a cosine distance, can be used.
-
-  \subsection{Scene Categorization}
-
-  One of the first works employing the BoW for the purpouse of scene categorization is \cite{csurka2004visual}.
-The authors suggested a general framework.
-What is more, algorthims performing each main pipeline's step were proposed and evaluated as well as a codebook construction method was developed.
-The \emph{Harris Affine Detector} was used for feature extraction and the \emph{SIFT} for the feature descripton step.
-The visual vocabulary has been generated by clustering only a limited number of keypoints from each category.
-After summarizing every image in the traning set with a histogram of visual words, supervised learning was used to train two classifiers: Na\`ive Bayes and a Support Vector Machine.
-As expected the Na\`ive Bayes resulted in a lower accuracy than SVM (72 vs.
-85\% on 7 categories).
-An analysis on the number of centroids in the clustering step depicts that the greater the size of the visual vocabulary the greater the accuracy.
-
-  Li \emph{et al} further refined the above approach by examining several keypoint detectors and descriptors.
-The main contribution of their work is, however, the development of a genuine classification algorithm based on a probabilistic graphical model.
-Accuracy of 76\% on a large 13 category dataset was achieved.
-
-  \subsection{Object Categorization}
-
-  In many cases object categorization might be addressed as a scene categorization problem.
-There are following differences: (1) an object should be localized on an image (i.e.
-its bounding box has to be found) and (2) in object categorization task information about a scene type might be used.
-The second case is symmetric, for in the scene categorization problem information about objects present in the scene can be utilized as well.
-Having said that, it is possible to consider an object categorization problem where images of singled-out objects are provided --- e.g.
-a single object covers the majority of an image's area.
-Such an approach was exploited in a recent work by Zhang \emph{et al} \cite{zhangcategory}.
-
-\section{BoW based classification}
-
-	The Bag of Words intermediate image represenation provides a concise way of summarizing images.
-It is invariant to affaine transformations, partial occlusion and, in some extent, to changing lighting conditions.
-What is more, it is easy to implement and computationally efficient.
-The efficiency can be enhanced even further with gpu based implementations as shown in \cite{van2011empowering}.
-In order to incorporate BoW into an object classification framework one has to feed the resulting histograms into a classification algorithms.
-Either generative or discriminative methods can be used.
-Below the main steps of BoW classification processing pipeline will be disscussed.
-
-\subsection{Detection}
-
-	Characteristic point detection is the first step in any Bag of Words framework.
-Numerous detection methods have been developed, but choosing the right one for the particular case might prove tricky.
-A good overview of various mechanisms is available in \cite{tsai2012bag}.
-The most common detectors make use of a Harris corner detector or image's first or second derivatives.
-A technique taking advantage of the Harris corner detector is for example a Harris-Laplace detector --- the Harris function is scale adapted and its outcome is a subject to a Laplacian-of-Gaussian operator, which selects relevant points in the scale space.
-Images' regions' 2\textsuperscript{nd} derviatives --- namely the regions' Hessians --- can be combined with a LoG operator.
-This combination allows selection of points significant in the two spaces: the scale space and the Hessian's determinant space.
-The latter entails the speed at which pixel intensities change in the neighbourhood of a point.
-
-	A number of more complicated recipes for salient region localization have been developed and implemented.
-These include Scale Invariant Feature Transform \cite{sift_keypoint}, SUSAN \cite{susan_keypoint} and Intrinistic Shape Siganutes \cite{iss_keypoint}.
-The majority of keypoint detection formulas is being develoepd for the 2D domain.
-A number of them have been adapted to 3D, however.
-A comparative evaluation of detection algorithms available in PCL can be find in \cite{pcl_keypoint_comparision}.
-Another comprehensive study is \cite{3d_keypoint_eval}.
-
-	All these formulas, called sparse feature detectors, resort to selection of maxima in specific state spaces.
-An entierly different scheme is to use a dense feature detector.
-This particular form requires users to specify a uniformly sampled grid from which points are taken.
-Dense detectors have an advantage of taking points from slow changing regions.
-A sparse detector might be unable to summarize a slow changing region such as clouds, sky or ocean.
-Li \emph{et al} showed that dense detectors outperforms the sparse ones.
-
-\subsection{Description}
-
-	Computing localization of a salient point is not enough.
-If a keypoint is to be affaine transform invariant, it has to be described in more general terms.
-Such description, usually in a form of coordinates in a multi-dimensional space, is provided by specialized algorithms.
-128-dimensional SIFT \cite{sift_features} is a 3D histogram of gradient locations and orientetions.
-It is the most often extracted as well as one of the most effective descriptors \cite{tsai2012bag}.
-Other methods include various color descriptors, binary descriptors such as 512-dimensional GIST \cite{ponce2011cv}.
-There are techniques designed for 3D exclusively.
-Among them one can find Persistent Point Feature Histogram \cite{pfh_rusu2008} and its faster alternative Fast Point Feature Histogram \cite{fpfh_rusu2009}, both implemented in PCL.
-
-\subsection{Vector Quantization}
-
-	The final step of extracting Bag of Words features is vector quantization.
-Generally clustering with the kMeans algorithm is used \cite{tsai2012bag}.
-The kMeans algorithm was developed in the 50's and a variety of modifications have been developed since \cite{kmeans_jain2010data}.
-Some of them are: faster than the original \emph{approximate kmeans}, \emph{hierarchical kmeans}, which automatically chooses the resulting number of clusters and a  \emph{soft kmeans} --- a variation of the algorithm that allows a fuzzy alignment (\textit{i.e.} each point can belong to several clusters with different weights.
-The soft kMeans is a compromise between kMeans' (relative to GMM, discussed below) low computational cost and GMM's precision.
-The number of resulting visual words depends on the number of clusters.
-
-	In order to improve performance multitude of pre- or postprocessing techniques can be resorted to.
-A weighting scheme such as Term Frequency (TF) or Term Frequency - Inverse Document Frequency (TF-IDF) can be used.
-Spatial information might be encoded so as to capture spatial reletions of the extracted features.
-
-	It has been shown that the vector quantization step is the computationally most expensive step in any Bag of Words framework.
-Fortunately, the majority of the cost is associated with the training part of the computation.
-When all the models are trained the only operation required in case of vector quantization is keypoint -- visual vocabulary matching.
-Even so, diverse algorithms have been used in order to minimize the impact of clustering on the overall efficiency.
-The \emph{approximate kMeans} is faster but insufficiently so as to solve the problem.
-Random Forests algorithm is considerably less expensive and can provide bettern Mean Average Precision (MAP) score.
-
-	Quite a different approach is using a Gaussian Mixture Model (GMM) algorithm.
-It is many times more expensive than kMeans, the tradeoff being higher precision.
-The GMM finds not only clusters' centroids but the gaussian distribiutions of points in each cluster.
-Therfore, in the keypoint-centroid matching stage a set of probabilities is obtained instead of a simple single-cluster assignment.
-These probabilities encode likelihoods of the keypoint belonging to each cluster.
-It is up to the user how to utilize this additional information.
-
-\subsection{Classification}
-
-	Predicting a class associated with an image requires feeding the visual words histograms into a classifiers.
-A simple example of a classifier would be a K-nearest neighbours algorithm.
-In this setting every histogram is treated as a point in a multi-dimensional space.
-A class of an image is determined by classes of the nearest neighbours.
-Manifold of distinct metrics can be used: L1, L2  and others.
-The number of nearest neighbours (K) has to be determined.
-More advanced classifiers can be divided into the two main classes: generative models and discriminative models.
-
-	Construction of a discriminative model requires a supervised learning approach.
-It can be seen as a learning by example method.
-The general aim is to compute an approximate mapping between representations of examples (the train set).
-The purpouse of this mapping is correct (e.g.
-with some success rate) prediction of labels for inputs which label is unknown.
-The model computation stage is called \emph{training} of a model.
-After the model has been trained previously unseen examples can be fed into the classifier.
-The clasifier calculates some similarity measure between the unlabled input example and all the modeled classes.
-The resulting label is a label of which class had the highest score in terms of the similarity measure.
-The KNN is an example of a discriminative model.
-The most widely used discriminative classificator is a Support Vector Machine.
-
-	The generative models are usually Baysian text-based models.
-Many of them heavily depends on the Probabilistic Graphical Models concept.
-They include \emph{Latent Semantic Analysis} with \emph{probabilistic Latent Semantic Analysis}, \emph{Latent Dirichlet Allocation} and others.
-These models allow discovery of topic distrubution in documents.
-In the image domain an image can be though of as a document and an object category as a topic.
-Under this conditions an image (and its category) can be modeled as a mixture of topics.
-Learning consists of finding topics distributions for each specific category.
+\include{streszczenie}
+\include{abstract}
+\include{introduction} %aka motivation
+\include{bow}
+\include{libs}
+\include{datasets}
+\include{architecture}
+\include{setup}
+\include{experiments}
+\include{conclusion}
 

### 2013-10-11 Disseration/bow.tex
added figures, class diagrams

\section{Bag of Words image representation}

  As portrayed by Tsai in \cite{tsai2012bag} the Bag of Words (BoW) model has originated from the text retrieval domain. The model enables text document representation in a form of a vector. Suppose we have a corpus of documents. A dictionary over the corpus is a set of words such that every word from the corpus can be matched to exactly one word in the dictionary and every two words in a dictionary are different. Given a dictionary, a histogram of incidence of words can be build. This histogram has the following form: for every entry in the dictionary there is a number of words in the document matching the entry. Such an approach obliterates any grammatical dependencies in order to retain only statistical information associated with words. It is believed that the words' frequencies encode enough data for further processing. The following questions emerge:

  \begin{itemize}
    \item How does this apply to the area of computer vision?
    \item How can one convert an image to a text document? 
  \end{itemize}

  In order to answer the first question one has to consider what digital images are --- they are nothing but strings of binary code. Translated to i.e. RGB colour space they can be displayed and understood by humans, but there are no direct methods that would let computers `understand' what does a picture contain. Suppose two images of the same object were taken from different viewing angles. Being easy for a human,  it is impossible for any computer to compare those two pictures (or objects they depict) in any simple manner. This example shows a need for an intermediate representation that would enable image processing. Advanced algorithms for characteristic region detection and description exist (SIFT, SURF, FAST among many others). Even then, however, the resulting representation is a low level one. Consider a scenario in which a robot is to adjust its behaviour depending on where it currently is (a type of a location, i.e. house, factory, mine). It order to define required adjustments a programmer would have to encode the low level representation of possibly many robot's destination environments. It is a variation of a problem described by Tsai \cite{tsai2012bag}, with respect to the Content Based Image Retrieval (\textit{CBIR}), as \emph{``the gap between the extracted and indexed low-level features by computers and the high-level concepts (or semantics) of user’s queries''}. Suppose a text document can be created from an image. This document can be translated into a BoW model. Since it preserves semantic information that can be extracted an impact of the semantic gap can be reduced.

  As for the second question, there is a quite well established pipeline that enables creation of text documents from images. The steps of the BoW methodology are as follows:
  \begin{itemize}
   \item Keypoint detection --- keypoints are local interest points or regions. They are usually computed in such a way so as to provide scale and location invariance. Rigid transformation and illumination invariance would be desired but it is somewhat harder to achieve
   \item Keypoint description --- each keypoint have to be described in a manner that distinguishes the particular keypoint in some way.
   \item Vector quantization --- clustering algorithms are used to find regions in the high dimensional space of keypoint descriptors. When clusters are found, each described keypoint can be assigned to a corresponding cluster. Then, an image can be represented by the numbers of clusters, to which the image's keypoints were assigned. The numbers themselves are called \emph{`visual words'}.
  \end{itemize}

\section{BoW in Computer Vision}

  The Bag of Words image representation has been extensively used in the areas of scene \cite{csurka2004visual,fei2005bayesian, tsai2012bag} and object categorisation \cite{zhangcategory} as well as CBIR \cite{li2010investigating,toldo2009bag} yielding state-of-the-art results. Advantages of this model are simplicity, computational efficiency and at least partial invariance to affine transformation, occlusion and lighting conditions.

  The Bag of Words is a type of intermediate representation. Therefore it is not sufficient to compute a BoW model of an image in order to predict its category. Additional operations are essential if the model is to be used in one of the enumerated fields.

  \subsection{Content Based Image Retrieval}

  One of the most notorious use-case of \emph{CBIR} is to search a database in order to find an object fulfilling certain conditions. As \cite{toldo2009bag} outlines, several criteria have to be met for the task to be performed efficiently. Firstly, all entries should be indexed in a concise way. Secondly, some (dis)similarity measure should be provided. Finally, an efficient search algorithm should be available.

  There are numerous methods suitable for computation of objects' signatures. Many of them can be used in the indexing step. All the methods were divided into three general categories in \cite{toldo2009bag}, specifically: feature based methods, graph based methods and other methods.

  Feature based methods can be either global or local. The former takes the form of a single vector or a point in a $d$ dimensional space --- the similarity measure being a point-wise distance in that space. The latter gives multiple such points for each object, rendering the computation of a similarity measure slightly more complicated. The global features takes forms of the models' volume, their mass or mass distributions. Others might incorporate the global features' distribution --- one conceivable approach would be to compute global features' distributions and summarise them into a histogram. These features have the advantage of being easy to compute and straightforward to implement. However, they are insensitive to any local shape variations, thus being ill-suited for detailed comparisons. On the other hand, they might be exploited in the preprocessing of the data with more sophisticated methods being used afterwards. Partial matching is not possible, since the global features do not encode any relations between parts of the objects.

  As for the local features, \cite{toldo2009bag} discusses only features describing neighbourhood of the points on boundaries of objects. Any settings that does not match this criteria are neglected. Moreover, the authors state that the local feature based methods are inefficient and indexing is rather complex. A Bag of Words based approach, described in \cite{li2010investigating} has no such drawbacks.

	Bag of Words techniques can be regarded as feature distributions, even though they are local feature based --- the local features being visual words. When all the image's visual words are summarised into a histogram a distribution is created. Being similar to a point in a multi-dimensional space, it is similar to a global feature. Consequently, similar methods apply, with the distinction being that the histogram is rather a vector then a point. Thus metrics well-suited to vector comparison, such as a cosine distance, can be used.

  \subsection{Scene Categorisation}

  One of the first works employing the BoW for the purpose of scene categorisation is \cite{csurka2004visual}. The authors suggested a general framework. What is more, algorithms performing each main pipeline's step were proposed and evaluated as well as a codebook construction method was developed. The \emph{Harris Affine Detector} was used for feature extraction and the \emph{SIFT} for the feature description step. The visual vocabulary has been generated by clustering only a limited number of keypoints from each category. After summarising every image in the training set with a histogram of visual words, supervised learning was used to train two classifiers: Na\`ive Bayes and a Support Vector Machine. As expected the Na\`ive Bayes resulted in a lower accuracy than SVM (72 vs. 85\% on 7 categories). An analysis on the number of centroids in the clustering step depicts that the greater the size of the visual vocabulary the greater the accuracy.

  Li \emph{et al} further refined the above approach by examining several keypoint detectors and descriptors. The main contribution of their work is, however, the development of a genuine classification algorithm based on a probabilistic graphical model. Accuracy of 76\% on a large 13 category dataset was achieved.

  \subsection{Object Categorisation}

  In many cases object categorisation might be addressed as a scene categorisation problem. There are following differences: (1) an object should be localised on an image (i.e. its bounding box has to be found) and (2) in object categorisation task information about a scene type might be used. The second case is symmetric, for in the scene categorisation problem information about objects present in the scene can be utilised as well. Having said that, it is possible to consider an object categorisation problem where images of singled-out objects are provided --- e.g. a single object covers the majority of an image's area. Such an approach was exploited in a recent work by Zhang \emph{et al} \cite{zhangcategory}.

\section{BoW based classification}

	The Bag of Words intermediate image representation provides a concise way of summarising images. It is invariant to affine transformations, partial occlusion and, in some extent, to changing lighting conditions. What is more, it is easy to implement and computationally efficient. The efficiency can be enhanced even further with gpu based implementations as shown in \cite{van2011empowering}. In order to incorporate BoW into an object classification framework one has to feed the resulting histograms into a classification algorithms. Either generative or discriminative methods can be used. Below the main steps of BoW classification processing pipeline will be discussed.

\subsection{Detection}

	Characteristic point detection is the first step in any Bag of Words framework. Numerous detection methods have been developed, but choosing the right one for the particular case might prove tricky. A good overview of various mechanisms is available in \cite{tsai2012bag}. The most common detectors make use of a Harris corner detector or image's first or second derivatives. A technique taking advantage of the Harris corner detector is for example a Harris-Laplace detector --- the Harris function is scale adapted and its outcome is a subject to a Laplacian-of-Gaussian operator, which selects relevant points in the scale space. Images' regions' 2\textsuperscript{nd} derivatives --- namely the regions' Hessians --- can be combined with a LoG operator. This combination allows selection of points significant in the two spaces: the scale space and the Hessian's determinant space. The latter entails the speed at which pixel intensities change in the neighbourhood of a point.

	A number of more complicated recipes for salient region localisation have been developed and implemented. These include Scale Invariant Feature Transform \cite{sift_keypoint}, SUSAN \cite{susan_keypoint} and Intrinistic Shape Signatures \cite{iss_keypoint}. The majority of keypoint detection formulas is being developed for the 2D domain. A number of them have been adapted to 3D, however. A comparative evaluation of detection algorithms available in PCL can be find in \cite{pcl_keypoint_comparision}. Another comprehensive study is \cite{3d_keypoint_eval}.

	All these formulas, called sparse feature detectors, resort to selection of maxima in specific state spaces. An entirely different scheme is to use a dense feature detector. This particular form requires users to specify a uniformly sampled grid from which points are taken. Dense detectors have an advantage of taking points from slow changing regions. A sparse detector might be unable to summarise a slow changing region such as clouds, sky or ocean. Li \emph{et al} showed that dense detectors outperforms the sparse ones.

\subsection{Description}

	Computing localisation of a salient point is not enough. If a keypoint is to be affine transform invariant, it has to be described in more general terms. Such description, usually in a form of coordinates in a multi-dimensional space, is provided by specialised algorithms. 128-dimensional SIFT \cite{sift_features} is a 3D histogram of gradient locations and orientations. It is the most often extracted as well as one of the most effective descriptors \cite{tsai2012bag}. Other methods include various colour descriptors, binary descriptors such as 512-dimensional GIST \cite{ponce2011cv}. There are techniques designed for 3D exclusively. Among them one can find Persistent Point Feature Histogram \cite{pfh_rusu2008} and its faster alternative Fast Point Feature Histogram \cite{fpfh_rusu2009}, both implemented in PCL.

\subsection{Vector Quantization}

	The final step of extracting Bag of Words features is vector quantization. Generally clustering with the kMeans algorithm is used \cite{tsai2012bag}. The kMeans algorithm was developed in the 50's and a variety of modifications have been developed since \cite{kmeans_jain2010data}. Some of them are: faster than the original \emph{approximate kmeans}, \emph{hierarchical kmeans}, which automatically chooses the resulting number of clusters and a  \emph{soft kmeans} --- a variation of the algorithm that allows a fuzzy alignment (\textit{i.e.} each point can belong to several clusters with different weights. The soft kMeans is a compromise between kMeans' (relative to GMM, discussed below) low computational cost and GMM's precision. The number of resulting visual words depends on the number of clusters.

	In order to improve performance multitude of pre- or postprocessing techniques can be resorted to. A weighting scheme such as Term Frequency (TF) or Term Frequency - Inverse Document Frequency (TF-IDF) can be used. Spatial information might be encoded so as to capture spatial relations of the extracted features.

	It has been shown that the vector quantization step is the computationally most expensive step in any Bag of Words framework. Fortunately, the majority of the cost is associated with the training part of the computation. When all the models are trained the only operation required in case of vector quantization is keypoint -- visual vocabulary matching. Even so, diverse algorithms have been used in order to minimise the impact of clustering on the overall efficiency. The \emph{approximate kMeans} is faster but insufficiently so as to solve the problem. Random Forests algorithm is considerably less expensive and can provide better Mean Average Precision (MAP) score.

	Quite a different approach is using a Gaussian Mixture Model (GMM) algorithm. It is many times more expensive than kMeans, the tradeoff being higher precision. The GMM finds not only clusters' centroids but the Gaussian distributions of points in each cluster. Therefore, in the keypoint-centroid matching stage a set of probabilities is obtained instead of a simple single-cluster assignment. These probabilities encode likelihoods of the keypoint belonging to each cluster. It is up to the user how to utilise this additional information.

\subsection{Classification}

	Predicting a class associated with an image requires feeding the visual words histograms into a classifiers. A simple example of a classifier would be a K-nearest neighbours algorithm. In this setting every histogram is treated as a point in a multi-dimensional space. A class of an image is determined by classes of the nearest neighbours. Manifold of distinct metrics can be used: L1, L2  and others. The number of nearest neighbours (K) has to be determined. More advanced classifiers can be divided into the two main classes: generative models and discriminative models.

	Construction of a discriminative model requires a supervised learning approach. It can be seen as a learning by example method. The general aim is to compute an approximate mapping between representations of examples (the train set). The purpose of this mapping is correct (e.g. with some success rate) prediction of labels for inputs which label is unknown. The model computation stage is called \emph{training} of a model. After the model has been trained previously unseen examples can be fed into the classifier. The classifier calculates some similarity measure between the unlabelled input example and all the modeled classes. The resulting label is a label of which class had the highest score in terms of the similarity measure. The KNN is an example of a discriminative model. The most widely used discriminative classificator is a Support Vector Machine.

	The generative models are usually Bayesian text-based models. Many of them heavily depends on the Probabilistic Graphical Models concept. They include \emph{Latent Semantic Analysis} with \emph{probabilistic Latent Semantic Analysis}, \emph{Latent Dirichlet Allocation} and others. These models allow discovery of topic distribution in documents. In the image domain an image can be though of as a document and an object category as a topic. Under this conditions an image (and its category) can be modeled as a mixture of topics. Learning consists of finding topics distributions for each specific category.

### 2013-10-11 src/Cluster/KMeansCluster.cpp

@@ -117,6 +117,7 @@ const std::vector<int> KMeansCluster::cluster(const cv::Mat &descriptors) {
 
 const std::vector<std::vector<int>> KMeansCluster::cluster(const std::vector<cv::Mat> &descriptors) {
 
+	INFO(logger, "Generating word descriptions");
 	std::vector<std::vector<int>> matched;
 	matched.reserve(descriptors.size());
 

### 2013-10-11 src/Common/Tagger3D.cpp

@@ -102,7 +102,7 @@ void Tagger3D::train() {
 	prepareCluster(descriptors);
 
 
-	INFO(logger, "Generating word descriptions");
+	INFO(logger, "Generating text descriptions");
 	wordDescriptors = cluster->cluster(descriptors);
 
 	INFO(logger, "Training classificator");
@@ -147,6 +147,7 @@ int Tagger3D::predict(const std::string& rgbPath,
 }
 
 int Tagger3D::run() {
+	INFO(logger, "Tagger3D running")
 
 	std::string modeStr = getParam<std::string>( mode );
 	int m = -1;
@@ -176,6 +177,9 @@ int Tagger3D::run() {
 
 void Tagger3D::saveDescriptors(const std::vector<cv::Mat>& descriptors,
 		const std::string& path) {
+
+	INFO(logger, "Saving descriptors of " << descriptors.size() << " point clouds");
+	INFO(logger, "Descriptors' dimensionality: " << descriptors[0].cols);
 
 	std::ofstream file(path + info, std::ios::binary);
 	if(!file.is_open()) {
@@ -211,10 +215,12 @@ void Tagger3D::saveDescriptors(const std::vector<cv::Mat>& descriptors,
 		}
 	}
 	file.close();
+	INFO(logger, "Descriptors have been saved");
 }
 
 std::vector<cv::Mat> Tagger3D::loadDescriptors(const std::string& path) {
 
+	INFO(logger, "Loading descriptors");
 	std::ifstream file(path + info, std::ios::binary);
 	if(!file.is_open()) {
 		std::runtime_error e("Couldn't open the file: " + path + info);
@@ -257,6 +263,8 @@ std::vector<cv::Mat> Tagger3D::loadDescriptors(const std::string& path) {
 		descriptors.push_back(mat.clone());
 	}
 
+	INFO(logger, "Loaded descriptors of " << descriptors.size() << " point clouds");
+	INFO(logger, "Descriptors' dimensionality: " << descriptors[0].cols);
 	return descriptors;
 }
 
@@ -276,8 +284,7 @@ std::vector<cv::Mat> Tagger3D::prepareDescriptors(const std::string &path) {
 }
 
 std::vector<cv::Mat> Tagger3D::computeDescriptors() {
-
-	INFO(logger, "computeDescriptors");
+	INFO(logger, "Computing descriptors");
 
 	std::vector<cv::Mat> descriptors;
 
[…]

### 2013-10-11 src/Config/Config.cpp

@@ -89,11 +89,19 @@ std::map<std::string, std::string> Config::getConfigMap() {
 	genericOps.add_options()
 			(versionTmp.c_str(), "Print version")
 			(helpTmp.c_str(), "Produce help message")
+			("readerType", po::value<std::string>(), "0 - rangeImg 1 - PCD")
+			("detectorType", po::value<std::string>(), "0 - SIFT 1 - ISS3D")
+			("descType", po::value<std::string>(), "0 - PFH 1 -FPFH")
 			;
 
 	/**
 	 * 	Options allowed on a command line and in a config file.
 	 */
+	po::options_description readerOps("Reader options");
+		readerOps.add_options()
+			("leafSize", po::value<std::string>(), "")
+			;
+
 	po::options_description detectorOps("Detector options");
 		detectorOps.add_options()
 			("gamma21", po::value<std::string>(), "")
@@ -143,7 +151,7 @@ std::map<std::string, std::string> Config::getConfigMap() {
 		(directory.c_str(), po::value<std::string>(), "Model directory")
 		(pictureTmp.c_str(), po::value<std::string>(), "Path to a picture")
 		;
-	configOps.add(descriptorOps).add(normalOps).add(detectorOps).add(clusterOps).add(predictorOps);
+	configOps.add(readerOps).add(descriptorOps).add(normalOps).add(detectorOps).add(clusterOps).add(predictorOps);
 
 	/**
 	 *	Hidden options. Allowed on a command line and in a config file.

### 2013-10-11 src/ImgReader/PcdReader.cpp

@@ -71,9 +71,20 @@ ColorVec PcdReader::readImgs() {
 ColorCloud::Ptr PcdReader::readImg() {
 
 	count++;
+	ColorCloud::Ptr ptr;
 	if(count < pcdVec.size())
-		return readImg( pcdVec[count++] );
-	return ColorCloud::Ptr(new ColorCloud());
+		ptr = readImg(pcdVec[count]);
+	else
+		ptr = ColorCloud::Ptr(new ColorCloud());
+
+	if(ptr->empty() && count < pcdVec.size()) {
+
+		std::runtime_error e("Corrupted point cloud #" + count);
+		ERROR(logger, "readImg: " << e.what());
+		throw e;
+	}
+
+	return ptr;
 }
 
 int PcdReader::readLabel() {

### 2013-10-11 src/Predictor/SVMPredictor.cpp

@@ -31,12 +31,8 @@ SVMPredictor::SVMPredictor(const std::map<std::string, std::string> &configMap) 
     storeHistogram = getParam<bool>(storeHistogramKey);
     dictionarySize = getParam<int>( dictionarySizeKey );
 
-    if (storeHistogram) {
-        if( remove( histogramPath.c_str() ) != 0 )   {
-        	ERROR(logger, "Cloudn't delete an old histogram file");
-        } else
-           INFO(logger, "Deleted histogram file");
-    }
+    if (storeHistogram)
+        remove( histogramPath.c_str());
 
     createSVM();
     maxValues = Mat::zeros(1, dictionarySize, svmMatType);
@@ -59,7 +55,7 @@ void SVMPredictor::createSVM() {
 void SVMPredictor::addImage(const std::vector<int> &vec, const int &label) {
 
     TRACE(logger, "addImage: adding image with label: " << label);
-    labelsMat.push_back(label);
+    labels.push_back(label);
 
 
     //make histogram
@@ -99,7 +95,7 @@ const cv::Mat SVMPredictor::computeMaxValues(const Mat& mat) const{
 }
 
 void SVMPredictor::train() {
-
+	INFO(logger, "Training SVM predictor");
 	TRACE(logger, "SVM train: Starting");
 	if( imgCount == 0 ) {
 
@@ -109,18 +105,18 @@ void SVMPredictor::train() {
 	cv::Mat normValues = computeMaxValues(DataMat);
     normalizeData(DataMat, normValues);
 
-    SVM.train(DataMat, labelsMat, Mat(), Mat(), params);
+    SVM.train(DataMat, cv::Mat(1, labels.size(), CV_32SC1, &labels[0]), Mat(), Mat(), params);
     SVM.save(svmPath.c_str());
     saveNormValues(normValues);
 
     INFO(logger, "SVM model saved: " + svmPath);
     DataMat.release();
-    labelsMat.release();
+    labels.clear();
 }
 
 
 std::vector<int> SVMPredictor::predict() {
-
+	INFO(logger, "Classifying")
 	TRACE(logger, "predict: Starting");
 	if( imgCount == 0 ) {
 
@@ -134,15 +130,10 @@ std::vector<int> SVMPredictor::predict() {
     for(int row = 0; row < DataMat.rows; ++row)
         predictions.push_back(SVM.predict(DataMat.row(row)));
 
[…]

### 2013-10-12 Disseration/abstract.tex
pfhrgb, changed layout of the diss

\begin{center}
\begin{LARGE}\textbf{Abstract}\end{LARGE}
\end{center}

\vspace{1.0cm}

Properties of special generalized functions and short-range selectors which are indispensable in the Shina Tan description of interacting Fermi systems [Annals of Physics 323, 2952 (2008)] are analyzed in details. Also all details of the proof of the Shina Tan energy theorem and properties of the contact are presented. The manuscript should be interesting for researchers who want to understand all elements of the Shina Tan extraordinary work.

### 2013-10-12 Disseration/article.tex
pfhrgb, changed layout of the diss

@@
-\documentclass[a4paper,12pt]{article}
+\documentclass[12pt]{report}
 \usepackage[utf8]{inputenc}
+%\usepackage{polski}
 \usepackage[T1]{fontenc}
-\usepackage[top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
+\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
 \usepackage{cite}
+\usepackage{graphicx}
+%\usepackage[polish]{babel}
+\usepackage{color}
 
@@
 
-%opening
-\title{Object Categorization based on RGBD data}
-\author{Adam Kosiorek}
 \bibliographystyle{abbrv}
 \begin{document}
+\pagestyle{empty}
+\color{white} . \color{black}
+\vspace{0.2cm}
 
-\maketitle
+\begin{center}
+\begin{Huge}Warsaw University of Technology
+\end{Huge}
+\end{center}
+
+\begin{center}
+\begin{LARGE}Faculty of Mechatronics
+
+\vspace{0.5cm}
+Institute of Automation and Robotics
+\vspace{0.5cm}
+\end{LARGE}
+\end{center}
+\begin{center}\includegraphics[width=5cm,angle=0]{figs/logopw}\end{center}
+
+\vspace{1.0cm}
+
+\begin{center}
+\begin{LARGE}\textbf{Adam Kosiorek}\end{LARGE}
+\end{center}
+
+\vspace{0.5cm}
+
+\begin{center}
+\begin{Huge}\textbf{3D Object Classification based on RGBD images}
+\vspace{0.5cm}
+\end{Huge}
+\end{center}
+
+\vspace{0.5cm}
+
+\begin{center}
+\begin{Large}bachelor thesis written under supervision of\end{Large}
+
+\vspace{0.2cm}
+
+\begin{LARGE}prof. dr. hab. Barbara Siemiątkowska\end{LARGE}
+\end{center}
+
+\vspace{1.8cm}
+
+\begin{center}
+\begin{Large}Warsaw 2014\end{Large}
+\end{center}
+
+\pagebreak
+
+\color{white} . \color{black}
+\vspace{0.2cm}
+\vspace{1.5cm}
+\pagebreak
+\pagestyle{plain}
 
@@
 \include{abstract}
+
+\tableofcontents
+
+\chapter{Introduction}
+\addcontentsline{toc}{chapter}{Introduction}
 \include{introduction} %aka motivation
@@
 \include{datasets}
+
+\chapter{Design}
+\addcontentsline{toc}{chapter}{Design}
 \include{architecture}
 \include{setup}
+
+\chapter{Experiments and results}
+\addcontentsline{toc}{chapter}{Experiments and results}
 \include{experiments}
 \include{conclusion}
+
+\listoffigures
+\listoftables
+
+\cite{OpenCV}
 

### 2013-10-12 Disseration/experiments.tex
pfhrgb, changed layout of the diss

\section{Experiments}

	The Bag of Words classification pipeline consists of four previously discussed steps. For there are many different algorithms suitable for each part of the pipeline, an extensive research is required in order to discover the best possible combination in a particular setting. The number of options grows combinatorial with number of candidates for each processing step. Moreover, many algorithms have different parameters that should be adjusted for the given conditions. Evaluation of every possibility is unfeasible due to the lack of time and computational power required. Therefore it was chosen to evaluate algorithms with their default parametrs under fixed conditions. Only the winning methods qualify for the parameter tuning.

\subsection{Detectors}

	ISS3D is generally better than SIFT

\subsection{Descriptors}

	FPFH is faster than both PFH and PFHRGB. PFH does not give any advantages over FPFH. PFHRGB delievers considerably higher accuracy.

\subsection{Codebook}

Only kmeans tested with varying numbers of clusters i.e. vocabulary size

\subsection{B3DO}

\subsection{tokyo}

### 2013-10-12 src/Common/Tagger3D.cpp

@@ -14,6 +14,7 @@
 #include "../Detector/Iss3dDetector.h"
 #include "../Descriptor/PFHDescriptor.h"
 #include "../Descriptor/FPFHDescriptor.h"
+#include "../Descriptor/PFHRGBDescriptor.h"
 #include "../Cluster/KMeansCluster.h"
 #include "../Predictor/SldaPredictor.h"
 #include "../Predictor/SVMPredictor.h"
@@ -51,6 +52,7 @@ Tagger3D::Tagger3D(const std::map<std::string, std::string> &configMap) : Proces
 	switch( getParam<int>( descType )) {
 	case PFH_DESC: descriptor = std::unique_ptr<Descriptor> (new PFHDescriptor(configMap)); break;
 	case FPFH_DESC: descriptor = std::unique_ptr<Descriptor> (new FPFHDescriptor(configMap)); break;
+	case PFHRGB_DESC: descriptor = std::unique_ptr<Descriptor> (new PFHRGBDescriptor(configMap)); break;
 	default:
 		std::runtime_error e("Invalid descriptor type");
 		ERROR(logger, e.what());

### 2013-10-12 src/Common/Tagger3D.h

@@ -136,7 +136,7 @@ private:
 	enum { TRAIN, TEST, DESC, CLUST, TRAIN_PRED, TEST_PRED, ALL };
 	enum { RANGEIMG_READER, PCD_READER };
 	enum { SIFT, ISS3D };
-	enum { PFH_DESC, FPFH_DESC };
+	enum { PFH_DESC, FPFH_DESC, PFHRGB_DESC };
 	enum { SLDA, SVM };
 
 

### 2013-10-12 src/Common/clouds.h

@@ -20,6 +20,7 @@ typedef pcl::PointCloud<pcl::PointWithScale> ScaleCloud;
 typedef pcl::PointCloud<pcl::PointXYZRGB> ColorCloud;
 typedef pcl::PointCloud<pcl::PFHSignature125> PfhCloud;
 typedef pcl::PointCloud<pcl::FPFHSignature33> FpfhCloud;
+typedef pcl::PointCloud<pcl::PFHRGBSignature250> PfhRgbCloud;
 typedef pcl::PointCloud<pcl::Normal> NormalCloud;
 
 /**
@@ -29,6 +30,7 @@ typedef std::vector<ScaleCloud::Ptr> ScaleVec;
 typedef std::vector<ColorCloud::Ptr> ColorVec;
 typedef std::vector<PfhCloud::Ptr> PfhVec;
 typedef std::vector<FpfhCloud::Ptr> FpfhVec;
+typedef std::vector<PfhRgbCloud::Ptr> PfhRgbVec;
 typedef std::vector<NormalCloud::Ptr> NormalVec;
 
 #endif /* CLOUDS_H_ */

### 2013-10-12 src/Config/Config.cpp

@@ -92,6 +92,7 @@ std::map<std::string, std::string> Config::getConfigMap() {
 			("readerType", po::value<std::string>(), "0 - rangeImg 1 - PCD")
 			("detectorType", po::value<std::string>(), "0 - SIFT 1 - ISS3D")
 			("descType", po::value<std::string>(), "0 - PFH 1 -FPFH")
+			("resize", po::value<std::string>(), "resize")
 			;
 
 	/**

### 2013-10-12 src/Descriptor/CloudParser/CloudParser.cpp

@@ -1,77 +1,0 @@
-/*
- * Tagger3D : CloudParser.cpp
- *
- *  Created on: 	31 lip 2013
- *  Author:			Adam Kosiorek
- *	Description:	
- */
-
-#include "CloudParser.h"
-
-namespace Tagger3D {
-
-CloudParser::CloudParser() {
-
-	DEBUG(logger, "Creating CloudParser")
-}
-
-CloudParser::~CloudParser() {
-
-	DEBUG(logger, "Deleting CloudParser");
-}
-
-cv::Mat CloudParser::parsePFH(const PfhCloud::Ptr &cloud) {
-
-	TRACE(logger, "parsePFH: parsing");
-	// TODO size does not equal the number of rows
-	int size = cloud->size();
-	cv::Mat mat( size, PFH125, CV_32FC1 );
-	for(int i = 0; i < size; i++) {
-		float* dPtr = mat.ptr<float>(i);
-		float* hPtr = cloud->points[i].histogram;
-		for(int j = 0; j < PFH125; j++)
-			dPtr[j] = hPtr[j];
-	}
-	TRACE(logger, "parse PFH: done parsing");
-	return mat;
-}
-
-std::vector<cv::Mat> CloudParser::parsePFH(const PfhVec &clouds) {
-
-	std::vector<cv::Mat> vec;
-	for(const auto &cloud : clouds) {
-
-		vec.push_back( parsePFH( cloud ) );
-	}
-	return vec;
-}
-
-cv::Mat CloudParser::parseFPFH(const FpfhCloud::Ptr &cloud) {
-
-	TRACE(logger, "parseFPFH: parsing");
-	// TODO size does not equal the number of rows
-	int size = cloud->size();
-	cv::Mat mat( size, FPFH33, CV_32FC1 );
-	for(int i = 0; i < size; i++) {
-		float* dPtr = mat.ptr<float>(i);
-		float* hPtr = cloud->points[i].histogram;
-		for(int j = 0; j < FPFH33; j++)
-			dPtr[j] = hPtr[j];
-	}
-	TRACE(logger, "parse FPFH: done parsing; mat size =  " << mat.size());
-	return mat;
-}
-
-std::vector<cv::Mat> CloudParser::parseFPFH(const FpfhVec &clouds) {
-
-	TRACE(logger, "parseFPFH: Starting batch processing");
-	std::vector<cv::Mat> vec;
-	for(const auto &cloud : clouds) {
-
[…]

### 2013-10-12 src/Descriptor/CloudParser/CloudParser.h

@@ -11,6 +11,7 @@
 
 #include "../../Common/logger.h"
 #include "../../Common/clouds.h"
+#include "PfhTraits.h"
 
 #include <pcl/point_cloud.h>
 #include <pcl/point_types.h>
@@ -26,20 +27,40 @@ public:
 	CloudParser();
 	virtual ~CloudParser();
 
-	cv::Mat parsePFH(const PfhCloud::Ptr &cloud);
-	std::vector<cv::Mat> parsePFH(const PfhVec &clouds);
+	template<typename T>
+	static cv::Mat parse(const typename T::Ptr &cloud);
 
-	cv::Mat parseFPFH(const FpfhCloud::Ptr &cloud);
-	std::vector<cv::Mat> parseFPFH(const FpfhVec &clouds);
+	template<typename T>
+	static std::vector<cv::Mat> parse(const std::vector<typename T::Ptr> &cloud);
 
-private:
-
-	static const int PFH125 = 125;
-	static const int FPFH33 = 33;
-
-	const std::string loggerName = "Main.CloudParser";
-	lgr::LoggerPtr logger = lgr::Logger::getLogger( loggerName );
 };
+
+template<typename T>
+inline cv::Mat CloudParser::parse(const typename T::Ptr& cloud) {
+
+	int size = cloud->size();
+	int matSize = PfhTraits<typename T::PointType>::size();
+	cv::Mat mat( size, matSize, CV_32FC1 );
+	for(int i = 0; i < size; i++) {
+		float* dPtr = mat.ptr<float>(i);
+		float* hPtr = cloud->points[i].histogram;
+		for(int j = 0; j < matSize; j++)
+			dPtr[j] = hPtr[j];
+	}
+	return mat;
+}
+
+template<typename T>
+inline std::vector<cv::Mat> CloudParser::parse(
+		const std::vector<typename T::Ptr>& clouds) {
+
+	std::vector<cv::Mat> vec;
+	for(const auto &cloud : clouds) {
+
+		vec.push_back( parse<T>( cloud ) );
+	}
+	return vec;
+}
 
 } /* namespace Tagger3D */
 #endif /* CLOUDPARSER_H_ */

### 2013-10-12 src/Descriptor/FPFHDescriptor.cpp

@@ -7,6 +7,7 @@
  */
 
 #include "FPFHDescriptor.h"
+#include "CloudParser/CloudParser.h"
 
 #include <assert.h>
 
@@ -17,7 +18,6 @@ FPFHDescriptor::FPFHDescriptor(const std::map<std::string, std::string> &configM
 	radiusSearch = getParam<float>( radiusSearchKey );
 	createFpfhDescriptor();
 	assert(descriptor != nullptr);
-	assert(parser != nullptr);
 }
 
 FPFHDescriptor::~FPFHDescriptor() {}
@@ -31,7 +31,6 @@ void FPFHDescriptor::createFpfhDescriptor() {
 	newDescriptor->setRadiusSearch( radiusSearch );
 
 	descriptor = std::move( newDescriptor );
-	parser = std::unique_ptr<CloudParser>( new CloudParser() );
 	TRACE(logger, "createFpfhDescriptor: Finished");
 }
 
@@ -46,7 +45,7 @@ cv::Mat FPFHDescriptor::describe(const ColorCloud::Ptr &cloud, const ScaleCloud:
 	descriptor->setInputCloud( keyCloudRgb );
 	descriptor->compute( *descriptors );
 	TRACE(logger, "describe fpfh: Finished; descriptors size = " << descriptors->size());
-	return parser->parseFPFH(descriptors);
+	return CloudParser::parse<FpfhCloud>(descriptors);
 }
 
 

### 2013-10-12 src/Descriptor/PFHDescriptor.cpp

@@ -7,7 +7,7 @@
  */
 
 #include "PFHDescriptor.h"
-
+#include "CloudParser/CloudParser.h"
 #include <pcl/search/kdtree.h>
 #include <assert.h>
 
@@ -18,7 +18,6 @@ PFHDescriptor::PFHDescriptor(const std::map<std::string, std::string> &configMap
 	radiusSearch = getParam<float>( radiusSearchKey );
 	createPfhDescriptor();
 	assert(descriptor != nullptr);
-	assert(parser != nullptr);
 }
 
 PFHDescriptor::~PFHDescriptor() {}
@@ -32,7 +31,6 @@ void PFHDescriptor::createPfhDescriptor() {
 	newDescriptor->setRadiusSearch( radiusSearch );
 
 	descriptor = std::move( newDescriptor );
-	parser = std::unique_ptr<CloudParser>( new CloudParser() );
 	TRACE(logger, "createPfhDescriptor: Finished");
 }
 
@@ -47,7 +45,7 @@ cv::Mat PFHDescriptor::describe(const ColorCloud::Ptr &cloud, const ScaleCloud::
 	descriptor->setInputCloud( keyCloudRgb );
 	descriptor->compute( *descriptors );
 	TRACE(logger, "describe: Finished");
-	return parser->parsePFH(descriptors);
+	return CloudParser::parse<PfhCloud>(descriptors);
 }
 
 

### 2013-10-12 src/Descriptor/PFHRGBDescriptor.cpp

@@ -1,0 +1,50 @@
+/*
+ * PFHRGBDescriptor.cpp
+ *
+ *   Created on: 11 paź 2013
+ *       Author: Adam Kosiorek
+ *	Description:
+ */
+
+#include "PFHRGBDescriptor.h"
+#include "CloudParser/CloudParser.h"
+
+namespace Tagger3D {
+
+PFHRGBDescriptor::PFHRGBDescriptor(const std::map<std::string, std::string> &configMap) : Descriptor(configMap) {
+
+	radiusSearch = getParam<float>( radiusSearchKey );
+	createDescriptor();
+	assert(descriptor != nullptr);
+}
+
+PFHRGBDescriptor::~PFHRGBDescriptor() {}
+
+void PFHRGBDescriptor::createDescriptor() {
+
+	TRACE(logger, "createDescriptor: Starting");
+	decltype(descriptor) newDescriptor( new descriptorType() );
+	pcl::search::KdTree<pcl::PointXYZRGB>::Ptr kdTree( new pcl::search::KdTree<pcl::PointXYZRGB>() );
+	newDescriptor->setSearchMethod( kdTree );
+	newDescriptor->setRadiusSearch( radiusSearch );
+
+	descriptor = std::move( newDescriptor );
+	TRACE(logger, "createDescriptor: Finished");
+}
+
+cv::Mat PFHRGBDescriptor::describe(const ColorCloud::Ptr &cloud, const ScaleCloud::Ptr &keyCloud, const NormalCloud::Ptr &normalCloud) {
+
+	TRACE(logger, "describe PFHRGB: Starting");
+	PfhRgbCloud::Ptr descriptors( new PfhRgbCloud() );
+	ColorCloud::Ptr keyCloudRgb( new ColorCloud() );
+	pcl::copyPointCloud( *keyCloud, *keyCloudRgb);
+	descriptor->setInputNormals( normalCloud );
+	descriptor->setSearchSurface( cloud );
+	descriptor->setInputCloud( keyCloudRgb );
+	descriptor->compute( *descriptors );
+	TRACE(logger, "describe PFHRGB: Finished; descriptors size = " << descriptors->size());
+	return CloudParser::parse<PfhRgbCloud>(descriptors);
+}
+
+
+} /* namespace Tagger3D */

### 2013-10-12 src/Descriptor/PFHRGBDescriptor.h

@@ -1,0 +1,45 @@
+/*
+ * PFHRGBDescriptor.h
+ *
+ *   Created on: 11 paź 2013
+ *       Author: Adam Kosiorek
+ *	Description:
+ */
+
+#ifndef PFHRGBDESCRIPTOR_H_
+#define PFHRGBDESCRIPTOR_H_
+
+#include "Descriptor.h"
+
+#include <pcl/features/pfhrgb.h>
+
+namespace Tagger3D {
+
+/*
+ *
+ */
+class PFHRGBDescriptor: public Descriptor {
+	/**
+	 *
+	 */
+public:
+	PFHRGBDescriptor(const std::map<std::string, std::string> &configM);
+	virtual ~PFHRGBDescriptor();
+
+	cv::Mat describe(const ColorCloud::Ptr &cloud, const ScaleCloud::Ptr &keyCloud, const NormalCloud::Ptr &normalCloud );
+
+private:
+	PFHRGBDescriptor();
+	void createDescriptor();
+	typedef pcl::PFHRGBEstimation<pcl::PointXYZRGB, pcl::Normal, pcl::PFHRGBSignature250> descriptorType;
+	std::unique_ptr<descriptorType> descriptor;
+
+	//	Config parameters
+	float radiusSearch;
+
+	//	Config keys
+	const std::string radiusSearchKey = moduleName + "radiusSearch";
+};
+
+} /* namespace Tagger3D */
+#endif /* PFHRGBDESCRIPTOR_H_ */

### 2013-10-12 src/ImgReader/PcdReader.cpp

@@ -34,11 +34,8 @@ ColorCloud::Ptr PcdReader::readImg(const std::string& pcdPath) {
 	ColorCloud::Ptr cloud(new ColorCloud());
 	pcl::io::loadPCDFile(pcdPath, *cloud);
 
-	if(leaf != 0) {
-
-		voxelGrid->setInputCloud(cloud);
-		voxelGrid->filter(*cloud);
-	}
+//	for(const auto& point : cloud->points)
+//		std::cout << "x: " << point.x << " y: " << point.y << " z: " << point.z << std::endl;
 
 //	pcl::visualization::CloudViewer viewer ("Simple Cloud Viewer");
 //	viewer.showCloud (cloud);
@@ -46,6 +43,19 @@ ColorCloud::Ptr PcdReader::readImg(const std::string& pcdPath) {
 //	{
 //	}
 
+	if(leaf != 0) {
+
+		voxelGrid->setInputCloud(cloud);
+		voxelGrid->filter(*cloud);
+	}
+
+//	for(const auto& point : cloud->points)
+//		std::cout << "x: " << point.x << " y: " << point.y << " z: " << point.z << std::endl;
+
+
+
+
+	//std::terminate();
 	DEBUG(logger, "Cloud size = " << cloud->size());
 	return cloud;
 }

### 2013-10-12 src/ImgReader/RangeImgReader.cpp

@@ -33,6 +33,11 @@ ColorCloud::Ptr RangeImgReader::matToCloud(const cv::Mat &colorImg, const cv::Ma
 	int height = depthImg.rows;
 	int width = depthImg.cols;
 
+	int height2 = height/2;
+	int width2 = width/2;
+	float factorX = factorX0 / width;
+	float factorY = factorY0 / height;
+
 	if( height != colorImg.rows || width != colorImg.cols ) {
 
 		std::runtime_error e("Images have different dimensions");
@@ -47,24 +52,28 @@ ColorCloud::Ptr RangeImgReader::matToCloud(const cv::Mat &colorImg, const cv::Ma
 	cloud->is_dense = false;
 
 	pcl::PointXYZRGB newPoint;
-	for (int i = 0; i < height; i++) {
+	for (int y = 0; y < height; y++) {
 
 		// For the sake of simplicity
 		typedef ushort MatType;
-		const MatType *depthPtr = depthImg.ptr<MatType>(i);
-		const cv::Vec3b *colorPtr = colorImg.ptr<cv::Vec3b>(i);
+		const MatType *depthPtr = depthImg.ptr<MatType>(y);
+		const cv::Vec3b *colorPtr = colorImg.ptr<cv::Vec3b>(y);
 
-		for (int j = 0; j < width; j++) {
-			MatType depth = depthPtr[j];
+		for (int x = 0; x < width; x++) {
+			MatType depth = depthPtr[x];
 //			std::cout << depth << " ";
 
 			if ( depth == depth) {            // if depthValue is not NaN
 
+//				depth /= 10;
 				newPoint.z = MatType(depth * depthScaleFactor);
-				newPoint.x = j;
-				newPoint.y = i;
-
-				cv::Vec3b vec = colorPtr[j];
+				newPoint.x = x;
+				newPoint.y = y;
+//				newPoint.z = depth;
+//				newPoint.x = (x - width2) * factorX * depth;
+//				newPoint.y = (y - height2) * factorY * depth;
+//				std::cout << "x0: " << x << " y0: " << y << " z: " << depth << " x: " << newPoint.x << " y: " << newPoint.y << std::endl;
+				cv::Vec3b vec = colorPtr[x];
 				newPoint.r = vec[2];
 				newPoint.g = vec[1];
 				newPoint.b = vec[0];

### 2013-10-12 src/ImgReader/RangeImgReader.h

@@ -52,6 +52,11 @@ private:
 
 
 	ColorCloud::Ptr matToCloud(const cv::Mat &colorImg, const cv::Mat &depthImg);
+
+	const float factorX0 =  320.0f * 3.501e-3f;
+	const float factorY0 = 240.0f * 3.501e-3f;
+
+
 };
 
 } /* namespace Tagger3D */

### 2013-10-12 src/Predictor/SVMPredictor.cpp

@@ -202,7 +202,7 @@ cv::Mat SVMPredictor::confusionMatrix(const std::vector<int> &labels, const std:
 	cv::Mat average(1, classes, CV_32FC1);
 	float avg = 0;
 	for(int i = 0 ; i < classes; i++) {
-		average.at<float>(0, i) = float(confusionMatrix.at<uchar>(i, i)) / classCount.at<int>(0, i);
+		average.at<float>(0, i) = float(confusionMatrix.at<uchar>(i, i)) / classCount.at<int>(0, i) * 100;
 		avg += confusionMatrix.at<uchar>(i, i);
 	}
 	avg /= size;
@@ -211,7 +211,7 @@ cv::Mat SVMPredictor::confusionMatrix(const std::vector<int> &labels, const std:
 	std::cout << "Entries per class: " << std::endl << classCount << std::endl;
 	std::cout << "Confusion Matrix:" << std::endl << confusionMatrix << std::endl;
 	std::cout << "Averages: " << std::endl << average << std::endl;
-	std::cout << "Average: " << avg << std::endl;
+	std::cout << "Average: " << avg * 100 << std::endl;
 
 
 }

### 2013-10-16 Disseration/abstract.tex
latest changes

@@
+\begin{center}
+\begin{LARGE}\textbf{Streszczenie}\end{LARGE}
+\end{center}
+
+\vspace{1.0cm}
+
+	W pracy przedstawiono podejście Bag of Words do klasyfikacji obiektów na podstawie trójwymiarowych chmur punktów.
+Wykorzystano metodę uczenia nadzorowanego, dzięki czemu można rozpoznawać dowolne kategorie obiektów.
+Opisano metodologię BoW, jej znaczenie w wizjii komputerowej, a także algorytmy znajdujące zastosowanie w poszczególnych stadiach procesu.
+Następnie przedstawiono problem klasyfikacji.
+Okrślono wymaganą funkcjonalność, zaprojektowano konfigurowalną i łatwo rozszerzalną aplikację oraz zaimplementowano ją w C++.
+Zbadano algorytmy pod kątem przydatności do BoW oraz sprawdzono skuteczność aplikacji na dwóch powszechnie uznawanych zbiorach danych.
+
+\vspace{3.0cm}
+
 \begin{center}
@@
 
-Properties of special generalized functions and short-range selectors which are indispensable in the Shina Tan description of interacting Fermi systems [Annals of Physics 323, 2952 (2008)] are analyzed in details.
-Also all details of the proof of the Shina Tan energy theorem and properties of the contact are presented.
-The manuscript should be interesting for researchers who want to understand all elements of the Shina Tan extraordinary work.
+	This paper introduces a Bag of Words semantic object classification framework based on three dimensional point clouds.
+The framework uses machine learning algorithms and a learning by example approach, thus an arbitrary set of categories can be used.
+Basic concepts of BoW and its role in computer vision are introduced.
+Then, the most popular algorithms for different steps of BoW are described and a problem of classification is explained.
+After a requirement analysis was performed a configurable and extensible application was designed and implemented in C++.
+Finally, algorithms for different steps of BoW classification are evaluated and results on two benchmark datasets are discussed.

### 2013-10-16 Disseration/architecture.tex
latest changes

\chapter{Design}
\addcontentsline{toc}{chapter}{Design}

\section{Software Functionality and Architecture}
	The programme resulting from this work is called ``Tagger3D'', for it's purpose is to tag an RGBD image of an object with a category label. The Bag of Words classification pipeline consists of four main parts discussed previously. In order to determine the best combination of algorithms for any given task an extensive research and evaluation has to be performed. In order to simplify the process the software system should be configurable, extensible and easy to maintain. Moreover, if it is to be used in any realistic setting it has to be efficient as well.

	\subsection{Required functionality}	
	There are three major functions that have to be supplied by the programme: (1) estimation, (2) batch inference and (3) inference. The first one is responsible for the model training. In order to perform this operation the following steps have to be completed: (i) detection and description of keypoints on the training set, (ii) codebook generation, (ii) classifier model training. The functions (2) and (3) are somewhat similar. Both require: (i) detection and description of keypoints on the test set, (ii) parsing keypoints' description into a visual vocabulary description and (iii) classification. The only is in the (i) step, e.g. the batch inference requires every image from the test set to be processed, whereas the inference can be done on any single image. The (3) have to be distinguished because it is the function that is to be used in a fully functional system mounted on i.e. a mobile robot.

		\subsubsection{Input/Output operations}	
		Additional functionality have to be provided in the field of input/output operations. Before any processing can be done each image have to be read into memory. Both batch inference and estimation are dataset dependant. What I mean by this is that a previously compiled database have to be accessible. The inference, on the other hand, is meant to be used in a production environment i.e. with a Kinect connected only. While the OpenNI Grabber framework from the PointCloud Library is essentially what is required for the inference, a little more elaboration has to be done on the demands of the estimation and batch inference environments. The two third party datasets used in the project have different formats and need to be tackled separately. The B3DO object dataset contains multiple objects in a single image. The locations of the images are available in xml files, while rgb and depth data are stored in separate files, 8-bit 3 channell jpeg and 16 bit one channel png respectively. Single objects have to be extracted from both pictures using the provided annotations and point cloud have to be build. The Zhang's dataset contain single objects. The rgb data is stored in 8 bit 3 channel jpegs and csv files contains euclidean coordinates of every rgb pixel. Both databases contain objects' labels that have to be loaded separately.

		A different problem is serialisation. If the models from the training stage are to be used during inference, they have to be serialised. This means that a standardised way of saving and loading of kMeans and SVM models have to be provided.

		\subsubsection{Configuration}		
		Every algorithm employed in the project have several configuration parameters. If the parameters were to be compiled with the code, every change would require a rebuild of the application or its parts. In order to address this issue a means of configuration from outside the code should be provided.

		\subsubsection{Interchangeability of algorithms}		
		Multitude of available algorithms makes it time consuming and computationally expensive to evaluate every available option. It should be possible to compile the programme with many algorithms suitable for performing the same task and decide which one should be used at run-time.

	\subsection{Architecture}

	\begin{figure}[ht]
	\centering
	\includegraphics[width=1.0\textwidth]{figs/short}
	\caption{Tagger3D class diagram}
	\label{fig:class_diagram}
	\end{figure}

	The described functionality can be achieved in the following way. The utilisation of Object Oriented Programming (OOP) can lead to production of modular, flexible and extensible software. Using C++ as the language of choice can result in high efficiency. The excellent metaprogramming tools provided by the C++ language help minimise the length of resulting hand-written code.

	\subsubsection{Configurability}
	In order to achieve configurability all the configuration parameters are stored in a configuration file. A separate object has been constructed for configuration file parsing. Simply called `Config', it makes use of the Boost.program\_options library to parse both the configuration file and command line arguments. It returns an associative array of (parameter, value) pairs. The convention is that if an object has to be configured the configuration map has to be passed in the object's constructor (other constructors are private).

	\subsubsection{Strategy Design Pattern}

	\begin{figure}[ht]
	\centering
	\includegraphics[width=1.0\textwidth]{figs/short}
	\caption{Strategy pattern}
	\label{fig:strategy}
	\end{figure}

	Design patterns has been introduced for the very first time by Gamma \emph{et al} in \cite{gamma1993design}. They are best practices that should be used to solved common, recurring problems in software design. One of the patterns is the strategy pattern. It enables implementation of multiple algorithms handling some task and selection the desired behaviour at run-time. It is the exact problem encountered here. It is stated that an interface should be defined for each task and multiple classes encapsulating different algorithms for handling the tasks should realise those interfaces. One modification has been done: Algorithms have often some common operations, thus an idea of an interface (a class without any implemented methods) was dropped in favour of a virtual class.

	The strategy pattern was used for every processing step of the pipeline so as to make it extensible. One might want to enhance this solution by using an abstract factory design pattern, which has not been done in this case. It might make the code easier to maintain and read. However, the project is relatively small and the bulk of an abstract factory is unnecessary.

	There six five classes that can be treated as algorithms' interfaces in a strategy pattern. They are: ImgReader, PointNormal, Detector, Descriptor, Cluster, Predictor. Each of them contains pure virtual computation methods --- 'read` in case of the ImgReader or 'predict' in case of the Predictor. Additionally, they have some common methods defined --- I/O methods in Cluster or batch processing methods (such that take a vector of elements instead of a single element as input) for the Detector and the Descriptor. Every pure virtual class has its specialisations. For example there is the PFHDescriptor class with a Point Feature Histogram descriptor or a KMeansCluster employing kMeans clustering algorithm. The Tagger3D class chooses specialisations of the algorithms at run-time, depending on the configuration parameters.

### 2013-10-16 Disseration/experiments.tex
latest changes

@@
+\chapter{Experiments and Results}
+\addcontentsline{toc}{chapter}{Experiments and results}
+
+\section{Experimental Setup}
+	Thanks to the configurability of the programme the majority of experiments were run in a batch processing mode.
+That is a script in bash was written that allowed running multiple tests in series without any maintenance from the user.
+In a single series of tests any parameters could be modified or any data processing algorithm could be exchanged.
+All experiments were run on a notebook with Intel Core i7 quad core 2.2 GHz cpu, 8 Gb of RAM and a nVidia M540 GPU.
+
 \section{Experiments}
-
 	The Bag of Words classification pipeline consists of four previously discussed steps.
@@
 The number of options grows combinatorial with number of candidates for each processing step.
-Moreover, many algorithms have different parameters that should be adjusted for the given conditions.
+Moreover, many algorithms have different parameters that should be adjusted for any given conditions.
 Evaluation of every possibility is unfeasible due to the lack of time and computational power required.
-Therefore it was chosen to evaluate algorithms with their default parametrs under fixed conditions.
-Only the winning methods qualify for the parameter tuning.
+Even if only a single library, PCL, is considered, there are far too many options with 12 keypoint detectors and more than 20 feature description algorithms.
 
 	\subsection{Detectors}
-
-	ISS3D is generally better than SIFT
+	In a paper \cite{pcl_keypoint_comparision} some keypoint detection algorithms from PCL are evaluated.
+It is stated that , albeit under slightly different conditions, the SIFT and ISS keypoint detectors achieve the highest performance.
+Therefore this paper compares only these two modules with respect to their usability in the BoW pipeline.
 
 	\subsection{Descriptors}
-
-	FPFH is faster than both PFH and PFHRGB. PFH does not give any advantages over FPFH. PFHRGB delievers considerably higher accuracy.
+	Recently a PCL's descriptors evaluation was performed in \cite{pcl_features}.
+The PFHRGB and SHOTCOLOR scored best.
+Only a little bit worse were PFH, FPFH, SHOT and USC.
+In this paper FPFH, PFH and PFHRGB are compared, motivation being that PFH is the original descriptor, FPFH is its approximate and thus faster version, while PFHRGB is an extension which makes use of colour information.
 
 	\subsection{Codebook}
+	KMeans is used in almost every implementation of the Bag of Words image processing pipeline \cite{tsai2012bag, toldo2009bag}.
+Csurka \emph{et al} showed that the number of visual words or centroids have a significant impact on the final results \cite{csurka2004visual}.
+Therefore a number of tests were run in order to determine the optimal dictionary size.
 
-Only kmeans tested with varying numbers of clusters i.e. vocabulary size
+	\begin{figure}[!ht]
+	\centering	
+	\includegraphics[width=.75\textwidth]{figs/clustering_centroids_b3do}
+	\caption{Influence of dictionary size on the overall accuracy. B3DO dataset with ISS keypoint detector and FPFH feature descriptor}
+	\label{fig:cluster_b3do}
+	\end{figure}
+
+	The results from the figure \ref{fig:cluster_b3do} partially confirm Csurka's findings.
+The performance raises with the increasing number of centroids up to the point of 1500 centroids and 65.22\%.
+Then it starts to diminish.
+The discrepancy might be caused by the following factors: (1) ISS detector finds too many or irrelevant points, thus introducing noise or (2) The FPFH descriptor has too few dimensions (33) to be divided into more than 1500 regions in a meaningful way.
 
 	\subsection{B3DO}
+	Extraction of single objects yielded 78 separate categories with number of entries ranging from 1 (tape) to 299 (table).
+8 categories were picked at random with a restriction that there should be at least 50 instances in each of them.
+Further, the objects were split into two sets (training and testing) with a proportion of 1:1.
+As names suggest, the estimation is performed on the test set and the evaluation on the test set.
 
-\subsection{tokyo}
+	The highest accuracy achieved for this dataset is 64\%.
+Table \ref{tab:b3do_conf_matrix} contains a confusion matrix, number of examples per category and accuracy.
+The confusion matrix depicts misclassification errors.
+Let m\subscript{i, j} be an element of the confusion matrix at the i\superscript{th} row and j\superscript{th} column.
+It shows how many elements from the i\superscript{th} category was assigned to the j\superscript{th} category.
+A high value of m\subscript{i, j} such that $i \neq j$ indicates that the classifier cannot distinguish between those two classes.
+
+	\begin{table}[!ht]
+	\centering
+	\caption{Results on the B3DO dataset with ISS keypoint detector, FPFH features and a dictionary of 1500 words. \textbf{Overall accuracy is 65.22\%}}
+	\includegraphics[width=0.9\textwidth]{figs/b3do_conf_matrix}	
+	\label{tab:b3do_conf_matrix}
+	\end{table}
+
+	\begin{figure}[!ht]
+	\centering	
+	\includegraphics[width=.75\textwidth]{figs/b3do_objects}
+	\caption{B3DO objects. Images are in their original sizes. a) cups b) bottles c) books d) keyboards}
+	\label{fig:b3do_objects}
+	\end{figure}
+
+	More than half of the bottles were assigned to the cup category and keyboards were often mistook for books.
+These two error types are easily explained by a high degree of similarity of objects (bottles and cups are usually round and tall, books and keyboards are flat and rectangular) Surprisingly, however, objects from half of the categories were frequently marked as cups.
+Some of these misclassification errors might be caused by very poor quality of images.
+Many of them are occluded poorly lit low resolution images.
+
+	\subsection{Tokyo}
+	\begin{table}[!ht]
+	\centering
+	\caption{Tokyo confusion matrix with ISS keypoint detector, PFH features and a dictionary of 3000 words}
+	\includegraphics[width=0.9\textwidth]{figs/tokyo_conf_matrix}	
+	\label{tab:tokyo_conf_matrix}
+	\end{table}
+
+	Every of the 343 images from Tokyo dataset was used. Data was split into test and train set in proportions 1:2 in order to provide more training examples due to low number of objects in some classes.
+
+	Even tough the overall accuracy achieved on Tokyo dataset is similar in value to that of the B3DO, the structure of the result is very different.
+It is clearly visible that there is a strong correlation between a per class accuracy and the number of entries in this class.
+The highest performance in the bicycle category is coupled with the largest number of entries.
+On the other end of the scale there are cart and printer categories with only 2 and 4 entries respectively.
+On top of that there are differences between some classes are marginal.
+The majority of carts and baskets were put into the bucket category.
+It does not surprise, for they are simply akin as can be seen in figure \ref{fig:tokyo} on the page \pageref{fig:tokyo}.
+
+\section{Conclusion}

### 2013-10-16 Disseration/introduction.tex
latest changes

\chapter{Introduction}
\addcontentsline{toc}{chapter}{Introduction}

	Capturing visual information of any kind have never been easier. Almost everyone of us posses a camera, be it a professional dSLR or a tiny one embedded into one of the ubiquitous smartphones. As human beings we have no difficulty understanding this data, just as we have no difficulty understanding what our eyes see. Unfortunately, the situation of our computers is the very opposite. Storage capacity of modern-day computers is overwhelming.  But even if hard-drives are full of images it is impossible to identify their semantic meaning without the aid of specialised algorithms, however. These algorithms often balance on the verge of image processing and machine learning --- they are a part of an area called computer vision. As Forsyth and Ponce \cite{ponce2011cv} have it: \begin{quote} computer vision is (...) an enterprise that uses statistical methods to disentangle data using models constructed with the aid of geometry, physics, and learning theory.\end{quote} The area of computer vision is not new. The original applications were industrial inspection or mobile robot navigation. More recent approaches consider problems such as human-machine interfaces, medical diagnostics, or image retrieval.

	How about semantic classification of scenes or objects? Suppose a mobile robot would know, or understand, what does it have to deal with. Suppose a robot would know that it is about to take, say, a glass of water. How would it affect the robot's behaviour? Could it have any impact on the force of the grip? or the speed and the manner of the planned object movement? Answers for all this questions are yes. Semantic classification is possible, but it requires clever mechanisms of computer vision and powerful computers. It can be seen as a part of a more general classification problem, which machine learning handles quite well. Suitable algorithms include, but are not limited to, artificial neural networks, deep belief networks, logistic regression, support vector machines and approaches based on probabilistic graphical models. One has to bear in mind that none of them can handle the problem directly. That is, it is inconceivable to feed a whole image as is into a classifier --- some degree of preprocessing is required. One such preprocessing technique is translation of image into a feature vector. What should this vector comprise of? A Bag of Words model is one technique that answers this question. This model has been first used for scene classification in 2004 in \cite{csurka2004visual} and maintains its popularity ever since.

	In this paper a technique for semantic object classification based on three dimensional point clouds is presented. The rest of this chapter is organised as follows: Section 1 describes the Bag of Words technique in detail. Construction of an image's model is discussed and the most popular algorithms are summarised. Section 2 provides basic information on the problem of classification, introduces basic concepts and methods of classification. Section 3 names C++ computer vision and general purpose libraries used in this project. Finally in Section 4 two datasets of RGBD images are outlined. The following chapters are titled ``Design'' and ``Experiments and Results''. The former contains description of required functionality of a programme for BoW object classification, its design and implementation details. The latter addresses topics of experimental setup, performed experiments and a summary of results.

\section{Bow of Words}

	The Bag of Words (BoW) model is a an intermediate representation used in natural language processing, information retrieval and data mining [need pub]. The model can be seen as a simplification, for it obliterates any grammatical information and even word order contained within an original text document. What is left is an unstructured group of words, usually in a form of a vector or a histogram of word incidence.

	\begin{figure}[!ht]
	\centering
	\includegraphics[width=0.7\textwidth]{figs/bow_example}
	\caption{Bag of Words histogram}
	\label{fig:bow_example}
	\end{figure}

	The figure \ref{fig:bow_example} shows a piece of text and its BoW model, where articles and punctuation marks were left out. In order to compare different documents a global dictionary must be built. The dictionary (codebook) is constructed by taking every word from all available documents and removing duplicates. One can image that if a dictionary is of any considerable size resulting representation of especially small documents will be very sparse.

	In natural language processing BoW representation is used to infer semantic meaning of documents [need pub]. If an image could be translated into a text document it might be possible to employ similar methods. A question arises: How does one make a text document from an image?

	\subsection{Processing Pipeline}	
	Tsai describes a well established pipeline that allows translation of images into text documents or BoW models \cite{tsai2012bag}. It consists of the following steps: (1) region detection, (2) feature extraction, (3) vector quantization and (4) BoW histogram formation as can be seen in the figure \ref{fig:bow_pipeline}. The author summarises the most commonly used methods for performing these tasks.

	\begin{figure}[!ht]
	\centering
	\includegraphics[width=0.75\textwidth]{figs/tsai2012}
	\caption{Bag of Words pipeline. The figure comes from \cite{tsai2012bag}}
	\label{fig:bow_pipeline}
	\end{figure}

		\subsubsection{Region Detection}
		Characteristic region detection is the first step in any Bag of Words framework. Numerous detection methods have been developed, but choosing the right one for any particular case might prove tricky. A good overview of various mechanisms is available in \cite{tsai2012bag}.

		The most common detectors make use of a Harris corner detector or image's first or second derivatives. A Harris-Laplace detector is an example of a Harris-based detector. The Harris function is scale adapted and its outcome is a subject to a Laplacian-of-Gaussian (LoG) operator, which selects relevant points in scale space. Images' regions' 2\textsuperscript{nd} derivatives, namely the regions' Hessians, can be combined with a LoG operator as well. This combination allows selection of points significant in the two spaces: the scale space and the Hessian's determinant space. The latter entails the speed at which pixel intensities change in the neighbourhood of a point.

		A number of more complicated recipes for salient region localisation have been developed and implemented. These include for example SIFT \cite{sift_keypoint}, SUSAN \cite{susan_keypoint} and Intrinistic Shape Signatures \cite{iss_keypoint}. The majority of keypoint detection formulas is being developed for the 2D domain. A number of them have been adapted to 3D, however. A comparative evaluation of detection algorithms available in the PointCloud Library (PCL, discussed below) can be find in \cite{pcl_keypoint_comparision}. Another comprehensive study is \cite{3d_keypoint_eval}. All these formulas, called sparse feature detectors, resort to selection of maxima in specific state spaces. An entirely different scheme is to use a dense feature detector. That is, take a uniformly sampled grid of points. Dense detectors, unlike the sparse ones, take points from slow changing regions such as clear sky and calm ocean water. Li \emph{et al} showed that dense detectors generally outperform the sparse ones \cite{fei2005bayesian}.

		\subsubsection{Feature Extraction}
		Suppose only coordinates of a keypoint were found. In case of even smallest rotation or translation they would change and the keypoint would be lost. Keypoints should be described in a way that makes them invariant to affine transforms, changes in light intensity or colour saturation. All these properties are hard to achieve, but methods that meet some of the criteria exist.

		Keypoint description is usually delivered in a form of coordinates in a high-dimensional space. One of the best algorithms is SIFT \cite{sift_features}, which is 3D histogram of gradients structured as a 128-dimensional vector of floating point values. It is the most often extracted descriptor in BoW pipelines. Other methods include various colour descriptors, binary descriptors such as 512-dimensional GIST \cite{ponce2011cv}. There are techniques designed for 3D exclusively. Among them are Persistent Point Feature Histogram (PFH) \cite{pfh_rusu2008}, its faster alternative FPFH \cite{fpfh_rusu2009} and PFHRGB, which takes into account colour information, all implemented in PCL.

		\subsubsection{Vector Quantization}
		When features are extracted they have to be normalised. Vector quantization step have two main phases. The first one is codebook construction from a training dataset. The second phase is responsible for parsing (or translation) raw image descriptors into a form compatible with the newly constructed codebook. The simplest way of building a dictionary is to find patterns or regions within the training dataset's descriptors. Then, the parsing phase would be nothing but assigning each descriptor to a certain region. Such an assignment can performed by a k-Nearest-Neighbours match. Slightly more advanced techniques of dictionary building involve using many kinds of descriptors, i.e. texture, shape and colour descriptors, or spatial information.

		The KMeans is the single most popular vector quantization algorithm used in the BoW pipelines \cite{tsai2012bag}. Developed in 1950's, it is well known and simple. kMeans divides all data into a predefined amount of clusters and computes the clusters' centroids. Many modifications and alternative versions have emerged \cite{kmeans_jain2010data}. Some of them are: faster than the original \emph{approximate kmeans}, \emph{hierarchical kmeans}, which automatically chooses the final number of clusters and a  \emph{soft kmeans} --- a variation of the algorithm that allows a fuzzy alignment (\textit{i.e.} each point can belong to several clusters with different weights). Vector quantization is responsible for the dictionary size, for the clusters' centroids are (in a simple approach) synonymous to the visual words. Thus the higher the number of clusters, the bigger the dictionary, which in turn allows for a more precise image description.

		If computational cost is of no concern, or if required precision is of the utmost priority, a Gaussian Mixture Model (GMM) can be used. The GMM partitions data into a set of clusters and finds their centroids. Additionally, it computes a probability distribution over each cluster, i.e. for every point its probability of membership in each cluster is returned. Both kMeans and soft-kMeans are specific variants of the GMM. The drawback of the GMM is its massive computational cost in comparison with still expensive kMeans.

		It should be underlined that the vector quantization step, especially the codebook construction process, is the most time-consuming part of the whole Bag of Words pipeline.

	\subsection{Applications in Computer Vision}
	The Bag of Words model is nothing but an intermediate representation. As such it is mainly used in the two following areas: Content Based Image Retrieval (CBIR) and Scene/Object Classification.

		\subsubsection{Content Based Image Retrieval}
		CBIR is a computer vision approach to image retrieval from large image databases. Tangelder \emph{et al} provides an overview of techniques applicable to 3D objects \cite{tangelder2008survey}. The task of image retrieval is to find a database entry fulfilling certain conditions. If it is to be performed efficiently several criteria have to be met \cite{toldo2009bag}, namely: (1) All entries should be indexed in a concise way, (2) a (dis)similarity measure should be provided and (3) an efficient search algorithm should be available.

		Indexing of objects is required so as not to compare the database entries explicitly. Therefore, for every object in a dataset a compact as well as a discriminative signature should be computed. Suitable algorithms can be divided into three general categories: (1) feature based methods, (2) graph based methods and (3) other methods.

		Feature based methods can be further divided into global features and local features. The global features take form of a single vector (or a point in a \emph{d} dimensional space). They are usually associated with object's mass or volume or distributions of these. Being easy to compute and straightforward to implement, their discriminative power is rather low --- they cannot be used for partial matching, but are well suited for an early preprocessing. Local features, on the other hand, describe object's characteristic regions. Their shape is similar to that of the global features, but instead of a single point in space there are multiple ones --- one for each considered region. Tangelder argues that local features based approaches are inefficient and lead to a complex indexing problem \cite{tangelder2008survey}. At the same time Toldo \emph{et al} and Li \emph{et al} show that Bag of Words local feature based approach has no such drawbacks. On the contrary --- it is easy to implement, efficient and provides state-of-the-art results.

		\subsubsection{Scene and Object Classification}
		Inspired by various works on pattern recognition and texture classification and an idea of a ``texton``, a building block from which textures are made, Csurka \emph{et al} is the first to apply the Bag of Words paradigm to the task of scene classification \cite{csurka2004visual}. In their early work authors suggested a a general framework described above. After translating images into text documents BoW histograms were built and fed into two classifiers: SVM and Na\`ive Bayes (discussed below).

		Fei-Fei \emph{et al} refined the above approach by examining several keypoint detectors and descriptors. The main contribution of their work is, however, the development of a genuine classification algorithm based on a probabilistic graphical model. Accuracy of 76\% on a large 13 category dataset was achieved.
		Object categorisation can be addressed in the same way. The only difference is that a bounding box of an object (or knowledge of object's coordinates) can be helpful. On the other hand, it is possible to consider an object classification problem where images of singled-out objects are provided --- e.g. a single object covers a majority of image's area like in \cite{zhangcategory}.

		Classification is not an integral part of the BoW pipeline. But the Bag of Words histograms can be used as a compact and discriminative representation that can be fed into any classifier.

\section{Problem of Classification}

	%What is classification?
	%Why does machine learning apply? What advantages does it give?

	%Discriminative vs Generative approach
	%Overview of algorithms: kNN, logistic regression, SVM, NN, PGM, Naive Bayes
	To classify means to, given a set of categories, produce a category label for a given set of features \cite{ponce2011cv}. Many problems might not seem like classification problems and image categorisation is one of them. Images are too complex to be processed by any classifier directly. We can think that there are too many details, too many aspects that decide whether a picture fits into a category or not. But it turns out that many problems can be abstracted in such a way that they become pure classification problemd. One such abstraction for photographs or point clouds is the Bag of Words model. Classifiers can be two-class classifiers (e.g. binary) or multi-class classifiers. It is a common practice to build multi-class classifiers from binary ones, however. The most popular classifiers are: k-Nearest Neighbours, Logistic Regression, Na\`ive Bayes and Support Vector Machine.

	\subsubsection{Na\`ive Bayes}
	Assume that we have a \textit{n}-dimensional feature vector $\mathbf{X}$ such that $\mathbf{X} = \left\{x_1, x_2, ... , x_\mathit{n}\right\}$ and an unknown category label \textit{C}. The probability of the category \textit{C} given the feature vector \textbf{X} is $P\left(\mathit{C}\middle|\mathbf{X}\right) = P\left(\mathit{C}\middle|\left\{x_1, x_2, ..., x_\mathit{n}\right\}\right)$. The strong (or na\`ive) Bayes assumption says that features are independent of each other, that is $P(\mathbf{X}) = P(x_1)*P(x_2)*...*P(x_\mathit{n})$. If so, we can compute probability distributions of every class in our training set given every feature. Then, for any new feature vector the joint probability distribution over a set of features can be calculated and an appropriate class label can be assigned.

	\subsubsection{k-Nearest Neighbours}
	The nearest neighbours classifier assumes that if there are labelled points in a neighbourhood of a newly added point, then the new point can be classified based on it's neighbours' labels. There is an issue of choosing the correct number of nearest neighbours (or k) to consider

	\subsubsection{Support Vector Machine}
	\begin{figure}[!ht]
	\centering
	\includegraphics[width=0.75\textwidth]{figs/svm}
	\caption{Classification by a Support Vector Machine. The distance of the separating plane from both datasets is maximal. The figure was originally published in \cite{ponce2011cv}}
	\label{fig:svm}
	\end{figure}

	Assume that a set of pairs $\{\{\mathbf{x}_1, y_1\}, \{\mathbf{x}_2, y_2\}, ...\}$ where $x_\mathit{i}$ are features and $y_\mathit{i} \in \{-1, 1\}$ are labels is given. Further assume that points with different labels are two linearly-separable datasets as shown in the figure \ref{fig:svm}, where dots and circles are points with different labels. Then, there exist parameters \textbf{\textit{w}} and  \textit{b} which satisfies	
	\begin{equation}
	                        y_\mathit{i}\left(\mathbf{w}*\mathbf{x}_\mathit{i} + w\right) > 0                                                                                                                                                                                                                                                                                                                                                                                                                       
	                                                                                                                                                                                                                                                                                                                                                                                                                                               \end{equation}
	for every $\mathbf{x}_\mathit{i}$ or a data point. This equation specifies constraints on a plane (or a hyperplane in general) that separates the dataset. A Support Vector Machine finds parameters \textbf{\textit{w}} and  \textit{b} so as to maximise the distance of this plane from both datasets.

\section{Libraries}

	One of the advantages of object oriented programming is that it is easier to reuse once created code. There exists a variety of third party libraries for the C++ programming language. One of the biggest and the most widely used are the general purpose Boost libraries \cite{Boost}. In the fields of computer vision there are, among others, OpenCV \cite{OpenCV} and PointCloud Library \cite{PCL}. Easy to use and intuitive logging is provided by the Apache log4cxx \cite{log4cxx}.

	\subsection{PointCloud Library}
	Being nothing but a large scale open source project, it is a great processing tool for 2D images and 3D point clouds. Often abbreviated as PCL, it contains numerous state-of-the-art algorithms for feature detection, surface reconstruction, segmentation and many other subareas of computer vision. It is well documented and easy to use. Recently a machine learning library containing algorithms such as Support Vector Machine has been added. Some algorithms are multi-threaded thanks to the OpenMP library. A GPU module boosts some algorithms. Unfortunately the PCL is relatively new and its stability could be better. Currently available 1.7.0 version is going to be replaced by soon-to-be-announced 2.0 version with incompatible API.

	Every feature detector and descriptor used in this project comes from the PCL.

	\subsection{OpenCV}
	Considerably more mature, the OpenCV library is yet another great image processing library. A multitude of methods implemented in both C (OpenCV 1.x) and C++ (OpenCV 2.x) allows for production of fully functional image processing or computer vision application with this single library. There are many machine learning mechanisms as well. Among them one can find kMeans, Gausian Mixture Model, Na\`ive Bayes or a Support Vector Machine. Some of the more demanding in terms of computational power are parallelized with Threading Building Blocks (TBB). A module exploiting powers of the nVidia's CUDA technology exists in order to enhance computation even more.

	In this paper OpenCV is used for input/output operations, image preprocessing. KMeans and SVM implementations are used as well.

	\subsection{Boost}
	Boost is a general purpose library. It contains more than 50 separate libraries, 12 of which were incorporated into the new C++11 standard. One of the most popular are libraries for smart pointers, multi-threading or meta-programming. Tagger3D uses only the functionality provided by the Boost.program\_options library. It enables convenient parsing of configuration files and command line arguments.

\section{Datasets}

	Multiple RGBD datasets were created. The purpose of authors of the vast majority of them were to provide a benchmark for tasks of tracking or instance-level object recognition. Others have small number of categories or very few examples in every category. Unfortunately, the most are not fit for the object classification problem.
	The RGB-D object dataset from the University of Washington \cite{dataset_washington} would be perfect, if not for the fact that it consists of video sequences. A technology like Kinect Fusion \cite{KinectFusion} makes it relatively easy to build a detailed 3D model (a point cloud or a mesh) from such data. The only problem is in the computational cost of this method and actions required to gather such data --- in a real setting a mobile robot would have to circle an object. Two datasets are used are for the purpose of this paper. The first one is the Berkely 3D Object dataset \cite{B3DO} and the second one is a dataset compiled by Zhang \emph{et al} at the University of Tokyo \cite{zhangcategory}. The datasets are going to be abbreviated as B3DO and Tokyo datasets respectively

	\subsection{Berkely 3D Object Dataset}
	\begin{figure}[!ht]
	\centering
	\includegraphics[width=0.5\textwidth]{figs/b3do_dataset}
	\caption{Berkely 3D Object Dataset. The figure comes from \cite{B3DO}}
	\label{fig:b3do}
	\end{figure}

	The Berkely 3D Object dataset was specifically designed for the purpose of object classification. It consists of cluttered images in indoor environment. There are around 50 classes with more than 20 examples in each of them. RGBD data is provided as pairs of images. There are 8 bit RGB jpeg pictures and 16 bit png files containing depth data in millimetres. Images are densely labelled --- for every pair of images there is an xml with annotations. Every annotation is comprised of a category label, bounding box coordinates and object's orientation.

	Before the B3DO database could be used it had to be preprocessed. Neither image segmentation nor object detection are addressed in this paper. Because of that the objects had to be extracted from the cluttered images.

	\subsection{The University of Tokyo Dataset}	
	\begin{figure}[!ht]
	\centering
	\includegraphics[width=1\textwidth]{figs/tokyo_horizontal}
	\caption{The Tokyo dataset: a) basket b) bicycle c) box d) bucket e) cart f) freezer g) notebook h) printer i) scanner j) scene}
	\label{fig:tokyo}
	\end{figure}

	The dataset compiled at the University of Tokyo is comprised of high quality images of objects in different settings. Factors such as viewpoint, object orientation, object's texture and environments are changing on different images. The aim of the authors of this dataset was slightly different - it was object detection and classification in casual images. There are 10 classes with varying amounts of per class examples. The database is available as two sets of files: 8 bit RGB jpeg files and csv files containing euclidean coordinates of every pixel in the corresponding colour image.

### 2013-10-16 Disseration/zyciorys.tex
latest changes

    \vspace*{1\baselineskip}
    \begin{tabular}{p{5cm} p{10cm}}
    \begin{minipage}{5cm}
    \center
    \includegraphics[width=4.5cm]{figs/ja}
    \end{minipage}
    &
    \begin{minipage}{12cm}
\par\noindent\vspace{1\baselineskip}
    \begin{flushleft}
    \par\noindent\vspace{1\baselineskip}
    \begin{tabular}[h]{l l}
    {\normalsize\it Degree:} & Automatic Control Engineering and Robotics
    \end{tabular}
    \par\noindent\vspace{1\baselineskip}
    \begin{tabular}[h]{l l}
    {\normalsize\it Major:} & Robotics
    \end{tabular}
    \par\noindent\vspace{1\baselineskip}
    \begin{tabular}[h]{l l}
    {\normalsize\it Birth date:} & {\normalsize 28 February 1991}
    \end{tabular}
    \par\noindent\vspace{1\baselineskip}
    \begin{tabular}[h]{l l}
    {\normalsize\it Study starting date:} & {\normalsize 1 October 2010 r.}
    \end{tabular}
    \par\noindent\vspace{1\baselineskip}
    \end{flushleft}
    \end{minipage}
    \end{tabular}
    \vspace*{1\baselineskip}
    \begin{center}
	{\large\bfseries Biography}\par\bigskip
    \end{center}

	I was born on 28 February 1991 in Olsztyn, Poland. I attended 5\superscript{th} Secondary School by the name of ``The Common Europe'' in Olsztyn. I started a Bachelor of Engineering degree on the Faculty of Mechatronics of Warsaw University of Technology on 1 October 2010. I did an internship in Faurecia R\&D S.A. in 2012. In 2013 I started working in IBM Poland Sp. z o.o. where I stayed for 6 months. Then I started working full-time in Samsung R\&D Centre Poland.

    \par
    \vspace{3\baselineskip}
    \hfill\parbox{15em}{{\small\dotfill}\\[-.3ex]
    \centerline{\footnotesize signature}}\par
    \vspace{3\baselineskip}

### 2013-10-16 src/main.cpp

@@ -37,7 +37,7 @@ int main(int argc, char** argv) {
 		exit(2);
 
 	t3d::Tagger3D tagger(configMap);
-	tagger.run();
+	//tagger.run();
 }
 
 void configureLogger(int &argc, char** argv, const lgr::LoggerPtr &logger) {

### 2013-10-20 Disseration/experiments.tex
desc_b3do fig

@@
 In this paper FPFH, PFH and PFHRGB are compared, motivation being that PFH is the original descriptor, FPFH is its approximate and thus faster version, while PFHRGB is an extension which makes use of colour information.
+
+	\begin{figure}[!ht]
+	\centering	
+	\includegraphics[width=.75\textwidth]{figs/desc_b3do}
+	\caption{Highest accuracy obtained with FPFH, PFH and PFHRGB descriptors on the B3DO dataset}
+	\label{fig:desc_b3do}
+	\end{figure}
+
+	The figure \ref{fig:desc_b3do} shows highest accuracy obtained with the tested descriptors on the B3DO dataset.
+FPFH scored the best result, even tough it is an approximate and theoretically the least precise of all evaluated descriptors.
+On the other hand, the PFHRGB scored better than PFH.
+It does not surprise, since the colour information is believed to have discriminative value.
 

### 2013-10-20 Disseration/architecture.tex
aa

@@
 The B3DO object dataset contains multiple objects in a single image.
-The locations of the images are available in xml files, while rgb and depth data are stored in separate files, 8-bit 3 channell jpeg and 16 bit one channel png respectively.
+The locations of the images are available in xml files, while rgb and depth data are stored in separate files, 8-bit 3 channel jpeg and 16 bit one channel png respectively.
 Single objects have to be extracted from both pictures using the provided annotations and point cloud have to be build.
@@
 Using C++ as the language of choice can result in high efficiency.
-The excellent metaprogramming tools provided by the C++ language help minimise the length of resulting hand-written code.
+The excellent meta-programming tools provided by the C++ language help minimise the length of resulting hand-written code.
 

### 2013-10-20 Disseration/experiments.tex
aa

@@
 In a single series of tests any parameters could be modified or any data processing algorithm could be exchanged.
-All experiments were run on a notebook with Intel Core i7 quad core 2.2 GHz cpu, 8 Gb of RAM and a nVidia M540 GPU.
+All experiments were run on a notebook with Intel Core i7 quad core 2.2 GHz CPU, 8 GB of RAM and a nVidia M540 GPU.
 
@@
 
-	\begin{figure}[!ht]
+	\begin{table}[!ht]
 	\centering	
-	\includegraphics[width=.75\textwidth]{figs/desc_b3do}
+	\includegraphics[width=.25\textwidth]{figs/desc_b3do}
 	\caption{Highest accuracy obtained with FPFH, PFH and PFHRGB descriptors on the B3DO dataset}
-	\label{fig:desc_b3do}
-	\end{figure}
+	\label{tab:desc_b3do}
+	\end{table}
 
-	The figure \ref{fig:desc_b3do} shows highest accuracy obtained with the tested descriptors on the B3DO dataset.
+	The figure \ref{tab:desc_b3do} shows highest accuracy obtained with the tested descriptors on the B3DO dataset.
 FPFH scored the best result, even tough it is an approximate and theoretically the least precise of all evaluated descriptors.

### 2013-10-20 Disseration/introduction.tex
aa

@@
 We can think that there are too many details, too many aspects that decide whether a picture fits into a category or not.
-But it turns out that many problems can be abstracted in such a way that they become pure classification problemd.
+But it turns out that many problems can be abstracted in such a way that they become pure classification problems.
 One such abstraction for photographs or point clouds is the Bag of Words model.
@@
 There are many machine learning mechanisms as well.
-Among them one can find kMeans, Gausian Mixture Model, Na\`ive Bayes or a Support Vector Machine.
+Among them one can find kMeans, Gaussian Mixture Model, Na\`ive Bayes or a Support Vector Machine.
 Some of the more demanding in terms of computational power are parallelized with Threading Building Blocks (TBB).
@@
 Two datasets are used are for the purpose of this paper.
-The first one is the Berkely 3D Object dataset \cite{B3DO} and the second one is a dataset compiled by Zhang \emph{et al} at the University of Tokyo \cite{zhangcategory}.
+The first one is the Berkeley 3D Object dataset \cite{B3DO} and the second one is a dataset compiled by Zhang \emph{et al} at the University of Tokyo \cite{zhangcategory}.
 The datasets are going to be abbreviated as B3DO and Tokyo datasets respectively
 
-	\subsection{Berkely 3D Object Dataset}
+	\subsection{Berkeley 3D Object Dataset}
 	\begin{figure}[!ht]
@@
 	\includegraphics[width=0.5\textwidth]{figs/b3do_dataset}
-	\caption{Berkely 3D Object Dataset. The figure comes from \cite{B3DO}}
+	\caption{Berkeley 3D Object Dataset. The figure comes from \cite{B3DO}}
 	\label{fig:b3do}
@@
 
-	The Berkely 3D Object dataset was specifically designed for the purpose of object classification.
+	The Berkeley 3D Object dataset was specifically designed for the purpose of object classification.
 It consists of cluttered images in indoor environment.

### 2013-10-20 src/Common/Tagger3D.cpp

@@ -15,6 +15,7 @@
 #include "../Descriptor/PFHDescriptor.h"
 #include "../Descriptor/FPFHDescriptor.h"
 #include "../Descriptor/PFHRGBDescriptor.h"
+#include "../Descriptor/PFHRGBgpu.h"
 #include "../Cluster/KMeansCluster.h"
 #include "../Predictor/SldaPredictor.h"
 #include "../Predictor/SVMPredictor.h"
@@ -52,7 +53,8 @@ Tagger3D::Tagger3D(const std::map<std::string, std::string> &configMap) : Proces
 	switch( getParam<int>( descType )) {
 	case PFH_DESC: descriptor = std::unique_ptr<Descriptor> (new PFHDescriptor(configMap)); break;
 	case FPFH_DESC: descriptor = std::unique_ptr<Descriptor> (new FPFHDescriptor(configMap)); break;
-	case PFHRGB_DESC: descriptor = std::unique_ptr<Descriptor> (new PFHRGBDescriptor(configMap)); break;
+	//case PFHRGB_DESC: descriptor = std::unique_ptr<Descriptor> (new PFHRGBDescriptor(configMap)); break;
+	case PFHRGB_DESC: descriptor = std::unique_ptr<Descriptor> (new PFHRGBgpu(configMap)); break;
 	default:
 		std::runtime_error e("Invalid descriptor type");
 		ERROR(logger, e.what());

### 2013-10-20 src/Descriptor/GpuDescriptor.cpp

@@ -1,0 +1,77 @@
+/*
+ * GpuDescriptor.cpp
+ *
+ *   Created on: 20 paź 2013
+ *       Author: Adam Kosiorek
+ *	Description:
+ */
+
+#include "GpuDescriptor.h"
+#include <pcl/gpu/features/features.hpp>
+
+namespace Tagger3D {
+
+GpuDescriptor::GpuDescriptor(const std::map<std::string, std::string> &configMap) : Descriptor(configMap) {}
+
+GpuDescriptor::~GpuDescriptor() {}
+
+cv::Mat GpuDescriptor::describe(const ColorCloud::Ptr &cloud,
+		const ScaleCloud::Ptr &keyCloud, const NormalCloud::Ptr &normalCloud ) {
+
+	pcl::gpu::DeviceArray<pcl::PointXYZ> points;
+	pcl::gpu::DeviceArray<pcl::PointXYZ> keypoints;
+	pcl::gpu::DeviceArray<pcl::PointXYZ> normals;
+
+	points.upload(xyzrgb2xyz(cloud->points));
+	keypoints.upload(scale2xyz(keyCloud->points));
+	normals.upload(normal2xyz(normalCloud->points));
+
+	return describe(points, keypoints, normals);
+}
+
+std::vector<pcl::PointXYZ> GpuDescriptor::xyzrgb2xyz
+	(std::vector<pcl::PointXYZRGB, Eigen::aligned_allocator<pcl::PointXYZRGB>> &vec) {
+
+	std::vector<pcl::PointXYZ> xyz;
+	xyz.reserve(vec.size());
+	for(const auto &point : vec) {
+
+		pcl::PointXYZ* p = new pcl::PointXYZ;
+		p->x = point.x;
+		p->y = point.y;
+		p->z = point.z;
+	    int r = std::max(1, std::min(255, static_cast<int>(point.r)));
+		int g = std::max(1, std::min(255, static_cast<int>(point.g)));
+		int b = std::max(1, std::min(255, static_cast<int>(point.b)));
+		p->data[3] = (b << 16) + (g << 8) + r;
+		xyz.push_back(*p);
+	}
+	return xyz;
+
+}
+
+std::vector<pcl::PointXYZ> GpuDescriptor::scale2xyz
+	(std::vector<pcl::PointWithScale, Eigen::aligned_allocator<pcl::PointWithScale>> &vec) {
+
+	std::vector<pcl::PointXYZ> xyz;
[…]

### 2013-10-20 src/Descriptor/GpuDescriptor.h

@@ -1,0 +1,43 @@
+/*
+ * GpuDescriptor.h
+ *
+ *   Created on: 20 paź 2013
+ *       Author: Adam Kosiorek
+ *	Description:
+ */
+
+#ifndef GPUDESCRIPTOR_H_
+#define GPUDESCRIPTOR_H_
+
+#include "Descriptor.h"
+#include <pcl/gpu/features/features.hpp>
+
+namespace Tagger3D {
+
+/*
+ *
+ */
+class GpuDescriptor: public Descriptor {
+	/**
+	 *
+	 */
+public:
+	GpuDescriptor(const std::map<std::string, std::string> &configMap);
+	virtual ~GpuDescriptor();
+
+	cv::Mat describe(const ColorCloud::Ptr &cloud, const ScaleCloud::Ptr &keyCloud, const NormalCloud::Ptr &normalCloud );
+
+protected:
+	virtual cv::Mat describe(const pcl::gpu::DeviceArray<pcl::PointXYZ> &cloud,
+			const pcl::gpu::DeviceArray<pcl::PointXYZ> &keycloud,const pcl::gpu::DeviceArray<pcl::PointXYZ> &normalCloud) = 0;
+
+private:
+	GpuDescriptor();
+
+	std::vector<pcl::PointXYZ> xyzrgb2xyz(std::vector<pcl::PointXYZRGB, Eigen::aligned_allocator<pcl::PointXYZRGB>> &vec);
+	std::vector<pcl::PointXYZ> scale2xyz(std::vector<pcl::PointWithScale, Eigen::aligned_allocator<pcl::PointWithScale>> &vec);
+	std::vector<pcl::PointXYZ> normal2xyz(std::vector<pcl::Normal, Eigen::aligned_allocator<pcl::Normal>> &vec);
+};
+
+} /* namespace Tagger3D */
+#endif /* GPUDESCRIPTOR_H_ */

### 2013-10-20 src/Descriptor/PFHRGBDescriptor.h

@@ -23,7 +23,7 @@ class PFHRGBDescriptor: public Descriptor {
 	 *
 	 */
 public:
-	PFHRGBDescriptor(const std::map<std::string, std::string> &configM);
+	PFHRGBDescriptor(const std::map<std::string, std::string> &configMap);
 	virtual ~PFHRGBDescriptor();
 
 	cv::Mat describe(const ColorCloud::Ptr &cloud, const ScaleCloud::Ptr &keyCloud, const NormalCloud::Ptr &normalCloud );
@@ -34,11 +34,8 @@ private:
 	typedef pcl::PFHRGBEstimation<pcl::PointXYZRGB, pcl::Normal, pcl::PFHRGBSignature250> descriptorType;
 	std::unique_ptr<descriptorType> descriptor;
 
-	//	Config parameters
-	float radiusSearch;
-
 	//	Config keys
-	const std::string radiusSearchKey = moduleName + "radiusSearch";
+	const std::string radiusSearch = moduleName + "radiusSearch";
 };
 
 } /* namespace Tagger3D */

### 2013-10-20 src/main.cpp

@@ -37,7 +37,7 @@ int main(int argc, char** argv) {
 		exit(2);
 
 	t3d::Tagger3D tagger(configMap);
-	//tagger.run();
+	tagger.run();
 }
 
 void configureLogger(int &argc, char** argv, const lgr::LoggerPtr &logger) {

### 2013-12-15 src/Common/Factory.h
added factory class, changing modes to desc, clust, train pred

@@ -1,0 +1,56 @@
+/*
+ * Factory.h
+ *
+ *  Created on: 14 gru 2013
+ *      Author: adam
+ */
+
+#ifndef FACTORY_H_
+#define FACTORY_H_
+
+#include "ProcessObject.h"
+
+#include "ImgReader.h"
+#include "PointNormal.h"
+#include "Detector.h"
+#include "Descriptor.h"
+#include "Cluster.h"
+#include "Predictor.h"
+
+#include <memory>
+
+namespace Tagger3D {
+
+class Factory: public ProcessObject {
+public:
+	Factory() = delete;
+	Factory(const std::map<std::string, std::string> &_configMap);
+	virtual ~Factory() = default;
+
+	std::unique_ptr<ImgReader> getReader() const;
+	std::unique_ptr<PointNormal> getPointNormal() const;
+	std::unique_ptr<Detector> getDetector() const;
+	std::unique_ptr<Descriptor> getDescriptor() const;
+	std::unique_ptr<Cluster> getCluster() const;
+	std::unique_ptr<Predictor> getPredictor() const;
+
+private:
+
+	const std::map<std::string, std::string> &configMap;
+
+	const std::string readerType = "readerType";
+	const std::string detectorType = "detectorType";
+	const std::string descType = "descType";
+	const std::string predictorType = "predictorType";
+
+	const std::string loggerName = "Main.Factory";
+
+	enum Dataset : unsigned char { B3DO, TOKYO };
+	enum DetectorType : unsigned char { SIFT, ISS3D };
+	enum DescriptorType : unsigned char { PFH, FPFH, PFHRGB };
+	enum PredictorType : unsigned char { SVM };
+};
+
+} // namespace Tagger3D
+
+#endif /* FACTORY_H_ */

### 2013-12-15 src/Common/ProcessObject.cpp

@@ -23,7 +23,7 @@ ProcessObject::ProcessObject(const std::map<std::string, std::string> &_configMa
 
 ProcessObject::~ProcessObject() {}
 
-bool ProcessObject::checkConfig(const std::string &key) {
+bool ProcessObject::checkConfig(const std::string &key) const{
 
 	if( !configMap.count(key) || configMap.find(key)->second.length() == 0) {
 
@@ -31,19 +31,6 @@ bool ProcessObject::checkConfig(const std::string &key) {
 	}
 
 	return true;
-}
-
-bool ProcessObject::checkConfig(const std::vector<std::string*> keys) {
-
-	for(std::string* key : keys) {
-
-		if( !checkConfig( *key) ) {
-
-			return false;
-		}
-
-		return true;
-	}
 }
 
 std::string ProcessObject::getParam(const std::string &key ) {

### 2013-12-15 src/Common/Tagger3D.h

@@ -10,12 +10,12 @@
 #define TAGGER3D_H_
 
 #include "ProcessObject.h"
-#include "../ImgReader/ImgReader.h"
-#include "../PointNormal/PointNormal.h"
-#include "../Detector/Detector.h"
-#include "../Descriptor/Descriptor.h"
-#include "../Cluster/Cluster.h"
-#include "../Predictor/Predictor.h"
+#include "ImgReader.h"
+#include "PointNormal.h"
+#include "Detector.h"
+#include "Descriptor.h"
+#include "Cluster.h"
+#include "Predictor.h"
 #include <memory>
 
 namespace Tagger3D {
@@ -100,7 +100,6 @@ private:
 
 	//	Parameters	------------------------------------------------------------
 
-
 	std::string trainDescPath;
 	std::string testDescPath;
 
@@ -120,10 +119,6 @@ private:
 		modeAll = "all";
 
 	// Config keys	---------------------------------------------------------------
-	const std::string readerType = moduleName + "readerType";
-	const std::string detectorType = moduleName + "detectorType";
-	const std::string descType = moduleName + "descType";
-	const std::string predictorType = moduleName + "predictorType";
 	const std::string trainCluster = moduleName + "trainCluster";
 
 	const std::string trainDescriptors = "trainDescriptors";
@@ -133,12 +128,7 @@ private:
 
 	// Enums -------------------------------------------------------------------
 
-	enum { TRAIN, TEST, DESC, CLUST, TRAIN_PRED, TEST_PRED, ALL };
-	enum { RANGEIMG_READER, PCD_READER };
-	enum { SIFT, ISS3D };
-	enum { PFH_DESC, FPFH_DESC, PFHRGB_DESC };
-	enum { SLDA, SVM };
-
+	enum : unsigned char { TRAIN, TEST, DESC, CLUST, TRAIN_PRED, TEST_PRED, ALL };
 
 };
 

### 2013-12-15 src/Common/Utils.cpp

@@ -1,0 +1,22 @@
+/*
+ * Utils.cpp
+ *
+ *  Created on: 14 gru 2013
+ *      Author: adam
+ */
+
+#include "Utils.h"
+
+namespace Tagger3D {
+
+Utils::Utils() {
+	// TODO Auto-generated constructor stub
+
+}
+
+Utils::~Utils() {
+	// TODO Auto-generated destructor stub
+}
+
+} //namespace Tagger3D
+

### 2013-12-15 src/Common/Utils.h

@@ -1,0 +1,25 @@
+/*
+ * Utils.h
+ *
+ *  Created on: 14 gru 2013
+ *      Author: adam
+ */
+
+#ifndef UTILS_H_
+#define UTILS_H_
+
+#include <memory>
+
+namespace Tagger3D {
+class Utils {
+public:
+	Utils();
+	virtual ~Utils();
+
+	template<typename T>
+	static T makeUnique(T obj) {return std::unique_ptr<T>(obj);};
+};
+
+} //namespace Tagger3D
+
+#endif /* UTILS_H_ */

### 2013-12-15 src/Predictor/SldaPredictor.cpp

@@ -1,106 +1,0 @@
-/*
- * SldaPredictor.cpp
- *
- *  Created on: Jul 4, 2013
- *      Author: Adam Kosiorek
- * Description: sLda predictor implementation
- */
-
-#include "SldaPredictor.h"
-
-#include <assert.h>
-
-namespace Tagger3D {
-
-SldaPredictor::SldaPredictor(const std::map<std::string, std::string> &_configMap) : Predictor(_configMap) {
-
-
-	sldaSettings = getParam<std::string>(settingsDir) + "/" + getParam<std::string>( sldaSettingsKey );
-
-	if( !fileExists(sldaSettings) ) {
-		std::runtime_error e("File " + sldaSettings + " does not exist");
-		ERROR(logger, e.what() );
-		throw e;
-	}
-
-	sldaInitMethod = getParam<std::string>( sldaInitMethodKey );
-	sldaModelDir = directory + "/" + getParam<std::string>( sldaModelDirKey);
-	alpha = getParam<float>( alphaKey );
-	numTopics = getParam<int>( numTopicsKey );
-	createSlda();
-	assert( sldaCorpus != nullptr );
-	assert( sldaSet != nullptr );
-	assert( sldaModel != nullptr );
-
-}
-
-SldaPredictor::~SldaPredictor() {}
-
-void SldaPredictor::createSlda() {
-
-	sldaCorpus = std::unique_ptr<corpus>( new corpus() );
-	sldaSet = std::unique_ptr<settings>( new settings() );
-	sldaModel = std::unique_ptr<slda>( new slda() );
-
-	sldaSet->read_settings( const_cast<char*>( sldaSettings.c_str()) );
-}
-
-void SldaPredictor::addImage(const std::vector<int> &vec, const int &label) {
-
-	TRACE(logger, "addImage: adding image with label: " << label);
-
-	sldaCorpus->read_vector( vec, label );
-	imgCount++;
-}
-
-void SldaPredictor::train() {
-
-	TRACE(logger, "train: Starting");
-	if( imgCount == 0 ) {
-
-		std::invalid_argument e("No image has been added");
-		ERROR(logger, "train: " << e.what() );
-		throw e;
-	}
-
-	make_directory( const_cast<char*>( directory.c_str()  ));
-	sldaModel->init(alpha, numTopics, sldaCorpus.get() );
[…]

### 2013-12-15 src/Predictor/SldaPredictor.h

@@ -1,72 +1,0 @@
-/*
- * SldaPredictor.h
- *
- *  Created on: Jul 4, 2013
- *      Author: Adam Kosiorek
- * Description: sLDA predictor class declaration
- */
-
-#ifndef SLDAPREDICTER_H_
-#define SLDAPREDICTER_H_
-
-#include "Predictor.h"
-
-#include "slda/corpus.h"
-#include "slda/utils.h"
-#include "slda/slda.h"
-
-#include <memory>
-
-namespace Tagger3D {
-
-/**
- * sLDA predictor class. Predicts to which category an image belongs to
- */
-class SldaPredictor: public Predictor {
-public:
-
-	/**
-	 * Parametric constructor
-	 * @param _configMap - a map of configuration parameters
-	 */
-	SldaPredictor(const std::map<std::string, std::string> &_configMap);
-
-	/**
-	 * Default descrutor
-	 */
-	virtual ~SldaPredictor();
-
-	void addImage(const std::vector<int> &vec, const int &label);
-	void train();
-	std::vector<int> predict();
-
-private:
-	SldaPredictor();
-	void createSlda();
-	void load();
-
-	std::unique_ptr<settings> sldaSet;
-	std::unique_ptr<corpus> sldaCorpus;
-	std::unique_ptr<slda>	sldaModel;
-
-	// Configuration parameters
-	std::string sldaSettings;
-	std::string sldaInitMethod;
-	std::string sldaModelDir;
-	float alpha;
-	int numTopics;
-
-	//	Configuration keys
-	const std::string sldaSettingsKey = moduleName + "settings";
-	const std::string sldaInitMethodKey = moduleName + "init";
-	const std::string sldaModelDirKey = moduleName + "model";
-	const std::string alphaKey = moduleName + "alpha";
-	const std::string numTopicsKey = moduleName + "num_topics";
-	const std::string settingsDir = moduleName + "settingsDir";
-
-
-
-};
-
-} /* namespace semantic_tagger */
-#endif /* SldaPREDICTER_H_ */

### 2013-12-15 src/Predictor/slda/corpus.cpp

@@ -1,162 +1,0 @@
-// (C) Copyright 2009, Chong Wang, David Blei and Li Fei-Fei
-
-// written by Chong Wang, chongw@cs.princeton.edu
-
-// This file is part of slda.
-
-// slda is free software; you can redistribute it and/or modify it under
-// the terms of the GNU General Public License as published by the Free
-// Software Foundation; either version 2 of the License, or (at your
-// option) any later version.
-
-// slda is distributed in the hope that it will be useful, but WITHOUT
-// ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or
-// FITNESS FOR A PARTICULAR PURPOSE.  See the GNU General Public License
-// for more details.
-
-// You should have received a copy of the GNU General Public License
-// along with this program; if not, write to the Free Software
-// Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA 02111-1307
-// USA
-
-#include "corpus.h"
-#include <assert.h>
-#include <stdio.h>
-
-corpus::corpus()
-{
-	logger = lgr::Logger::getLogger("Main.Predictor.corpus");
-	TRACE(logger, "Creating corpus");
-    num_docs = 0;
-    size_vocab = 0;
-    num_classes = 0;
-    num_total_words = 0;
-}
-
-corpus::~corpus()
-{
-    for (int i = 0; i < num_docs; i ++)
-    {
-        document * doc = docs[i];
-        delete doc;
-    }
-    docs.clear();
-
-    num_docs = 0;
-    size_vocab = 0;
-    num_classes = 0;
-    num_total_words = 0;
-}
-
-void corpus::read_vector(const vector<int> &vec, const int &label){
-
-	std::map<int, int> unigram_map; //word<->count
-	std::map<int,int>::iterator it;
-
-	TRACE(logger, "Reading vector");
-
-
-	for (auto &it : vec)
-	    unigram_map.insert ( std::pair<int,int>(it, 0) );
-
-	for (auto &it : vec)
-		unigram_map[it] += 1;
-
-	TRACE(logger, "map size: "<< unigram_map.size() );
-
-	document * doc = new document(unigram_map.size());
-
-	int nw = 0;
-
-	int counter = 0;
-	for (std::map<int,int>::iterator it=unigram_map.begin(); it!=unigram_map.end(); ++it) {
-
-		doc->words[counter]= it->first;
-		doc->counts[counter]= it->second;
-		doc->total += it->second;
-		if (it->first >= nw){
-			nw = it->first + 1;
-		}
[…]

### 2013-12-15 src/Predictor/slda/corpus.h

@@ -1,90 +1,0 @@
-// (C) Copyright 2009, Chong Wang, David Blei and Li Fei-Fei
-
-// written by Chong Wang, chongw@cs.princeton.edu
-
-// This file is part of slda.
-
-// slda is free software; you can redistribute it and/or modify it under
-// the terms of the GNU General Public License as published by the Free
-// Software Foundation; either version 2 of the License, or (at your
-// option) any later version.
-
-// slda is distributed in the hope that it will be useful, but WITHOUT
-// ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or
-// FITNESS FOR A PARTICULAR PURPOSE.  See the GNU General Public License
-// for more details.
-
-// You should have received a copy of the GNU General Public License
-// along with this program; if not, write to the Free Software
-// Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA 02111-1307
-// USA
-
-#ifndef CORPUS_H
-#define CORPUS_H
-
-#include "../../Common/logger.h"
-
-#include <vector>
-#include <map>
-#include<iostream>
-#include <cstddef>
-
-using namespace std;
-
-class document
-{
-public:
-    int * words;
-    int * counts;
-    int length;
-    int total;
-    int label;
-public:
-    document()
-    {
-        words = NULL;
-        counts = NULL;
-        length = 0;
-        total = 0;
-        label = -1;
-    }
-    document(int len)
-    {
-        length = len;
-        words = new int [length];
-        counts = new int [length];
-        total = 0;
-        label = -1;
-    }
-    ~document()
-    {
-        if (words != NULL)
-        {
-            delete [] words;
-            delete [] counts;
-            length = 0;
-            total = 0;
-            label = -1;
-        }
-    }
-};
-
-class corpus
-{
-public:
-    corpus();
-    ~corpus();
-    void read_data(const char * data_filename, const char * label_filename);
-    void read_vector(const vector<int>&, const int&);
-    int max_corpus_length();
-    int num_docs;
-    int size_vocab;
-    int num_classes;
-    int num_total_words;
-    vector<document*> docs;
-
-private:
-    lgr::LoggerPtr logger;
-};
-
-#endif // CORPUS_H

### 2013-12-15 src/Predictor/slda/slda.cpp

@@ -1,1164 +1,0 @@
-// (C) Copyright 2009, Chong Wang, David Blei and Li Fei-Fei
-
-// written by Chong Wang, chongw@cs.princeton.edu
-
-// This file is part of slda.
-
-// slda is free software; you can redistribute it and/or modify it under
-// the terms of the GNU General Public License as published by the Free
-// Software Foundation; either version 2 of the License, or (at your
-// option) any later version.
-
-// slda is distributed in the hope that it will be useful, but WITHOUT
-// ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or
-// FITNESS FOR A PARTICULAR PURPOSE.  See the GNU General Public License
-// for more details.
-
-// You should have received a copy of the GNU General Public License
-// along with this program; if not, write to the Free Software
-// Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA 02111-1307
-// USA
-
-#include "slda.h"
-#include <time.h>
-#include "utils.h"
-#include "assert.h"
-#include "opt.h"
-#include <gsl/gsl_multimin.h>
-#include <gsl/gsl_rng.h>
-#include <gsl/gsl_randist.h>
-#include "float.h"  // to use DBL_MAX
-
-
-#include <iostream>
-
-
-
-const double lowest_double = -DBL_MAX;
-const int NUM_INIT = 50;
-const int LAG = 10;
-const int LDA_INIT_MAX = 0;
-const int MSTEP_MAX_ITER = 50;
-
-slda::slda()
-{
-	logger = lgr::Logger::getLogger("Main.Predictor.slda");
-	TRACE(logger, "Creating SLDA");
-    //ctor
-    alpha = 1.0;
-    num_topics = 0;
-    num_classes = 0;
-    size_vocab = 0;
-
-    log_prob_w = NULL;
-    eta = NULL;
-    showResults = false;
-    showAverage = false;
-}
-
-slda::~slda()
-{
-	TRACE(logger, "Destroying SLDA");
-    free_model();
-}
-
-/*
- * init the model
- */
-
-void slda::init(double alpha_, int num_topics_,
-                const corpus * c)
-{
-    alpha = alpha_;
-    num_topics = num_topics_;
-    size_vocab = c->size_vocab;
-    num_classes = c->num_classes;
-
-    log_prob_w = new double * [num_topics];
-    for (int k = 0; k < num_topics; k++)
-    {
[…]

### 2013-12-15 src/Predictor/slda/slda.h

@@ -1,96 +1,0 @@
-// (C) Copyright 2009, Chong Wang, David Blei and Li Fei-Fei
-
-// written by Chong Wang, chongw@cs.princeton.edu
-
-// This file is part of slda.
-
-// slda is free software; you can redistribute it and/or modify it under
-// the terms of the GNU General Public License as published by the Free
-// Software Foundation; either version 2 of the License, or (at your
-// option) any later version.
-
-// slda is distributed in the hope that it will be useful, but WITHOUT
-// ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or
-// FITNESS FOR A PARTICULAR PURPOSE.  See the GNU General Public License
-// for more details.
-
-// You should have received a copy of the GNU General Public License
-// along with this program; if not, write to the Free Software
-// Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA 02111-1307
-// USA
-
-#ifndef SLDA_H
-#define SLDA_H
-
-#include "../../Common/logger.h"
-#include "settings.h"
-#include "corpus.h"
-
-typedef struct {
-    double * z_bar_m;
-    double * z_bar_var;
-} z_stat;
-
-typedef struct {
-    double ** word_ss;
-    double * word_total_ss;
-    int num_docs;
-    z_stat * z_bar;
-    int * labels;
-    int * tot_labels;
-} suffstats;
-
-class slda
-{
-public:
-    slda();
-    ~slda();
-    void free_model();
-    void init(double alpha_, int num_topics_, const corpus * c);
-    void v_em(corpus * c, const settings * setting,
-              const char * start, const char * directory);
-
-    void save_model(const char * filename);
-    void save_model_text(const char * filename);
-    void load_model(const char * model_filename);
-    void infer_only(corpus * c, const settings * setting,
-                    const char * directory);
-
-    suffstats * new_suffstats(int num_docs);
-    void free_suffstats(suffstats * ss);
-    void zero_initialize_ss(suffstats * ss);
-    void random_initialize_ss(suffstats * ss, corpus * c);
-    void corpus_initialize_ss(suffstats* ss, corpus * c);
-    void load_model_initialize_ss(suffstats* ss, corpus * c);
-    void mle(suffstats * ss, int eta_update, const settings * setting);
-
-    double doc_e_step(document* doc, double* gamma, double** phi, suffstats * ss, int eta_update, const settings * setting);
-
[…]

### 2013-12-15 src/Predictor/slda/utils.cpp

@@ -1,161 +1,0 @@
-#include "utils.h"
-
-/*
- * given log(a) and log(b), return log(a + b)
- *
- */
-
-double log_sum(double log_a, double log_b)
-{
-    double v;
-
-    if (log_a < log_b)
-        v = log_b+log(1 + exp(log_a-log_b));
-    else
-        v = log_a+log(1 + exp(log_b-log_a));
-
-    return v;
-}
-
-/**
- * Proc to calculate the value of the trigamma, the second
- * derivative of the loggamma function. Accepts positive matrices.
- * From Abromowitz and Stegun.  Uses formulas 6.4.11 and 6.4.12 with
- * recurrence formula 6.4.6.  Each requires workspace at least 5
- * times the size of X.
- *
- **/
-
-double trigamma(double x)
-{
-    double p;
-    int i;
-
-    x = x+6;
-    p = 1/(x*x);
-    p = (((((0.075757575757576*p-0.033333333333333)*p+0.0238095238095238)*p-0.033333333333333)*p+0.166666666666667)*p+1)/x+0.5*p;
-    for (i=0; i<6 ;i++)
-    {
-        x = x-1;
-        p = 1/(x*x)+p;
-    }
-    return p;
-}
-
-
-/*
- * taylor approximation of first derivative of the log gamma function
- *
- */
-
-double digamma(double x)
-{
-    double p;
-    x = x+6;
-    p = 1/(x*x);
-    p = (((0.004166666666667*p-0.003968253986254)*p+0.008333333333333)*p-0.083333333333333)*p;
-    p = p+log(x)-0.5/x-1/(x-1)-1/(x-2)-1/(x-3)-1/(x-4)-1/(x-5)-1/(x-6);
-    return p;
-}
-
-/*
- * this log gamma function has the implementation of this function
- *
- */
-
-/* double lgamma(double x)
- * {
- * double x0,x2,xp,gl,gl0;
- * int n,k;
- * static double a[] = {
- * 8.333333333333333e-02,
- * -2.777777777777778e-03,
- * 7.936507936507937e-04,
- * -5.952380952380952e-04,
- * 8.417508417508418e-04,
- * -1.917526917526918e-03,
- * 6.410256410256410e-03,
- * -2.955065359477124e-02,
- * 1.796443723688307e-01,
- * -1.39243221690590
- * };
- *
- * x0 = x;
[…]

### 2013-12-15 src/Predictor/slda/utils.h

@@ -1,20 +1,0 @@
-#ifndef UTILS_H
-#define UTILS_H
-
-#include <stdio.h>
-#include <math.h>
-#include <float.h>
-#include <stdlib.h>
-#include <sys/stat.h>
-#include <sys/types.h>
-
-double log_sum(double log_a, double log_b);
-double trigamma(double x);
-double digamma(double x);
-//double lgamma(double x);
-void make_directory(char* name);
-int argmax(double* x, int n);
-int map_idx(int row, int col, int dim); 
-
-#endif
-

### 2013-12-15 src/Predictor/svm/svm-train.c

@@ -1,379 +1,0 @@
-#include <stdio.h>
-#include <stdlib.h>
-#include <string.h>
-#include <ctype.h>
-#include <errno.h>
-#include "svm.h"
-#define Malloc(type,n) (type *)malloc((n)*sizeof(type))
-
-void print_null(const char *s) {}
-
-void exit_with_help()
-{
-	printf(
-	"Usage: svm-train [options] training_set_file [model_file]\n"
-	"options:\n"
-	"-s svm_type : set type of SVM (default 0)\n"
-	"	0 -- C-SVC		(multi-class classification)\n"
-	"	1 -- nu-SVC		(multi-class classification)\n"
-	"	2 -- one-class SVM\n"
-	"	3 -- epsilon-SVR	(regression)\n"
-	"	4 -- nu-SVR		(regression)\n"
-	"-t kernel_type : set type of kernel function (default 2)\n"
-	"	0 -- linear: u'*v\n"
-	"	1 -- polynomial: (gamma*u'*v + coef0)^degree\n"
-	"	2 -- radial basis function: exp(-gamma*|u-v|^2)\n"
-	"	3 -- sigmoid: tanh(gamma*u'*v + coef0)\n"
-	"	4 -- precomputed kernel (kernel values in training_set_file)\n"
-	"-d degree : set degree in kernel function (default 3)\n"
-	"-g gamma : set gamma in kernel function (default 1/num_features)\n"
-	"-r coef0 : set coef0 in kernel function (default 0)\n"
-	"-c cost : set the parameter C of C-SVC, epsilon-SVR, and nu-SVR (default 1)\n"
-	"-n nu : set the parameter nu of nu-SVC, one-class SVM, and nu-SVR (default 0.5)\n"
-	"-p epsilon : set the epsilon in loss function of epsilon-SVR (default 0.1)\n"
-	"-m cachesize : set cache memory size in MB (default 100)\n"
-	"-e epsilon : set tolerance of termination criterion (default 0.001)\n"
-	"-h shrinking : whether to use the shrinking heuristics, 0 or 1 (default 1)\n"
-	"-b probability_estimates : whether to train a SVC or SVR model for probability estimates, 0 or 1 (default 0)\n"
-	"-wi weight : set the parameter C of class i to weight*C, for C-SVC (default 1)\n"
-	"-v n: n-fold cross validation mode\n"
-	"-q : quiet mode (no outputs)\n"
-	);
-	exit(1);
-}
[…]

### 2014-01-02 Disseration/introduction.tex
dissertation update

@@
 
-	Capturing visual information of any kind have never been easier.
-Almost everyone of us posses a camera, be it a professional dSLR or a tiny one embedded into one of the ubiquitous smartphones.
-As human beings we have no difficulty understanding this data, just as we have no difficulty understanding what our eyes see.
-Unfortunately, the situation of our computers is the very opposite.
-Storage capacity of modern-day computers is overwhelming.
-But even if hard-drives are full of images it is impossible to identify their semantic meaning without the aid of specialised algorithms, however.
-These algorithms often balance on the verge of image processing and machine learning --- they are a part of an area called computer vision.
-As Forsyth and Ponce \cite{ponce2011cv} have it: \begin{quote} computer vision is (...) an enterprise that uses statistical methods to disentangle data using models constructed with the aid of geometry, physics, and learning theory.\end{quote} The area of computer vision is not new.
-The original applications were industrial inspection or mobile robot navigation.
-More recent approaches consider problems such as human-machine interfaces, medical diagnostics, or image retrieval.
+	Capturing visual information have never been easier.
+Terabytes of photographs and movies are uploaded on the Web every day, causing unprecedented growth of popular storage services.
+The traditional means of annotation cease to suffice.
+Hand-tagging and description have strong cultural dependencies and introduce ambiguity.
+Without any better solution, databases become increasingly harder to navigate and browse.
+Matters could have been better if computers understood content they deal with.
+But even the latest software is far from and cannot be considered intelligent in general terms.
+On the other hand, an area of machine learning define routines for learning complex and strongly non-linear functions mapping an arbitrary input to a given set of outputs.
+This is how computer vision can be used to make sense of any visual content, provided that there is enough data.
+As Forsyth and Ponce \cite{ponce2011cv} have it:
+
+	\begin{quote} 
+		computer vision is (...) an enterprise that uses statistical methods to disentangle data using models constructed with the aid of geometry, physics, and learning theory.
+	\end{quote}
+
+	The area of computer vision is not new and have initially dealt with industrial inspection or mobile robot navigation.
+Recent applications include human-machine interfaces, medical diagnostics and image retrieval.
 

### 2014-01-03 Disseration/introduction.tex
aa

@@
 
-	Capturing visual information have never been easier.
-Terabytes of photographs and movies are uploaded on the Web every day, causing unprecedented growth of popular storage services.
-The traditional means of annotation cease to suffice.
-Hand-tagging and description have strong cultural dependencies and introduce ambiguity.
-Without any better solution, databases become increasingly harder to navigate and browse.
-Matters could have been better if computers understood content they deal with.
-But even the latest software is far from and cannot be considered intelligent in general terms.
-On the other hand, an area of machine learning define routines for learning complex and strongly non-linear functions mapping an arbitrary input to a given set of outputs.
-This is how computer vision can be used to make sense of any visual content, provided that there is enough data.
+	It has never been easier to capture visual information.
+Popular storage services grow lighting fast due to terabytes of photographs and movies we upload every day.
+The growth is so fast that hand-tagging and description, the traditional means of annotation, cease to suffice.
+They are ambiguous, emotional and rarely optimal.
+With no better solution at hand, databases are becoming increasingly harder to browse.
+Another, but quite similar setting occurs in the field of mobile robotics.
+A mobile robot is there to interact with its enviornment.
+If so, it would be desirable for the robot to know what kind of an enviornment it is in.
+The problem can be treated as a scene or object classification problem, one of the most popular computer vision issues in the last decade.
 As Forsyth and Ponce \cite{ponce2011cv} have it:
@@
 
-	How about semantic classification of scenes or objects?
-Suppose a mobile robot would know, or understand, what does it have to deal with.
-Suppose a robot would know that it is about to take, say, a glass of water.
-How would it affect the robot's behaviour?
-Could it have any impact on the force of the grip?
-or the speed and the manner of the planned object movement?
-Answers for all this questions are yes.
-Semantic classification is possible, but it requires clever mechanisms of computer vision and powerful computers.
-It can be seen as a part of a more general classification problem, which machine learning handles quite well.
-Suitable algorithms include, but are not limited to, artificial neural networks, deep belief networks, logistic regression, support vector machines and approaches based on probabilistic graphical models.
-One has to bear in mind that none of them can handle the problem directly.
-That is, it is inconceivable to feed a whole image as is into a classifier --- some degree of preprocessing is required.
-One such preprocessing technique is translation of image into a feature vector.
-What should this vector comprise of?
-A Bag of Words model is one technique that answers this question.
-This model has been first used for scene classification in 2004 in \cite{csurka2004visual} and maintains its popularity ever since.
+	This paper tackles two issues.
+Firstly, the Bag of Words approach to image classification is reviewed.
+The Bag of Words approach for classification has originated from the text document classification domain.
+The approach makes a strong assumption that word occurance define the meaning of the document.
+It was first used for image classification in 2004 by Csurka \textit{et al} \cite{csurka2004visual}.
+Since we cannot simply translate an image to natural language a pipeline that help us achieve this goal is needed.
+It usually consist of steps such as keypoint detection, feature extraction, vector quantization and, finally, classification.
 
-	In this paper a technique for semantic object classification based on three dimensional point clouds is presented.
+	Secondly, a configurable and flexible application for point cloud classification is designed and implemented in C++.
+There are many algorithms suitable for the bag of words pipeline.
+In order to choose an optimal solution for a specific problem extensive evaluation of the algorithms have to be performed.
+The process can be greatly simplified by a programme that would be: (1) easily extensible, that is adding new algorithms wold be painless and (2) configurable, with every parameter (and algorithm) adjustable at runtime.
+
+       \section{scope and purpose of this work}
+       The goal of this work is to design a flexible and configurable application for point cloud classification.
+The point cloud should be registered by the Microsoft Kinect.
+The scope of the work is as follows:
+       \begin{itemize}
+        \item literature review in the area of bag of words image classification
+        \item design of a pipeline for bag of words classification of point clouds
+        \item design of a configurable programme for point cloud classification
+        \item implementation of the programme in C++ using OpenCV and/or PointCloud Library
+        \item evaluation of algorithms for bag of words classification
+        \item evaluation of the programme on two scientific point cloud databases
+       \end{itemize}
+
 	The rest of this chapter is organised as follows: Section 1 describes the Bag of Words technique in detail.

### 2014-01-04 Disseration/introduction.tex
przeredagowane 1/2

@@
 With no better solution at hand, databases are becoming increasingly harder to browse.
-Another, but quite similar setting occurs in the field of mobile robotics.
-A mobile robot is there to interact with its enviornment.
-If so, it would be desirable for the robot to know what kind of an enviornment it is in.
+Another but quite similar setting occurs in the field of mobile robotics.
+A mobile robot is there to interact with its environment.
+If so, it would be desirable for the robot to know what kind of surroundings it is in.
 The problem can be treated as a scene or object classification problem, one of the most popular computer vision issues in the last decade.
@@
 	This paper tackles two issues.
-Firstly, the Bag of Words approach to image classification is reviewed.
-The Bag of Words approach for classification has originated from the text document classification domain.
-The approach makes a strong assumption that word occurance define the meaning of the document.
-It was first used for image classification in 2004 by Csurka \textit{et al} \cite{csurka2004visual}.
-Since we cannot simply translate an image to natural language a pipeline that help us achieve this goal is needed.
-It usually consist of steps such as keypoint detection, feature extraction, vector quantization and, finally, classification.
+Firstly, the Bag of Words (or BoW for short) approach to image classification is reviewed.
+The Bag of Words method has originated from the natural language processing domain \rednote{ref}.
+It makes a strong assumption that the word occurrence in a text document define the meaning of the document.
+It were Csurka \textit{et al} who have first used BoW for image classification in 2004 \cite{csurka2004visual}.
+Since we cannot simply translate an image into natural language a pipeline that help us achieve this goal is needed.
+It usually consist of: keypoint detection, feature extraction, vector quantization and classification, steps that will be discussed later.
 
 	Secondly, a configurable and flexible application for point cloud classification is designed and implemented in C++.
-There are many algorithms suitable for the bag of words pipeline.
-In order to choose an optimal solution for a specific problem extensive evaluation of the algorithms have to be performed.
+Many algorithms are suitable for the bag of words pipeline.
+To choose an optimal combination for a specific problem we have to perform extensive evaluation of those algorithms.
 The process can be greatly simplified by a programme that would be: (1) easily extensible, that is adding new algorithms wold be painless and (2) configurable, with every parameter (and algorithm) adjustable at runtime.
+
+	The rest of this work is organised as follows: Section 1 summarises purpose and scope of this work.
+Section 2 describes the Bag of Words technique in detail.
+Construction of an image model is discussed and the most popular algorithms are outlined.
+Section 3 provides basic information on the problem of classification, introduces basic concepts and methods of classification.
+Section 4 names C++ computer vision and general purpose libraries used in this project.
+Finally, in Section 6 we describe two renown RGBD image datasets we have chosen to test our application at.
+The following chapters are titled ``Design'' and ``Experiments and Results''.
+The former analyses functionality of a programme for BoW object classification, its design and implementation details.
+The latter addresses the topics of experimental setup, performed experiments and a summary of results.
 
@@
 		The goal of this work is to design a flexible and configurable application for point cloud classification.
-The point cloud should be registered by the Microsoft Kinect.
+The point cloud should be registered by the Microsoft Kinect RGBD camera.
 The scope of the work is as follows:
@@
 		\item implementation of the programme in C++ using OpenCV and/or PointCloud Library
-        \item evaluation of algorithms for bag of words classification
-        \item evaluation of the programme on two scientific point cloud databases
+		\item evaluation of algorithms for the bag of words classification
+		\item evaluation of the programme on two scientific RGBD object databases
 		\end{itemize}
-
-	The rest of this chapter is organised as follows: Section 1 describes the Bag of Words technique in detail.
-Construction of an image's model is discussed and the most popular algorithms are summarised.
-Section 2 provides basic information on the problem of classification, introduces basic concepts and methods of classification.
-Section 3 names C++ computer vision and general purpose libraries used in this project.
-Finally in Section 4 two datasets of RGBD images are outlined.
-The following chapters are titled ``Design'' and ``Experiments and Results''.
-The former contains description of required functionality of a programme for BoW object classification, its design and implementation details.
-The latter addresses topics of experimental setup, performed experiments and a summary of results.
 
@@
 
-	The Bag of Words (BoW) model is a an intermediate representation used in natural language processing, information retrieval and data mining [need pub].
+	The Bag of Words model is a an intermediate representation used in natural language processing, information retrieval and data mining \rednote{pub}.
 The model can be seen as a simplification, for it obliterates any grammatical information and even word order contained within an original text document.
@@
 One can image that if a dictionary is of any considerable size resulting representation of especially small documents will be very sparse.
+Classification algorithms can be optimised for sparse data in order to boost performance.
 
-	In natural language processing BoW representation is used to infer semantic meaning of documents [need pub].
-If an image could be translated into a text document it might be possible to employ similar methods.
+	In natural language processing BoW is used to infer semantic meaning of documents \rednote{pub}.
+If we could translate an image into a text document we might be able to employ similar methods.
 A question arises: How does one make a text document from an image?
@@
 	\subsection{Processing Pipeline}	
-	Tsai describes a well established pipeline that allows translation of images into text documents or BoW models \cite{tsai2012bag}.
+	Tsai describes a well established pipeline that allows translation of images into text documents \cite{tsai2012bag}.
 It consists of the following steps: (1) region detection, (2) feature extraction, (3) vector quantization and (4) BoW histogram formation as can be seen in the figure \ref{fig:bow_pipeline}.
@@
 Numerous detection methods have been developed, but choosing the right one for any particular case might prove tricky.
-A good overview of various mechanisms is available in \cite{tsai2012bag}.
 
+		\rednote{describe fundamentals of keypoint detection in greater detail}
 		The most common detectors make use of a Harris corner detector or image's first or second derivatives.
@@
 
-		A number of more complicated recipes for salient region localisation have been developed and implemented.
+		A number of more advanced recipes for salient region localisation have been developed and implemented.
 These include for example SIFT \cite{sift_keypoint}, SUSAN \cite{susan_keypoint} and Intrinistic Shape Signatures \cite{iss_keypoint}.
@@
 That is, take a uniformly sampled grid of points.
-Dense detectors, unlike the sparse ones, take points from slow changing regions such as clear sky and calm ocean water.
-Li \emph{et al} showed that dense detectors generally outperform the sparse ones \cite{fei2005bayesian}.
+Dense detectors have an advantage in that they sample slow changing regions in terms of gradient or hessian of an image.
+Examples of such regions would be a clear sky or a calm ocean.
+Li \emph{et al} showed that dense detectors generally outperform sparse ones \cite{fei2005bayesian}.
 
 		\subsubsection{Feature Extraction}
-		Suppose only coordinates of a keypoint were found.
-In case of even smallest rotation or translation they would change and the keypoint would be lost.
-Keypoints should be described in a way that makes them invariant to affine transforms, changes in light intensity or colour saturation.
-All these properties are hard to achieve, but methods that meet some of the criteria exist.
+		Suppose only coordinates of a keypoint were known.
+In case of even the smallest rotation or translation they would change and the keypoint would be lost.
+Keypoints should be described in a way that makes them invariant to affine transformations, changes in light intensity or colour saturation.
+It is hard to achieve all of these properties simultaneously, but methods that meet some of them exist.
 
-		Keypoint description is usually delivered in a form of coordinates in a high-dimensional space.
-One of the best algorithms is SIFT \cite{sift_features}, which is 3D histogram of gradients structured as a 128-dimensional vector of floating point values.
-It is the most often extracted descriptor in BoW pipelines.
+		Keypoint description takes form of coordinates in a high-dimensional space.
+One of the most precise and repeatable algorithm is SIFT \cite{sift_features}, which is a 3D histogram of gradients structured as a 128-dimensional vector of floating point values.
+It is the most often extracted descriptor in BoW pipelines \rednote{ref}.
 Other methods include various colour descriptors, binary descriptors such as 512-dimensional GIST \cite{ponce2011cv}.
@@
 Vector quantization step have two main phases.
-The first one is codebook construction from a training dataset.
+The first one is a codebook construction from a training dataset.
 The second phase is responsible for parsing (or translation) raw image descriptors into a form compatible with the newly constructed codebook.
-The simplest way of building a dictionary is to find patterns or regions within the training dataset's descriptors.
-Then, the parsing phase would be nothing but assigning each descriptor to a certain region.
-Such an assignment can performed by a k-Nearest-Neighbours match.
-Slightly more advanced techniques of dictionary building involve using many kinds of descriptors, i.e.
-texture, shape and colour descriptors, or spatial information.
+The simplest way of building a dictionary is to find patterns or regions within the descriptors computed on a training dataset.
+Then, the parsing phase is about assigning a descriptor to one of the codebook elements (e.g.
+to one of the regions).
+Suppose we use centroids or medoids of the discovered regions as our codebook's entries.
+Then, we can match a descriptor to one of the centroids performing a nearest neighbour search.
+The descriptor parsed this way is called a \textit{visual word}.
+Finally, we build a histogram of visual word occurrence.
+The histogram have a fixed size equal to the codebook size.
+Each bin of the histogram tells us how many visual words of a particular kind were in the description of the corresponding image.
 
-		The KMeans is the single most popular vector quantization algorithm used in the BoW pipelines \cite{tsai2012bag}.
-Developed in 1950's, it is well known and simple.
+		The kMeans is the single most popular vector quantization algorithm used in the BoW pipelines \cite{tsai2012bag}.
+Developed in 1950's, it is well known and simple to implement.
 kMeans divides all data into a predefined amount of clusters and computes the clusters' centroids.
 Many modifications and alternative versions have emerged \cite{kmeans_jain2010data}.
-Some of them are: faster than the original \emph{approximate kmeans}, \emph{hierarchical kmeans}, which automatically chooses the final number of clusters and a  \emph{soft kmeans} --- a variation of the algorithm that allows a fuzzy alignment (\textit{i.e.} each point can belong to several clusters with different weights).
-Vector quantization is responsible for the dictionary size, for the clusters' centroids are (in a simple approach) synonymous to the visual words.
-Thus the higher the number of clusters, the bigger the dictionary, which in turn allows for a more precise image description.
+Some of them are: faster than the original \emph{approximate kmeans}, \emph{hierarchical kmeans}, which automatically chooses the final number of clusters and a \emph{soft kmeans} --- a variation of the algorithm that allows a fuzzy alignment.
+The fuzzy alignment mean that each point can belong to several clusters with different weights.
+A weight can be proportional for instance to the inverse square of the distance to a centroid.
 
 		If computational cost is of no concern, or if required precision is of the utmost priority, a Gaussian Mixture Model (GMM) can be used.
-The GMM partitions data into a set of clusters and finds their centroids.
-Additionally, it computes a probability distribution over each cluster, i.e.
-for every point its probability of membership in each cluster is returned.
-Both kMeans and soft-kMeans are specific variants of the GMM.
+The GMM partitions data into a set of clusters, finds their means and covariances.
+In the parsing step we compute a probability distribution of a descriptor over all the clusters.
+We can then build a fuzzy aligned histogram taking the probability distribution as weights.
+The GMM can be thought of as a generalisation of the kMeans algorithm.
 The drawback of the GMM is its massive computational cost in comparison with still expensive kMeans.
+Recently, Perronnin \textit{et al} proposed GMM based fisher-kernel vector quantization step with superior results \cite{fisher1, fisher2}.
 
-		It should be underlined that the vector quantization step, especially the codebook construction process, is the most time-consuming part of the whole Bag of Words pipeline.
+		After we choose a vector quantization algorithm, we have to decide what size of a dictionary to use.
+In a simplest case, when the kMeans is used, we can treat each clusters' centroid as a visual word.
+Therefore, the dictionary size defines how much information we retain in a BoW histogram.
+A big training set containing many classes with large inter-class and inter-class variance is likely to require a huge codebook.
+On the other hand, too big a dictionary might introduce quantization artefacts.
+One has to bear in mind that the vector quantization step is the most time-consuming part of the BoW pipeline.
+The highest computational complexity is associated with the codebook construction step and it is$O(n^3)$, where $n$ is the codebook size.
+
+		It is possible to combine several feature extraction algorithms before creating the codebook (Early Fusion) or create many codebooks and concatenate resulting histograms (Late Fusion).
+Both schemes are as simple as vector concatenation.
+The Early Fusion concatenates two feature vectors if they have been extracted from the same keypoint.
+The Late Fusion joins histograms, outputted by separate quantization steps.
 
 	\subsection{Applications in Computer Vision}
-	The Bag of Words model is nothing but an intermediate representation. As such it is mainly used in the two following areas: Content Based Image Retrieval (CBIR) and Scene/Object Classification.
+	The Bag of Words approach is a tool than enables us to represent an image by a single feature vector of a chosen size.
+Its most popular applications in computer vision are Content Based Image Retrieval (CBIR) and Scene/Object Classification.
 
@@
 Tangelder \emph{et al} provides an overview of techniques applicable to 3D objects \cite{tangelder2008survey}.
-The task of image retrieval is to find a database entry fulfilling certain conditions.
-If it is to be performed efficiently several criteria have to be met \cite{toldo2009bag}, namely: (1) All entries should be indexed in a concise way, (2) a (dis)similarity measure should be provided and (3) an efficient search algorithm should be available.
+The task of image retrieval is to find a database entry that fulfil certain conditions.
+If we wanted to perform the task efficiently, we would have to meet the following criteria \cite{toldo2009bag}: (1) All entries should be indexed in a concise way, (2) a (dis)similarity measure should be provided and (3) an efficient search algorithm should be available.
 
-		Indexing of objects is required so as not to compare the database entries explicitly.
-Therefore, for every object in a dataset a compact as well as a discriminative signature should be computed.
+		Database entries (images) should be indexed beforehand.
+Otherwise we would have to compare all the entries explicitly.
+An index must be compact as well as discriminative.
 Suitable algorithms can be divided into three general categories: (1) feature based methods, (2) graph based methods and (3) other methods.
@@
 Being easy to compute and straightforward to implement, their discriminative power is rather low --- they cannot be used for partial matching, but are well suited for an early preprocessing.
+
 		Local features, on the other hand, describe object's characteristic regions.
@@
 
+		Feature based methods can be either local or global.
+Local features describe characteristic regions of an object, which have to be identified first.
+We have to carry out similar computation for each salient region.
+An outcome is a set of vectors, one vector for each region in \emph{d} dimensional space, where \emph{d} is dimensionality of the descriptor.
+Global features are generally easier (faster) to compute and more compact --- they take form of a single \emph{d} dimensional vector.
+Often global features are more computationally efficient and can be easily used for object indexing .
+Before the advent of BoW it was not clear how to use local features for indexing, nor there was any straight-forward dissimilarity measure available \cite{tangelder2008survey}.
+The Bag of Words approach solved these issues.
+What is more, it is easy to implement, efficient and provides state-of-the-art results \cite{li2010investigating}.
+
 		\subsubsection{Scene and Object Classification}
-		Inspired by various works on pattern recognition and texture classification and an idea of a ``texton``, a building block from which textures are made, Csurka \emph{et al} is the first to apply the Bag of Words paradigm to the task of scene classification \cite{csurka2004visual}.
-In their early work authors suggested a a general framework described above.
-After translating images into text documents BoW histograms were built and fed into two classifiers: SVM and Na\`ive Bayes (discussed below).
+		Scene and object classification are among the most popular issues of computer vision nowadays \rednote{ref}.
+We would like to perform those tasks automatically for the sake of surveillance, navigation or automatic image tagging.
+The very first attempt to use BoW in scene classification was made by Csurka \textit{et al} in 2004 \cite{csurka2004visual}.
+They were inspired by an idea of a ``texton'', a building block of texture introduced earlier in pattern recognition and texture classification.
+The authors suggested a BoW pipeline described above.
+Then, they fed the resulting BoW histograms into two classifiers: Support Vector Machine (SVM) and Na\`ve Bayes (both discussed below).
+Fei-Fei \emph{et al} refined the original approach by examining several keypoint detectors and descriptors \cite{fei2005bayesian}.
+Moreover, they developed a novel probabilistic graphical model for classification.
+They achieved accuracy of 76\% on a large 13 category dataset.
 
-		Fei-Fei \emph{et al} refined the above approach by examining several keypoint detectors and descriptors.
-The main contribution of their work is, however, the development of a genuine classification algorithm based on a probabilistic graphical model.
-Accuracy of 76\% on a large 13 category dataset was achieved.
-		Object categorisation can be addressed in the same way.
-The only difference is that a bounding box of an object (or knowledge of object's coordinates) can be helpful.
-On the other hand, it is possible to consider an object classification problem where images of singled-out objects are provided --- e.g.
-a single object covers a majority of image's area like in \cite{zhangcategory}.
-
-		Classification is not an integral part of the BoW pipeline. But the Bag of Words histograms can be used as a compact and discriminative representation that can be fed into any classifier.
+		One of the best entries in an ILSVRC2013\footnote{\url{http://www.image-net.org/challenges/LSVRC/2013/results.php}} challenge, attempting to classify millions of images into 1000 categories, was submitted by a fisher vector based BoW approach as well.
+The top-5\footnote{top-5 --- the classification result is successful if the ground-truth category is in one of the five most probable categories predicted} accuracy rate was close to 85\%.
 
@@
 
-	%What is classification?
-	%Why does machine learning apply? What advantages does it give?
-
-	%Discriminative vs Generative approach
-	%Overview of algorithms: kNN, logistic regression, SVM, NN, PGM, Naive Bayes
 	To classify means to, given a set of categories, produce a category label for a given set of features \cite{ponce2011cv}.
-Many problems might not seem like classification problems and image categorisation is one of them.
-Images are too complex to be processed by any classifier directly.
-We can think that there are too many details, too many aspects that decide whether a picture fits into a category or not.
-But it turns out that many problems can be abstracted in such a way that they become pure classification problems.
-One such abstraction for photographs or point clouds is the Bag of Words model.
+Image classification fits this description perfectly.
+The only difficulty lies in complexity of a raw image.
+Suppose we have a $320$ by $240$ three channel colour image.
+This amounts to a total of $230400$ dimensions, far too many to feed into any classifier directly.
+Fortunately, a Bag of Words histogram is a compact and discriminative intermediate representation that solves this issue.
+It can be used with any classifier.
 Classifiers can be two-class classifiers (e.g.
 binary) or multi-class classifiers.
-It is a common practice to build multi-class classifiers from binary ones, however.
-The most popular classifiers are: k-Nearest Neighbours, Logistic Regression, Na\`ive Bayes and Support Vector Machine.
+The latter are often a combination of several binary classifiers.
+The most popular classifiers are: k-Nearest Neighbours, Logistic Regression, Softmax Regression, Na\`ive Bayes and Support Vector Machine.
 
@@
 
-	\subsubsection{k-Nearest Neighbours}
+	\subsubsection{k-Nearest Neighbours (kNN)}
 	The nearest neighbours classifier assumes that if there are labelled points in a neighbourhood of a newly added point, then the new point can be classified based on it's neighbours' labels.
-There is an issue of choosing the correct number of nearest neighbours (or k) to consider
+There is an issue of choosing the correct number of nearest neighbours (or k) to consider.
 
-	\subsubsection{Support Vector Machine}
+	\subsubsection{Support Vector Machine (SVM)}
 	\begin{figure}[!ht]
@@
 Further assume that points with different labels are two linearly-separable datasets as shown in the figure \ref{fig:svm}, where dots and circles are points with different labels.
-Then, there exist parameters \textbf{\textit{w}} and  \textit{b} which satisfies
+Then, parameters \textbf{\textit{w}} and  \textit{b} exist such that
 	\begin{equation}
-	                        y_\mathit{i}\left(\mathbf{w}*\mathbf{x}_\mathit{i} + w\right) > 0
+	                        y_\mathit{i}\left(\mathbf{w}*\mathbf{x}_\mathit{i} + b\right) > 0
 	                                                                                                                                                                                                                                                                                                                                                                                                                                               \end{equation}
 	for every $\mathbf{x}_\mathit{i}$ or a data point.
-This equation specifies constraints on a plane (or a hyperplane in general) that separates the dataset.
-A Support Vector Machine finds parameters \textbf{\textit{w}} and  \textit{b} so as to maximise the distance of this plane from both datasets.
+This equation specifies constraints on a plane (or a hyperplane in general) that separates different classes.
+A Support Vector Machine finds the parameters \textbf{\textit{w}} and  \textit{b} so as to maximise the distance of the plane from members of both classes.
+We can combine several SVM classifiers in a 1-versus-all or an all-versus-all scheme.
 
@@
 
-	One of the advantages of object oriented programming is that it is easier to reuse once created code.
-There exists a variety of third party libraries for the C++ programming language.
-One of the biggest and the most widely used are the general purpose Boost libraries \cite{Boost}.
-In the fields of computer vision there are, among others, OpenCV \cite{OpenCV} and PointCloud Library \cite{PCL}.
-Easy to use and intuitive logging is provided by the Apache log4cxx \cite{log4cxx}.
+	We use the following third party libraries in this work:
+	\begin{itemize}
+	 \item Boost\footnote{\url{http://www.boost.org/}} --- of the biggest general purpose libraries
+	 \item OpenCV\footnote{\url{http://opencv.org/}} --- a general computer vision library
+	 \item PointCloud Library\footnote{\url{http://pointclouds.org/}} \cite{PCL} --- a library for point cloud processing
+	 \item libsvm\footnote{\url{http://www.csie.ntu.edu.tw/~cjlin/libsvm/}} \cite{libsvm} --- a renown and very efficient SVM classifier implementation
+	 \item Apache log4cxx\footnote{\url{http://logging.apache.org/log4cxx/}} --- Easy to use and intuitive logger
+	\end{itemize}
 

### 2014-01-06 Disseration/architecture.tex
done editing, now have to run some tests

@@
 \section{Software Functionality and Architecture}
-	The programme resulting from this work is called ``Tagger3D'', for it's purpose is to tag an RGBD image of an object with a category label.
-The Bag of Words classification pipeline consists of four main parts discussed previously.
-In order to determine the best combination of algorithms for any given task an extensive research and evaluation has to be performed.
-In order to simplify the process the software system should be configurable, extensible and easy to maintain.
-Moreover, if it is to be used in any realistic setting it has to be efficient as well.
+
+	We have decided to call our project ``Tagger3D''.
+Since the purpose is to classify (or tag) point clouds, the name seems suitable.
+An optimal combination of algorithms for a bag of words pipeline is task and data specific.
+To find a combo of routines that yields superior performance we have to evaluate numerous algorithms.
+The process can be simplified; We are going to design an application that can be easily configured and extended.
+It should be possible to configure and choose an algorithm at run-time.
+Moreover, it should enable real time classification if it is to be used in any real setting.
 
 	\subsection{Required functionality}	
-	There are three major functions that have to be supplied by the programme: (1) estimation, (2) batch inference and (3) inference.
-The first one is responsible for the model training.
-In order to perform this operation the following steps have to be completed: (i) detection and description of keypoints on the training set, (ii) codebook generation, (ii) classifier model training.
-The functions (2) and (3) are somewhat similar.
-Both require: (i) detection and description of keypoints on the test set, (ii) parsing keypoints' description into a visual vocabulary description and (iii) classification.
-The only is in the (i) step, e.g.
-the batch inference requires every image from the test set to be processed, whereas the inference can be done on any single image.
-The (3) have to be distinguished because it is the function that is to be used in a fully functional system mounted on i.e.
-a mobile robot.
+	There are three major functions that have to be supported by the programme:
+	\begin{enumerate}
+	 \item train --- performs training
+	 \item test --- evaluates the previously trained classifier
+	 \item infer --- predicts a category of a single object
+	\end{enumerate}
+
+	Before any of them can be implemented, we have to identify common features.
+Inference and testing is very similar.
+The only difference is that the latter should process a whole testing dataset and compute statistics.
+The inference and training processes looks as follows:
+
+	\begin{tabular}{p{0.5\textwidth}p{0.5\textwidth}}
+		Inference:
+		\begin{enumerate}
+			\item RGBD image reading and preprocessing
+			\item Point cloud construction
+			\item Salient region identification
+			\item Feature Extraction
+			\item Vector Quantization
+			\item Classification
+		\end{enumerate} 
+		&
+		Training:
+		\begin{enumerate}
+		\item RGBD image reading and preprocessing
+		\item Point cloud construction
+		\item Salient region identification
+		\item Feature Extraction
+		\item Codebook Construction
+		\item Vector Quantization
+		\item Classificator training
+		\end{enumerate} \\
+	\end{tabular}
+
+	The only differences is that training stage requires codebook construction and classifier training, whereas inference uses the classifier for prediction.
+If we compare training to testing it is clear that they both deal with large amounts of data.
+Inference is not that data-intensive and can be carried out for a single image.
+In order to simplify training we have decided to split the training and testing phases into several sub-routines.
+Such treatment let us change settings of an algorithm without the need to retrain the stages that lay before considered algorithm in the pipeline (\emph{e.g.} there is no need to extract features once more only because we have changed the dictionary size).
+The final application has the following operational modes, accessible from the command line:
+
+	\begin{enumerate}
+		\item Feature Extraction
+		\item Codebook Generation
+		\item Classifier Training
+		\item Classifier Evaluation
+		\item Inference
+	\end{enumerate}
+
+	In order to ensure that the application is configurable and easily extensible we used singleton and strategy design patterns and resorted to the Boost's program\_options package for configuration file parsing.
 
 		\subsubsection{Input/Output operations}	
-		Additional functionality have to be provided in the field of input/output operations.
-Before any processing can be done each image have to be read into memory.
-Both batch inference and estimation are dataset dependant.
-What I mean by this is that a previously compiled database have to be accessible.
-The inference, on the other hand, is meant to be used in a production environment i.e.
-with a Kinect connected only.
-While the OpenNI Grabber framework from the PointCloud Library is essentially what is required for the inference, a little more elaboration has to be done on the demands of the estimation and batch inference environments.
-The two third party datasets used in the project have different formats and need to be tackled separately.
-The B3DO object dataset contains multiple objects in a single image.
-The locations of the images are available in xml files, while rgb and depth data are stored in separate files, 8-bit 3 channel jpeg and 16 bit one channel png respectively.
-Single objects have to be extracted from both pictures using the provided annotations and point cloud have to be build.
-The Zhang's dataset contain single objects.
-The rgb data is stored in 8 bit 3 channel jpegs and csv files contains euclidean coordinates of every rgb pixel.
-Both databases contain objects' labels that have to be loaded separately.
-
-		A different problem is serialisation.
-If the models from the training stage are to be used during inference, they have to be serialised.
-This means that a standardised way of saving and loading of kMeans and SVM models have to be provided.
+		This work is extremely data dependent.
+Every operation requires external data.
+Both training and testing a classifier consumes hundreds of images.
+Datasets used in this projects have different and incompatible formats.
+Not only an object responsible for run-time input/output operations is needed, but also a set of scripts for data preprocessing.
+Additionally, some serialisation method have to be supplied.
+The training of the classifier is far too computationally expensive to be computed every time the application starts.
+Once the classifier is trained, all the models should be stored for further usage.
+A way of saving and loading codebook and svm model is required.
 
 		\subsubsection{Configuration}		
-		Every algorithm employed in the project have several configuration parameters.
-If the parameters were to be compiled with the code, every change would require a rebuild of the application or its parts.
-In order to address this issue a means of configuration from outside the code should be provided.
+		Every algorithm used in this work have several configuration parameters.
+If the parameters were to be compiled with the code, every change would require a rebuild of parts of the application.
+A run-time configuration functionality is essential.
 
@@
 		Multitude of available algorithms makes it time consuming and computationally expensive to evaluate every available option.
-It should be possible to compile the programme with many algorithms suitable for performing the same task and decide which one should be used at run-time.
+It should be possible to build the programme with a number of algorithms suitable for performing the same task and decide which one should be used at run-time.
 
@@
 	\centering
-	\includegraphics[width=1.0\textwidth]{figs/short}
+	\includegraphics[width=1.0\textwidth]{figs/class}
 	\caption{Tagger3D class diagram}
@@
 
-	The described functionality can be achieved in the following way.
-The utilisation of Object Oriented Programming (OOP) can lead to production of modular, flexible and extensible software.
-Using C++ as the language of choice can result in high efficiency.
-The excellent meta-programming tools provided by the C++ language help minimise the length of resulting hand-written code.
+	C++ is one of the most efficient languages on the market.
+It is perfect for Object Oriented Programming (OOP) --- a paradigm that makes writing modular, flexible and extensible software easier.
+The excellent meta-programming tools provided by the language help to minimise the length of the hand-written code.
+Among OOP's best practices is to use design patterns - a set of well-known, documented and tested methods of solving certain architectural problems.
+Using design patterns leads to cleaner code which is easier to maintain and reuse.
 
 	\subsubsection{Configurability}
-	In order to achieve configurability all the configuration parameters are stored in a configuration file.
-A separate object has been constructed for configuration file parsing.
-Simply called `Config', it makes use of the Boost.program\_options library to parse both the configuration file and command line arguments.
-It returns an associative array of (parameter, value) pairs.
-The convention is that if an object has to be configured the configuration map has to be passed in the object's constructor (other constructors are private).
+	The programme is configurable through a text file of a standard *.ini format. It should be formatted as follows:
+	\begin{tabular}{c}
+	 param1 = 2
+	 param2 = aha
+	 [section]
+	 param3 = no
+	\end{tabular}
+
+	On top of the file there is a global section.
+Parameters can be accessed by their names.
+We can define sections but putting a section's name in brackets.
+the param3 can be accessed as ``section.param3''.
+An object ``Config'' was created for the purpose of configuration file parsing.
+It uses the Boost.program\_options module.
+Returned associative array of (parameter, value) pairs contains all parameters from a configuration file.
+We use a convention that if any object has to be configured by the configuration map it has to accept this map in it's constructor.
 
@@
 	\centering
-	\includegraphics[width=1.0\textwidth]{figs/short}
+	\includegraphics[width=0.5\textwidth]{figs/strategy}
 	\caption{Strategy pattern}
@@
 
-	Design patterns has been introduced for the very first time by Gamma \emph{et al} in \cite{gamma1993design}.
-They are best practices that should be used to solved common, recurring problems in software design.
+	Design patterns were for the very first time by Gamma \emph{et al} in 1993 \cite{gamma1993design}.
+They are best practices that should be used to solve recurring problems in software design.
 One of the patterns is the strategy pattern.
-It enables implementation of multiple algorithms handling some task and selection the desired behaviour at run-time.
+It enables implementation of multiple algorithms to handle one task.
+Then, a specific algorithm can be selected at run-time.
 It is the exact problem encountered here.
-It is stated that an interface should be defined for each task and multiple classes encapsulating different algorithms for handling the tasks should realise those interfaces.
-One modification has been done: Algorithms have often some common operations, thus an idea of an interface (a class without any implemented methods) was dropped in favour of a virtual class.
+It is stated that an interface should be defined for each task and multiple classes encapsulating different algorithms for handling the task should realise the interface.
+One modification has been done: Algorithms have often some common operations, thus an idea of an interface (a class without any implemented methods) was dropped in favour of an abstract class with some methods implemented.
 
 	The strategy pattern was used for every processing step of the pipeline so as to make it extensible.
-One might want to enhance this solution by using an abstract factory design pattern, which has not been done in this case.
-It might make the code easier to maintain and read.
-However, the project is relatively small and the bulk of an abstract factory is unnecessary.
+This property can be enhanced further by using a pattern of abstract factory.
+The idea was dropped in this case, however.
+The project is relatively small and the bulk of an abstract factory is beyond reason.
 
-	There six five classes that can be treated as algorithms' interfaces in a strategy pattern.
-They are: ImgReader, PointNormal, Detector, Descriptor, Cluster, Predictor.
+	Six parts of the pipeline are a subject of strategy pattern.
+The interfaces representing them are: ImgReader, PointNormal, Detector, Descriptor, Cluster, Predictor.
 Each of them contains pure virtual computation methods --- 'read` in case of the ImgReader or 'predict' in case of the Predictor.
-Additionally, they have some common methods defined --- I/O methods in Cluster or batch processing methods (such that take a vector of elements instead of a single element as input) for the Detector and the Descriptor.
-Every pure virtual class has its specialisations.
-For example there is the PFHDescriptor class with a Point Feature Histogram descriptor or a KMeansCluster employing kMeans clustering algorithm.
-The Tagger3D class chooses specialisations of the algorithms at run-time, depending on the configuration parameters.
+Additionally, they have some common methods defined --- I/O methods in Cluster or batch processing methods (such that take a vector of elements instead of a single element as an input) for the Detector and the Descriptor.
+Every pure virtual class have its specialisations.
+For instance there is the PFHDescriptor class with a Point Feature Histogram descriptor or a KMeansCluster employing kMeans clustering algorithm.
+The Factory class chooses specialisations of the algorithms at run-time, depending on the configuration parameters.

### 2014-01-06 Disseration/experiments.tex
done editing, now have to run some tests

@@
 \section{Experimental Setup}
-	Thanks to the configurability of the programme the majority of experiments were run in a batch processing mode.
-That is a script in bash was written that allowed running multiple tests in series without any maintenance from the user.
+	Thanks to the configurability of the programme we were able to run the majority of experiments in a batch processing mode.
+That is, we wrote a script in bash that allowed running multiple tests in series without any maintenance.
 In a single series of tests any parameters could be modified or any data processing algorithm could be exchanged.
@@
 \section{Experiments}	
-	The Bag of Words classification pipeline consists of four previously discussed steps.
-For there are many different algorithms suitable for each part of the pipeline, an extensive research is required in order to discover the best possible combination in a particular setting.
-The number of options grows combinatorial with number of candidates for each processing step.
-Moreover, many algorithms have different parameters that should be adjusted for any given conditions.
-Evaluation of every possibility is unfeasible due to the lack of time and computational power required.
-Even if only a single library, PCL, is considered, there are far too many options with 12 keypoint detectors and more than 20 feature description algorithms.
+	As already stated, a BoW pipeline consists of:
+	\begin{inparaenum}[\upshape(1\upshape)]
+	\item keypoint detection
+	\item feature extraction 
+	\item vector quantization and
+	\item classification.
+	\end{inparaenum}
+	The number of possible combinations grows combinatorial with the amount of candidates for each part.
+We have to bear in mind that each algorithm contains a set of parameters that have to be adjusted for optimal performance.
+It would require a great deal of time and computational power to conduct exhaustive evaluation.
+Even if we consider only a single library --- PCL, we would have far too many options with 12 keypoint detectors and more than 20 feature descriptors.
+A literature review can help perform an early selection of algorithms.
 
 	\subsection{Detectors}
-	In a paper \cite{pcl_keypoint_comparision} some keypoint detection algorithms from PCL are evaluated.
-It is stated that , albeit under slightly different conditions, the SIFT and ISS keypoint detectors achieve the highest performance.
-Therefore this paper compares only these two modules with respect to their usability in the BoW pipeline.
+	\rednote{run tests of SIFT, ISS, US}
+	Keypoint detection algorithms have been compared with respect to repeatability, invariance \cite{pcl_keypoint_comparision} as well as object retrieval and recognition \cite{3d_keypoint_eval}.
+3D-SIFT and ISS achieve the highest robustness for invariance.
+ISS appears to be the best choice for object retrieval.
+Dense detector (or uniform sampling) achieved the best performance in 2d image classification \cite{tsai2012bag}.
+Therefore, this paper compares SIFT, ISS and Uniform Sampling keypoint detection techniques.
 
 	\subsection{Descriptors}
-	Recently a PCL's descriptors evaluation was performed in \cite{pcl_features}.
-The PFHRGB and SHOTCOLOR scored best.
-Only a little bit worse were PFH, FPFH, SHOT and USC.
-In this paper FPFH, PFH and PFHRGB are compared, motivation being that PFH is the original descriptor, FPFH is its approximate and thus faster version, while PFHRGB is an extension which makes use of colour information.
+	\rednote{run tests on all PFH and SHOT descriptors and USC}
+	PCL descriptors have been evaluated in terms of object retrieval performance \cite{pcl_features}.
+PFHRGB and SHOTCOLOR are the most successful.
+Simpler versions of those, that is: PFH, FPFH, SHOT and USC scored a little worse.
+We evaluate all of them in terms of BoW performance.
 
@@
 	\subsection{Codebook}
+	\rednote{implement and run fisher}
 	KMeans is used in almost every implementation of the Bag of Words image processing pipeline \cite{tsai2012bag, toldo2009bag}.
-Csurka \emph{et al} showed that the number of visual words or centroids have a significant impact on the final results \cite{csurka2004visual}.
-Therefore a number of tests were run in order to determine the optimal dictionary size.
+Csurka \emph{et al} showed that the number of visual words has a significant impact on the final results \cite{csurka2004visual}.
+We run a number of tests to determinate an optimal codebook size.
 

### 2014-01-06 Disseration/introduction.tex
done editing, now have to run some tests

@@
 Then, parameters \textbf{\textit{w}} and  \textit{b} exist such that
-	\begin{equation}
-	                        y_\mathit{i}\left(\mathbf{w}*\mathbf{x}_\mathit{i} + b\right) > 0
+	\begin{equation}	                        y_\mathit{i}\left(\mathbf{w}*\mathbf{x}_\mathit{i} + b\right) > 0
 	\end{equation}
@@
 
-	We use the following third party libraries in this work:
+	We use the following third party C++ libraries:
 	\begin{itemize}
@@
 
-	\subsection{PointCloud Library}
-	Being nothing but a large scale open source project, it is a great processing tool for 2D images and 3D point clouds.
-Often abbreviated as PCL, it contains numerous state-of-the-art algorithms for feature detection, surface reconstruction, segmentation and many other subareas of computer vision.
-It is well documented and easy to use.
-Recently a machine learning library containing algorithms such as Support Vector Machine has been added.
-Some algorithms are multi-threaded thanks to the OpenMP library.
-A GPU module boosts some algorithms.
-Unfortunately the PCL is relatively new and its stability could be better.
-Currently available 1.7.0 version is going to be replaced by soon-to-be-announced 2.0 version with incompatible API.
-
-	Every feature detector and descriptor used in this project comes from the PCL.
+	\subsection{Boost}
+	Boost is a general purpose library available under the Boost Software License\footnote{\url{http://www.boost.org/LICENSE_1_0.txt}}.
+It is free for both commercial and non-commercial use.
+Boost comprises of more than 50 separate libraries.
+12 of the most popular libraries have been incorporated into the new C++11 standard.
+Because of that, Boost may become redundant in many applications.
+The original library had contained conveniences such as smart pointers, multi-threading utilities and meta-programming tools.
+We excessively use smart pointers and meta-programming utilities; but the only package from the trimmed down Boost used in this project is the Boost.program\_options library.
+It enables convenient parsing of configuration files and command line arguments.
 
 	\subsection{OpenCV}
-	Considerably more mature, the OpenCV library is yet another great image processing library.
-A multitude of methods implemented in both C (OpenCV 1.x) and C++ (OpenCV 2.x) allows for production of fully functional image processing or computer vision application with this single library.
-There are many machine learning mechanisms as well.
-Among them one can find kMeans, Gaussian Mixture Model, Na\`ive Bayes or a Support Vector Machine.
-Some of the more demanding in terms of computational power are parallelized with Threading Building Blocks (TBB).
-A module exploiting powers of the nVidia's CUDA technology exists in order to enhance computation even more.
+	OpenCV is a general computer vision library available under the BSD License\footnote{\url{http://opensource.org/licenses/BSD-3-Clause}}.
+It is free for commercial and non-commercial use.
+It was designed for computational efficiency and real-time applications.
+OpenCV takes advantage of the underlying hardware employs hardware-specific optimisation e.g.
+SSE4.
+Some algorithms are written in nVidia CUDA and can use GPU for faster execution.
+Others use Threading Building Blocks (TBB, Intel's multithreading library) to enable concurrency.
+OpenCV is available for the most popular desktop and mobile platforms.
+It is written in optimised C and C++ and provides two interfaces: the original OpenCV 1.x C interface and a newer OpenCV 2.x C++ interface.
+This single library allows production of fully functional computer vision programmes.
+Many machine learning routines are available, too.
+Among them are: kMeans, Gaussian Mixture Model, Na\`ive Bayes, SVM, Random Forests and Boosting.
+We use OpenCV for input/output operations, image processing and vector quantization.
 
-	In this paper OpenCV is used for input/output operations, image preprocessing. KMeans and SVM implementations are used as well.
+	\subsection{PointCloud Library}
+	PointCloud Library (PCL) is a computer vision library suitable for point clouds processing, manipulation and visualisation.
+It is released under the BSD license and is free for both commercial and non-commercial use.
+PCL contains numerous state-of-the-art algorithms for feature detection, surface reconstruction, segmentation to name just a few areas.
+It is well documented and easy to use.
+Recently, a machine learning module containing SVM, kMeans and other algorithms.
+Some routines are multi-threaded thanks to the OpenMP library.
+A GPU module makes use of CUDA to lessen computation time.
+Unfortunately, the PCL is relatively new and its stability could be better.
+Currently available 1.7.1 version is going to be replaced by a soon-to-be-announced 2.0 version with incompatible API.
+In this project we try to build an application for point cloud applications.
+We extensively use PCL for operations like downsampling, keypoint detection, feature extraction.
 
-	\subsection{Boost}
-	Boost is a general purpose library.
-It contains more than 50 separate libraries, 12 of which were incorporated into the new C++11 standard.
-One of the most popular are libraries for smart pointers, multi-threading or meta-programming.
-Tagger3D uses only the functionality provided by the Boost.program\_options library.
-It enables convenient parsing of configuration files and command line arguments.
+	\subsection{libsvm}
+	\rednote{describe}
+	\subsection{Apache log4cxx}
+	\rednote{describe}
 
@@
 
-	Multiple RGBD datasets were created.
-The purpose of authors of the vast majority of them were to provide a benchmark for tasks of tracking or instance-level object recognition.
-Others have small number of categories or very few examples in every category.
-Unfortunately, the most are not fit for the object classification problem.
-	The RGB-D object dataset from the University of Washington \cite{dataset_washington} would be perfect, if not for the fact that it consists of video sequences.
-A technology like Kinect Fusion \cite{KinectFusion} makes it relatively easy to build a detailed 3D model (a point cloud or a mesh) from such data.
-The only problem is in the computational cost of this method and actions required to gather such data --- in a real setting a mobile robot would have to circle an object.
-Two datasets are used are for the purpose of this paper.
-The first one is the Berkeley 3D Object dataset \cite{B3DO} and the second one is a dataset compiled by Zhang \emph{et al} at the University of Tokyo \cite{zhangcategory}.
-The datasets are going to be abbreviated as B3DO and Tokyo datasets respectively
+	Machine Learning algorithms provide a way of learning a function that maps input to the desired output.
+Classification algorithms require supervised training and labelled data.
+If we wanted to compare any algorithms we would have to do so on a common dataset.
+That is why multiple scientific datasets have been created: ImageNet\footnote{\url{http://www.image-net.org/}}, PascalVoc\footnote{\url{http://pascallin.ecs.soton.ac.uk/challenges/VOC/}}, LabelMe\footnote{\url{http://labelme.csail.mit.edu/Release3.0/browserTools/php/dataset.php}} and SUN\footnote{\url{http://groups.csail.mit.edu/vision/SUN/}} among others.
+Unfortunately, they contain RGB and grayscale images without any depth information.
+Therefore they cannot be used in this paper.
+On the other hand, the vast majority of RGBD datasets are focused on tracking or instance-level recognition.
+Others have very few categories or insufficient number of examples per category.
+We managed to find only two datasets suited to our needs.
+They are: the Berkeley 3D Object (B3DO) dataset \cite{B3DO} and a dataset compiled by Zhang \emph{et al} at the University of Tokyo\cite{zhangcategory}.
+The latter will be abbreviated Tokyo dataset from now on.
+
+	An interesting dataset is provided by the University of Washington \cite{dataset_washington}.
+It consists of video sequences that capture objects' round views in RGBD.
+Kinect Fusion\footnote{\url{http://msdn.microsoft.com/en-us/library/dn188670.aspx}} technology could be used to prepare excellent point clouds from the videos.
+We have decided against it, for a huge computational cost associated with this way of point cloud construction.
+Furthermore, in a real setting a mobile robot would have to circle an object in order to gather enough data.
 
@@
 
-	The Berkeley 3D Object dataset was specifically designed for the purpose of object classification.
+	The Berkeley 3D Object dataset was specifically designed for the purpose of object detection and classification.
 It consists of cluttered images in indoor environment.
 There are around 50 classes with more than 20 examples in each of them.
-RGBD data is provided as pairs of images.
-There are 8 bit RGB jpeg pictures and 16 bit png files containing depth data in millimetres.
-Images are densely labelled --- for every pair of images there is an xml with annotations.
-Every annotation is comprised of a category label, bounding box coordinates and object's orientation.
-
-	Before the B3DO database could be used it had to be preprocessed.
-Neither image segmentation nor object detection are addressed in this paper.
-Because of that the objects had to be extracted from the cluttered images.
+RGBD data are provided as pairs of colour images (8 bit RGB jpeg files) and depth maps (16 bit png files).
+Images are densely labelled --- for every pair of images there is an xml file with annotations.
+Each annotation states a category of an object as well as it's bounding box location.
+Images are cluttered, with many labelled and random objects per image.
+Labelled objects are often partially occluded.
+We do not address image segmentation nor object detection; we had to extract objects from the images before we could use the dataset.
 
@@
 
-	The dataset compiled at the University of Tokyo is comprised of high quality images of objects in different settings.
-Factors such as viewpoint, object orientation, object's texture and environments are changing on different images.
-The aim of the authors of this dataset was slightly different - it was object detection and classification in casual images.
-There are 10 classes with varying amounts of per class examples.
-The database is available as two sets of files: 8 bit RGB jpeg files and csv files containing euclidean coordinates of every pixel in the corresponding colour image.
+	The Tokyo dataset is comprised of high quality images of objects in different settings, with changing viewpoint, object orientation and texture.
+The dataset is presented as colour images (8 bit RGB jpeg files) and depth maps (csv files with XYZ coordinates of each pixel).	This dataset is aimed at the task of object classification in casual images.
+There is one labelled object per image, without any bounding box given.
+Scenes are sometimes cluttered, with many random objects present at a scene.

### 2014-01-06 Disseration/titlepage.tex
done editing, now have to run some tests

\pagestyle{empty}
\color{white} . \color{black}
\vspace{0.2cm}

\begin{center}
\begin{Huge}Warsaw University of Technology
\end{Huge}
\end{center}

\begin{center}
\begin{LARGE}Faculty of Mechatronics

\vspace{0.5cm}
Institute of Automation and Robotics
\vspace{1.0cm}
\end{LARGE}
\end{center}
\begin{center}\includegraphics[width=5cm,angle=0]{figs/logopw}\end{center}

\vspace{0.5cm}

\begin{center}
\begin{LARGE}\textbf{Adam Kosiorek}\end{LARGE}
\end{center}

\vspace{0.5cm}

\begin{center}
\begin{Huge}\textbf{3D Object Classification based on RGBD images}
\vspace{0.5cm}
\end{Huge}
\end{center}

\vspace{0.5cm}

\begin{center}
\begin{Large}bachelor thesis written under supervision of\end{Large}

\vspace{0.2cm}

\begin{Large}prof. dr. hab. Barbara Siemiątkowska\end{Large}
\end{center}

\vspace{1.8cm}

\begin{center}
\begin{Large}Warsaw 2014\end{Large}
\end{center}

### 2014-01-06 src/Common/Factory.h

@@ -45,10 +45,10 @@ private:
 
 	const std::string loggerName = "Main.Factory";
 
-	enum Dataset : unsigned char { B3DO, TOKYO };
-	enum DetectorType : unsigned char { SIFT, ISS3D, DENSE };
-	enum DescriptorType : unsigned char { PFH, FPFH, PFHRGB };
-	enum PredictorType : unsigned char { SVM };
+	enum Dataset { B3DO, TOKYO };
+	enum DetectorType { SIFT, ISS3D, DENSE };
+	enum DescriptorType { PFH, FPFH, PFHRGB };
+	enum PredictorType { SVM };
 };
 
 } // namespace Tagger3D

### 2014-01-06 src/Common/Tagger3D.h

@@ -103,7 +103,7 @@ private:
 	const std::vector<std::string> modeStrings = {"desc", "clust", "train", "pred"};
 
 	// Enums -------------------------------------------------------------------
-	enum Mode : unsigned char { DESC, CLUST, TRAIN, PRED };
+	enum Mode { DESC, CLUST, TRAIN, PRED };
 };
 
 } /* namespace Tagger3D */

### 2014-02-04 Disseration/architecture.tex
aha

@@
-\chapter{Design}
-\addcontentsline{toc}{chapter}{Design}
+\chapter{Design and Implementation}
+%\addcontentsline{toc}{chapter}{Design}
 
@@
 	\subsubsection{Configurability}
-	The programme is configurable through a text file of a standard *.ini format. It should be formatted as follows:
-	\begin{tabular}{c}
-	 param1 = 2
-	 param2 = aha
-	 [section]
-	 param3 = no
-	\end{tabular}
+	The programme is configurable through a text file of a standard *.ini format. It should be formatted as follows:\\ \ \\
+	 param1 = 2\\
+	 param2 = aha\\
+	 {[section]}\\
+	 param3 = no\\
 
@@
 The Factory class chooses specialisations of the algorithms at run-time, depending on the configuration parameters.
+
+\section{Implementation}
+
+	The complete program consists of more than 5600 lines of code in C++ and additional several hundreds of code in data preprocessing scripts.
+
+	\subsection{Data preprocessing scripts}
+		\begin{description}
+			\item[imgListPrep.py] A script in python we have written for the purpose of listing hundreds of images (colour images and depth maps) and their corresponding labels in text files.
+These files are later used for batch processing such as training, but also for further data preprocessing.
+			\item[b3doPrep] A short C++ programme used for object extraction from the B3DO dataset.
+It uses TinyXML, a lightweight C++ library for XML processing.
+It reads lists of files(depth maps, colour images and image annotations stored in the XML format) and iterates over them.
+Each iteration consists of loading an image, extracting labels and locations of bounding boxes from the XML, extracting the regions of interests and saving them at a new location.
+			\item[divImgsByCats.py] Another short python script. Used mainly for splitting all the extracted objects into separate folders, one for every category.
+			\item[pcdPrep] One more short C++ application.
+It was created for the reason of handling the Tokyo dataset.
+The dataset comes in a rather difficult-to-manage form.
+This application processes the raw files and saves them as point clouds in a PointCloud Library's PCD format.
+			\item[grid.py and easy.py] These python scripts are an integral part of the libsvm library.
+Usually distributed as executables with the library, they help to perform corssvalidation and avoid overfitting.
+We have modified both scripts significantly in order to tune their performance on the very specific hardware describe in the Experiments section.
+		\end{description}
+
+		While the data prepared by pcdPrep is readily available for usage by the main programme the case with the B3DO dataset is quite different.
+The colour images and depth maps still have to be converted to point clouds because any further processing can be undertaken.
+That is because if the application were to work on-line with a Microsoft Kinect plugged in, it would have to handle the raw data from Kinect, which comes in a form of two images.
+
+	\subsection{Conversion of colour images and depth maps into point clouds}
+
+		The colour data and the depth data come from different cameras.
+The colour data come from 640 x 320 RGB camera, while the depth data come from active 320 x 240 infrared sensor.
+Only after registration the depth data is interpolated to match the colour data in resolution.
+Even after that operation, however, individual points from both images does not match exactly.
+That might introduce noise into the point cloud.
+We have not solved this issue and so that would be an area for further improvement.
+It did, however, focused our attention on another problem.
+If the two images do not fit perfectly it might be the case that one of the cameras have registered some points that had been invisible for the other one.
+Precisely, if there are any points in the colour image that the depth camera have not captured their depth would be meaningless.
+The Kinect's firmware does, in fact, address this issue.
+The depth value of every such point is set to NaN or Not a Number values.
+Before proceeding to the next stage we filter out all points, whose depth value has been set to NaN;
+
+		Another problem is that only the Z coordinate is given explicitly in the depth map.
+The XY coordinates have to be inferred from the Z coordinate and the point's location relative to the sensor.
+We assumed that the sensor's position should correspond to the middle of the image or the the pixel at (320, 240).
+The Kinect specification says that the horizontal and vertical fields of view are respectively $57^{\circ}$ and $43^{\circ}$.
+We can compute the coordinates as: \\
+
+		\begin{centering}
+			$factorH = tg (\frac{57}{2}) * \frac{\pi}{180}$\\
+			$factorV = tg (\frac{43}{2}) * \frac{\pi}{180}$\\
+			$X = depth * factorH * (pixelX / 320)$\\
+			$Y = depth * factorV * (pixelX / 240)$\\
+			$Z = depth$\\
+		\end{centering}
+
+	\subsection{Input/Output Objects}
+
+		As stated in the input/output section above, the application is very data dependent.
+Therefore, some objects for input/output operations were designed and implemented.
+The whole public API is delivered by the IoUtils class.
+It's methods allow reading and writing of text files, binary files of different formats, vectors of elements, vectors of vectors of elements and OpenCV's Mat objects.
+Elements that can be worked with are all C/C++ primitive types, all user defined types with defined std::string toString() method and OpenCV's Mat objects.
+In order to enhance performance, the IoUtils statically uses an object of type VectorIO for any vector input/output operation.
+The VectorIO is a template class parametrized by a type that is to be read into or written from a vector to a file on a hard drive.
+The VectorIO class uses a default implementation for all C/C++ primitive type and has template specialisations for the following types: std::vector, std::string, cv::Mat, any user defined object with a public std::string toString() method.
+Moreover, both IoUtils and VectorIO uses custom type trait classes that provide file extensions, size of types in bytes or processing algorithms for different data types.

### 2014-02-04 Disseration/experiments.tex
aha

@@
 \chapter{Experiments and Results}
-\addcontentsline{toc}{chapter}{Experiments and results}
+%\addcontentsline{toc}{chapter}{Experiments and results}
 
@@
 
-	\subsection{Detectors}
-	\rednote{run tests of SIFT, ISS, US}
-	Keypoint detection algorithms have been compared with respect to repeatability, invariance \cite{pcl_keypoint_comparision} as well as object retrieval and recognition \cite{3d_keypoint_eval}.
-3D-SIFT and ISS achieve the highest robustness for invariance.
-ISS appears to be the best choice for object retrieval.
-Dense detector (or uniform sampling) achieved the best performance in 2d image classification \cite{tsai2012bag}.
+	\subsection{Detectors and descriptors}
+	Keypoint detection algorithms have been compared with respect to repeatability, invariance in \cite{pcl_keypoint_comparision} and in terms of object retrieval and recognition in \cite{3d_keypoint_eval}.
+3D-SIFT and ISS achieve the highest robustness for invariance, while the latter appears to be the best choice for object retrieval.
+Dense detector (or uniform sampling) achieved the best performance in 2D image classification \cite{tsai2012bag}.
 Therefore, this paper compares SIFT, ISS and Uniform Sampling keypoint detection techniques.
 
-	\subsection{Descriptors}
-	\rednote{run tests on all PFH and SHOT descriptors and USC}
-	PCL descriptors have been evaluated in terms of object retrieval performance \cite{pcl_features}.
-PFHRGB and SHOTCOLOR are the most successful.
-Simpler versions of those, that is: PFH, FPFH, SHOT and USC scored a little worse.
-We evaluate all of them in terms of BoW performance.
+	PCL descriptors have been evaluated in terms of object retrieval performance in \cite{pcl_features}.
+PFHRGB and SHOTCOLOR delivered the best performance, while their simpler counterparts (PFH, FPFH, SHOT) were only a little worse.
+USC, which is a global descriptor and thus not suitable for the Bag of Words approach, achieved very similar accuracy.
+We focus on the family of PFH algorithms.
 
@@
 	\centering	
-	\includegraphics[width=.25\textwidth]{figs/desc_b3do}
+	\includegraphics[width=.55\textwidth]{figs/desc_b3do}
 	\caption{Highest accuracy obtained with FPFH, PFH and PFHRGB descriptors on the B3DO dataset}
@@
 
-	The figure \ref{tab:desc_b3do} shows highest accuracy obtained with the tested descriptors on the B3DO dataset.
-FPFH scored the best result, even tough it is an approximate and theoretically the least precise of all evaluated descriptors.
-On the other hand, the PFHRGB scored better than PFH.
-It does not surprise, since the colour information is believed to have discriminative value.
+	The best results achieved are shown in the figure \ref{tab:desc_b3do}.
+They were scored on the B3DO dataset.
+As for the detection algorithms, the ISS provided consistently the highest accuracy.
+The SIFT and Uniform Sampling provide very similar accuracy, but the latter is significantly faster.
+SIFT is in fact slowest of the three.
+As for the descriptors, the FPFH delivered the best performance even though it is an approximate and theoretically the least precise algorithm.
+It is also the fastest of the three.
+It appears that the combination of ISS and FPFH is not only surprisingly good in terms of accuracy, but it is also the fastest.
+These two algorithms allow near real time point-cloud processing and classification.
+PFHRGB and SIFT are several times slower.
 
 	\subsection{Codebook}
-	\rednote{implement and run fisher}
 	KMeans is used in almost every implementation of the Bag of Words image processing pipeline \cite{tsai2012bag, toldo2009bag}.
 Csurka \emph{et al} showed that the number of visual words has a significant impact on the final results \cite{csurka2004visual}.
-We run a number of tests to determinate an optimal codebook size.
+We run a number of tests to discover an optimal codebook size for our setting.
 
@@
 The performance raises with the increasing number of centroids up to the point of 1500 centroids and 65.22\%.
-Then it starts to diminish.
-The discrepancy might be caused by the following factors: (1) ISS detector finds too many or irrelevant points, thus introducing noise or (2) The FPFH descriptor has too few dimensions (33) to be divided into more than 1500 regions in a meaningful way.
+The discrepancies might be caused by the following factors: (1) ISS detector finds too many or irrelevant points, thus introducing noise or (2) The FPFH descriptor has too few dimensions (33) to be divided into more than 1500 regions in a meaningful way.
 
 	\subsection{B3DO}
-	Extraction of single objects yielded 78 separate categories with number of entries ranging from 1 (tape) to 299 (table).
-8 categories were picked at random with a restriction that there should be at least 50 instances in each of them.
-Further, the objects were split into two sets (training and testing) with a proportion of 1:1.
-As names suggest, the estimation is performed on the test set and the evaluation on the test set.
+	The majority of the point clouds in the B3DO dataset contain several different objects.
+We have extracted every individual object from the clouds and divided them into 78 separate categories.
+Unfortunately, they were badly balanced \emph{i.e.} the number of objects in a category varies from 1 (tape) to 299 (table).
+We have picked 8 categories at random with a restriction that there should be at least 50 object instances in a category.
+Then, the objects were split into two sets (training and testing) with a proportion of 1:1.
+As the names suggest, they are used for estimation and evaluation respectively.
 
@@
 Table \ref{tab:b3do_conf_matrix} contains a confusion matrix, number of examples per category and accuracy.
-The confusion matrix depicts misclassification errors.
+The confusion matrix depicts classification errors.
 Let m\subscript{i, j} be an element of the confusion matrix at the i\superscript{th} row and j\superscript{th} column.
@@
 \section{Conclusion}
+
+	In this paper we have tackled the issue of three dimensional point cloud classification with a bag of words-based approach.
+The main focus was put on the design and efficient implementation of the pipeline in a way that allows easy addition of algorithms and switching them at run-time.
+What is more, we have gone to great lengths in order to find scientific databases that are suitable for the task of point cloud classification.
+We believe that the presence of such databases is fundamental, for it allows meaningful comparison with other researchers.
+We have experienced the following problems: Firstly, point cloud processing is computationally expensive and inefficient.
+Due to the lack of structure in point clouds (\textit{i.e.} no predefined relationship between points) additional calculations have to be performed (\textit{e.g.} finding nearest neighbours requires distance comparison for all points in a cloud, whereas for a 2D image one instantly knows where adjacent pixels lie).
+Secondly, there are virtually no databases that would allow extensive training of the bag of words-based pipeline.
+Machine learning algorithms have ravenous appetite for labelled data.
+As the newest findings in the state-of-the-art 2D object classification suggest, an order of tens of thousands of samples is a prerequisite for any satisfactory results We had to make do with as few as 330 objects in our training set.
+Moreover, there is very little interest in the scientific community for this particular task.
+The majority of research is conducted on retrieval of CAD-like objects from mesh databases.
+Last, but not least, there is no 3D detection or description algorithm designed solely for the purpose of bag of words object classification.
+
+	In conclusion I would not recommend any bag-of-words based approach classification of real point clouds registered with a low quality camera such as Microsoft Kinect.
+Being computationally expensive and rather inefficient, it delivers inferior performance in terms of accuracy and speed when compared to 2D RGB image based algorithms.
+To makes matters worse, generalisation of 2D algorithms to the 3D domain can be very involved, causing the cutting-edge inventions of the 2D image processing scientists unavailable for the purpose of 3D point cloud processing.

### 2014-02-04 Disseration/introduction.tex
aha

@@
 \chapter{Introduction}
-\addcontentsline{toc}{chapter}{Introduction}
+%\addcontentsline{toc}{chapter}{Introduction}
 
@@
 Firstly, the Bag of Words (or BoW for short) approach to image classification is reviewed.
-The Bag of Words method has originated from the natural language processing domain \rednote{ref}.
+The Bag of Words method has originated from the natural language processing domain \cite{tsai2012bag}.
 It makes a strong assumption that the word occurrence in a text document define the meaning of the document.
@@
 
-	\section{scope and purpose of this work}
+	\section{Scope and purpose of this work}
 		The goal of this work is to design a flexible and configurable application for point cloud classification.
@@
 
-\section{Bow of Words}
+\section{Bag of Words}
 
-	The Bag of Words model is a an intermediate representation used in natural language processing, information retrieval and data mining \rednote{pub}.
+	The Bag of Words model is a an intermediate representation used in natural language processing, information retrieval and data mining.
 The model can be seen as a simplification, for it obliterates any grammatical information and even word order contained within an original text document.
@@
 
-	In natural language processing BoW is used to infer semantic meaning of documents \rednote{pub}.
+	In natural language processing BoW is used to infer semantic meaning of documents.
 If we could translate an image into a text document we might be able to employ similar methods.
@@
 
-		\rednote{describe fundamentals of keypoint detection in greater detail}
 		The most common detectors make use of a Harris corner detector or image's first or second derivatives.
@@
 One of the most precise and repeatable algorithm is SIFT \cite{sift_features}, which is a 3D histogram of gradients structured as a 128-dimensional vector of floating point values.
-It is the most often extracted descriptor in BoW pipelines \rednote{ref}.
+It is the most often extracted descriptor in BoW pipelines.
 Other methods include various colour descriptors, binary descriptors such as 512-dimensional GIST \cite{ponce2011cv}.
@@
 		\subsubsection{Scene and Object Classification}
-		Scene and object classification are among the most popular issues of computer vision nowadays \rednote{ref}.
+		Scene and object classification are among the most popular issues of computer vision nowadays.
 We would like to perform those tasks automatically for the sake of surveillance, navigation or automatic image tagging.
@@
 
-	\subsection{libsvm}
-	\rednote{describe}
 	\subsection{Apache log4cxx}
-	\rednote{describe}
+	Apache log4cxx is an efficient and easy to use logger for C++ programmes.
+It is based on a Apache log4j logger for Java applications.
+It provides a set of static methods for logging.
+It support simultaneous output to multiple destinations and have very well defined logging levels.
+It is perfectly documented as well.
 

### 2014-02-04 Disseration/ppt/main.tex
aha

\documentclass[8pt]{beamer}
\usetheme{Montpellier} 
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{polski}
\usepackage[polish]{babel}

\newcommand{\argmax}[1]{\underset{#1}{\operatorname{arg}\,\operatorname{max}}\;}
\beamertemplatenavigationsymbolsempty

\makeatletter
\setbeamertemplate{footline}
{
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{author in head/foot}%
    \usebeamerfont{author in head/foot}\insertshortauthor~~\beamer@ifempty{\insertshortinstitute}{}{(\insertshortinstitute)}
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{title in head/foot}%
    \usebeamerfont{title in head/foot}\insertshorttitle
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,right]{date in head/foot}%
    \usebeamerfont{date in head/foot}\insertshortdate{}\hspace*{2em}
    \insertframenumber\hspace*{2ex} 
  \end{beamercolorbox}}%
  \vskip0pt%
}
\makeatother

\author[Adam Kosiorek]{Adam Kosiorek\\ \footnotesize pod kierunkiem prof. dr hab. B. Siemiątkowskiej}
\begin{document}
\title[Rozpoznawanie obiektów 3D na podstawie danych RGBD]{\HUGE Politechnika Warszawska\\ Wydział Mechatroniki \\ \ \\ \Large Rozpoznawanie obiektów 3D na podstawie danych RGBD} 
\date{11 lutego 2014}

\thispagestyle{empty}
\titlepage
\thispagestyle{empty}
\frame{\frametitle{Spis treści}\tableofcontents}
\begin{document}

\section{Założenia i zakres pracy}

\begin{frame}
  \setcounter{framenumber}{1}
  \frametitle{Założenia}

   Założeniem pracy jest zbadanie zagadnienia klasyfikacji obiektów 3D na podstawie zdjęć RGBD. Zdjęcia powinny byc zrobione kamerą Microsoft Kinect oraz być reprezentowane w formie chmur punktów. Ponadto zakłada się: \ \\
  \begin{itemize}
   \item Zaprojektowanie algorytmu rozpoznawania obrazów podejściem Bag of Words
   \item 
  \end{itemize}

\end{frame}

\begin{frame}{Zakres pracy}
\end{frame}

\section{Podejście Bag of Words}
\begin{frame}
  \frametitle{Bag of Words - Wprowadzenie}
  \begin{figure}
    \includegraphics[scale=0.3]{../figs/bow_example-eps-converted-to}
  \end{figure}

  \begin{itemize}
   \item Częstośc występowania słów
   \item Usunięcie gramatyki, kolejności słów
   \item Histogram jako forma pośrednia
   \item Wymaga utworzenia słownika
   \item Reprezentacja rzadka w przypadku dużego słownika
   \item Używany m. in. do znajdowania rozkładu tematów w obrazie
  \end{itemize}

\end{frame}

\begin{frame}
	\frametitle{Bag of Words w obrazach}

	\begin{columns}

	 \begin{column}{6cm}
	 \begin{figure}
	   \includegraphics[scale=0.15]{../figs/tsai2012}
	   \end{figure}
	 \end{column}

	 \begin{column}{3cm}
	  \footnotesize Grafika pochodzi z C. Tsai. \textit{Bag-of-words representation in image annotation: A review. ISN Artificial Intelligence, 2012}.
	 \end{column}

	\end{columns}

	\begin{enumerate}
	 \item Wykrycie punktów charakterystycznych
	 \begin{itemize}
	  \item współrzędne (x, y) oraz skala obrazka
	 \end{itemize}

	 \item Opisanie otoczenia wykrytych punktów
	 \begin{itemize}
	  \item opis jednoznaczny, zazwyczaj poprzez histogram gradientów
	 \end{itemize}
	 \item Budowanie słownika i kwantyzacja
	 \begin{itemize}
	  \item punkty układają się w obszary, które można wykryć - klasteryzacja
	 \end{itemize}
	 \item Klasyfikacja
	 \begin{itemize}
	  \item klasyfikator uczący się - Support Vector Machine, Modele graficzne, Boosting
	 \end{itemize}
	\end{enumerate}

\end{frame}

\begin{frame}
	\frametitle{}
\end{frame}

\begin{frame}
	\frametitle{}
\end{frame}

\begin{frame}
	\frametitle{}
\end{frame}

\begin{frame}
	\frametitle{}
\end{frame}

\begin{frame}
	\frametitle{}
\end{frame}

\end{document}

### 2014-02-04 src/ImgReader/RangeImgReader.cpp

@@ -31,11 +31,6 @@ ColorCloud::Ptr RangeImgReader::matToCloud(const cv::Mat &colorImg, const cv::Ma
 	int height = depthImg.rows;
 	int width = depthImg.cols;
 
-	int height2 = height/2;
-	int width2 = width/2;
-	float factorX = factorX0 / width;
-	float factorY = factorY0 / height;
-
 	if( height != colorImg.rows || width != colorImg.cols ) {
 
 		std::runtime_error e("Images have different dimensions");
@@ -62,9 +57,8 @@ ColorCloud::Ptr RangeImgReader::matToCloud(const cv::Mat &colorImg, const cv::Ma
 			if ( depth == depth) {            // if depthValue is not NaN
 
 				newPoint.z = depth;
-				newPoint.x = (x - width2) * factorX * depth;
-				newPoint.y = (y - height2) * factorY * depth;
-//				std::cout << "x0: " << x << " y0: " << y << " z: " << newPoint.z << " x: " << newPoint.x << " y: " << newPoint.y << std::endl;
+				newPoint.x = depth * depthH * (x / depthWidthHalf);
+				newPoint.y = depth * depthV * (y / depthHeightHalf);
 				cv::Vec3b vec = colorPtr[x];
 				newPoint.r = vec[2];
 				newPoint.g = vec[1];

### 2014-02-04 src/ImgReader/RangeImgReader.h

@@ -51,6 +51,15 @@ private:
 	const float factorX0 =  320.0f * 3.501e-3f;
 	const float factorY0 = 240.0f * 3.501e-3f;
 
+	const float depthWidth = 320.0f;
+	const float depthHeight = 240.0f;
+	const float depthWidthHalf = depthWidth / 2.0f;
+	const float depthHeightHalf = depthHeight / 2.0f;
+	const float depthHFOV = 57.0f;
+	const float depthVFOV = 43.0f;
+	const float depthH = tan ( (depthHFOV / 2.0f) * ( M_PI / 180.0f ) );
+	const float depthV = tan ( (depthVFOV / 2.0f) * ( M_PI / 180.0f ) );
+
 
 };
 

### 2014-02-04 utils/ListsPrep/divImgsByCats.py

@@ -1,0 +1,49 @@
+'''
+Created on 22 sie 2013
+
+@author: adam
+'''
+
+import getopt, sys, os, exceptions, shutil, re
+
+def main():
+    
+    root = ""
+    pattern = r"([a-z]+)"
+    
+    try:
+        
+        opts, args = getopt.getopt(sys.argv[1:], "r:")
+        
+    except getopt.GetoptError:        
+        print "python divImgsByCats.py -r <img root directory>"
+        sys.exit(2)
+        
+    if len(opts) < 1:
+        print "python divImgsByCats.py -r <img root directory>"
+        sys.exit(2)
+        
+    for opt, arg in opts:
+        if opt == "-r":
+            root = arg
+        
+    imgs = os.listdir(root);
+    os.chdir(root)    
+    for img in imgs:
+        
+        #category = str(img).split("_")[0]
+        match = re.match(pattern, img, re.I)
+        if match:
+            category = match.group(0)
+        if not os.path.exists(category):
+            os.mkdir(category)
+        
+        shutil.move(img, os.path.join(root, category))
+            
+if __name__ == "__main__":
+    main()
+            
+    
+    
+    
+    

### 2014-02-04 utils/ListsPrep/imgListPrep.py

@@ -1,0 +1,69 @@
+'''
+Created on 22 sie 2013
+
+@author: adam
+'''
+
+import sys, getopt, os, exceptions, random
+
+def main():
+    
+    try:
+        
+        opts, args = getopt.getopt(sys.argv[1:], "r:p:")
+    except getopt.GetoptError:
+        
+        print "python imgListPrep.py -r <rootDir> -p <trainset percentage in the dataset>"
+        sys.exit(2)
+        
+    if len(opts) < 2:
+        print "python imgListPrep.py -r <rootDir> -p <trainset percentage in the dataset>"
+        sys.exit(2)
+        
+    for opt, arg in opts:
+        if opt == "-r":
+            root = arg
+        if opt == "-p":
+            ratio = float(arg)
+         
+    catFolders = os.listdir(root)
+    imgsByCat = []
+    os.chdir(root)
+    for folder in catFolders:
+        
+        listOfDirs = os.listdir(folder)
+        random.shuffle(listOfDirs)
+        newList = []
+        for dir in listOfDirs:
+            newList.append(os.path.join(root, folder, dir))          
+        imgsByCat.append(newList)
+        
+    trainset = open("train.txt", "w")
+    testset = open("test.txt", "w")
+    trainlabels = open("train_labels.txt", "w")
+    testlabels = open("test_labels.txt", "w")
+    
+    cat = 0
+    for imgs in imgsByCat:
+        
+        trainsetSize = int(len(imgs) * ratio) 
+        trainImgs = imgs[0:trainsetSize]
+        testImgs = imgs[trainsetSize + 1 : len(imgs) - 1]
+        for img in trainImgs:
+            trainset.write(img + "\n")
+            trainlabels.write(str(cat) + "\n")
+            
+        for img in testImgs:
+            testset.write(img + "\n")
+            testlabels.write(str(cat) + "\n")
+        cat += 1
+        
+    trainset.close()
+    testset.close()
+    trainlabels.close()
+    testlabels.close()
+        
+if __name__ == "__main__":
+    main()
+    
+    

### 2014-02-04 utils/PcdPrep/src/B3DO/AnnotatedObjectExtractor.cpp

@@ -1,0 +1,22 @@
+/*
+ * AnnotatedObjectExtractor.cpp
+ *
+ *   Created on: 29 sie 2013
+ *       Author: Adam Kosiorek
+ *	Description:
+ */
+
+#include "AnnotatedObjectExtractor.h"
+
+namespace Tagger3D {
+
+AnnotatedObjectExtractor::AnnotatedObjectExtractor() {
+	// TODO Auto-generated constructor stub
+
+}
+
+AnnotatedObjectExtractor::~AnnotatedObjectExtractor() {
+	// TODO Auto-generated destructor stub
+}
+
+} /* namespace Tagger3D */

### 2014-02-04 utils/PcdPrep/src/B3DO/AnnotatedObjectExtractor.h

@@ -1,0 +1,27 @@
+/*
+ * AnnotatedObjectExtractor.h
+ *
+ *   Created on: 29 sie 2013
+ *       Author: Adam Kosiorek
+ *	Description:
+ */
+
+#ifndef ANNOTATEDOBJECTEXTRACTOR_H_
+#define ANNOTATEDOBJECTEXTRACTOR_H_
+
+namespace Tagger3D {
+
+/*
+ *
+ */
+class AnnotatedObjectExtractor {
+	/**
+	 *
+	 */
+public:
+	AnnotatedObjectExtractor();
+	virtual ~AnnotatedObjectExtractor();
+};
+
+} /* namespace Tagger3D */
+#endif /* ANNOTATEDOBJECTEXTRACTOR_H_ */

### 2014-02-04 utils/PcdPrep/src/PcdCreator/TokyoCreator.cpp

@@ -1,0 +1,146 @@
+/*
+ * TokyoCreator.cpp
+ *
+ *   Created on: 29 sie 2013
+ *       Author: Adam Kosiorek
+ *	Description:
+ */
+
+#include "TokyoCreator.h"
+
+#include <opencv2/highgui/highgui.hpp>
+#include <opencv2/imgproc/imgproc.hpp>
+#include <pcl/filters/filter.h>
+#include <pcl/io/pcd_io.h>
+#include <boost/algorithm/string.hpp>
+#include <boost/filesystem.hpp>
+#include <boost/algorithm/string.hpp>
+
+#include <iostream>
+#include <fstream>
+#include <stdexcept>
+
+namespace fs = boost::filesystem;
+
+TokyoCreator::TokyoCreator() {
+	// TODO Auto-generated constructor stub
+
+}
+
+TokyoCreator::~TokyoCreator() {
+	// TODO Auto-generated destructor stub
+}
+
+ColorCloud::Ptr TokyoCreator::createPointCloud(
+			const std::string &jpgPath, const std::string &csvPath) {
+
+	cv::Mat colorImg = cv::imread(jpgPath, -1);
+	cv::Mat spaceImg = csv2mat(csvPath);
+
+	if( !colorImg.data )
+		throw std::runtime_error("Cloud not read image " + jpgPath);
+	if( !spaceImg.data )
+		throw std::runtime_error("Cloud not read image " + csvPath);
+
+	int height = spaceImg.rows;
+	int width = spaceImg.cols;
+	if( spaceImg.rows != colorImg.rows || spaceImg.cols != colorImg.cols )
+		throw std::runtime_error("Images have different dimensions");
+
+	ColorCloud::Ptr cloud( new ColorCloud() );
+	cloud->height = height;
+	cloud->width = width;
+	cloud->reserve(height * width);
+	cloud->is_dense = false;
+	pcl::PointXYZRGB newPoint;
+	for (int i = 0; i < height; i++) {
+
+		cv::Vec3b *spacePtr = spaceImg.ptr<cv::Vec3b>(i);
+		cv::Vec3b *colorPtr = colorImg.ptr<cv::Vec3b>(i);
+
+		for (int j = 0; j < width; j++) {
+
+				cv::Vec3b colorVec = colorPtr[j];
+				cv::Vec3b spaceVec = spacePtr[j];
+
+				newPoint.x = spaceVec[0];
[…]

### 2014-02-04 utils/PcdPrep/src/main.cpp

@@ -1,0 +1,30 @@
+/*
+ * main.cpp
+ *
+ *   Created on: 29 sie 2013
+ *       Author: Adam Kosiorek
+ *	Description:
+ */
+
+#include "PcdCreator/TokyoCreator.h"
+
+#include <iostream>
+
+int main(int argc, char** argv) {
+
+	if(argc < 3) {
+
+		std::cerr << "ImgPrep <colorPath> <spacePath> <destPath>" << std::endl;
+		exit(2);
+	}
+
+	TokyoCreator creator;
+	std::string colorPath = argv[1];
+	std::string spacePath = argv[2];
+	std::string destPath = argv[3];
+	creator.batchProcess(colorPath, spacePath, destPath);
+
+	return 1;
+}
+
+

### 2014-02-04 utils/source.sh

@@ -1,0 +1,15 @@
+#!/bin/bash
+
+cd src
+
+for file in $(find $PWD); do
+	if [[ -d $file ]]; then
+		echo $file
+		echo ""
+		echo ""
+	else 
+		cat $file
+		echo ""
+		echo ""
+	fi
+done

### 2014-02-04 utils/src/CMakeSettings.h

@@ -1,0 +1,18 @@
+/*
+ * CMakeSettings.h
+ *
+ *  Created on: 26 Jul 2013
+ *      Author: Adam Kosiorek
+ */
+
+#ifndef CMAKESETTINGS_H_
+#define CMAKESETTINGS_H_
+
+#define	PROJECT_NAME "Tagger3D"
+#define VERSION_MAJOR 1
+#define VERSION_MINOR 0
+#define VERSION_PATCH 0
+#define VERSION "Tagger3D Version: 1.00"
+
+
+#endif /* CMAKESETTINGS_H_ */

### 2014-02-04 utils/src/Cluster/Cluster.cpp

@@ -1,0 +1,46 @@
+/*
+ * Cluster.cpp
+ *
+ *  Created on: 	20-06-2013
+ *  Author:			Adam Kosiorek
+ *	Description:
+ */
+
+#include "Cluster.h"
+
+#include <stdexcept>
+
+namespace Tagger3D {
+
+Cluster::Cluster(const std::map<std::string, std::string>& _configMap)
+	: ProcessObject(_configMap),
+	  loaded(false) {
+
+	logger = lgr::Logger::getLogger(loggerName);
+	DEBUG(logger, "Creating Cluster");
+
+	clusterCount = getParam<int>(clusterCountKey);
+	dimCount = getParam<int>(dimCountKey);
+}
+
+Cluster::~Cluster() {
+
+	DEBUG(logger, "Destroying Cluster");
+}
+
+cv::Mat Cluster::cluster(const std::vector<cv::Mat> &descriptors) {
+
+	const cv::Mat *dPtr = &descriptors[0];
+	long size = descriptors.size();
+
+	cv::Mat clustered = cluster(dPtr[0]);
+	clustered.reserve(size);
+	for(int i = 1; i < size; ++i) {
+		clustered.push_back(cluster(dPtr[i]));
+	}
+
+	return clustered.clone();
+}
+
+
+} /* namespace Tagger3D */

### 2014-02-04 utils/src/Cluster/Cluster.h

@@ -1,0 +1,93 @@
+/*
+ * Cluster.h
+ *
+ *  Created on: 		20-06-2013
+ *  	Author:			Adam Kosiorek
+ *	Description:
+ */
+
+#ifndef CLUSTER_H_
+#define CLUSTER_H_
+
+#include "../Common/ProcessObject.h"
+
+#include <opencv2/core/core.hpp>
+
+#include <vector>
+
+namespace Tagger3D {
+/**
+ *	The class is a pure virtual class - an interface for clasterization.
+ */
+class Cluster : public ProcessObject {
+public:
+
+
+	/**
+	 *	Parametric constructor.
+	 *	@param	_configMap	A map of configuration parameters
+	 *	@return	void
+	 *	@throws std::invalid_argument
+	 */
+	Cluster(const std::map<std::string, std::string> &_configMap);
+
+	/**
+	 * Default destructor.
+	 */
+	virtual ~Cluster();
+
+	/**
+	 *	The method computes a bag of words description of an input image.
+	 *	@param	descriptors	A set of descriptors for which a bag of words description is to be found.
+	 *	@return cv::Mat	A vector of visual words.
+	 */
+	virtual cv::Mat cluster(const cv::Mat &descriptors) = 0;
+	virtual cv::Mat cluster(const std::vector<cv::Mat> &descriptors);
+
+
+	/**
+	 *	The method trains the clasterizator.
+	 *	@iparam	nputData	a cv::Matrix of [number of descriptor] x [number of points].
+	 *				If points from multiple images are passed than:
+	 *				number of points = number of points in a single image x number of images.
+	 *	@return	bool	true if the training succeded, false otherwise.
+	 */
+	virtual void train(const std::vector<cv::Mat> &descriptors) = 0;
+
+	/**
+	 *	The method saves the KMeans (trained model and configuration) to a folder
+	 * 	specified in a config file.
+	 * 	In case the folder does not exist it will be created.
+	 * 	Note that there should be only one KMeans per folder stored.
+	 * 	@ return true if save successful, false otherwise
+	 */
+	virtual void save() = 0;
+
+
+	/**
+	 *	The method loads the KMeans(trained model and configuration) from a folder
+	 *	specified in a config file.
+	 *	Note that there should be only one KMeans per folder.
+	 *	@return	true if load successful, false otherwise
+	 */
+	virtual void load() = 0;
+
+	virtual bool isLoaded() = 0;
+
[…]

### 2014-02-04 utils/src/Cluster/FisherCluster.h

@@ -1,0 +1,41 @@
+/*
+ * FisherCluster.h
+ *
+ *  Created on: 21 gru 2013
+ *      Author: adam
+ */
+
+#ifndef FISHERCLUSTER_H_
+#define FISHERCLUSTER_H_
+
+#include <Cluster.h>
+
+extern "C" {
+	#include <vl/generic.h>
+	#include <vl/fisher.h>
+	#include <vl/gmm.h>
+
+}
+
+namespace Tagger3D {
+
+class FisherCluster: public Cluster {
+public:
+	FisherCluster() = delete;
+	FisherCluster(const std::map<std::string, std::string> &_configMap);
+	virtual ~FisherCluster();
+
+	virtual cv::Mat cluster(const cv::Mat &descriptors) override;
+	virtual void train(const std::vector<cv::Mat> &descriptors) override;
+	void save() override;
+	void load() override;
+	bool isLoaded() override { return loaded; } ;
+
+private:
+	VlGMM* gmm = nullptr;
+	long encodingSize;
+};
+
+} /* namespace Tagger3D */
+
+#endif /* FISHERCLUSTER_H_ */

### 2014-02-04 utils/src/Cluster/KMeansCluster.cpp

@@ -1,0 +1,147 @@
+/*
+ * KMeansCluster.cpp
+ *
+ *  Created on: 	20-06-2013
+ *  Author:			Adam Kosiorek
+ *	Description:
+ */
+
+#include "KMeansCluster.h"
+#include "IoUtils.h"
+
+#include <opencv2/opencv.hpp>
+//#define NDEBUG
+#include <assert.h>
+
+namespace Tagger3D {
+
+KMeansCluster::KMeansCluster(const std::map<std::string, std::string>& _configMap)
+		: Cluster(_configMap){
+
+	TRACE(logger,"configuring" );
+	kMeans = nullptr;
+	descriptorMatcher = nullptr;
+
+	criteriaEps = getParam<float>(criteriaEpsKey);
+	criteriaItr = getParam<int>(criteriaItrKey);
+	attempts = getParam<int>(attemptsKey);
+	flags = getParam<int>(flagsKey);
+	matcherType = getParam<std::string>(matcherTypeKey);
+	centroidIoName = getParam<std::string>(centroidIoNameKey);
+
+	if( attempts == 0) {
+		std::invalid_argument e("Attemps should be > 0");
+		ERROR(logger, "Constructor: " << e.what() );
+		throw e;
+	}
+
+
+	if( criteriaEps == 0 && criteriaItr == 0) {
+
+		std::invalid_argument e("Invalid end criteria");
+		ERROR(logger, "Constructor: " << e.what() );
+		throw e;
+	}
+
+	createKMeans();
+	createDescriptorMatcher();
+}
+
+void KMeansCluster::createKMeans() {
+
+	TRACE(logger,"createKMeans: Starting" );
+	cv::TermCriteria termCriteria;
+	if(criteriaEps == 0) {
+
+		termCriteria = cv::TermCriteria(cv::TermCriteria::COUNT, criteriaItr, criteriaEps);
+	} else if(criteriaItr == 0) {
+
+		termCriteria = cv::TermCriteria(cv::TermCriteria::EPS, criteriaItr, criteriaEps);
+	} else {
+
+		termCriteria = cv::TermCriteria(cv::TermCriteria::COUNT + cv::TermCriteria::EPS, criteriaItr, criteriaEps);
+	}
+
+	kMeans = std::unique_ptr<cv::BOWKMeansTrainer>(new cv::BOWKMeansTrainer(clusterCount, termCriteria, attempts, flags));
+	TRACE(logger,"createKMeans: Finished" );
+}
[…]

### 2014-02-04 utils/src/Common/Factory.cpp

@@ -1,0 +1,111 @@
+/*
+ * Factory.cpp
+ *
+ *  Created on: 14 gru 2013
+ *      Author: adam
+ */
+
+#include "Factory.h"
+
+#include "RangeImgReader.h"
+#include "PcdReader.h"
+#include "NormalEstimator.h"
+#include "Detector.h"
+#include "SIFTDetector.h"
+#include "Iss3dDetector.h"
+#include "DenseDetector.h"
+
+#include "PFHDescriptor.h"
+#include "FPFHDescriptor.h"
+#include "PFHRGBDescriptor.h"
+#include "ShotDescriptor.h"
+#include "ShotColorDescriptor.h"
+
+#include "KMeansCluster.h"
+#include "LibSVMPredictor.h"
+#include "CvSVMPredictor.h"
+
+#include <stdexcept>
+
+namespace Tagger3D {
+
+Factory::Factory(const std::map<std::string, std::string> &_configMap)
+: ProcessObject(_configMap),
+  configMap(_configMap) {
+
+	logger = lgr::Logger::getLogger(loggerName);
+	DEBUG(logger, "Creating Tagger3D");
+}
+
+std::unique_ptr<ImgReader> Factory::getReader() const {
+
+	std::unique_ptr<ImgReader> imgReader;
+	switch(getParam<int>(readerType)) {
+	case Dataset::TOKYO: imgReader = std::unique_ptr<ImgReader>(new RangeImgReader(configMap)); break;
+	case Dataset::B3DO: imgReader = std::unique_ptr<ImgReader>(new PcdReader(configMap)); break;
+	default:
+		std::runtime_error e("Invalid reader type");
+		ERROR(logger, e.what());
+		throw e;
+	}
+	return imgReader;
+}
+
+std::unique_ptr<PointNormal> Factory::getPointNormal() const {
+
+	return std::unique_ptr<PointNormal> (new NormalEstimator(configMap));
+}
+
+std::unique_ptr<Detector> Factory::getDetector() const {
+
+	std::unique_ptr<Detector> detector;
+	switch( getParam<int>(detectorType)) {
+	case DetectorType::SIFT: detector = std::unique_ptr<Detector> (new SIFTDetector(configMap)); break;
+	case DetectorType::ISS3D: detector = std::unique_ptr<Detector> (new Iss3dDetector(configMap)); break;
+	case DetectorType::DENSE: detector = std::unique_ptr<Detector> (new DenseDetector(configMap)); break;
+	default:
[…]

### 2014-02-04 utils/src/Common/ProcessObject.cpp

@@ -1,0 +1,46 @@
+/*
+ * Tagger3D : ProcessObject.cpp
+ *
+ *  Created on: 	27 lip 2013
+ *  Author:			Adam Kosiorek
+ *	Description:	
+ */
+
+#include "ProcessObject.h"
+#include <fstream>
+
+namespace Tagger3D {
+
+ProcessObject::ProcessObject(const std::map<std::string, std::string> &_configMap) : configMap(_configMap) {
+
+	if( _configMap.empty() ) {
+
+		throw std::invalid_argument("Empty configuration map");
+	}
+
+	directory = getParam<std::string>( directoryKey);
+}
+
+ProcessObject::~ProcessObject() {}
+
+bool ProcessObject::checkConfig(const std::string &key) const{
+
+	if( !configMap.count(key) || configMap.find(key)->second.length() == 0) {
+
+		return false;
+	}
+
+	return true;
+}
+
+std::string ProcessObject::getParam(const std::string &key ) {
+
+	if( !checkConfig( key )) {
+
+		throw std::runtime_error("No parameter " + key + " in the configMap");
+	}
+
+	return configMap.find(key)->second;
+}
+
+} /* namespace Tagger3D */

### 2014-02-04 utils/src/Common/ProcessObject.h

@@ -1,0 +1,80 @@
+/*
+ * Tagger3D : ProcessObject.h
+ *
+ *  Created on: 	27 lip 2013
+ *  Author:			Adam Kosiorek
+ *	Description:	
+ */
+
+#ifndef PROCESSOBJECT_H_
+#define PROCESSOBJECT_H_
+
+#include "logger.h"
+
+#include <string>
+#include <map>
+#include <vector>
+
+#include <sstream>
+#include <typeinfo>
+#include <stdio.h>
+#include <stdexcept>
+#include <iostream>
+
+#include "Utils.h"
+
+namespace Tagger3D {
+
+class ProcessObject {
+public:
+	ProcessObject(const std::map<std::string, std::string> &_configMap);
+	virtual ~ProcessObject();
+
+protected:
+	template<typename T>
+	T getParam(const std::string &key) const;
+	std::string getParam(const std::string &key);
+	bool fileExists(const std::string &path);
+
+	const std::string separator = ".";
+	lgr::LoggerPtr logger;
+	std::string directory;
+	const std::string mode = "mode";
+
+
+private:
+	ProcessObject();
+	bool checkConfig(const std::string &key) const;
+	template<typename T>
+	T stringToNumber(const std::string &s, T def = T() ) const;
+
+	std::map<std::string, std::string> configMap;
+
+
+	const std::string directoryKey = "directory";
+};
+
+template<typename T>
+T ProcessObject::getParam(const std::string &key) const {
+
+	if( !checkConfig( key )) {
+
+		throw std::runtime_error("No parameter " + key + " in the configMap");
+	}
+
+	std::string value = configMap.find(key)->second;
+	return stringToNumber<T>(value);
+}
+
+template<typename T>
+T ProcessObject::stringToNumber(const std::string &s, T def) const {
+
+	std::stringstream ss(s);
+	T result;
+	return ss >> result ? result : def;
+}
+
+} /* namespace Tagger3D */
+#endif /* PROCESSOBJECT_H_ */
+
+

### 2014-02-04 utils/src/Common/Tagger3D.h

@@ -1,0 +1,110 @@
+/*
+ * Tagger3D.h
+ *
+ *   Created on: 23 sie 2013
+ *       Author: Adam Kosiorek
+ *	Description:
+ */
+
+#ifndef TAGGER3D_H_
+#define TAGGER3D_H_
+
+#include "ProcessObject.h"
+#include "ImgReader.h"
+#include "PointNormal.h"
+#include "Detector.h"
+#include "Descriptor.h"
+#include "Cluster.h"
+#include "Predictor.h"
+#include "IoUtils.h"
+#include <memory>
+
+namespace Tagger3D {
+
+/**
+ * Tagger3D is an object categorization.
+ * Provided an RGB-D input it predicts a category of an object.
+ */
+class Tagger3D: public ProcessObject {
+
+	//	-------------------------------------------------------------------------
+	//	Methods	------------------------------------------------------------------
+public:
+	Tagger3D() = delete;
+	Tagger3D(const std::map<std::string, std::string> &configMap);
+	virtual ~Tagger3D();
+
+	/**
+	 * Performs model training
+	 * @param	void
+	 * @return	void
+	 */
+	void train();
+
+	/**
+	 * Performs batch prediction in order to evaluate an average accuracy
+	 * @param void
+	 * @return void
+	 */
+	void test();
+
+	/**
+	 * Predicts a category membership of a provided tuple of rgb and depth images
+	 * @param	rgbPath	path to an rgb image
+	 * @param	depthPath	path to a depth image
+	 * @return	an int value being a category number
+	 */
+	int predict(const std::string &rgbPath, const std::string &depthPath);
+
+	/**
+	 * Launched one of the train, test or predict mode based on the config settings
+	 * @param none
+	 * @return an int number of a category in case the prediction mode was launched
+	 */
+	void run();
+
+	//	Separate run options ------------------------------------------------
+	void descRun();
+	void clustRun();
+	void trainRun();
+	void predRun();
+
+private:
+	std::vector<cv::Mat> computeDescriptors();
+	int getRunMode();
+	int getCatNum(const std::vector<float> &vec) const;
+
+	//	-----------------------------------------------------------------------
+	// Fields	----------------------------------------------------------------
+public:
+private:
+	// Pointers	----------------------------------------------------------------
+	std::unique_ptr<ImgReader> imgReader;
+	std::unique_ptr<PointNormal> pointNormal;
+	std::unique_ptr<Detector> detector;
[…]

### 2014-02-04 utils/src/Common/logger.h

@@ -1,0 +1,23 @@
+/*
+ * logger.h
+ *
+ *  		Created on: 24 Jul 2013
+ *      	Author: Adam Kosiorek
+ *      	Description:	The header contains macros simplyfing the usage of LOG4CXX
+ */
+
+#ifndef LOGGER_H_
+#define LOGGER_H_
+
+#include <log4cxx/logger.h>
+
+#define TRACE(a, b) LOG4CXX_TRACE(a, b)
+#define DEBUG(a, b) LOG4CXX_DEBUG(a, b)
+#define INFO(a, b) LOG4CXX_INFO(a, b)
+#define WARN(a, b) LOG4CXX_WARN(a, b)
+#define ERROR(a, b) LOG4CXX_ERROR(a, b)
+#define FATAL(a, b) LOG4CXX_FATAL(a, b)
+
+namespace lgr = log4cxx;
+
+#endif /* LOGGER_H_ */

### 2014-02-04 utils/src/Config/Config.h

@@ -1,0 +1,49 @@
+/*
+ * Tagger3D : Config.h
+ *
+ *  Created on: 	22 lip 2013
+ *  Author:			Adam Kosiorek
+ *	Description:	A config file parser.
+ */
+
+#ifndef CONFIG_H_
+#define CONFIG_H_
+
+#include "../Common/logger.h"
+
+#include <boost/program_options/variables_map.hpp>
+
+namespace Tagger3D {
+
+class Config {
+public:
+
+	Config(const int _argc, const char **_argv);
+	virtual ~Config();
+
+	/**
+	 *	Prepares and returns a config map.
+	 *	@retun	std::map<std::string, std::string> containing pairs of key=valuegetConfigMap
+	 */
+	std::map<std::string,std::string> getConfigMap();
+
+private:
+
+	int argc;
+	const char** argv;
+
+	const std::string config = "config";
+	const std::string help = "help";
+	const std::string version = "version";
+	const std::string picture = "picture";
+	const std::string mode = "mode";
+	const std::string directory = "directory";
+
+	std::map<std::string,std::string> parseConfigFile(std::string filePath);
+
+	const std::string loggerName = "Main.Config";
+	lgr::LoggerPtr logger;
+};
+
+} /* namespace Tagger3D */
+#endif /* CONFIG_H_ */

### 2014-02-04 utils/src/Descriptor/CloudParser/CloudParser.h

@@ -1,0 +1,96 @@
+/*
+ * Tagger3D : CloudParser.h
+ *
+ *  Created on: 	31 lip 2013
+ *  Author:			Adam Kosiorek
+ *	Description:	Class for parsing different types of point clouds to cv::Mat
+ */
+
+#ifndef CLOUDPARSER_H_
+#define CLOUDPARSER_H_
+
+#include "../../Common/logger.h"
+#include "../../Common/clouds.h"
+#include "PfhTraits.h"
+
+#include <pcl/point_cloud.h>
+#include <pcl/point_types.h>
+#include <opencv2/core/core.hpp>
+
+#include <vector>
+
+namespace Tagger3D {
+
+class CloudParser {
+
+public:
+	CloudParser();
+	virtual ~CloudParser();
+
+	template<typename T>
+	static cv::Mat parse(const typename T::Ptr &cloud);
+
+	template<typename T>
+	static std::vector<cv::Mat> parse(const std::vector<typename T::Ptr> &cloud);
+
+};
+
+template<typename T>
+inline cv::Mat CloudParser::parse(const typename T::Ptr& cloud) {
+
+	int size = cloud->size();
+	int matSize = PfhTraits<typename T::PointType>::size();
+	cv::Mat mat( size, matSize, CV_32FC1 );
+	for(int i = 0; i < size; i++) {
+		float* dPtr = mat.ptr<float>(i);
+		float* hPtr = cloud->points[i].histogram;
+		for(int j = 0; j < matSize; j++)
+			dPtr[j] = hPtr[j];
+	}
+	return mat;
+}
+
+template<>
+inline cv::Mat CloudParser::parse<pcl::PointCloud<pcl::SHOT352>>(const pcl::PointCloud<pcl::SHOT352>::Ptr& cloud) {
+
+	int size = cloud->size();
+	static int matSize = 352;
+	cv::Mat mat( size, matSize, CV_32FC1 );
+	for(int i = 0; i < size; i++) {
+		float* dPtr = mat.ptr<float>(i);
+		float* hPtr = cloud->points[i].descriptor;
+		for(int j = 0; j < matSize; j++)
+			dPtr[j] = hPtr[j];
+	}
+	return mat;
+}
+
+template<>
+inline cv::Mat CloudParser::parse<pcl::PointCloud<pcl::SHOT1344>>(const pcl::PointCloud<pcl::SHOT1344>::Ptr& cloud) {
+
[…]

### 2014-02-04 utils/src/Descriptor/CloudParser/PfhTraits.h

@@ -1,0 +1,24 @@
+/*
+ * PfhTraits.h
+ *
+ *   Created on: 11 paź 2013
+ *       Author: Adam Kosiorek
+ *	Description:
+ */
+
+#ifndef PFHTRAITS_H_
+#define PFHTRAITS_H_
+
+template<typename T>
+struct PfhTraits {
+	static int size() { return -1; };
+	typedef int type;
+};
+
+template<> struct PfhTraits<pcl::FPFHSignature33>{ static int size() { return 33; }; };
+template<> struct PfhTraits<pcl::PFHSignature125>{ static int size() { return 125; }; };
+template<> struct PfhTraits<pcl::PFHRGBSignature250>{ static int size() { return 250; }; };
+template<> struct PfhTraits<pcl::SHOT352>{ static int size() { return 352; }; };
+template<> struct PfhTraits<pcl::SHOT1344>{ static int size() { return 1344; }; };
+
+#endif /* PFHTRAITS_H_ */

### 2014-02-04 utils/src/Descriptor/FPFHDescriptor.cpp

@@ -1,0 +1,53 @@
+/*
+ * FPFHDescriptor.cpp
+ *
+ *   Created on: 30 sie 2013
+ *       Author: Adam Kosiorek
+ *	Description:
+ */
+
+#include "FPFHDescriptor.h"
+#include "CloudParser/CloudParser.h"
+
+#include <assert.h>
+
+namespace Tagger3D {
+
+FPFHDescriptor::FPFHDescriptor(const std::map<std::string, std::string> &configMap) : Descriptor(configMap) {
+
+	radiusSearch = getParam<float>( radiusSearchKey );
+	createFpfhDescriptor();
+	assert(descriptor != nullptr);
+}
+
+FPFHDescriptor::~FPFHDescriptor() {}
+
+void FPFHDescriptor::createFpfhDescriptor() {
+
+	TRACE(logger, "createFpfhDescriptor: Starting");
+	decltype(descriptor) newDescriptor( new pcl::FPFHEstimationOMP<pcl::PointXYZRGB, pcl::Normal, pcl::FPFHSignature33>() );
+	pcl::search::KdTree<pcl::PointXYZRGB>::Ptr kdTree( new pcl::search::KdTree<pcl::PointXYZRGB>() );
+	newDescriptor->setSearchMethod( kdTree );
+	newDescriptor->setRadiusSearch( radiusSearch );
+
+	descriptor = std::move( newDescriptor );
+	TRACE(logger, "createFpfhDescriptor: Finished");
+}
+
+cv::Mat FPFHDescriptor::describe(const ColorCloud::Ptr &cloud, const ScaleCloud::Ptr &keyCloud, const NormalCloud::Ptr &normalCloud) {
+
+	TRACE(logger, "describe fpfh: Starting");
+	FpfhCloud::Ptr descriptors( new FpfhCloud() );
+	ColorCloud::Ptr keyCloudRgb( new ColorCloud() );
+	pcl::copyPointCloud( *keyCloud, *keyCloudRgb);
+	descriptor->setInputNormals( normalCloud );
+	descriptor->setSearchSurface( cloud );
+	descriptor->setInputCloud( keyCloudRgb );
+	descriptor->compute( *descriptors );
+	TRACE(logger, "describe fpfh: Finished; descriptors size = " << descriptors->size());
+	return CloudParser::parse<FpfhCloud>(descriptors);
+}
+
+
+
+} /* namespace Tagger3D */

### 2014-02-04 utils/src/Descriptor/FPFHDescriptor.h

@@ -1,0 +1,45 @@
+/*
+ * FPFHDescriptor.h
+ *
+ *   Created on: 30 sie 2013
+ *       Author: Adam Kosiorek
+ *	Description:
+ */
+
+#ifndef FPFHDESCRIPTOR_H_
+#define FPFHDESCRIPTOR_H_
+
+#include "Descriptor.h"
+
+#include <pcl/features/fpfh_omp.h>
+
+namespace Tagger3D {
+
+/*
+ *
+ */
+class FPFHDescriptor: public Descriptor {
+	/**
+	 *
+	 */
+public:
+	FPFHDescriptor(const std::map<std::string, std::string> &configM);
+	virtual ~FPFHDescriptor();
+
+	cv::Mat describe(const ColorCloud::Ptr &cloud, const ScaleCloud::Ptr &keyCloud, const NormalCloud::Ptr &normalCloud );
+
+private:
+	FPFHDescriptor();
+	void createFpfhDescriptor();
+
+	std::unique_ptr<pcl::FPFHEstimationOMP<pcl::PointXYZRGB, pcl::Normal, pcl::FPFHSignature33>> descriptor;
+
+	//	Config parameters
+	float radiusSearch;
+
+	//	Config keys
+	const std::string radiusSearchKey = moduleName + "radiusSearch";
+};
+
+} /* namespace Tagger3D */
+#endif /* FPFHDESCRIPTOR_H_ */

### 2014-02-04 utils/src/Descriptor/PFHDescriptor.h

@@ -1,0 +1,40 @@
+/*
+ * Tagger3D : PFHDescriptor.h
+ *
+ *  Created on: 	24 lip 2013
+ *  Author:			Adam Kosiorek
+ *	Description:	
+ */
+
+#ifndef PFHDESCRIPTOR_H_
+#define PFHDESCRIPTOR_H_
+
+#include "Descriptor.h"
+
+#include <pcl/features/pfh.h>
+
+
+namespace Tagger3D {
+
+class PFHDescriptor : public Descriptor {
+public:
+	PFHDescriptor(const std::map<std::string, std::string> &configMap);
+	virtual ~PFHDescriptor();
+
+	cv::Mat describe(const ColorCloud::Ptr &cloud, const ScaleCloud::Ptr &keyCloud, const NormalCloud::Ptr &normalCloud );
+
+private:
+	PFHDescriptor();
+	void createPfhDescriptor();
+
+	std::unique_ptr<pcl::PFHEstimation<pcl::PointXYZRGB, pcl::Normal, pcl::PFHSignature125>> descriptor;
+
+	//	Config parameters
+	float radiusSearch;
+
+	//	Config keys
+	const std::string radiusSearchKey = moduleName + "radiusSearch";
+};
+
+} /* namespace Tagger3D */
+#endif /* PFHDESCRIPTOR_H_ */

### 2014-02-04 utils/src/Descriptor/PFHRGBDescriptor.cpp

@@ -1,0 +1,46 @@
+/*
+ * PFHRGBDescriptor.cpp
+ *
+ *   Created on: 11 paź 2013
+ *       Author: Adam Kosiorek
+ *	Description:
+ */
+
+#include "PFHRGBDescriptor.h"
+#include "CloudParser/CloudParser.h"
+
+namespace Tagger3D {
+
+PFHRGBDescriptor::PFHRGBDescriptor(const std::map<std::string, std::string> &configMap) : Descriptor(configMap) {
+	createDescriptor();
+	assert(descriptor != nullptr);
+}
+
+void PFHRGBDescriptor::createDescriptor() {
+
+	TRACE(logger, "createDescriptor: Starting");
+	decltype(descriptor) newDescriptor( new descriptorType() );
+	pcl::search::KdTree<pcl::PointXYZRGB>::Ptr kdTree( new pcl::search::KdTree<pcl::PointXYZRGB>() );
+	newDescriptor->setSearchMethod( kdTree );
+	newDescriptor->setRadiusSearch(getParam<float>(radiusSearch));
+
+	descriptor = std::move( newDescriptor );
+	TRACE(logger, "createDescriptor: Finished");
+}
+
+cv::Mat PFHRGBDescriptor::describe(const ColorCloud::Ptr &cloud, const ScaleCloud::Ptr &keyCloud, const NormalCloud::Ptr &normalCloud) {
+
+	TRACE(logger, "describe PFHRGB: Starting");
+	PfhRgbCloud::Ptr descriptors( new PfhRgbCloud() );
+	ColorCloud::Ptr keyCloudRgb( new ColorCloud() );
+	pcl::copyPointCloud( *keyCloud, *keyCloudRgb);
+	descriptor->setInputNormals( normalCloud );
+	descriptor->setSearchSurface( cloud );
+	descriptor->setInputCloud( keyCloudRgb );
+	descriptor->compute( *descriptors );
+	TRACE(logger, "describe PFHRGB: Finished; descriptors size = " << descriptors->size());
+	return CloudParser::parse<PfhRgbCloud>(descriptors);
+}
+
+
+} /* namespace Tagger3D */

### 2014-02-04 utils/src/Descriptor/PFHRGBDescriptor.h

@@ -1,0 +1,43 @@
+/*
+ * PFHRGBDescriptor.h
+ *
+ *   Created on: 11 paź 2013
+ *       Author: Adam Kosiorek
+ *	Description:
+ */
+
+#ifndef PFHRGBDESCRIPTOR_H_
+#define PFHRGBDESCRIPTOR_H_
+
+#include "Descriptor.h"
+
+#include <pcl/features/pfhrgb.h>
+
+namespace Tagger3D {
+
+/*
+ *
+ */
+class PFHRGBDescriptor: public Descriptor {
+	/**
+	 *
+	 */
+public:
+	PFHRGBDescriptor() = delete;
+	PFHRGBDescriptor(const std::map<std::string, std::string> &configMap);
+	virtual ~PFHRGBDescriptor() = default;
+
+	cv::Mat describe(const ColorCloud::Ptr &cloud, const ScaleCloud::Ptr &keyCloud, const NormalCloud::Ptr &normalCloud );
+
+private:
+
+	void createDescriptor();
+	typedef pcl::PFHRGBEstimation<pcl::PointXYZRGB, pcl::Normal, pcl::PFHRGBSignature250> descriptorType;
+	std::unique_ptr<descriptorType> descriptor;
+
+	//	Config keys
+	const std::string radiusSearch = moduleName + "radiusSearch";
+};
+
+} /* namespace Tagger3D */
+#endif /* PFHRGBDESCRIPTOR_H_ */

### 2014-02-04 utils/src/Descriptor/ShotColorDescriptor.h

@@ -1,0 +1,38 @@
+/*
+ * ShotColorDescriptor.h
+ *
+ *  Created on: 6 sty 2014
+ *      Author: adam
+ */
+
+#ifndef SHOTCOLORDESCRIPTOR_H_
+#define SHOTCOLORDESCRIPTOR_H_
+
+#include <Descriptor.h>
+
+#include <pcl/features/shot_omp.h>
+
+namespace Tagger3D {
+
+class ShotColorDescriptor: public Descriptor {
+public:
+	ShotColorDescriptor() = delete;
+	ShotColorDescriptor(const std::map<std::string, std::string> &configMap);
+	virtual ~ShotColorDescriptor() = default;
+
+	cv::Mat describe(const ColorCloud::Ptr &cloud, const ScaleCloud::Ptr &keyCloud, const NormalCloud::Ptr &normalCloud );
+
+private:
+
+	void createDescriptor();
+	typedef pcl::SHOT1344 PointType;
+	typedef pcl::SHOTColorEstimationOMP<pcl::PointXYZRGB, pcl::Normal, PointType> descriptorType;
+	std::unique_ptr<descriptorType> descriptor;
+
+	//	Config keys
+	const std::string supportRadius = moduleName + "supportRadius";
+};
+
+} /* namespace Tagger3D */
+
+#endif /* SHOTCOLORDESCRIPTOR_H_ */

### 2014-02-04 utils/src/Detector/DenseDetector.cpp

@@ -1,0 +1,33 @@
+/*
+ * DenseDetector.cpp
+ *
+ *  Created on: 16 gru 2013
+ *      Author: adam
+ */
+
+#include <DenseDetector.h>
+
+namespace Tagger3D {
+
+DenseDetector::DenseDetector(const std::map<std::string, std::string> &_configMap)
+	: Detector(_configMap) {
+
+	detector = std::unique_ptr<detectorType>(new detectorType());
+	detector->setRadiusSearch(getParam<float>(radiusSearch));
+}
+
+ScaleCloud::Ptr DenseDetector::detect(const ColorCloud::Ptr &cloud) {
+	TRACE(logger, "detect: Starting")
+
+	pcl::PointCloud<int> sampled_indices;
+	ScaleCloud::Ptr destCloud = ScaleCloud::Ptr(new ScaleCloud());
+
+	detector->setInputCloud(cloud);
+	detector->compute (sampled_indices);
+	pcl::copyPointCloud (*cloud, sampled_indices.points, *destCloud);
+
+	TRACE(logger, "detect: Finished")
+	return destCloud;
+}
+
+} /* namespace Tagger3D */

### 2014-02-04 utils/src/Detector/Detector.h

@@ -1,0 +1,34 @@
+/*
+ * Tagger3D : Detector.h
+ *
+ *  Created on: 	24 lip 2013
+ *  Author:			Adam Kosiorek
+ *	Description:	
+ */
+
+#ifndef DETECTOR_H_
+#define DETECTOR_H_
+
+#include "../Common/clouds.h"
+#include "../Common/ProcessObject.h"
+
+namespace Tagger3D {
+
+class Detector : public ProcessObject {
+public:
+	Detector() = delete;
+	Detector(const std::map<std::string, std::string> &configMap);
+	virtual ~Detector();
+
+	virtual ScaleCloud::Ptr detect(const ColorCloud::Ptr &cloud) = 0;
+	virtual ScaleVec detect(const ColorVec &clouds);
+
+protected:
+	const std::string moduleName = "detector" + separator;
+
+private:
+	const std::string loggerName = "Main.Detector";
+};
+
+} /* namespace Tagger3D */
+#endif /* DETECTOR_H_ */

### 2014-02-04 utils/src/Detector/Iss3dDetector.cpp

@@ -1,0 +1,67 @@
+/*
+ * Iss3dDetector.cpp
+ *
+ *   Created on: 8 wrz 2013
+ *       Author: Adam Kosiorek
+ *	Description:
+ */
+
+#include "Iss3dDetector.h"
+
+#include <pcl/search/kdtree.h>
+#include <assert.h>
+
+namespace Tagger3D {
+
+Iss3dDetector::Iss3dDetector(const std::map<std::string, std::string> &configMap)
+	: Detector(configMap) {
+
+	createDetector();
+	assert(detector != nullptr);
+}
+
+void Iss3dDetector::createDetector() {
+
+	detectorPtrType temp(new pcl::ISSKeypoint3D<pcl::PointXYZRGB, pcl::PointXYZRGB>);
+	pcl::search::KdTree<pcl::PointXYZRGB>::Ptr tree( new pcl::search::KdTree<pcl::PointXYZRGB>() );
+	float resolution = getParam<float>(modelResolution);
+	salientRadius = 6 * resolution;
+	nonMaxRadius = 4 * resolution;
+	normalRadius = 4 * resolution;
+	borderRadius = 1 * resolution;
+
+	temp->setSearchMethod(tree);
+	temp->setSalientRadius(salientRadius);
+	temp->setNonMaxRadius(nonMaxRadius);
+	temp->setBorderRadius(borderRadius);
+	temp->setNormalRadius(normalRadius);
+	temp->setThreshold21(getParam<float>(gamma21));
+	temp->setThreshold32(getParam<float>(gamma32));
+	temp->setMinNeighbors(getParam<int>(minNeighbours));
+	temp->setNumberOfThreads(getParam<int>(threads));
+	detector = std::move(temp);
+}
+
+ScaleCloud::Ptr Iss3dDetector::detect(const ColorCloud::Ptr &cloud) {
+
+	TRACE(logger, "detect: Starting");
+	ColorCloud::Ptr keyPoints(new ColorCloud() );
+	//detector->setSearchSurface( cloud );
+	detector->setInputCloud( cloud );
+
+	detector->compute( *keyPoints);
+	DEBUG(logger, "Detected " << keyPoints->size() << " keypoints");
+	TRACE(logger, "detect: Finished");
+	if(keyPoints->size() == 0) {
+
+		std::runtime_error e("Could not find any keypoints");
+		ERROR(logger, "detect: " << e.what() );
+		throw e;
[…]

### 2014-02-04 utils/src/Detector/Iss3dDetector.h

@@ -1,0 +1,55 @@
+/*
+ * Iss3dDetector.h
+ *
+ *   Created on: 8 wrz 2013
+ *       Author: Adam Kosiorek
+ *	Description:
+ */
+
+#ifndef ISS3DDETECTOR_H_
+#define ISS3DDETECTOR_H_
+
+#include "Detector.h"
+
+#include <pcl/keypoints/iss_3d.h>
+
+namespace Tagger3D {
+
+/*
+ *
+ */
+class Iss3dDetector: public Detector {
+	/**
+	 *
+	 */
+public:
+	Iss3dDetector() = delete;
+	Iss3dDetector(const std::map<std::string, std::string> &configMap);
+	virtual ~Iss3dDetector() = default;
+
+	ScaleCloud::Ptr detect(const ColorCloud::Ptr &cloud);
+
+	typedef pcl::ISSKeypoint3D<pcl::PointXYZRGB, pcl::PointXYZRGB> detectorType;
+	typedef std::unique_ptr<detectorType> detectorPtrType;
+
+private:
+	void createDetector();
+
+	 detectorPtrType detector;
+
+	const std::string
+		gamma21 = moduleName + "gamma21",
+		gamma32 = moduleName + "gamma32",
+		minNeighbours = moduleName + "minNeighbours",
+		threads = moduleName + "threads",
+		modelResolution = moduleName + "modelResolution";
+
+	float
+		salientRadius,
+		nonMaxRadius,
+		normalRadius,
+		borderRadius;
+};
+
+} /* namespace Tagger3D */
+#endif /* ISS3DDETECTOR_H_ */

### 2014-02-04 utils/src/Detector/SIFTDetector.cpp

@@ -1,0 +1,62 @@
+/*
+ * Tagger3D : SIFTDetector.cpp
+ *
+ *  Created on: 	24 lip 2013
+ *  Author:			Adam Kosiorek
+ *	Description:	
+ */
+
+#include "SIFTDetector.h"
+
+#include <pcl/search/kdtree.h>
+#include <assert.h>
+
+namespace Tagger3D {
+
+SIFTDetector::SIFTDetector(const std::map<std::string, std::string> &configMap) : Detector(configMap) {
+
+	minScale = getParam<float>(minScaleKey);
+	octaves = getParam<int>(octavesKey);
+	scalesPerOctave = getParam<int>(scalesPerOctaveKey);
+	minContrast = getParam<float>(minContrastKey);
+	createSiftDetector();
+	assert( siftDetector != nullptr );
+}
+
+SIFTDetector::~SIFTDetector() {}
+
+bool SIFTDetector::createSiftDetector() {
+
+	TRACE(logger, "createSiftDetector: Starting");
+	decltype(siftDetector) detector( new pcl::SIFTKeypoint<pcl::PointXYZRGB, pcl::PointWithScale>() );
+	pcl::search::KdTree<pcl::PointXYZRGB>::Ptr kdTree( new pcl::search::KdTree<pcl::PointXYZRGB>() );
+	detector->setSearchMethod(kdTree);
+	detector->setScales(minScale, octaves, scalesPerOctave);
+	detector->setMinimumContrast(minContrast);
+
+	siftDetector = std::move( detector );
+
+	TRACE(logger, "createSiftDetector: Finished");
+	return true;
+}
+
+ScaleCloud::Ptr SIFTDetector::detect(const ColorCloud::Ptr &cloud) {
+
+	TRACE(logger, "detect: Starting");
+	ScaleCloud::Ptr keyPoints(new ScaleCloud() );
+	siftDetector->setSearchSurface( cloud );
+	siftDetector->setInputCloud( cloud );
+
+	siftDetector->compute( *keyPoints);
+	DEBUG(logger, "Detected " << keyPoints->size() << " keypoints");
+	TRACE(logger, "detect: Finished");
+	if(keyPoints->size() == 0) {
+
+		std::runtime_error e("Could not find any keypoints");
+		ERROR(logger, "detect: " << e.what() );
+		throw e;
+	}
+	return keyPoints;
+}
+
+} /* namespace Tagger3D */

### 2014-02-04 utils/src/Detector/SIFTDetector.h

@@ -1,0 +1,44 @@
+/*
+ * Tagger3D : SIFTDetector.h
+ *
+ *  Created on: 	24 lip 2013
+ *  Author:			Adam Kosiorek
+ *	Description:	
+ */
+
+#ifndef SIFTDETECTOR_H_
+#define SIFTDETECTOR_H_
+
+#include "Detector.h"
+#include <pcl/keypoints/sift_keypoint.h>
+
+namespace Tagger3D {
+
+class SIFTDetector : public Detector {
+public:
+	SIFTDetector(const std::map<std::string, std::string> &configMap);
+	virtual ~SIFTDetector();
+
+	ScaleCloud::Ptr detect(const ColorCloud::Ptr &cloud);
+
+private:
+	SIFTDetector();
+	bool createSiftDetector();
+
+	std::unique_ptr<pcl::SIFTKeypoint<pcl::PointXYZRGB, pcl::PointWithScale>> siftDetector;
+
+	float minScale;
+	int octaves;
+	int scalesPerOctave;
+	float minContrast;
+
+	const std::string minScaleKey = moduleName + "minScale";
+	const std::string octavesKey = moduleName + "octaves";
+	const std::string scalesPerOctaveKey = moduleName + "scalesPerOctave";
+	const std::string minContrastKey = moduleName + "minContrast";
+
+
+};
+
+} /* namespace Tagger3D */
+#endif /* SIFTDETECTOR_H_ */

### 2014-02-04 utils/src/ImgReader/ImgReader.cpp

@@ -1,0 +1,102 @@
+/*
+ * Tagger3D : ImgReader.cpp
+ *
+ *  Created on: 	22 lip 2013
+ *  Author:			Adam Kosiorek
+ *	Description:
+ */
+
+#include "ImgReader.h"
+#include <opencv2/core/types_c.h>
+#include <fstream>
+namespace Tagger3D {
+
+ImgReader::ImgReader(const std::map<std::string, std::string> &configMap) : ProcessObject(configMap) {
+
+	logger = lgr::Logger::getLogger( loggerName );
+	DEBUG(logger, "Creating ImgReader");
+}
+
+ImgReader::~ImgReader() {
+
+	DEBUG(logger, "Destroying ImgReader");
+}
+
+void ImgReader::init() {
+
+	currentMode = -1;
+	std::string stringMode = getParam<std::string>(mode);
+	int tmpMode;
+	bool att = false;
+	if(stringMode == "train") {tmpMode = TRAIN; att = true;}
+	else if(stringMode == "test") {tmpMode = TEST; att = true;}
+	if(att)
+		setMode(tmpMode);
+	else
+		setMode(getParam<int>( mode ));
+}
+
+std::vector<std::string> ImgReader::getLineList(const std::string &path) {
+
+	TRACE(logger, "getImgList: Starting");
+	std::ifstream listFile( path );
+	if( !listFile.good()) {
+
+		std::runtime_error e("Cannot open the following file " + path);
+		ERROR(logger, e.what());
+		throw e;
+	}
+
+	std::string line;
+	std::vector<std::string> imgList;
+	while( !listFile.eof() ) {
+
+		std::getline(listFile, line);
+		if( !line.empty() ) {
+			imgList.push_back( line );
+		}
+
+	}
+	TRACE(logger, "getImgList: Finished");
+	return imgList;
+}
+
+std::string ImgReader::typeToStr(const int &type) {
+
+  std:: string r;
+
+  uchar depth = type & CV_MAT_DEPTH_MASK;
+  uchar chans = 1 + (type >> CV_CN_SHIFT);
+
+  switch ( depth ) {
+    case CV_8U:  r = "8U"; break;
+    case CV_8S:  r = "8S"; break;
+    case CV_16U: r = "16U"; break;
+    case CV_16S: r = "16S"; break;
+    case CV_32S: r = "32S"; break;
+    case CV_32F: r = "32F"; break;
+    case CV_64F: r = "64F"; break;
[…]

### 2014-02-04 utils/src/ImgReader/ImgReader.h

@@ -1,0 +1,59 @@
+/*
+ * Tagger3D : ImgReader.h
+ *
+ *  Created on: 	22 lip 2013
+ *  Author:			Adam Kosiorek
+ *	Description:
+ */
+#ifndef IMGREADER_H_
+#define IMGREADER_H_
+
+#include "../Common/clouds.h"
+#include "../Common/ProcessObject.h"
+
+#include <pcl/point_types.h>
+#include <pcl/point_cloud.h>
+namespace Tagger3D {
+
+class ImgReader : public ProcessObject{
+public:
+	ImgReader(const std::map<std::string, std::string> &configMap);
+	virtual ~ImgReader();
+
+	/**
+	 *	Reads a single image.
+	 *	@return a range image.
+	 */
+	virtual ColorCloud::Ptr readImg() = 0;
+
+	/**
+	 * Returns a label for a previously read image
+	 */
+	virtual int readLabel() = 0;
+
+	/**
+	 * Reads labels for a batch of images
+	 * @return a vector of labels
+	 */
+	virtual std::vector<int> readLabels();
+
+	virtual void setMode(int mode) = 0;
+
+	enum { TRAIN, TEST };
+protected:
+	std::string typeToStr(const int &type);
+	std::vector<std::string> getLineList(const std::string &path);
+	std::string moduleName = "ImgReader" + separator;
+	std::vector<std::string> labelVec;
+
+	int currentMode;
+
+	void init();
+
+
+private:
+	const std::string loggerName = "Main.ImgReader";
+};
+
+} /* namespace Tagger3D */
+#endif /* IMGREADER_H_ */

### 2014-02-04 utils/src/ImgReader/PcdReader.cpp

@@ -1,0 +1,112 @@
+/*
+ * PcdReader.cpp
+ *
+ *   Created on: 29 sie 2013
+ *       Author: Adam Kosiorek
+ *	Description:
+ */
+
+#include "PcdReader.h"
+
+#include <pcl/io/pcd_io.h>
+#include <pcl/visualization/cloud_viewer.h>
+
+#include <assert.h>
+
+namespace Tagger3D {
+
+PcdReader::PcdReader(const std::map<std::string, std::string> &configMap) : ImgReader(configMap) {
+
+	init();
+	voxelGrid = std::unique_ptr<pcl::VoxelGrid<pcl::PointXYZRGB>>(new pcl::VoxelGrid<pcl::PointXYZRGB>());
+	assert(voxelGrid != nullptr);
+	leaf = getParam<float>( leafSize );
+	voxelGrid->setLeafSize(leaf, leaf, leaf);
+
+	count = -1;
+}
+
+PcdReader::~PcdReader() {}
+
+ColorCloud::Ptr PcdReader::readImg(const std::string& pcdPath) {
+
+	ColorCloud::Ptr cloud(new ColorCloud());
+	pcl::io::loadPCDFile(pcdPath, *cloud);
+
+//	for(const auto& point : cloud->points)
+//		std::cout << "x: " << point.x << " y: " << point.y << " z: " << point.z << std::endl;
+
+//	pcl::visualization::CloudViewer viewer ("Simple Cloud Viewer");
+//	viewer.showCloud (cloud);
+//	while (!viewer.wasStopped ())
+//	{
+//	}
+
+	if(leaf != 0) {
+
+		voxelGrid->setInputCloud(cloud);
+		voxelGrid->filter(*cloud);
+	}
+
+//	for(const auto& point : cloud->points)
+//		std::cout << "x: " << point.x << " y: " << point.y << " z: " << point.z << std::endl;
+
+
+
+
+	//std::terminate();
+	DEBUG(logger, "Cloud size = " << cloud->size());
+	return cloud;
+}
+
+ColorCloud::Ptr PcdReader::readImg() {
+
+	count++;
+	ColorCloud::Ptr ptr;
+	if(count < pcdVec.size())
+		ptr = readImg(pcdVec[count]);
+	else
+		ptr = ColorCloud::Ptr(new ColorCloud());
+
+	if(ptr->empty() && count < pcdVec.size()) {
+
+		std::runtime_error e("Corrupted point cloud #" + count);
+		ERROR(logger, "readImg: " << e.what());
[…]

### 2014-02-04 utils/src/ImgReader/RangeImgReader.cpp

@@ -1,0 +1,198 @@
+/*
+ * Tagger3D : RangeImgReader.cpp
+ *
+ *  Created on: 	22 lip 2013
+ *  Author:			Adam Kosiorek
+ *	Description:
+ */
+
+#include "RangeImgReader.h"
+
+#include <opencv2/highgui/highgui.hpp>
+#include <opencv2/imgproc/imgproc.hpp>
+#include <pcl/filters/filter.h>
+#include <pcl/visualization/cloud_viewer.h>
+#include <fstream>
+
+namespace Tagger3D {
+
+RangeImgReader::RangeImgReader(const std::map<std::string, std::string> &configMap) : ImgReader(configMap) {
+
+	init();
+	count = -1;
+	resize = getParam<int>( resizeKey );
+}
+
+RangeImgReader::~RangeImgReader() {}
+
+ColorCloud::Ptr RangeImgReader::matToCloud(const cv::Mat &colorImg, const cv::Mat &depthImg) {
+
+	TRACE(logger, "MatToCloud: Starting");
+	int height = depthImg.rows;
+	int width = depthImg.cols;
+
+	int height2 = height/2;
+	int width2 = width/2;
+	float factorX = factorX0 / width;
+	float factorY = factorY0 / height;
+
+	if( height != colorImg.rows || width != colorImg.cols ) {
+
+		std::runtime_error e("Images have different dimensions");
+		ERROR(logger, "MatToCloud: " << e.what() );
+		throw e;
+	}
+	ColorCloud::Ptr cloud( new ColorCloud() );
+	cloud->height = height;
+	cloud->width = width;
+	cloud->reserve(height * width);
+	cloud->is_dense = false;
+
+	pcl::PointXYZRGB newPoint;
+	for (int y = 0; y < height; y++) {
+
+		// For the sake of simplicity
+		typedef ushort MatType;
+		const MatType *depthPtr = depthImg.ptr<MatType>(y);
+		const cv::Vec3b *colorPtr = colorImg.ptr<cv::Vec3b>(y);
+
+		for (int x = 0; x < width; x++) {
+			float depth = depthPtr[x] / 1000.0f;
+
+			if ( depth == depth) {            // if depthValue is not NaN
+
+				newPoint.z = depth;
+				newPoint.x = (x - width2) * factorX * depth;
+				newPoint.y = (y - height2) * factorY * depth;
[…]

### 2014-02-04 utils/src/PointNormal/NormalEstimator.cpp

@@ -1,0 +1,69 @@
+/*
+ * Tagger3D : NormalEstimator.cpp
+ *
+ *  Created on: 	28 lip 2013
+ *  Author:			Adam Kosiorek
+ *	Description:	
+ */
+
+#include "NormalEstimator.h"
+
+#include <pcl/search/kdtree.h>
+#include <pcl/filters/filter.h>
+#include <assert.h>
+
+namespace Tagger3D {
+
+NormalEstimator::NormalEstimator(const std::map<std::string, std::string> &configMap) : PointNormal(configMap) {
+
+	createNormalEstimator();
+	assert( normalEstimator != nullptr );
+}
+
+void NormalEstimator::createNormalEstimator() {
+
+	TRACE(logger, "createNormalEstimator: Starting");
+	std::unique_ptr<pcl::NormalEstimationOMP<pcl::PointXYZRGB, pcl::Normal>> estimator(new pcl::NormalEstimationOMP<pcl::PointXYZRGB, pcl::Normal>() );
+	pcl::search::KdTree<pcl::PointXYZRGB>::Ptr kdTree( new pcl::search::KdTree<pcl::PointXYZRGB>() );
+	estimator->setSearchMethod( kdTree );
+
+	float radius = getParam<float>( normalRadius );
+	if(radius > 0)
+		estimator->setRadiusSearch( radius );
+	else {
+		int k = getParam<int>( kNN );
+		assert(k > 0);
+		estimator->setKSearch(k);
+	}
+
+	normalEstimator = std::move( estimator );
+	TRACE(logger, "createNormalEstimator: Finished");
+}
+
+NormalCloud::Ptr NormalEstimator::computeNormals(const ColorCloud::Ptr &cloud) {
+
+	TRACE(logger, "computeNormals: Starting");
+
+	NormalCloud::Ptr normalCloud( new NormalCloud() );
+	normalEstimator->setInputCloud( cloud );
+	normalEstimator->compute( *normalCloud );
+	pcl::removeNaNNormalsFromPointCloud( *normalCloud, *normalCloud, index);
+
+	TRACE(logger, "computeNormals: Finished");
+	return normalCloud;
+}
+
+NormalVec NormalEstimator::computeNormals(const ColorVec &clouds) {
+
+	TRACE(logger, "computeNormals: Starting batch processing");
+	NormalVec vec;
+	for(auto &cloud : clouds) {
+
[…]

### 2014-02-04 utils/src/PointNormal/NormalEstimator.h

@@ -1,0 +1,39 @@
+/*
+ * Tagger3D : NormalEstimator.h
+ *
+ *  Created on: 	28 lip 2013
+ *  Author:			Adam Kosiorek
+ *	Description:	
+ */
+
+#ifndef NORMALESTIMATOR_H_
+#define NORMALESTIMATOR_H_
+
+#include "PointNormal.h"
+
+#include <pcl/features/normal_3d_omp.h>
+
+namespace Tagger3D {
+
+class NormalEstimator: public PointNormal {
+public:
+	NormalEstimator() = delete;
+	NormalEstimator(const std::map<std::string, std::string> &configMap);
+	virtual ~NormalEstimator() = default;
+
+	NormalCloud::Ptr computeNormals(const ColorCloud::Ptr &cloud);
+	NormalVec computeNormals(const ColorVec &clouds);
+
+
+private:
+	void createNormalEstimator();
+
+	std::unique_ptr<pcl::NormalEstimationOMP<pcl::PointXYZRGB, pcl::Normal>> normalEstimator;
+
+	//	Config keys
+	const std::string normalRadius = moduleName + "normalRadius";
+	const std::string kNN = moduleName + "kNN";
+};
+
+} /* namespace Tagger3D */
+#endif /* NORMALESTIMATOR_H_ */

### 2014-02-04 utils/src/PointNormal/PointNormal.cpp

@@ -1,0 +1,46 @@
+/*
+ * Tagger3D : PointNormal.cpp
+ *
+ *  Created on: 	28 lip 2013
+ *  Author:			Adam Kosiorek
+ *	Description:	
+ */
+
+#include "PointNormal.h"
+
+namespace Tagger3D {
+
+PointNormal::PointNormal(const std::map<std::string, std::string> &configMap) : ProcessObject(configMap){
+
+	logger = lgr::Logger::getLogger( loggerName );
+	DEBUG(logger, "Creating PointNormal");
+}
+
+PointNormal::~PointNormal() {
+
+	DEBUG(logger, "Destroying PointNormal");
+}
+
+void PointNormal::cleanupInputCloud( ColorCloud::Ptr &cloud) {
+
+	TRACE(logger, "cleanupInputCloud: Starting");
+	size_t j = 0;
+	size_t indexSize = index.size();
+	size_t cloudSize = cloud->points.size();
+	if( cloudSize == indexSize ) {
+
+		return;
+	}
+
+	for(size_t i = 0; i < indexSize; ++i) {
+
+		cloud->points[i] = cloud->points[index[i]];
+	}
+
+	cloud->resize(indexSize);
+	cloud->height = 1;
+	cloud->width = indexSize;
+	TRACE(logger, "cleanupInputCloud: Finished");
+}
+
+} /* namespace Tagger3D */

### 2014-02-04 utils/src/PointNormal/PointNormal.h

@@ -1,0 +1,39 @@
+/*
+ * Tagger3D : PointNormal.h
+ *
+ *  Created on: 	28 lip 2013
+ *  Author:			Adam Kosiorek
+ *	Description:	
+ */
+
+#ifndef POINTNORMAL_H_
+#define POINTNORMAL_H_
+
+#include "../Common/clouds.h"
+#include "../Common/ProcessObject.h"
+
+#include <pcl/point_types.h>
+#include <pcl/point_cloud.h>
+
+namespace Tagger3D {
+
+class PointNormal: public Tagger3D::ProcessObject {
+public:
+	PointNormal(const std::map<std::string, std::string> &configMap);
+	virtual ~PointNormal();
+
+	virtual NormalCloud::Ptr computeNormals(const ColorCloud::Ptr &cloud) = 0;
+	virtual NormalVec computeNormals(const ColorVec &clouds) = 0;
+	void cleanupInputCloud(ColorCloud::Ptr &cloud);
+
+protected:
+	const std::string moduleName = "PointNormal" + separator;
+	std::vector<int> index;
+
+private:
+	PointNormal();
+	const std::string loggerName = "Main.PointNormal";
+};
+
+} /* namespace Tagger3D */
+#endif /* POINTNORMAL_H_ */

### 2014-02-04 utils/src/Predictor/CvSVMPredictor.h

@@ -1,0 +1,77 @@
+/*
+ * CvSVMPredictor.h
+ *
+ *  Created on: August 22, 2013
+ *      Author: Adam Kosiorek
+ * Description: SVM predictor class declaration
+ */
+
+#ifndef SVMPREDICTER_H_
+#define SVMPREDICTER_H_
+
+#include "Predictor.h"
+
+#include <opencv2/core/core.hpp>
+#include <opencv2/highgui/highgui.hpp>
+#include <opencv2/ml/ml.hpp>
+
+
+namespace Tagger3D {
+
+/**
+ * SVM predictor class. Predicts to which category an image belongs to
+ */
+class CvSVMPredictor: public Predictor {
+public:
+
+	CvSVMPredictor();
+	/**
+	 * Parametric constructor
+	 * @param _configMap - a map of configuration parameters
+	 */
+	CvSVMPredictor(const std::map<std::string, std::string> &_configMap,
+			const std::string &predictorType = "predictor");
+
+	/**
+	 * Default descrutor
+	 */
+	virtual ~CvSVMPredictor();
+
+	virtual void train(cv::Mat &data, const std::vector<int> &labels) override;
+	virtual std::vector<float> predict(const cv::Mat &visualWords) override;
+	virtual void load() override;
+	virtual void save() override;
+
+private:
+	virtual void createSVM();
+
+    CvSVMParams params;
+    CvSVM SVM;
+
+    // Configuration parameters
+    std::string svmPath;
+    std::string histogramPath;
+    bool storeHistogram;
+    int dictionarySize;
+
+    //	Configuration keys
+    const std::string svmType = moduleName + "svmType";
+    const std::string kernelType = moduleName + "kernelType";
+    const std::string termCrit = moduleName + "termCrit";
+    const std::string svmPathKey = moduleName + "svmPath";
+    const std::string epsilon = moduleName + "eps";
+    const std::string maxIter = moduleName + "maxIter";
+    const std::string degree = moduleName + "degree";
+    const std::string gamma = moduleName + "gamma";
+    const std::string C = moduleName + "C";
+
+    const int svmMatType = CV_32F;
+
+    const std::string normValuesFile = "maxValues.xml";
+    const std::string key = "key";
+
+
+};
+
+} /* namespace semantic_tagger */
+#endif /* SVMPREDICTER_H_ */

### 2014-02-04 utils/src/Predictor/LibSVMPredictor.h

@@ -1,0 +1,73 @@
+/*
+ * LibSVMPredictor.h
+ *
+ *  Created on: August 22, 2013
+ *      Author: Adam Kosiorek
+ * Description: SVM predictor class declaration
+ */
+
+#ifndef SVMPREDICTOR_H_
+#define SVMPREDICTOR_H_
+
+#include "Predictor.h"
+
+#include <svm.h>
+#include <opencv2/core/core.hpp>
+
+namespace Tagger3D {
+
+/**
+ * SVM predictor class. Predicts to which category an image belongs to
+ */
+class LibSVMPredictor: public Predictor {
+public:
+	LibSVMPredictor() = delete;
+
+	/**
+	 * Parametric constructor
+	 * @param _configMap - a map of configuration parameters
+	 */
+	LibSVMPredictor(const std::map<std::string, std::string> &_configMap,
+			const std::string &predictorType = "predictor");
+
+	/**
+	 * Default descrutor
+	 */
+	virtual ~LibSVMPredictor();
+
+	virtual void train(cv::Mat &data, const std::vector<int> &labels) override;
+	virtual std::vector<float> predict(const cv::Mat &visualWords) override;
+	virtual void load() override;
+    virtual void save() override;
+
+private:
+    virtual void createSVM();
+
+    // Configuration parameters
+    std::string model;
+    std::string histogramPath;
+
+    bool storeHistogram;
+
+    //	Configuration keys
+    const std::string svmTypeKey = moduleName + "svmType";
+    const std::string kernelTypeKey = moduleName + "kernelType";
+
+    const std::string degreeKey = moduleName + "degree";
+    const std::string gammaKey = moduleName + "gamma";
+    const std::string coef0Key = moduleName + "coef0";
+    const std::string epsKey = moduleName + "eps";
+    const std::string cache_sizeKey = moduleName + "cacheSize";
+    const std::string pKey = moduleName + "p";
+    const std::string shrinkingKey = moduleName + "shrinking";
+    const std::string probabilityKey = moduleName + "probability";
+    const std::string nr_weightKey = moduleName + "nrWeight";
+    const std::string CKey = moduleName + "C";
+    const std::string modelKey = moduleName + "svmPath";
+
+    svm_parameter params;
+    svm_model* svmModel;
+};
+
+} /* namespace Tagger3d */
+#endif /* SVMPREDICTOR_H_ */

### 2014-02-04 utils/src/Predictor/Predictor.cpp

@@ -1,0 +1,91 @@
+/*
+ * Predictor.cpp
+ *
+ *  Created on: Jul 4, 2013
+ *      Author: Adam Kosiorek
+ * Description: Predictor base class implementation
+ */
+
+#include "Predictor.h"
+
+#include <opencv2/core/core.hpp>
+
+namespace Tagger3D {
+
+Predictor::Predictor(const std::map<std::string, std::string> &_configMap,
+		const std::string predictorType)
+
+	: ProcessObject(_configMap),
+	  moduleName(predictorType + separator) {
+
+
+	logger = lgr::Logger::getLogger(loggerName);
+	DEBUG(logger, "Creating Predictor");
+
+	if( _configMap.empty() ) {
+
+		throw std::invalid_argument("Empty configuration map");
+	}
+	io = IoUtils::getInstance();
+	class_number = getParam<int>(class_numberKey);
+	normalizationPath = getParam<std::string>(normalizationPathKey);
+}
+
+Predictor::~Predictor() {
+
+	TRACE(logger, "Destroying Predictor");
+}
+
+void Predictor::normaliseData(cv::Mat &mat) {
+
+	assert(!v_max.empty());
+	mat = (mat / repeat(v_max,  mat.rows, 1)) * 2 - 1;
+}
+
+const cv::Mat Predictor::computeMaxValues(const cv::Mat& mat) {
+//	v_max = cv::Mat(1, mat.cols, CV_32SC1);
+	cv::reduce(mat, v_max, REDUCE_TO_ROW, CV_REDUCE_MAX);
+	TRACE(logger, "v_max size = " << v_max.size());
+	return v_max;
+}
+
+cv::Mat Predictor::confusionMatrix(const std::vector<int> &labels, const std::vector<int> &predictions) const {
+
+	int size = labels.size();
+	int classes = labels[size-1] + 1;
+	const int *lPtr = &labels[0];
+	const int *pPtr = &predictions[0];
+	cv::Mat confusionMatrix = cv::Mat::zeros(classes, classes, CV_8UC1);
+	for(int i = 0; i < size; i++) {
+
+		confusionMatrix.at<uchar>(lPtr[i], pPtr[i]) += 1;
+	}
+
+	cv::Mat classCount;
+	cv::reduce(confusionMatrix, classCount, 1, CV_REDUCE_SUM, CV_32SC1);
+	cv::Mat average(1, classes, CV_32FC1);
+	float avg = 0;
[…]

### 2014-02-04 utils/src/Predictor/Predictor.h

@@ -1,0 +1,93 @@
+/*
+ * Predictor.h
+ *
+ *  	Created on: Jul 4, 2013
+ *      Author: Adam Kosiorek
+ *  	Description: Predictor base class declaration
+ */
+
+#ifndef PREDICTOR_H_
+#define PREDICTOR_H_
+
+#include "ProcessObject.h"
+#include "IoUtils.h"
+
+#include "opencv2/imgproc/imgproc.hpp"
+#include "opencv2/highgui/highgui.hpp"
+
+#include <vector>
+#include <memory>
+
+namespace Tagger3D {
+
+/**
+ * Base class for predictors.
+ */
+class Predictor : public ProcessObject {
+public:
+
+	Predictor() = delete;
+	/**
+	 * Parametric constructor
+	 * @param _configMap	a key-value map of configuration parameters
+	 */
+	Predictor(const std::map<std::string, std::string> &_configMap,	const std::string predictorType);
+
+	/**
+	 * Default descrutors
+	 */
+	virtual ~Predictor();
+
+	/**
+	 * Trains the predictor using specified vectors of visual words and their labels
+	 * @param	vecs a vector of vectors of visual words
+	 * @param	labels a vector of labels
+	 */
+	virtual void train(cv::Mat &data, const std::vector<int> &labels) = 0;
+
+	/**
+	 * Predics a class of an input image
+	 * @param	visualWords	a vec of visual words describing a single image
+	 * @return	void
+	 */
+    virtual std::vector<float> predict(const cv::Mat &visualWords) = 0;
+
+    virtual void load() = 0;
+    virtual void save() = 0;
+
+protected:
+
+	virtual void createSVM() = 0;
+	virtual void normaliseData(cv::Mat &mat);
+	virtual const cv::Mat computeMaxValues(const cv::Mat& mat) ;
+	cv::Mat confusionMatrix(const std::vector<int> &labels, const std::vector<int> &predictions) const;
+	void saveVMax();
+	void loadVMax();
+
+	/**
+	 * Name of the module in a config map
+	 */
+	const std::string moduleName;
+    std::shared_ptr<IoUtils> io;
+
+    int class_number;
+    int dims;
+    std::string normalizationPath;
+
+private:
+
+	/**
+	 * Name of the logger
+	 */
+	const std::string loggerName = "Main.Predictor";
+	const std::string class_numberKey = moduleName + "classes";
[…]

### 2014-02-04 utils/src/Utilities/IoUtils.h

@@ -1,0 +1,401 @@
+/*
+ * IoUtils.h
+ *
+ *  Created on: 4 Oct 2013
+ *      Author: Adam Kosiorek
+ * Description: 
+ */
+
+#ifndef IOUTILS_H_
+#define IOUTILS_H_
+
+#include "logger.h"
+#include "TypeTraits.h"
+#include "VectorIO.h"
+
+#include <opencv2/core/core.hpp>
+#include <fstream>
+#include <stdexcept>
+#include <memory>
+#include<iterator>
+ #include <iostream>
+
+extern "C" {
+    #include <vl/generic.h>
+    #include <vl/fisher.h>
+    #include <vl/gmm.h>
+}
+
+namespace Tagger3D {
+
+/*
+ *
+ */
+class IoUtils {
+
+//	Methods ----------------------------------------------------------------------------------
+public:
+	virtual ~IoUtils();
+
+
+    VlGMM* loadGMMText(const std::string &filename, int& dimension, int& numClusters) const{
+        FILE * pFile;
+        pFile = fopen (filename.c_str(),"r");
+        fscanf (pFile, "dimension: %d numClusters: %d", &dimension, &numClusters);
+        int& DIM = dimension;
+        int& NUMCLUST = numClusters;
+        VlGMM* gmm = vl_gmm_new (VL_TYPE_FLOAT, DIM, NUMCLUST) ;
+
+        //loading means
+        float* means = new float[DIM*NUMCLUST];
+        for(int clust = 0; clust < NUMCLUST; ++clust){
+            for(int dim = 0; dim < DIM; ++dim){
+                fscanf(pFile, "%f", &means[clust*DIM+dim]);
+            }
+        }
+        vl_gmm_set_means (gmm, means);
+        delete [] means;
+
+        //loading priors
+        float* priors = new float[DIM*NUMCLUST];
+        for(int clust = 0; clust < NUMCLUST; ++clust){
+            for(int dim = 0; dim < DIM; ++dim){
+                fscanf(pFile, "%f", &priors[clust*DIM+dim]);
+            }
+        }
+        vl_gmm_set_priors (gmm, priors);
+        delete [] priors;
+
+        //loading covariances
+        float* covariances = new float[DIM*NUMCLUST];
+        for(int clust = 0; clust < NUMCLUST; ++clust){
+            for(int dim = 0; dim < DIM; ++dim){
+                fscanf(pFile, "%f", &covariances[clust*DIM+dim]);
+            }
[…]

### 2014-02-04 utils/src/Utilities/TypeTraits.h

@@ -1,0 +1,121 @@
+/*
+ * CvTypeTraits.h
+ *
+ *  Created on: 4 Oct 2013
+ *      Author: Adam Kosiorek
+ * Description: 
+ */
+
+#ifndef CVTYPETRAITS_H_
+#define CVTYPETRAITS_H_
+
+#include <opencv2/core/types_c.h>
+#include <opencv2/core/core.hpp>
+#include <stdexcept>
+
+//	CvTypeTraits -------------------------------------------------------------------------------------
+
+template<typename T> struct CvTypeTraits {
+static int type() { throw std::logic_error("Unimplemented"); }
+};
+
+template<> struct CvTypeTraits<uchar> {
+	static int type() {	return CV_8UC1; }
+};
+
+template<> struct CvTypeTraits<ushort> {
+	static int type() {	return CV_16UC1; }
+};
+
+template<> struct CvTypeTraits<int> {
+	static int type() {	return CV_32SC1; }
+};
+
+template<> struct CvTypeTraits<float> {
+	static int type() {	return CV_32FC1; }
+};
+
+template<> struct CvTypeTraits<double> {
+	static int type() {	return CV_64FC1; }
+};
+
+
+//	CvMatTraits -------------------------------------------------------------------------------------
+
+
+template<int i> struct CvMatTraits {
+	typedef int type;
+};
+
+template<> struct CvMatTraits<CV_8UC1> {
+	typedef uchar type;
+};
+
+template<> struct CvMatTraits<CV_16UC1> {
+	typedef ushort type;
+};
+
+template<> struct CvMatTraits<CV_32SC1> {
+	typedef int type;
+};
+
+template<> struct CvMatTraits<CV_32FC1> {
+	typedef float type;
+};
+
+template<> struct CvMatTraits<CV_64FC1> {
+	typedef double type;
+};
+
+//	Type traits -------------------------------------------------------------------------------------
+
+//	Vector
+template<typename T>
+struct isVector{ static const int value = 0; };
+
+template<typename T, typename A>
+struct isVector<std::vector<T, A>>{ static const int value = 1; };
+
+//	Mat
+template<typename T>
+struct isMat{ static const int value = 0; };
+
+template<>
+struct isMat<cv::Mat>{ static const int value = 1; };
+
+//	Type names --------------------------------------------------------------------------------------
+
+template<typename T> struct TypeStr {
+	static std::string str() { throw std::logic_error("Unimplemented"); };
+};
+
[…]

### 2014-02-04 utils/src/Utilities/Utils.cpp

@@ -1,0 +1,63 @@
+/*
+ * Utils.cpp
+ *
+ *  Created on: 21 Nov 2013
+ *      Author: Adam Kosiorek
+ * Description: 
+ */
+
+#include "Utilities/Utils.h"
+
+#include "opencv2/highgui/highgui.hpp"
+
+#include <stdexcept>
+
+namespace Tagger3D {
+
+Utils::Utils() {
+	// TODO Auto-generated constructor stub
+
+}
+
+Utils::~Utils() {
+	// TODO Auto-generated destructor stub
+}
+
+
+int Utils::visualizeKeypoints(const cv::Mat &img, std::vector<cv::KeyPoint> &keys){
+
+    cv::Mat imgWithKeys;    // save image with visualised keypoints
+    try {
+		cv::drawKeypoints(img, keys, imgWithKeys);
+		cv::imshow("KeyPoints Visualisation", imgWithKeys);
+    } catch(std::runtime_error &e) {
+        return 0;
+    }
+    cv::waitKey(0);
+    return 1;
+}
+
+std::string Utils::cvType2Str(int type) {
+  std::string r;
+
+  uchar depth = type & CV_MAT_DEPTH_MASK;
+  uchar chans = 1 + (type >> CV_CN_SHIFT);
+
+  switch ( depth ) {
+    case CV_8U:  r = "8U"; break;
+    case CV_8S:  r = "8S"; break;
+    case CV_16U: r = "16U"; break;
+    case CV_16S: r = "16S"; break;
+    case CV_32S: r = "32S"; break;
+    case CV_32F: r = "32F"; break;
+    case CV_64F: r = "64F"; break;
+    default:     r = "User"; break;
+  }
+
+  r += "C";
+  r += (chans+'0');
+
+  return r;
+}
+
+} /* namespace Tagger3D */

### 2014-02-06 Disseration/article.tex
latest changes
added factory class, changing modes to desc, clust, train pred
przeredagowane 1/2
done editing, now have to run some tests
aha

--- 2013-10-11 Disseration/article.tex
@@
-\documentclass[a4paper,12pt]{article}
+%TODO
+%	- run cluster and descriptors tests
+%	- find out what's wrong with sift detector
+%	- run detector tests
+%	- prepare strategy pattern class diagram and describe it
+%	- write conclusions
+%	- describe libraries
+%	- write abstracts
+%	- go through introduction
+%
+%
+%
+
+\documentclass[12pt]{report}
 \usepackage[utf8]{inputenc}
 \usepackage[T1]{fontenc}
-\usepackage[top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
+\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
 \usepackage{cite}
+\usepackage{graphicx}
+\usepackage{color}
+\usepackage[font=footnotesize]{caption}
+\usepackage{amsmath}
+\usepackage[hidelinks]{hyperref}
+\usepackage{paralist}
+\usepackage{tocbibind}
+%\usepackage[nottoc,notlof,notlot]{tocbibind}
 
-%\setlength{\parskip}{6pt}%
+%\renewcommand{\chaptername}{}
+%\renewcommand{\thechapter}{}
+
 \linespread{1.5}
@@
 \newcommand{\subscript}[1]{\ensuremath{_{\textrm{#1}}}}
+\newcommand\rednote[1]{\textcolor{red}{#1}}
 
-%opening
-\title{Object Categorization based on RGBD data}
-\author{Adam Kosiorek}
+\makeatletter
+% Redefine the \chapter* header macro to remove vertical space
+\def\@makeschapterhead#1{%
+  %\vspace*{50\p@}% Remove the vertical space
+  {\parindent \z@ \raggedright
+    \normalfont
+    \interlinepenalty\@M
+    \Huge \bfseries  #1\par\nobreak
+    \vskip 20\p@
+  }}
+\makeatother
+
 \bibliographystyle{abbrv}
@@
 
-\maketitle
+\include{titlepage}
+%\include{zyciorys}
 
-\include{streszczenie}
+\pagestyle{plain}
+
 \include{abstract}
-\include{introduction} %aka motivation
-\include{bow}
-\include{libs}
-\include{datasets}
+
+\tableofcontents
+\include{introduction}
 \include{architecture}
-\include{setup}
 \include{experiments}
-\include{conclusion}
+
+\listoffigures
+\listoftables
 
@@
 
+\appendix
+\chapter{Source code}
+	The source code of the main programme as well as all the scripts and a sample configuration file are included on an attached CD.
 \end{document}

### 2014-02-06 Disseration/zyciorys.tex
aha

@@
+  \documentclass[12pt]{report}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
+\usepackage{cite}
+\usepackage{graphicx}
+\usepackage{color}
+\usepackage[font=footnotesize]{caption}
+\usepackage{amsmath}
+\usepackage[hidelinks]{hyperref}
+\usepackage{paralist}
+\usepackage{tocbibind}
+%\usepackage[nottoc,notlof,notlot]{tocbibind}
+
+%\renewcommand{\chaptername}{}
+%\renewcommand{\thechapter}{}
+
+\linespread{1.5}
+
+\newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}
+\newcommand{\subscript}[1]{\ensuremath{_{\textrm{#1}}}}
+\newcommand\rednote[1]{\textcolor{red}{#1}}
+
+\makeatletter
+% Redefine the \chapter* header macro to remove vertical space
+\def\@makeschapterhead#1{%
+  %\vspace*{50\p@}% Remove the vertical space
+  {\parindent \z@ \raggedright
+    \normalfont
+    \interlinepenalty\@M
+    \Huge \bfseries  #1\par\nobreak
+    \vskip 20\p@
+  }}
+\makeatother
+
+\begin{document}
+
   \vspace*{1\baselineskip}
@@
 I started a Bachelor of Engineering degree on the Faculty of Mechatronics of Warsaw University of Technology on 1 October 2010.
-I did an internship in Faurecia R\&D S.A.
+I did an internship in Faurecia~R\&D~S.A.
 in 2012.
-In 2013 I started working in IBM Poland Sp.
-z o.o.
-where I stayed for 6 months.
-Then I started working full-time in Samsung R\&D Centre Poland.
+I joined IBM Poland Sp.~z~o.~o.
+in January, 2013.
+Then, I started working full-time in Samsung R\&D Centre Poland as a Computer Vision Engineer.
+I am an avid long distance runner and a keen reader of fantastic literature and thrillers.
 
@@
     \vspace{3\baselineskip}
+
+\end{document}

### 2014-02-06 Disseration/ppt/main.tex
aha2

@@
 
-\begin{frame}
-  \setcounter{framenumber}{1}
-  \frametitle{Założenia}
+\begin{frame}{Założenia}
+  %\setcounter{framenumber}{1}
 
-   Założeniem pracy jest zbadanie zagadnienia klasyfikacji obiektów 3D na podstawie zdjęć RGBD.
-Zdjęcia powinny byc zrobione kamerą Microsoft Kinect oraz być reprezentowane w formie chmur punktów.
-Ponadto zakłada się: \ \\
+   Założeniem pracy jest zbadanie zagadnienia klasyfikacji metodą Bag of Words obiektów 3D na podstawie zdjęć RGBD.
+Zdjęcia powinny byc reprezentowane w formie chmur punktów.
+Ponadto zakłada się, że: \ \\
   \begin{itemize}
-   \item Zaprojektowanie algorytmu rozpoznawania obrazów podejściem Bag of Words
-   \item 
+   \item Analizowane dane pochodzą z kamery RGBD Microsoft Kinect
+   \item Implementacja algorytmu w języku C++ z wykorzystaniem bibliotek OpenCV i/lub PointCloud Library
+   \item Testy aplikacji na ogólnie dostępnej, naukowej bazie danych
   \end{itemize}
@@
 \begin{frame}{Zakres pracy}
+  \begin{enumerate}
+    \item Przegląd istniejących rozwiązań dotyczących klasyfikacji obiektów na podstawie chmur punktów
+    \item Opracowanie algorytmu klasyfikacji obiektów na podstawie chmur punktów
+    \item Implementacja algorytmu w języku C++ 
+    \item Przeprowadzenie testów szybkości oraz skuteczności klasyfikacji 
+    \item Opracowanie wniosków końcowych
+  \end{enumerate}
 \end{frame}
@@
 \section{Podejście Bag of Words}
-\begin{frame}
-  \frametitle{Bag of Words - Wprowadzenie}
+\begin{frame} {Bag of Words - Wprowadzenie}
   \begin{figure}
@@
 
-\begin{frame}
-	\frametitle{Bag of Words w obrazach}
-
+\begin{frame}{Bag of Words w obrazach}	
 	\begin{columns}
@@
 	 \begin{itemize}
-	  \item opis jednoznaczny, zazwyczaj poprzez histogram gradientów
+ 	  \item opis jednoznaczny, zazwyczaj poprzez przestrzenny histogram gradientów
 	 \end{itemize}
@@
 	\end{enumerate}	
+\end{frame}{}
+
+\section{Projekt Aplikacji}
+
+\begin{frame}{Projekt Aplikacji}
+	 \begin{columns}
+
+	 \begin{column}{6cm}
+	  \begin{figure}
+	    \includegraphics[width=1.0\textwidth]{../figs/class}	   
+	  \end{figure}
+	  \centering \footnotesize Architektura
+	 \end{column}
+
+	 \begin{column}{6cm}
+	  \begin{figure}
+	  \includegraphics[width=0.5\textwidth]{../figs/strategy}	
+	  \end{figure}
+	  \centering \footnotesize Strategia
+	 \end{column}
+
+	\end{columns}
+
+  \begin{columns}
+
+    \begin{column}{6cm}
+    \begin{itemize}
+    \item Główny obiekt \textit{Tagger3D} zarządza całą aplikacją
+    \item Fabryka odpowiedzialna za tworzenie innych obiektów, konfigurowana w czasie działania programu
+    \item Każdy etap procesu BoW ma wydzielony interfejs - wzorzec projektowy Strategia
+      \begin{itemize}
+	\item Detector, Descriptor itd.
+      \end{itemize}
+    \end{itemize}
+
+    \end{column}
+
+    \begin{column}{6cm}
+    \begin{itemize}
+     \item Strategia umożliwia wymianę algorytmów w czasie działania programu, w sposób niewidzialny dla aplikacji
+     \item Konfiguracja w pliku tekstowym
+     \item Obiekt IoUtils oparty o szablony obsługuje operacje wejścia/wyjścia
+    \end{itemize}
+
+    \end{column}
+
+    \end{columns}
+\end{frame}
+
+\section{Bazy danych}
+
+\begin{frame}{Berkely 3D Object Dataset}
+
+	\begin{columns}
+
+	 \begin{column}{6cm}
+	 \begin{figure}[!ht]
+	    \includegraphics[width=0.65\textwidth]{../figs/b3do_objects}
+	  \footnotesize \caption{Obiekty z B3DO. Zdjęcia w oryginalnej jakości. a) kubek b) butelka c) książka d) klawiatura}
+	  \label{fig:b3do_objects}
+	  \end{figure}
+	 \end{column}
+
+	  \begin{column}{6cm}	  
+	  \begin{itemize}
+	   \item 78 kategorii obiektów
+	   \item Wiele obiektów na jednym zdjęciu
+	   \item Niska jakość zdjęć, wiele zdjęć niedoświetlonych, zaszumionych
+	   \item Obiekty przysłonięte
+	   \item Kolorowe zdjęcia i mapy głębi; Adnoacje w XML
+	   \item Skrypty w Pythonie i C++ do ekstrakcji pojedynczych obiektów i podziału na kategorie.
+	   \item Od 1 do 299 instancji w jednej kategorii
+	   \item Losowy wybór 8 kategorii tak, żeby było~>~50 instancji w każdej kategorii
+	  \end{itemize}
+
+	 \end{column}
+	\end{columns}	
+\end{frame}
+
+\begin{frame}{University of Tokyo Dataset}
+	\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=0.6\textwidth]{../figs/tokyo_horizontal}
+	\footnotesize \caption{The Tokyo dataset: a) kosz b) rower c) pudełko d) wiadro e) wózek f) lodówka g) notebook h) drukarka i) skaner j) scena}
+	\label{fig:tokyo}
+	\end{figure}
+
+		\begin{columns}
+		\begin{column}{6cm}
+			\begin{itemize}
+			\item 10 kategorii
+			\item 1 obiekt (oznaczony) na zdjęciu	
+			\item Mogą być obiekty nieoznaczone, których nie należy brać pod uwagę
+			\item Zdjęcia dobrej jakości, dobrze naświetlone
+			\item Wszystkie zdjęcia w kategorii to instancje jednego obiektu
+			\end{itemize}
+		\end{column}
+		\begin{column}{7cm}     
+			\begin{itemize}
+			%\setcounter{enumi}{3}
+			\item Skomplikowane sceny
+			\item Małe różnice pomiędzy klasami obiektów
+			  \begin{itemize}
+			  \item skaner i drukarka
+			  \item koszyk i wiadro
+			  \end{itemize}
+			  \item Dane w formie kolorowe: zdjęcie + plik .csv z absolutnymi współrzędnymi wszystkich pixeli
+			  \item Skrypty Python i C++ - przeksztąłcenie do chmury punktów w formacie PCD
+			\end{itemize}
+		\end{column}
+	\end{columns}
 
@@
 
-\begin{frame}
-	\frametitle{}
+\section{Wyniki i podsumowanie}
+
+\begin{frame}{Porównanie algorytmów}
+
+	\begin{columns}
+
+	\begin{column}{5cm}
+	\begin{table}[!ht]	
+	\includegraphics[scale=0.08]{../figs/desc_b3do} \\ 
+	\centering
+	\footnotesize Porównanie algorytmów. \\
+	\vspace{1cm}
+	\includegraphics[scale=0.2]{../figs/clustering_centroids_b3do} \\ 
+	\centering
+	\footnotesize Wpływ rozmiaru słownika na skuteczność klasyfikacji.
+	\end{table}
+
+	 \end{column}
+
+	  \begin{column}{7cm}	  
+	  \begin{itemize}
+	   \item Wstępna selekcja algorytmów na podstawie przeglądu literatury
+	   \item Rodzina deskryptorów PFH uzyskuje najlepsze wyniki w dopasowywaniu chmur punktów:
+	    \begin{description}
+	      \item[PFH] Algorytm bazowy, 125 wymiarów
+	      \item[FPFH] Algorytm przybliżony, 33 wymiary
+	      \item[PFHRGB] Algorytm uwzględnia kolor, 250 wymiarów
+	    \end{description}
+	   \item Detektory: 
+	       \begin{description}
+	      \item[SIFT] Najlepszy algorytm 2D
+	      \item[ISS] Najlepsze wyniki w dopasowywaniu chmur punktów
+	      \item[US] Najprostszy, równomierna siatka punktów
+	    \end{description}
+	   \item Optymalny rozmiar słownika
+	  \end{itemize}
+
+	 \end{column}
+	\end{columns}
+
 \end{frame}
 
-\begin{frame}
-	\frametitle{}
+\begin{frame}{Wyniki B3DO}
+		\begin{columns}
+
+	 \begin{column}{6cm}
+	\begin{table}[!ht]	
+	\includegraphics[scale=0.1]{../figs/b3do_conf_matrix}	\\ \ \\
+	\centering
+	\footnotesize \textbf{Wynik: 65.22\%} Wyniki na bazie B3DO, detektor ISS, ekstraktor FPFH, słownik o wielkości 1500 słów.
+	\end{table}
+	 \end{column}
+
+	  \begin{column}{6cm}	  
+	  \begin{itemize}
+	   \item Im lepiej rozdzielone kategorie obiektów, tym wyższa wyniki
+	   \item Najwyższy wynik: stół, 100\%
+	   \item Niskie wyniki wynikają bezpośrednio z podobieństwa między klasami: 
+	   \begin{itemize}
+	    \item książka, 35\%, mylona z filiżanką i butelką
+	    \item butelka, 45\%, mylona z filiżanką
+	   \end{itemize}
+	  \end{itemize}
+
+	 \end{column}
+	\end{columns}	
 \end{frame}
 
-\begin{frame}
-	\frametitle{}
+\begin{frame}{Wyniki Tokyo}
+	\begin{columns}
+
+	 \begin{column}{5cm}
+	\begin{table}[!ht]	
+	\includegraphics[scale=0.1]{../figs/tokyo_conf_matrix} \\ \ \\
+	\centering
+	\footnotesize \textbf{Wynik: 62.30\%} Wyniki na bazie Tokyo, detektor ISS, ekstraktor PFH, słownik o wielkości 3000 słów.
+	\end{table}
+
+	 \end{column}
+
+	  \begin{column}{6cm}	  
+	  \begin{itemize}
+	   \item Wyraźna zależność między ilością instancji w danej klasie i skutecznością klasyfikacji
+	   \item Najwyższy wynik: rower, 94\%, największa ilośc obiektów
+	   \item Najniższe wyniki przy klasach, w których są odpowiednio 4, 2 i 2 obiekty: 
+	    \begin{itemize}
+	      \item wózek, 0\%
+	      \item skaner, 0\%
+	      \item drukarka, 0\%
+	    \end{itemize}
+	   \item Notebook jest mylon z pudełkiem
+	   \item Wiadro jest mylone z pudełkiem
+	   \item Kosz jest mylony z wiadrem
+	  \end{itemize}
+
+	 \end{column}
+	\end{columns}	
 \end{frame}
 
-\begin{frame}
-	\frametitle{}
-\end{frame}
+\begin{frame}{Podsumowanie}
+	\begin{itemize}
+	 \item Uzyskane wyniki na bazach B3DO i TOKYO są odpowiednio $5.21$ i $6.23$ razy lepsze od kategoryzacji losowej (odpowiednio 12.5\% i 10\%)
+	 \item Zrealizowano wszystkie założenia projektowe
+	 \item Wystąpiły następujące problemy
+	  \begin{itemize}
+	    \item W zasadzie brak baz danych nadających się do zadania klasyfikacji obiektów na podstawie danych RGBD
+	    \item Bardzo wymagające przetwarzanie chmur punktów ze względu na brak jakiejkolwiek struktury
+	    \item Najlepsze algorytmy dostępne są tylko do 2D, brak możliwości ich prostego uogólnienia do 3D
+	  \end{itemize}
 
-\begin{frame}
-	\frametitle{}
+	  \item Możliwości poprawy skuteczności i/lub szybkości działania aplikacji:
+	    \begin{itemize}
+	      \item Przeniesienie obliczeń do domeny 2D; RGB i D jako niezależne obrazy + złożenie wyników klasyfikacji
+	      \item Trening klasyfikatorów na znacznie większych bazach danych
+	      \item Przeniesienie obliczeń na GPU
+	    \end{itemize}
+
+	\end{itemize}
+
 \end{frame}

### 2014-02-07 gpu/GpuDescriptor.cpp
cleanup

@@ -1,77 +1,0 @@
-/*
- * GpuDescriptor.cpp
- *
- *   Created on: 20 paź 2013
- *       Author: Adam Kosiorek
- *	Description:
- */
-
-#include "GpuDescriptor.h"
-#include <pcl/gpu/features/features.hpp>
-
-namespace Tagger3D {
-
-GpuDescriptor::GpuDescriptor(const std::map<std::string, std::string> &configMap) : Descriptor(configMap) {}
-
-GpuDescriptor::~GpuDescriptor() {}
-
-cv::Mat GpuDescriptor::describe(const ColorCloud::Ptr &cloud,
-		const ScaleCloud::Ptr &keyCloud, const NormalCloud::Ptr &normalCloud ) {
-
-	pcl::gpu::DeviceArray<pcl::PointXYZ> points;
-	pcl::gpu::DeviceArray<pcl::PointXYZ> keypoints;
-	pcl::gpu::DeviceArray<pcl::PointXYZ> normals;
-
-	points.upload(xyzrgb2xyz(cloud->points));
-	keypoints.upload(scale2xyz(keyCloud->points));
-	normals.upload(normal2xyz(normalCloud->points));
-
-	return describe(points, keypoints, normals);
-}
-
-std::vector<pcl::PointXYZ> GpuDescriptor::xyzrgb2xyz
-	(std::vector<pcl::PointXYZRGB, Eigen::aligned_allocator<pcl::PointXYZRGB>> &vec) {
-
-	std::vector<pcl::PointXYZ> xyz;
-	xyz.reserve(vec.size());
-	for(const auto &point : vec) {
-
-		pcl::PointXYZ* p = new pcl::PointXYZ;
-		p->x = point.x;
-		p->y = point.y;
-		p->z = point.z;
-	    int r = std::max(1, std::min(255, static_cast<int>(point.r)));
-		int g = std::max(1, std::min(255, static_cast<int>(point.g)));
-		int b = std::max(1, std::min(255, static_cast<int>(point.b)));
-		p->data[3] = (b << 16) + (g << 8) + r;
-		xyz.push_back(*p);
-	}
-	return xyz;
-
-}
-
-std::vector<pcl::PointXYZ> GpuDescriptor::scale2xyz
-	(std::vector<pcl::PointWithScale, Eigen::aligned_allocator<pcl::PointWithScale>> &vec) {
-
-	std::vector<pcl::PointXYZ> xyz;
[…]

### 2014-02-07 gpu/PFHRGBgpu.cpp

@@ -1,54 +1,0 @@
-/*
- * PFHRGBgpu.cpp
- *
- *   Created on: 20 paź 2013
- *       Author: Adam Kosiorek
- *	Description:
- */
-
-#include "PFHRGBgpu.h"
-#include "CloudParser/CloudParser.h"
-
-namespace Tagger3D {
-
-PFHRGBgpu::PFHRGBgpu(const std::map<std::string, std::string> &configMap) : GpuDescriptor(configMap) {
-
-	createDescriptor();
-	assert(descriptor != nullptr);}
-
-PFHRGBgpu::~PFHRGBgpu() {}
-
-void PFHRGBgpu::createDescriptor() {
-
-	TRACE(logger, "creating gpu::PFHRB descriptor");
-	descriptor = std::unique_ptr<descriptorType>(new descriptorType()) ;
-	descriptor->setRadiusSearch(getParam<float>(radiusSearch), 0);
-}
-
-cv::Mat PFHRGBgpu::describe(const pcl::gpu::DeviceArray<pcl::PointXYZ> &cloud,
-				const pcl::gpu::DeviceArray<pcl::PointXYZ> &keyCloud,const pcl::gpu::DeviceArray<pcl::PointXYZ> &normalCloud) {
-
-	TRACE(logger, "describe PFHRGB: Starting");
-	pcl::gpu::DeviceArray2D<pcl::PFHRGBSignature250> tempDescriptors;
-	descriptor->setInputNormals( normalCloud );
-	descriptor->setSearchSurface( cloud );
-	descriptor->setInputCloud( keyCloud );
-	descriptor->compute( tempDescriptors );
-	TRACE(logger, "describe PFHRGB: Finished; descriptors size = " << tempDescriptors.rows() << "x" << tempDescriptors.cols());
-	PfhRgbCloud::Ptr c(new PfhRgbCloud());
-	int rows = tempDescriptors.rows();
-	int cols = tempDescriptors.cols();
-	for(int i = 0; i < rows; i++) {
-		pcl::PFHRGBSignature250 ptr = tempDescriptors.ptr(i)[0];
-		c->push_back(ptr);
-//		for(int j = 0; j < cols; j++) {
-//			TRACE(logger, "i = " << i << " j = " << j);
-//			c->push_back(ptr);
-//			TRACE(logger, "one point");
-//		}
-	}
-	TRACE(logger, "done");
-	return CloudParser::parse<PfhRgbCloud>(c);
-}
-
-} /* namespace Tagger3D */

### 2014-02-07 gpu/PFHRGBgpu.h

@@ -1,41 +1,0 @@
-/*
- * PFHRGBgpu.h
- *
- *   Created on: 20 paź 2013
- *       Author: Adam Kosiorek
- *	Description:
- */
-
-#ifndef PFHRGBGPU_H_
-#define PFHRGBGPU_H_
-
-#include "GpuDescriptor.h"
-
-namespace Tagger3D {
-
-/*
- *
- */
-class PFHRGBgpu: public GpuDescriptor {
-	/**
-	 *
-	 */
-public:
-	PFHRGBgpu(const std::map<std::string, std::string> &configMap);
-	virtual ~PFHRGBgpu();
-
-	virtual cv::Mat describe(const pcl::gpu::DeviceArray<pcl::PointXYZ> &cloud,
-				const pcl::gpu::DeviceArray<pcl::PointXYZ> &keycloud,const pcl::gpu::DeviceArray<pcl::PointXYZ> &normalCloud);
-
-private:
-	PFHRGBgpu();
-	void createDescriptor();
-	typedef pcl::gpu::PFHRGBEstimation descriptorType;
-	std::unique_ptr<descriptorType> descriptor;
-
-	//	Config keys
-	const std::string radiusSearch = moduleName + "radiusSearch";
-};
-
-} /* namespace Tagger3D */
-#endif /* PFHRGBGPU_H_ */

### 2014-02-07 docs/eng/abstract.tex
conference prep

\begin{center}
\begin{LARGE}\textbf{Streszczenie}\end{LARGE}
\end{center}

\vspace{1.0cm}

	W pracy przedstawiono podejście Bag of Words (BoW) w semantycznej klasyfikacji obiektów na podstawie danych RGBD zarejestrowanych kamerą Microsoft Kinect. Omówiono koncepcję BoW w przetwarzaniu języka naturalnego oraz opisano ścieżkę przetwarzania BoW w widzeniu maszynowym. Opisano etapy ścieżki przetwarzania, to jest: detekcję punktów charakterystycznych, opis tych punktów, kwantyzację oraz krótko scharakteryzowano najpopularniejsze algorytmy. Omówiono zastosowania BoW w widzeniu maszynowym. Następnie omówiono problem klasyfikacji i najpopularniejsze klasyfikatory, m. in.: Na\'ive Bayes i k-Najbliższych Sąsiadów.

	Przegląd literatury pozwolił na wyodrębnienie szeregu wymagań, które aplikacja powinna spełniać. Zaprojektowano proces przetwarzania oraz architekturę aplikacji. Omówiono zewnętrzne biblioteki programistyczne używane w projekcie. Są to: STL, Boost, OpenCV, PointCloud Library, Apache log4cxx i libsvm. Program napisano w języku C++ w sposób zorientowany obiektowo. Pozwoliło to na stworzenie aplikacji wydajnej, rozszerzalnej oraz konfigurowalnej. Algorytmy mogą być wybierane i konfigurowane w czasie działania programu. Nowe algorytmy mogą być łatwo dodawane, z tylko niewielką ingerencją w kod źródłowy. Uczenie aplikacji polega na przetworzeniu przykładów wraz z odpowiadającymi im etykietami. Dzięki temu użytkownik może wytrenować aplikację na własnych przykładach i wykorzystywać ją do rozpoznawanie obiektów dowolnej kategorii.

	Kroki przetwarzania BoW są dosyć ogólne, dlatego też istnieje wiele algorytmów, które mogą być w tym celu stosowane. Przegląd literatury pozwolił na wstępną selekcję obiecujących pod względem wydajności i skuteczności kandydatów. W poniższej pracy przetestowano następujące algorytmu: detekcja odbywa się za pomocą algorytmów SIFT, ISS3D i Uniform Sampling; do opisu punktów wykorzystano FPFH, PFH i PFHRGB; kwantyzację wykonano za pomocą algorytmu KMeans; jako klasyfikator użyto SVM z jądrem RBF trenowany metodą All-vs-All.

	Uzyskano skuteczność klasyfikacji 65.22\% na zbiorze 8 kategorii z Berkely 3D Object Dataset oraz 62.3\% na zabiorze 10 kategorii udostępnionych przez Zhanga z Tokyo University.

\vspace{3.0cm}

\pagebreak

\begin{center}
\begin{LARGE}\textbf{Abstract}\end{LARGE}
\end{center}

\vspace{1.0cm}

	This paper introduces a Bag of Words (BoW) semantic object classification framework based on RGBD data registered by the Microsoft Kinect camera. The concept of the BoW in natural language processing is introduced. Then, we describe the BoW pipeline for image processing. Each stage of the pipeline is described, namely: region detection, feature extraction and vector quantization and some famous algorithms are characterised. Applications of BoW in image processing and their results are discussed. Additionally, we describe the problem of classification and elaborate on the most popular classifiers, e.g. Na\'ive Bayes or k-Nearest Neighbours.

	After a thorough literature review we assembled a set of core requirements the application should meet. Then, we designed a processing pipeline and the programme's architecture. We provide a short description of third party libraries used in the project. They are: STL, Boost, OpenCV, PointCloud Library, Apache log4cxx and libsvm. We implemented the application solely in the C++ programming language in an object oriented way. The efforts resulted in an efficient, extensible and configurable application. Every algorithm can be chosen and configured at runtime. New algorithms can be easily added, with only a little adjustment of the source code. The application employs a learning-by-example paradigm and therefore can be retrained on any user-specified data in order to classify objects into a set of arbitrary categories.

	There is a plethora of algorithms available for every step of the Bag of Words pipeline. After identifying candidates with high performance potential we integrated  and evaluated the following algorithms: Salient region detection is done by SIFT, ISS3D and Uniform Sampling. The description is performed by FPFH, PFH and PFHRGB. Vector quantization was carried out by the KMeans algorithm. As a classifier we used an SVM with the RBF kernel trained with an All-vs-All.
	We achieved the accuracy of 65.22\% on 8 categories of the Berkely 3D Object Dataset and 62.3\% on a 10 category dataset compiled by Zhang from the Tokyo University.

### 2014-02-10 docs/kkr13/kkr13-eng.tex
aha

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% This file is delivered as an usage example of the file 'kkr13-eng.sty'.
% The style file 'kkr13-eng.sty' has been prepared for papers intended 
% to be presented at the XIII National Conference on Robotics in Poland.
%
% The file 'kkr13-eng.sty' contains definitions of macros for English
% and Polish authors. Thus their names are in English and Polish respectively.
% They define the same operations. English and Polish names are used
% only for authors' convenience. 
% Therefore both types of macros can be used in this type of the document.
% The same type of macros are defined in the style file defined for papers 
% written in Polish.
% Below there is a list of macros names in English and their equivalent forms
% in Polish.
%
%       \articleTitle          =   \tytulArtykulu
%       \titleFootNote         =   \stopkaPrzypisTytulu
%       \articleAuthor         =   \autorArtykulu
%       \affiliation           =   \instytucja
%       \theSameAffiliationAs  =   \instytucjaTaSamaJak
%       \articleShortTitle     =   \naglowekTytulSkrocony
%       \breakAuthorsLine      =   \zlamLinieAutorow
%       \authorsForHeader      =   \naglowekAutorzyArtykulu
%       \authorsCustomizedList =   \wlasnaListaAutorow
%       \abstract              =   \streszczenie
%       \Equation              =   \wzor
%       \refeq                 =   \refwzor
%       \reffig                =   \refrys
%       \refFig                =   \refRys
%
% Author: Bogdan Kreczmer 
% Last modification:      2013.12.09
% 
% In the case of any doubt, please, contact via e-mail.
% The address of the author is:
%  bogdan.kreczmer@pwr.wroc.pl
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt,twoside]{article}
\usepackage{kkr13-eng}

\articleTitle{3D Object Recognition Based on RGBD Images}

%
% For information of a project (if any)
%
\titleFootNote{The work described in this paper was conducted with author's Bachelor's dissertation}

%
% Parameters:
%   1 - initials of the first and middle name of an author
%   2 - the first and middle name of an author
%   3 - the last name of an author
%
\articleAuthor{A.}{Adam}{Kosiorek}

\affiliation[institute1]{ Institute of Automation and Robotics, The Faculty of Mechatronics of Warsaw University of\\ Technology, email: iair@mchtr.pw.edu.pl, website: http://iair.mchtr.pw.edu.pl}

\begin{document}

\abstract{ %
 The paper presents a very short example of usage of the style file named
 {\tt kkr13-eng.sty}.
}

\maketitle

\section{ TEXT OF THE PAPER }

The instruction presents typographic layout of the text
and technical requirements 
 to the papers intendant to be presented at the Conference.
Fonts sizes are declared in points (1pt =  0,35146mm).

\subsection{For {\LaTeX} users}

 To fulfill the requirements described below a style file {\tt kkr13-eng.sty}
 can be used. It is available at the Conference website
 {\tt http://kkr13.pwr.wroc.pl}. The bibliography style coincides with 
 the plain BibTeX style {\tt plain.bst}.

\subsection{ The manuscript preparation}

 The total number of pages for a regular paper should not exceed 10 pages.
 The authors of the papers for plenary sessions are recommended not to
 exceed 20 pages (the number of pages should be even).
 The text of the paper has to be written using 
 the 11pt font size. The space between lines should be equal to 5mm, 
 the width of the text is 13.1cm, the height is 20.8cm. 
 The indentation is 1.25cm 
 (the indentation must not be created at the beginning of a section or 
 subsection). The alignment of the text is centered along horizontal line.
 The format of a page is A4.

\subsubsection{\small Mathematical formulae}

 The number of a formula has to be written
 in parentheses shifted to the right (see below). Symbols of variables 
 should be written in italic.
 \begin{equation}
   x = \frac{a^{(1-z)} + b}{10 - d_2}
 \end{equation}

 \noindent
 Intervals of values should be written without spaces, e.g.\ 4--45MPa.

\section{FIGURES AND TABLES}

\subsection{Figures and their arrangement}

 Figures should be numbered with the Arabic numerals (see fig. 
 \ref{fig-example}).

 \begin{figure}[hbtp]
  \fbox{\rule{0mm}{45mm}\rule{85mm}{0mm}}
  \caption{The figure caption}
  \label{fig-example}
 \end{figure}

\subsection{Tables}

 Tables have to be formated in the way presented below (see table 
 \ref{tab-example}). The tables have to be numbered  separately from 
 the figures.

 \begin{table}[hbtp]
  \caption{The table caption}
   \label{tab-example}
   \begin{tabular}{|c|c|c|c|c|}\hline
       Column 1 & Column 2 & Column 3 &  Column 4 & Column 5\\ \hline
       $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$\\ \hline
    \end{tabular}
 \end{table}

\section{CITATIONS}

Citations of papers should be marked  with square brackets, e.g.
\cite{Ming}. The references have to be arranged in 
the alphabetic order relative to the authors' surnames (see the example
below).

\begin{thebibliography}{99}
\bibitem{Litwiniec}
    A. Litwin et al. Transport phenomena in InSb doped with various impurities.
    In: 11 International Conference on the Physics of Semiconductors.
   {\em Proceedings}. Warszawa -- Poland, July 25--29, 
    1972. Vol. 2, pp. 952--957.

 \bibitem{Lamadrid} 
  J.~G. de~Lamadrid.
  \newblock Avoidance of obstacles with unknown trajectories: Locally optimal
   paths and periodic sensor readings.
   \newblock {\em The Inter. Journal of Robotics Research}, 13(6):496--507,
   December 1994.

 \bibitem{Ming}
   A~Ming, K.~Kajihara, M.~Kajitani, and M.~Shimojo.
   \newblock Development of a rapid obstacle sensing system using sonar 
   ring for mobile robot.
   \newblock In {\em Proc. Int. Conf. on Robotics and Automation}, 
   volume~3, pp. 3068 -- 3073, Washington, D.C., May 2002.

 \bibitem{Singh:1987:Convex:Shapes}
   J.~Sanjiv Singh and Meghanad~D. Wagh.
   \newblock Robot path planning using intersecting convex shapes: Analysis and
   simulation.
   \newblock {\em IEEE Journal of Robotics and Automation}, RA-3(2):101 -- 108,
   April 1987.
\end{thebibliography}
\end{document}

### 2014-02-10 docs/ppt/ppt.tex
aha

--- 2014-02-06 Disseration/ppt/main.tex
@@
 \usepackage[polish]{babel}
+\usepackage{mathptmx}
 
@@
 
-\author[Adam Kosiorek]{Adam Kosiorek\\ \footnotesize pod kierunkiem prof. dr hab. B. Siemiątkowskiej}
+\author[Adam Kosiorek]{Adam Kosiorek \\ \footnotesize pod kierunkiem prof. dr hab. B. Siemiątkowskiej}
 \begin{document}
@@
 \thispagestyle{empty}
-\frame{\frametitle{Spis treści}\tableofcontents}
+\frame{\frametitle{Plan prezentacji}\tableofcontents}
 \begin{document}
@@
   \begin{figure}
-    \includegraphics[scale=0.3]{../figs/bow_example-eps-converted-to}
+    \includegraphics[scale=0.15]{../figs/bow_example}
   \end{figure}
@@
   \begin{itemize}
-   \item Częstośc występowania słów
+   \item Histogram jako forma pośrednia
+   \item Częstość występowania słów
    \item Usunięcie gramatyki, kolejności słów  
-   \item Histogram jako forma pośrednia
    \item Wymaga utworzenia słownika
    \item Reprezentacja rzadka w przypadku dużego słownika
-   \item Używany m. in. do znajdowania rozkładu tematów w obrazie
+   \item Używany m. in. do znajdowania rozkładu tematów w dokumencie (pLSA, LDA)
   \end{itemize}
@@
 	 \end{column}
-
+	 -
 	 \begin{column}{3cm}
@@
 	 \begin{itemize}
-	  \item współrzędne (x, y) oraz skala obrazka
+	  \item współrzędne (x, y) oraz skala obrazka (SIFT, FAST)
 	 \end{itemize}
@@
 	 \begin{itemize}
- 	  \item opis jednoznaczny, zazwyczaj poprzez przestrzenny histogram gradientów
+ 	  \item opis jednoznaczny, zazwyczaj poprzez przestrzenny histogram gradientów (SIFT, SURF, HOG)
 	 \end{itemize}
@@
 	 \begin{itemize}
-	  \item punkty układają się w obszary, które można wykryć - klasteryzacja
+	  \item punkty układają się w obszary, które można wykryć - klasteryzacja (KMeans, GMM, Fisher Vector)
 	 \end{itemize}
@@
 	 \begin{itemize}
-	  \item klasyfikator uczący się - Support Vector Machine, Modele graficzne, Boosting
+	  \item klasyfikator uczący się - (SVM, PGM, Boosting)
 	 \end{itemize}
@@
 
-\section{Projekt Aplikacji}
+\section{Projekt aplikacji}
 
-\begin{frame}{Projekt Aplikacji}
+\begin{frame}{Projekt aplikacji}
 	 \begin{columns}
@@
 	  \begin{figure}
-	    \includegraphics[width=1.0\textwidth]{../figs/class}	   
+	    \includegraphics[width=1.1\textwidth]{../figs/class}	   
 	  \end{figure}
@@
 	  \begin{figure}
-	  \includegraphics[width=0.5\textwidth]{../figs/strategy}	
+	  \includegraphics[width=0.6\textwidth]{../figs/strategy}	
 	  \end{figure}
@@
 	    \includegraphics[width=0.65\textwidth]{../figs/b3do_objects}
-	  \footnotesize \caption{Obiekty z B3DO. Zdjęcia w oryginalnej jakości. a) kubek b) butelka c) książka d) klawiatura}
-	  \label{fig:b3do_objects}
 	  \end{figure}
+	  \centering \footnotesize Obiekty z B3DO. Zdjęcia w oryginalnej jakości. a) kubek b) butelka c) książka d) klawiatura
 	 \end{column}
@@
 	\includegraphics[width=0.6\textwidth]{../figs/tokyo_horizontal}
-	\footnotesize \caption{The Tokyo dataset: a) kosz b) rower c) pudełko d) wiadro e) wózek f) lodówka g) notebook h) drukarka i) skaner j) scena}
-	\label{fig:tokyo}
 	\end{figure}
+	\centering \footnotesize Baza danych Tokyo: a) kosz b) rower c) pudełko d) wiadro e) wózek f) lodówka g) notebook h) drukarka i) skaner j) scena
+	\normalsize
 
@@
 			  \end{itemize}
-			  \item Dane w formie kolorowe: zdjęcie + plik .csv z absolutnymi współrzędnymi wszystkich pixeli
+			  \item Dane w formie: kolorowe zdjęcie + plik .csv z absolutnymi współrzędnymi wszystkich pixeli
 			  \item Skrypty Python i C++ - przeksztąłcenie do chmury punktów w formacie PCD

### 2014-02-10 docs/ppt/ppt.tex
ppt

@@
-\documentclass[8pt]{beamer}
+\documentclass[10pt]{beamer}
 \usetheme{Montpellier} 
@@
 
-\author[Adam Kosiorek]{Adam Kosiorek \\ \footnotesize pod kierunkiem prof. dr hab. B. Siemiątkowskiej}
+\author[Adam Kosiorek]{\Large Adam Kosiorek \\ \large  pod kierunkiem prof. dr hab. B. Siemiątkowskiej}
 \begin{document}
@@
 \section{Podejście Bag of Words}
-\begin{frame} {Bag of Words - Wprowadzenie}
+\begin{frame} {Bag of Words --- wprowadzenie}
   \begin{figure}
@@
 
-\begin{frame}{Bag of Words w obrazach}	
+\begin{frame}{Bag of Words --- obrazy}	
 	\begin{columns}
@@
 	 \begin{figure}
-	   \includegraphics[scale=0.15]{../figs/tsai2012}
+	   \includegraphics[scale=0.18]{../figs/tsai2012}
 	   \end{figure}
@@
 	\begin{enumerate}
-	 \item Wykrycie punktów charakterystycznych
-	 \begin{itemize}
-	  \item współrzędne (x, y) oraz skala obrazka (SIFT, FAST)
-	 \end{itemize}
-
-	 \item Opisanie otoczenia wykrytych punktów
-	 \begin{itemize}
- 	  \item opis jednoznaczny, zazwyczaj poprzez przestrzenny histogram gradientów (SIFT, SURF, HOG)
-	 \end{itemize}
-	 \item Budowanie słownika i kwantyzacja 
-	 \begin{itemize}
-	  \item punkty układają się w obszary, które można wykryć - klasteryzacja (KMeans, GMM, Fisher Vector)
-	 \end{itemize}
-	 \item Klasyfikacja
-	 \begin{itemize}
-	  \item klasyfikator uczący się - (SVM, PGM, Boosting)
-	 \end{itemize}
+	 \item Wykrycie punktów charakterystycznych --- x, y, skala (SIFT, FAST)
+	 \item Opisanie otoczenia wykrytych punktów --- histogram gradientów (SURF, HOG)
+	 \item Budowanie słownika --- klasteryzacja (KMeans, GMM)
+	 \item Klasyfikacja --- uczenie nadzorowane (SVM, Boosting)
 	\end{enumerate}	
@@
 \begin{frame}{Projekt aplikacji}
-	 \begin{columns}
+ \begin{figure}
+	    \includegraphics[width=0.9\textwidth]{../figs/class}	   
+	  \end{figure}
+	  \centering \footnotesize Architektura \normalsize
+	  \begin{itemize}
+    \item Główny obiekt --- \textit{Tagger3D}
+    \item Fabryka --- tworzenie innych obiektów
+    \item Konfiguracja w pliku tekstowym (Boost)
 
-	 \begin{column}{6cm}
+    \end{itemize}
+
+\end{frame}
+
+\begin{frame}{Projekt aplikacji c.d.}
+
 	  \begin{figure}
-	    \includegraphics[width=1.1\textwidth]{../figs/class}	   
-	  \end{figure}
-	  \centering \footnotesize Architektura
-	 \end{column}
-
-	 \begin{column}{6cm}
-	  \begin{figure}
-	  \includegraphics[width=0.6\textwidth]{../figs/strategy}	
+	  \includegraphics[width=0.5\textwidth]{../figs/strategy}	
 	  \end{figure}
 	  \centering \footnotesize Strategia
-	 \end{column}
 
-	\end{columns}
-
-  \begin{columns}
-
-    \begin{column}{6cm}
     \begin{itemize}
-    \item Główny obiekt \textit{Tagger3D} zarządza całą aplikacją
-    \item Fabryka odpowiedzialna za tworzenie innych obiektów, konfigurowana w czasie działania programu
-    \item Każdy etap procesu BoW ma wydzielony interfejs - wzorzec projektowy Strategia
-      \begin{itemize}
-	\item Detector, Descriptor itd.
-      \end{itemize}
-    \end{itemize}
-
-    \end{column}
-
-    \begin{column}{6cm}
-    \begin{itemize}
-     \item Strategia umożliwia wymianę algorytmów w czasie działania programu, w sposób niewidzialny dla aplikacji
-     \item Konfiguracja w pliku tekstowym
+     \item Strategia --- wymiana algorytmów w sposób niewidzialny dla aplikacji
+     \item Każdy etap BoW ma wydzielony interfejs (Detector, Descriptor)
      \item Obiekt IoUtils oparty o szablony obsługuje operacje wejścia/wyjścia
@@
 
-    \end{column}
-
-    \end{columns}
 \end{frame}
@@
 \begin{frame}{Berkely 3D Object Dataset}
+  \begin{figure}[!ht]
+	    \includegraphics[scale=0.45]{../figs/b3do_objects}
+	  \end{figure}
+	  \centering Obiekty z B3DO. Zdjęcia w oryginalnej jakości. a)~kubek b)~butelka c)~książka d)~klawiatura
+\end{frame}
 
-	\begin{columns}
+\begin{frame}{Berkely 3D Object Dataset c.d.}
 
-	 \begin{column}{6cm}
-	 \begin{figure}[!ht]
-	    \includegraphics[width=0.65\textwidth]{../figs/b3do_objects}
-	  \end{figure}
-	  \centering \footnotesize Obiekty z B3DO. Zdjęcia w oryginalnej jakości. a) kubek b) butelka c) książka d) klawiatura
-	 \end{column}
-
-	  \begin{column}{6cm}	  
 	  \begin{itemize}
@@
 
-	 \end{column}
-	\end{columns}	
 \end{frame}
@@
 	\begin{figure}[!ht]
-	\centering
-	\includegraphics[width=0.6\textwidth]{../figs/tokyo_horizontal}
+	\includegraphics[scale=0.18]{../figs/tokyo_horizontal}
 	\end{figure}
-	\centering \footnotesize Baza danych Tokyo: a) kosz b) rower c) pudełko d) wiadro e) wózek f) lodówka g) notebook h) drukarka i) skaner j) scena
-	\normalsize
+	\centering Baza danych Tokyo: a)~kosz b)~rower c)~pudełko d)~wiadro e)~wózek f)~lodówka g)~notebook h)~drukarka i)~skaner j)~scena
+\end{frame}
+
+\begin{frame}{University of Tokyo Dataset c.d.}
 
 		\begin{columns}
-		\begin{column}{6cm}
+		\begin{column}{5cm}
 			\begin{itemize}
 			\item 10 kategorii
-			\item 1 obiekt (oznaczony) na zdjęciu	
-			\item Mogą być obiekty nieoznaczone, których nie należy brać pod uwagę
 			\item Zdjęcia dobrej jakości, dobrze naświetlone
@@
 		\end{column}
-		\begin{column}{7cm}     
+		\begin{column}{6cm}     
 			\begin{itemize}
-			%\setcounter{enumi}{3}
-			\item Skomplikowane sceny
-			\item Małe różnice pomiędzy klasami obiektów
+			\item Małe różnice pomiędzy klasami obiektów:
 			  \begin{itemize}
@@
 
-\section{Wyniki i podsumowanie}
+\section{Wyniki}
 
@@
 
-	\begin{column}{5cm}
+	\begin{column}{6cm}
 	\begin{table}[!ht]	
-	\includegraphics[scale=0.08]{../figs/desc_b3do} \\ 
+	\includegraphics[scale=0.09]{../figs/desc_b3do} \\ 
 	\centering
-	\footnotesize Porównanie algorytmów. \\
-	\vspace{1cm}
-	\includegraphics[scale=0.2]{../figs/clustering_centroids_b3do} \\ 
+	\footnotesize Porównanie algorytmów \\
+	\vspace{0.5cm}
+	\includegraphics[scale=0.30]{../figs/clustering_centroids_b3do} \\ 
 	\centering
-	\footnotesize Wpływ rozmiaru słownika na skuteczność klasyfikacji.
+	\footnotesize Wpływ rozmiaru słownika na skuteczność klasyfikacji
 	\end{table}
@@
 
-	  \begin{column}{7cm}	  
+	  \begin{column}{6cm}	  
 	  \begin{itemize}
-	   \item Wstępna selekcja algorytmów na podstawie przeglądu literatury
-	   \item Rodzina deskryptorów PFH uzyskuje najlepsze wyniki w dopasowywaniu chmur punktów:
-	    \begin{description}
-	      \item[PFH] Algorytm bazowy, 125 wymiarów
-	      \item[FPFH] Algorytm przybliżony, 33 wymiary
-	      \item[PFHRGB] Algorytm uwzględnia kolor, 250 wymiarów
-	    \end{description}
+	   \item Selekcja na podstawie literatury
+	   \item Deskryptory PFH najlepsze w dopasowywaniu chmur punktów:
+	    \begin{itemize}
+	      \item PFH --- Algorytm bazowy, 125 wymiarów
+	      \item FPFH --- przybliżony, 33 wymiary
+	      \item PFHRGB --- uwzględnia kolor, 250 wymiarów
+	    \end{itemize}
 	   \item Detektory: 
-	       \begin{description}
-	      \item[SIFT] Najlepszy algorytm 2D
-	      \item[ISS] Najlepsze wyniki w dopasowywaniu chmur punktów
-	      \item[US] Najprostszy, równomierna siatka punktów
-	    \end{description}
+	       \begin{itemize}
+	      \item SIFT --- Najlepszy algorytm 2D
+	      \item ISS --- Najlepsze wyniki w dopasowywaniu chmur punktów
+	      \item US --- Najprostszy, równomierna siatka punktów
+	    \end{itemize}
 	   \item Optymalny rozmiar słownika
@@
 
-	 \begin{column}{6cm}
+	 \begin{column}{8cm}
 	\begin{table}[!ht]	
-	\includegraphics[scale=0.1]{../figs/b3do_conf_matrix}	\\ \ \\
-	\centering
-	\footnotesize \textbf{Wynik: 65.22\%} Wyniki na bazie B3DO, detektor ISS, ekstraktor FPFH, słownik o wielkości 1500 słów.
+	\includegraphics[scale=0.15]{../figs/b3do_conf_matrix}
 	\end{table}
 	 \end{column}
-
-	  \begin{column}{6cm}	  
+	  \begin{column}{2.8cm}	  
+	  \footnotesize \textbf{Wynik: 65.22\%} Wyniki na bazie B3DO, detektor ISS, ekstraktor FPFH, słownik o wielkości 1500 słów
+	 \end{column}
+	\end{columns}		
 		\begin{itemize}
-	   \item Im lepiej rozdzielone kategorie obiektów, tym wyższa wyniki
+	   \item Im lepiej rozdzielone kategorie obiektów, tym wyższe wyniki
 	   \item Najwyższy wynik: stół, 100\%
@@
 	   \begin{itemize}
-	    \item książka, 35\%, mylona z filiżanką i butelką
-	    \item butelka, 45\%, mylona z filiżanką
+	    \item książka, 35\%, mylona z kubkiem i butelką
+	    \item butelka, 45\%, mylona z kubkiem
 	   \end{itemize}
 	  \end{itemize}
-
-	 \end{column}
-	\end{columns}	
 \end{frame}
@@
 	\begin{columns}	
+	 \begin{column}{8cm}
+	\begin{table}[!ht]	
+	\includegraphics[scale=0.18]{../figs/tokyo_conf_matrix}
+	\centering
 
-	 \begin{column}{5cm}
-	\begin{table}[!ht]	
-	\includegraphics[scale=0.1]{../figs/tokyo_conf_matrix} \\ \ \\
-	\centering
-	\footnotesize \textbf{Wynik: 62.30\%} Wyniki na bazie Tokyo, detektor ISS, ekstraktor PFH, słownik o wielkości 3000 słów.
 	\end{table}
@@
 
-	  \begin{column}{6cm}	  
-	  \begin{itemize}
-	   \item Wyraźna zależność między ilością instancji w danej klasie i skutecznością klasyfikacji
-	   \item Najwyższy wynik: rower, 94\%, największa ilośc obiektów
-	   \item Najniższe wyniki przy klasach, w których są odpowiednio 4, 2 i 2 obiekty: 
-	    \begin{itemize}
-	      \item wózek, 0\%
-	      \item skaner, 0\%
-	      \item drukarka, 0\%
-	    \end{itemize}
-	   \item Notebook jest mylon z pudełkiem
-	   \item Wiadro jest mylone z pudełkiem
-	   \item Kosz jest mylony z wiadrem
-	  \end{itemize}
+	  \begin{column}{2.8cm}	  
+\footnotesize \textbf{Wynik: 62.30\%} Wyniki na bazie Tokyo, detektor ISS, ekstraktor PFH, słownik o wielkości 3000 słów
 
@@
 	\end{columns}
+
+		  \begin{itemize}
+	   \item liczność w klasie \textasciitilde \ skuteczność klasyfikacji
+	   \item Najwyższy wynik: rower, 94\%, największa ilośc obiektów
+	   \item Najniższe wyniki : wózek, skaner, drukarka --- po 4, 2, 2 obiekty
+	   \item Notebook i wiadro mylone z pudełkiem, a kosz z wiadrem
+	  \end{itemize}
 \end{frame}
 
-\begin{frame}{Podsumowanie}
-	\begin{itemize}
-	 \item Uzyskane wyniki na bazach B3DO i TOKYO są odpowiednio $5.21$ i $6.23$ razy lepsze od kategoryzacji losowej (odpowiednio 12.5\% i 10\%)
-	 \item Zrealizowano wszystkie założenia projektowe
-	 \item Wystąpiły następujące problemy
+\section{Podsumowanie}
+
+\begin{frame}{Podsumowanie --- problemy}
+ Wystąpiły następujące problemy:
 	  \begin{itemize}
 	    \item W zasadzie brak baz danych nadających się do zadania klasyfikacji obiektów na podstawie danych RGBD
-	    \item Bardzo wymagające przetwarzanie chmur punktów ze względu na brak jakiejkolwiek struktury
+	    \item Wymagające przetwarzanie chmur punktów ze względu na brak struktury
 	    \item Najlepsze algorytmy dostępne są tylko do 2D, brak możliwości ich prostego uogólnienia do 3D
 	  \end{itemize}
+\end{frame}
 
-	  \item Możliwości poprawy skuteczności i/lub szybkości działania aplikacji:
+\begin{frame}{Podsumowanie --- poprawa skuteczności i szybkości}
+ Możliwości poprawy skuteczności i/lub szybkości działania aplikacji:
 	    \begin{itemize}
@@
 	      \end{itemize}
+\end{frame}
 
+\begin{frame}{Podsumowanie}
+	\begin{itemize}
+	\item Zrealizowano wszystkie założenia projektowe
+	 \item Uzyskane wyniki na bazach B3DO i Tokyo są odpowiednio $5.21$ i $6.23$ razy lepsze od kategoryzacji losowej (odpowiednio 12.5\% i 10\%)
 	\end{itemize}

### 2014-02-13 docs/kkr13/kkr13-eng.tex
kkr

@@
 \usepackage{kkr13-eng}
+\usepackage{todonotes}
+\usepackage[hidelinks]{hyperref}
+\usepackage{array}
+\usepackage{booktabs}
+\newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}
+\newcommand{\subscript}[1]{\ensuremath{_{\textrm{#1}}}}
 
-\articleTitle{3D Object Recognition Based on RGBD Images}
+\articleTitle{3D Object Classification \\ Based on RGBD Images}
 
@@
 %
-\titleFootNote{The work described in this paper was conducted with author's Bachelor's dissertation}
+\titleFootNote{The work described in this paper was conducted within author's Bachelor's dissertation}
 
@@
 
-\abstract{ %
- The paper presents a very short example of usage of the style file named
- {\tt kkr13-eng.sty}.
+\listoftodos
+
+\abstract{
+
+  This paper introduces a Bag of Words (BoW) semantic object classification framework based on RGBD data registered by a Microsoft Kinect camera.
+The BoW concept in natural language processing is introduced and a BoW image processing pipeline is described.
+Each part of the pipeline (region detection, feature extraction and vector quantization) is characterised and the most successful algorithms are outlined.
+Applications of BoW in image processing and their results are discussed.
+Additionally, the problem of classification is described.
+Algorithms with high performance potential were identified and evaluated.
+Salient region detection is done by SIFT, ISS3D and Uniform Sampling.
+Description is performed by FPFH, PFH and PFHRGB.
+Vector quantization was carried out by the KMeans algorithm.
+An SVM with the RBF kernel trained with an All-vs-All was used as a classifier.
+We achieved the accuracy of 65.22\% on 8 categories of the Berkely 3D Object Dataset and 62.3\% on a 10 category dataset compiled by Zhang from the Tokyo University.
 }
@@
 
-\section{ TEXT OF THE PAPER }
+\section{ INTRODUCTION }
 
-The instruction presents typographic layout of the text
-and technical requirements 
- to the papers intendant to be presented at the Conference.
-Fonts sizes are declared in points (1pt =  0,35146mm).
+  It has never been easier to capture visual information.
+Popular storage services grow lighting fast due to terabytes of photographs and movies uploaded every day.
+The growth is so fast that hand-tagging and description, the traditional means of annotation, cease to suffice.
+They are ambiguous, emotional and rarely optimal.
+With no better solution at hand databases are becoming increasingly harder to browse.
+Another, but quite similar setting occurs in the field of mobile robotics.
+A mobile robot is there to interact with its environment.
+If so, it would be desirable for the robot to know what kind of surroundings it is in.
+The problem can be treated as a scene or object classification problem, one of the most popular computer vision issues in the last decade.
+\todo[inline]{ref}
 
-\subsection{For {\LaTeX} users}
+  This paper tackles two issues.
+Firstly, the Bag of Words (or BoW for short) approach to image classification is reviewed.
+The Bag of Words method originated from the natural language processing domain \cite{tsai2012bag}.
+It makes a strong assumption that word occurrence in a text document define its meaning.
+It were Csurka \textit{et al} who first used BoW for image classification in 2004 \cite{csurka2004visual}.
+Since images cannot be simply casted into natural language documents a pipeline that help us achieve this goal is needed.
+It usually consist of: keypoint detection, feature extraction, vector quantization, together with codebook construction, and classification, steps that will be discussed later.
 
- To fulfill the requirements described below a style file {\tt kkr13-eng.sty}
- can be used. It is available at the Conference website
- {\tt http://kkr13.pwr.wroc.pl}. The bibliography style coincides with 
- the plain BibTeX style {\tt plain.bst}.
+  Being efficient, efective and flexible, a Bag of Words processing pipeline is, however, a blessing in a disguise.
+While in fact it can provide satisfactory results with little effort, it is cumbersome to tune, thus spectacular performance is hard to achieve.
+One reason is the abundance of suitable algorithms available.
+Wide variety of building blocks might make it flexible, but it renders choosing an optimal combination infeasible.
 
-\subsection{ The manuscript preparation}
+  The rest of this work is organised as follows: Section 2 describes the Bag of Words technique in detail.
+Construction of an image model is discussed and the most popular algorithms are outlined.
+Basic information on a problem of classification are introduced the most popular approaches of solving it are discussed.
+Section 3 describes two renown RGBD image datasets suitable for evaluation of RGBD data-based object classifiers.
+Section 4 addresses the topics of experimental setup, conducted experiments and provides the results.
+Finally, Section 5 concludes this work.
 
- The total number of pages for a regular paper should not exceed 10 pages.
- The authors of the papers for plenary sessions are recommended not to
- exceed 20 pages (the number of pages should be even).
- The text of the paper has to be written using 
- the 11pt font size. The space between lines should be equal to 5mm, 
- the width of the text is 13.1cm, the height is 20.8cm. 
- The indentation is 1.25cm 
- (the indentation must not be created at the beginning of a section or 
- subsection). The alignment of the text is centered along horizontal line.
- The format of a page is A4.
+\section{ BAG OF WORDS }
+
+  Bag of Words is an intermediate representation in a form of a histogram used in natural language processing, information retrieval and data mining.
+It obliterates any grammatical information as well as word order in order to perserve word incidence only.
+
+  \begin{figure}[!ht]
+  \centering
+  \includegraphics[width=0.7\textwidth]{../figs/bow_example}
+  \caption{Bag of Words histogram}
+  \label{fig:bow_example}
+  \end{figure}
+
+  The figure \ref{fig:bow_example} shows a piece of text and its BoW model, where articles and punctuation marks were left out.
+In order to compare different documents a global dictionary must be built.
+The dictionary (codebook) is constructed by taking every word from all available documents and removing duplicates.
+One can image that if a dictionary is of any considerable size resulting representation of especially small documents will be very sparse.
+Classification algorithms can be optimised for sparse data in order to boost performance.
+
+  In natural language processing BoW is used to infer semantic meaning of documents.
+If we could translate an image into a text document we might be able to employ similar methods.
+A question arises: How does one make a text document from an image?
+
+  \subsection{Processing Pipeline}	
+    Tsai describes a well established pipeline that allows translation of images into text documents \cite{tsai2012bag}.
+It consists of the following steps: (1) region detection, (2) feature extraction, (3) vector quantization and (4) BoW histogram formation as can be seen in the figure \ref{fig:bow_pipeline}.
+The author summarises the most commonly used methods for performing these tasks.
+
+    \begin{figure}[!ht]
+    \centering
+    \includegraphics[width=0.75\textwidth]{../figs/tsai2012}
+    \caption{Bag of Words pipeline. The figure comes from \cite{tsai2012bag}}
+    \label{fig:bow_pipeline}
+    \end{figure}
+
+  \subsubsection{Region Detection}
+    Characteristic region detection is the first step in any Bag of Words framework.
+Numerous detection methods have been developed, but choosing the right one for any particular case might prove tricky.
+
+    The most common detectors make use of a Harris corner detector or image's first or second derivatives.
+A Harris-Laplace detector is an example of a Harris-based detector.
+The Harris function is scale adapted and its outcome is a subject to a Laplacian-of-Gaussian (LoG) operator, which selects relevant points in scale space.
+Images' regions' 2\textsuperscript{nd} derivatives, namely the regions' Hessians, can be combined with a LoG operator as well.
+This combination allows selection of points significant in the two spaces: the scale space and the Hessian's determinant space.
+The latter entails the speed at which pixel intensities change in the neighbourhood of a point.
+
+    A number of more advanced recipes for salient region localisation have been developed and implemented.
+These include for example SIFT \cite{sift_keypoint}, SUSAN \cite{susan_keypoint} and Intrinistic Shape Signatures \cite{iss_keypoint}.
+The majority of keypoint detection formulas is being developed for the 2D domain.
+A number of them have been adapted to 3D, however.
+A comparative evaluation of detection algorithms available in the PointCloud Library (PCL, discussed below) can be find in \cite{pcl_keypoint_comparision}.
+Another comprehensive study is \cite{3d_keypoint_eval}.
+All these formulas, called sparse feature detectors, resort to selection of maxima in specific state spaces.
+An entirely different scheme is to use a dense feature detector.
+That is, take a uniformly sampled grid of points.
+Dense detectors have an advantage in that they sample slow changing regions in terms of gradient or hessian of an image.
+Examples of such regions would be a clear sky or a calm ocean.
+Li \emph{et al} showed that dense detectors generally outperform sparse ones \cite{fei2005bayesian}.
+
+  \subsubsection{Feature Extraction}
+    Suppose only coordinates of a keypoint were known.
+In case of even the smallest rotation or translation they would change and the keypoint would be lost.
+Keypoints should be described in a way that makes them invariant to affine transformations, changes in light intensity or colour saturation.
+It is hard to achieve all of these properties simultaneously, but methods that meet some of them exist.
+
+    Keypoint description takes form of coordinates in a high-dimensional space.
+One of the most precise and repeatable algorithm is SIFT \cite{sift_features}, which is a 3D histogram of gradients structured as a 128-dimensional vector of floating point values.
+It is the most often extracted descriptor in BoW pipelines.
+Other methods include various colour descriptors, binary descriptors such as 512-dimensional GIST \cite{ponce2011cv}.
+There are techniques designed for 3D exclusively.
+Among them are Persistent Point Feature Histogram (PFH) \cite{pfh_rusu2008}, its faster alternative FPFH \cite{fpfh_rusu2009} and PFHRGB, which takes into account colour information, all implemented in PCL.
+
+  \subsubsection{Vector Quantization}
+    When features are extracted they have to be normalised.
+Vector quantization step have two main phases.
+The first one is a codebook construction from a training dataset.
+The second phase is responsible for parsing (or translation) raw image descriptors into a form compatible with the newly constructed codebook.
+The simplest way of building a dictionary is to find patterns or regions within the descriptors computed on a training dataset.
+Then, the parsing phase is about assigning a descriptor to one of the codebook elements (e.g.
+to one of the regions).
+Suppose we use centroids or medoids of the discovered regions as our codebook's entries.
+Then, we can match a descriptor to one of the centroids performing a nearest neighbour search.
+The descriptor parsed this way is called a \textit{visual word}.
+Finally, we build a histogram of visual word occurrence.
+The histogram have a fixed size equal to the codebook size.
+Each bin of the histogram tells us how many visual words of a particular kind were in the description of the corresponding image.
+
+    The kMeans is the single most popular vector quantization algorithm used in the BoW pipelines \cite{tsai2012bag}.
+Developed in 1950's, it is well known and simple to implement.
+kMeans divides all data into a predefined amount of clusters and computes the clusters' centroids.
+Many modifications and alternative versions have emerged \cite{kmeans_jain2010data}.
+Some of them are: faster than the original \emph{approximate kmeans}, \emph{hierarchical kmeans}, which automatically chooses the final number of clusters and a \emph{soft kmeans} --- a variation of the algorithm that allows a fuzzy alignment.
+The fuzzy alignment mean that each point can belong to several clusters with different weights.
+A weight can be proportional for instance to the inverse square of the distance to a centroid.
+
+    If computational cost is of no concern, or if required precision is of the utmost priority, a Gaussian Mixture Model (GMM) can be used.
+The GMM partitions data into a set of clusters, finds their means and covariances.
+In the parsing step we compute a probability distribution of a descriptor over all the clusters.
+We can then build a fuzzy aligned histogram taking the probability distribution as weights.
+The GMM can be thought of as a generalisation of the kMeans algorithm.
+The drawback of the GMM is its massive computational cost in comparison with still expensive kMeans.
+Recently, Perronnin \textit{et al} proposed GMM based fisher-kernel vector quantization step with superior results \cite{fisher1, fisher2}.
+
+    After we choose a vector quantization algorithm, we have to decide what size of a dictionary to use.
+In a simplest case, when the kMeans is used, we can treat each clusters' centroid as a visual word.
+Therefore, the dictionary size defines how much information we retain in a BoW histogram.
+A big training set containing many classes with large inter-class and inter-class variance is likely to require a huge codebook.
+On the other hand, too big a dictionary might introduce quantization artefacts.
+One has to bear in mind that the vector quantization step is the most time-consuming part of the BoW pipeline.
+The highest computational complexity is associated with the codebook construction step and it is$O(n^3)$, where $n$ is the codebook size.
+
+    It is possible to combine several feature extraction algorithms before creating the codebook (Early Fusion) or create many codebooks and concatenate resulting histograms (Late Fusion).
+Both schemes are as simple as vector concatenation.
+The Early Fusion concatenates two feature vectors if they have been extracted from the same keypoint.
+The Late Fusion joins histograms, outputted by separate quantization steps.
+
+  \subsection{Applications in Computer Vision}
+    The Bag of Words approach is a tool than enables us to represent an image by a single feature vector of a chosen size.
+Its most popular applications in computer vision are Content Based Image Retrieval (CBIR) and Scene/Object Classification.
+
+  \subsubsection{Content Based Image Retrieval}
+    CBIR is a computer vision approach to image retrieval from large image databases.
+Tangelder \emph{et al} provides an overview of techniques applicable to 3D objects \cite{tangelder2008survey}.
+The task of image retrieval is to find a database entry that fulfil certain conditions.
+If we wanted to perform the task efficiently, we would have to meet the following criteria \cite{toldo2009bag}: (1) All entries should be indexed in a concise way, (2) a (dis)similarity measure should be provided and (3) an efficient search algorithm should be available.
+
+    Database entries (images) should be indexed beforehand.
+Otherwise we would have to compare all the entries explicitly.
+An index must be compact as well as discriminative.
+Suitable algorithms can be divided into three general categories: (1) feature based methods, (2) graph based methods and (3) other methods.
+
+    Feature based methods can be further divided into global features and local features.
+The global features take form of a single vector (or a point in a \emph{d} dimensional space).
+They are usually associated with object's mass or volume or distributions of these.
+Being easy to compute and straightforward to implement, their discriminative power is rather low --- they cannot be used for partial matching, but are well suited for an early preprocessing.
+
+    Local features, on the other hand, describe object's characteristic regions.
+Their shape is similar to that of the global features, but instead of a single point in space there are multiple ones --- one for each considered region.
+Tangelder argues that local features based approaches are inefficient and lead to a complex indexing problem \cite{tangelder2008survey}.
+At the same time Toldo \emph{et al} and Li \emph{et al} show that Bag of Words local feature based approach has no such drawbacks.
+On the contrary --- it is easy to implement, efficient and provides state-of-the-art results.
+
+    Feature based methods can be either local or global.
+Local features describe characteristic regions of an object, which have to be identified first.
+We have to carry out similar computation for each salient region.
+An outcome is a set of vectors, one vector for each region in \emph{d} dimensional space, where \emph{d} is dimensionality of the descriptor.
+Global features are generally easier (faster) to compute and more compact --- they take form of a single \emph{d} dimensional vector.
+Often global features are more computationally efficient and can be easily used for object indexing .
+Before the advent of BoW it was not clear how to use local features for indexing, nor there was any straight-forward dissimilarity measure available \cite{tangelder2008survey}.
+The Bag of Words approach solved these issues.
+What is more, it is easy to implement, efficient and provides state-of-the-art results \cite{li2010investigating}.
+
+  \subsubsection{Scene and Object Classification}
+    Scene and object classification are among the most popular issues of computer vision nowadays.
+We would like to perform those tasks automatically for the sake of surveillance, navigation or automatic image tagging.
+The very first attempt to use BoW in scene classification was made by Csurka \textit{et al} in 2004 \cite{csurka2004visual}.
+They were inspired by an idea of a ``texton'', a building block of texture introduced earlier in pattern recognition and texture classification.
+The authors suggested a BoW pipeline described above.
+Then, they fed the resulting BoW histograms into two classifiers: Support Vector Machine (SVM) and Na\`ve Bayes (both discussed below).
+Fei-Fei \emph{et al} refined the original approach by examining several keypoint detectors and descriptors \cite{fei2005bayesian}.
+Moreover, they developed a novel probabilistic graphical model for classification.
+They achieved accuracy of 76\% on a large 13 category dataset.
+
+    One of the best entries in an ILSVRC2013\footnote{\url{http://www.image-net.org/challenges/LSVRC/2013/results.php}} challenge, attempting to classify millions of images into 1000 categories, was submitted by a fisher vector based BoW approach as well.
+The top-5\footnote{top-5 --- the classification result is successful if the ground-truth category is in one of the five most probable categories predicted} accuracy rate was close to 85\%.
+
+\section{Problem of Classification}
+
+    To classify means to, given a set of categories, produce a category label for a given set of features \cite{ponce2011cv}.
+Image classification fits this description perfectly.
+The only difficulty lies in complexity of a raw image.
+Suppose we have a $320$ by $240$ three channel colour image.
+This amounts to a total of $230400$ dimensions, far too many to feed into any classifier directly.
+Fortunately, a Bag of Words histogram is a compact and discriminative intermediate representation that solves this issue.
+It can be used with any classifier.
+Classifiers can be two-class classifiers (e.g.
+binary) or multi-class classifiers.
+The latter are often a combination of several binary classifiers.
+The most popular classifiers are: k-Nearest Neighbours, Logistic Regression, Softmax Regression, Na\`ive Bayes and Support Vector Machine.
+
+    \subsubsection{Na\`ive Bayes}
+    Assume that we have a \textit{n}-dimensional feature vector $\mathbf{X}$ such that $\mathbf{X} = \left\{x_1, x_2, ...
+, x_\mathit{n}\right\}$ and an unknown category label \textit{C}.
+The probability of the category \textit{C} given the feature vector \textbf{X} is $P\left(\mathit{C}\middle|\mathbf{X}\right) = P\left(\mathit{C}\middle|\left\{x_1, x_2, ..., x_\mathit{n}\right\}\right)$.
+The strong (or na\`ive) Bayes assumption says that features are independent of each other, that is $P(\mathbf{X}) = P(x_1)*P(x_2)*...*P(x_\mathit{n})$.
+If so, we can compute probability distributions of every class in our training set given every feature.
+Then, for any new feature vector the joint probability distribution over a set of features can be calculated and an appropriate class label can be assigned.
+
+    \subsubsection{k-Nearest Neighbours (kNN)}
+    The nearest neighbours classifier assumes that if there are labelled points in a neighbourhood of a newly added point, then the new point can be classified based on it's neighbours' labels.
+There is an issue of choosing the correct number of nearest neighbours (or k) to consider.
+
+    \subsubsection{Support Vector Machine (SVM)}
+    \begin{figure}[!ht]
+    \centering
+    \includegraphics[width=0.75\textwidth]{../figs/svm}
+    \caption{Classification by a Support Vector Machine. The distance of the separating plane from both datasets is maximal. The figure was originally published in \cite{ponce2011cv}}
+    \label{fig:svm}
+    \end{figure}
+
+    Assume that a set of pairs $\{\{\mathbf{x}_1, y_1\}, \{\mathbf{x}_2, y_2\}, ...\}$ where $x_\mathit{i}$ are features and $y_\mathit{i} \in \{-1, 1\}$ are labels is given.
+Further assume that points with different labels are two linearly-separable datasets as shown in the figure \ref{fig:svm}, where dots and circles are points with different labels.
+Then, parameters \textbf{\textit{w}} and  \textit{b} exist such that
+    \begin{equation}	                        y_\mathit{i}\left(\mathbf{w}*\mathbf{x}_\mathit{i} + b\right) > 0
+    \end{equation}
+    for every $\mathbf{x}_\mathit{i}$ or a data point.
+This equation specifies constraints on a plane (or a hyperplane in general) that separates different classes.
+A Support Vector Machine finds the parameters \textbf{\textit{w}} and  \textit{b} so as to maximise the distance of the plane from members of both classes.
+We can combine several SVM classifiers in a 1-versus-all or an all-versus-all scheme.
+
+\section{ DATASETS }
+
+  Datasets are essential for the following reasons: (1) Supervised learning algorithms have ravenous apetite for labelled data.
+An open database of labelled RGBD images would be of a great help in evaluation of algorithms.
+(2) If any comparison of algorithms is to be meaningful it should be performed on the same data.
+There is a multitude of RGB datasets available: ImageNet\footnote{\url{http://www.image-net.org/}}, PascalVoc\footnote{\url{http://pascallin.ecs.soton.ac.uk/challenges/VOC/}}, LabelMe\footnote{\url{http://labelme.csail.mit.edu/Release3.0/browserTools/php/dataset.php}} and SUN\footnote{\url{http://groups.csail.mit.edu/vision/SUN/}}, among others.
+Unfortunately, they do not contain any depth information and cannot be used for the purpose of object classification based on RGBD data.
+On the other hand, the vast majority of RGBD datasets are focused on tracking or instance-level recognition, have insufficient number of examples per category or have too few categories.
+Author managed to find only two datasets suited to his needs.
+They are: the Berkeley 3D Object (B3DO) dataset \cite{B3DO} and a dataset compiled by Zhang \emph{et al} at the University of Tokyo\cite{zhangcategory}.
+The latter will be abbreviated Tokyo dataset from now on.
+
+  \subsection{Berkeley 3D Object Dataset}
+    \begin{figure}[!ht]
+    \centering	
+    \includegraphics[width=.75\textwidth]{../figs/b3do_objects}
+    \caption{B3DO objects: a) cups b) bottles c) books d) keyboards}
+    \label{fig:b3do_objects}
+    \end{figure}
+
+    The Berkeley 3D Object dataset, shown in \refFig{fig:b3do_objects}, was specifically designed for the purpose of object detection and classification.
+It consists of cluttered images in indoor environment, with many labelled and random objects per image.
+The images are often poorly lit and objects are partially occluded.
+There are around 50 classes with more than 20 examples in each of them.
+RGBD data are provided as pairs of colour images (8 bit RGB jpeg files) and depth maps (16 bit png files).
+Images are densely labelled --- for every pair of images there is an xml file with annotations.
+Each annotation states a category of an object as well as it's bounding box location.
+Since neigher image segmentation nor object detection is addressed in this paper we had to extract objects from the images before the dataset could be used.
+
+  \subsection{The University of Tokyo Dataset}	
+    \begin{figure}[!ht]
+    \centering
+    \includegraphics[width=1\textwidth]{../figs/tokyo_horizontal}
+    \caption{The Tokyo dataset: a) basket b) bicycle c) box d) bucket e) cart f) freezer g) notebook h) printer i) scanner j) scene}
+    \label{fig:tokyo}
+    \end{figure}
+
+    The Tokyo dataset, shown in \refFig{fig:tokyo}, is comprised of high quality images of single labelled objects in different settings, with changing viewpoint, object orientation and texture.
+Additional unlabelled object can be present, however, and should not be taken into account.
+No bounding boxes are given, which renders the classification task similar to the scene classification problem.
+The dataset is presented as colour images (8 bit RGB jpeg files) and depth maps (csv files with XYZ coordinates of each pixel).
+This dataset is aimed at the task of object classification in casual images.
+
+\section{ EXPERIMENTS }
+  There is a plenty of algorithms suitable for any of the four steps of Bag of Words image processing.
+Most of them have multiple tunable parameters and their performance might be interdependant on each other.
+Comprehensive evaluation is inevitable if an optimal combination is to be selected.
+Considering the PointCloud Library\footnote{\url{http://pointclouds.org/}} (PCL) alone yields far too many options to test, with 12 keypoint detectors and more than 20 feature descriptors.
+A literature review helped to narrow the scope of evaluation considerably.
+All experiments were run on a notebook with Intel Core i7 quad core 2.2 GHz CPU, 8 GB of RAM and a nVidia M540 GPU.
+
+  \subsection{Detectors and descriptors}
+    Keypoint detection algorithms were compared with respect to repeatability, invariance in \cite{pcl_keypoint_comparision} and in terms of object retrieval and recognition in \cite{3d_keypoint_eval}.
+3D-SIFT and ISS both achieve the highest robustness, while the latter appears to be the best choice for object retrieval.
+Dense detector (or uniform sampling) achieves the best performance in 2D image classification \cite{tsai2012bag}.
+Therefore, this paper compares SIFT, ISS and Uniform Sampling keypoint detection techniques.
+Additionaly, PCL descriptors were evaluated in terms of performance in object retrieval in \cite{pcl_features}.
+PFHRGB and SHOTCOLOR delivered the best results, while their simpler counterparts (PFH, FPFH, SHOT) were only a little worse.
+USC, which is a global descriptor and thus not suitable for the Bag of Words approach, achieved very similar accuracy.
+The family of PFH descriptors is evaluated in this paper.
+
+    \begin{table}[!hbtp]
+    \centering
+      \caption{Highest accuracy obtained with FPFH, PFH and PFHRGB descriptors on the B3DO dataset}
+      \label{tab:desc_b3do}
+     \begin{tabular}{*4c}
+     \toprule
+       Detector & ISS3D & SIFT & Uniform Sampling  \\ 
+       Descriptor & \multicolumn{3}{c}{Accuracy {[\%]}} \\
+     \midrule
+       FPFH & 65.22 &  56.52 & 56.07  \\ 
+       PFH & 59.32 &  54.83 & 59.50 \\
+       PFHRGB & 63.35 & 52.34 & 53.27 \\
+
+   \bottomrule
+    \end{tabular}
+    \end{table}
+
+    The best results of each detector/descriptor combination on the B3DO dataset are shown in table \ref{tab:desc_b3do}.
+ISS consistently proved to be the most successful detection algorithm in this setting.
+SIFT and Uniform Sampling scored similar accuracy but the latter is significantly faster.
+SIFT is in fact the slowest of the three.
+As for the descriptors, FPFH delivered the best performance even though it is an approximate and theoretically the least precise algorithm.
+It is also the fastest of the three.
+It appears that the combination of ISS and FPFH is not only surprisingly good in terms of accuracy; it is also the fastest.
+These two algorithms allow near real time point-cloud processing and classification.
+PFHRGB and SIFT are several times slower.
+
+  \subsection{Codebook}
+    KMeans is used in almost every implementation of the Bag of Words image processing pipeline \cite{tsai2012bag, toldo2009bag}.
+Csurka \emph{et al} showed that the number of visual words has a significant impact on the final results \cite{csurka2004visual}.
+A number of tests were run to discover an optimal codebook size for the current setting.
+
+    \begin{figure}[!ht]
+    \centering	
+    \includegraphics[width=.75\textwidth]{../figs/clustering_centroids_b3do}
+    \caption{Influence of dictionary size on the overall accuracy. B3DO dataset with ISS keypoint detector and FPFH feature descriptor}
+    \label{fig:cluster_b3do}
+    \end{figure}
+
+    The results from \refFig{fig:cluster_b3do} partially confirm Csurka's findings.
+The performance raises with the increasing number of centroids up to the point of 1500 centroids and 65.22\%.
+The discrepancies might be caused by the following factors: (1) ISS detector finds too many or irrelevant points, thus introducing noise or (2) The FPFH descriptor has too few dimensions (33) to be divided into more than 1500 regions in a meaningful way.
+
+  \subsection{B3DO}
+    Extracting objects from the B3DO datasets yielded far too many and unbalanced categories.
+Nnumber of objects in a category varies from 1 (tape) to 299 (table).
+8 categories were picked at random with a restriction that there should be at least 50 object instances in a category.
+Then, the objects were split into train and test set with a proportion of 1:1.
+They were used for estimation and evaluation respectively.
+
+    The highest accuracy achieved for this dataset is 65.22\%.
+Table \ref{tab:b3do_conf_matrix} contains a confusion matrix, number of examples per category and accuracy.
+The confusion matrix depicts classification errors.
+Let m\subscript{i, j} be an element of the confusion matrix at the i\superscript{th} row and j\superscript{th} column.
+It shows how many elements from the i\superscript{th} category was assigned to the j\superscript{th} category.
+A high value of m\subscript{i, j} such that $i \neq j$ indicates that the classifier cannot distinguish those two classes.
+
+    \begin{table}[!ht]
+    \centering
+    \caption{Results on the B3DO dataset with ISS keypoint detector, FPFH features and a dictionary of 1500 words; \textbf{Average accuracy: 65.22\%}}
+    \includegraphics[width=0.9\textwidth]{../figs/b3do_conf_matrix}	
+    \label{tab:b3do_conf_matrix}
+    \end{table}
+
+    More than half of the bottles were assigned to the cup category and keyboards were often mistook for books.
+These two error types are easily explained by a high degree of similarity of objects (bottles and cups are usually round and tall, books and keyboards are flat and rectangular) Surprisingly, however, objects from half of the categories were frequently marked as cups.
+Some of these misclassification errors might be caused by very poor quality of images.
+Many of them are occluded poorly lit low resolution images.
+
+  \subsection{Tokyo}
+    \begin{table}[!ht]
+    \centering
+    \caption{Results on the Tokyo dataset with ISS keypoint detector, PFH features and a dictionary of 3000 words; \textbf{Average accuracy: 62.30\%}}
+    \includegraphics[width=1\textwidth]{../figs/tokyo_conf_matrix}	
+    \label{tab:tokyo_conf_matrix}
+    \end{table}
+
+    Every of the 343 images from Tokyo dataset were used.
+Data was split into test and train set in proportions 1:2 in order to provide more training examples due to low number of objects in some classes.
+Even tough the overall accuracy achieved on the Tokyo dataset is similar in value to that of the B3DO, the structure of the result is very different.
+It is clearly visible that there is a strong correlation between a per class accuracy and the number of entries in this class.
+The highest performance in the bicycle category is coupled with the largest number of entries.
+On the other end of the scale there are cart and printer categories with only 2 and 4 entries respectively.
+On top of that, differences between some classes are marginal.
+The majority of carts and baskets were put into the bucket category.
+It does not surprise, for they are simply akin as can be seen in \refFig{fig:tokyo}.
+
+\section{ CONCLUSION }
+
+  In this paper we have tackled the issue of three dimensional point cloud classification with a bag of words-based approach.
+
+  The main focus was put on the design and efficient implementation of the pipeline in a way that allows easy addition of algorithms and switching them at run-time.
+
+  What is more, we have gone to great lengths in order to find scientific databases that are suitable for the task of point cloud classification.
+We believe that the presence of such databases is fundamental, for it allows meaningful comparison with other researchers.
+We have experienced the following problems: Firstly, point cloud processing is computationally expensive and inefficient.
+Due to the lack of structure in point clouds (\textit{i.e.} no predefined relationship between points) additional calculations have to be performed (\textit{e.g.} finding nearest neighbours requires distance comparison for all points in a cloud, whereas for a 2D image one instantly knows where adjacent pixels lie).
+Secondly, there are virtually no databases that would allow extensive training of the bag of words-based pipeline.
+Machine learning algorithms have ravenous appetite for labelled data.
+As the newest findings in the state-of-the-art 2D object classification suggest, an order of tens of thousands of samples is a prerequisite for any satisfactory results We had to make do with as few as 330 objects in our training set.
+Moreover, there is very little interest in the scientific community for this particular task.
+The majority of research is conducted on retrieval of CAD-like objects from mesh databases.
+Last, but not least, there is no 3D detection or description algorithm designed solely for the purpose of bag of words object classification.
+
+  In conclusion I would not recommend any bag-of-words based approach classification of real point clouds registered with a low quality camera such as Microsoft Kinect.
+Being computationally expensive and rather inefficient, it delivers inferior performance in terms of accuracy and speed when compared to 2D RGB image based algorithms.
+To makes matters worse, generalisation of 2D algorithms to the 3D domain can be very involved, causing the cutting-edge inventions of the 2D image processing scientists unavailable for the purpose of 3D point cloud processing.
 

### 2014-02-14 docs/kkr13/kkr13-eng.tex
kkr

@@
 \usepackage{booktabs}
+\usepackage{cite}
 \newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}
@@
 
+\bibliographystyle{abbrv}
 \begin{document}
 
-\listoftodos
+%\listoftodos
 
@@
 The BoW concept in natural language processing is introduced and a BoW image processing pipeline is described.
-Each part of the pipeline (region detection, feature extraction and vector quantization) is characterised and the most successful algorithms are outlined.
+Each part of the pipeline (region detection, feature extraction and vector quantization) is characterized and the most successful algorithms are outlined.
 Applications of BoW in image processing and their results are discussed.
@@
 If so, it would be desirable for the robot to know what kind of surroundings it is in.
-The problem can be treated as a scene or object classification problem, one of the most popular computer vision issues in the last decade.
-\todo[inline]{ref}
+The problem can be treated as a scene or object classification problem, one of the most popular computer vision issues in the last decade \cite{ponce2011cv}.
 
@@
 It were Csurka \textit{et al} who first used BoW for image classification in 2004 \cite{csurka2004visual}.
-Since images cannot be simply casted into natural language documents a pipeline that help us achieve this goal is needed.
-It usually consist of: keypoint detection, feature extraction, vector quantization, together with codebook construction, and classification, steps that will be discussed later.
+Since images cannot be simply cast into natural language documents a pipeline that help us achieve this goal is needed.
+It usually consist of: keypoint detection, feature extraction, vector quantization together with codebook construction and classification, steps that will be discussed later.
 
-  Being efficient, efective and flexible, a Bag of Words processing pipeline is, however, a blessing in a disguise.
+  Being efficient, effective and flexible, a Bag of Words processing pipeline is, however, a blessing in a disguise.
 While in fact it can provide satisfactory results with little effort, it is cumbersome to tune, thus spectacular performance is hard to achieve.
@@
 Construction of an image model is discussed and the most popular algorithms are outlined.
-Basic information on a problem of classification are introduced the most popular approaches of solving it are discussed.
+Then, applications of BoW in computer vision are reported and the problem of classification is introduced.
 Section 3 describes two renown RGBD image datasets suitable for evaluation of RGBD data-based object classifiers.
@@
 
-  Bag of Words is an intermediate representation in a form of a histogram used in natural language processing, information retrieval and data mining.
-It obliterates any grammatical information as well as word order in order to perserve word incidence only.
+  The Bag of Words model is an intermediate representation in a form of a histogram used in natural language processing, information retrieval and data mining.
+It obliterates any grammatical information as well as word order so as to preserve word incidence only.
 
@@
 
-  The figure \ref{fig:bow_example} shows a piece of text and its BoW model, where articles and punctuation marks were left out.
-In order to compare different documents a global dictionary must be built.
-The dictionary (codebook) is constructed by taking every word from all available documents and removing duplicates.
-One can image that if a dictionary is of any considerable size resulting representation of especially small documents will be very sparse.
+  \refFig{fig:bow_example} shows a piece of text and its BoW model, with articles and punctuation marks left out.
+In order to compare different documents a global dictionary (codebook) must be built.
+It is constructed by taking every unique word from all available documents.
+One can image that if a dictionary is of any considerable size the resulting representation of especially small documents can be very sparse.
 Classification algorithms can be optimised for sparse data in order to boost performance.
@@
     Tsai describes a well established pipeline that allows translation of images into text documents \cite{tsai2012bag}.
-It consists of the following steps: (1) region detection, (2) feature extraction, (3) vector quantization and (4) BoW histogram formation as can be seen in the figure \ref{fig:bow_pipeline}.
+It consists of the following steps: (1) region detection, (2) feature extraction, (3) vector quantization and (4) BoW histogram formation as can be seen in \refFig{fig:bow_pipeline}.
 The author summarises the most commonly used methods for performing these tasks.
@@
     Characteristic region detection is the first step in any Bag of Words framework.
-Numerous detection methods have been developed, but choosing the right one for any particular case might prove tricky.
-
-    The most common detectors make use of a Harris corner detector or image's first or second derivatives.
+Numerous detection methods have been developed, which might choosing the right one tricky.
+The most common detectors use a Harris corner detector or 1\textsuperscript{st} or 2\textsuperscript{nd} image derivatives.
 A Harris-Laplace detector is an example of a Harris-based detector.
-The Harris function is scale adapted and its outcome is a subject to a Laplacian-of-Gaussian (LoG) operator, which selects relevant points in scale space.
-Images' regions' 2\textsuperscript{nd} derivatives, namely the regions' Hessians, can be combined with a LoG operator as well.
-This combination allows selection of points significant in the two spaces: the scale space and the Hessian's determinant space.
-The latter entails the speed at which pixel intensities change in the neighbourhood of a point.
+The Harris function is scale adapted and its outcome is subjected to a Laplacian-of-Gaussian (LoG) operator, which selects points in scale space.
+2\textsuperscript{nd} image derivatives~---~Hessians can be combined with a LoG operator in order to further select points in the Hessian's determinant space.
 
     A number of more advanced recipes for salient region localisation have been developed and implemented.
-These include for example SIFT \cite{sift_keypoint}, SUSAN \cite{susan_keypoint} and Intrinistic Shape Signatures \cite{iss_keypoint}.
-The majority of keypoint detection formulas is being developed for the 2D domain.
-A number of them have been adapted to 3D, however.
-A comparative evaluation of detection algorithms available in the PointCloud Library (PCL, discussed below) can be find in \cite{pcl_keypoint_comparision}.
-Another comprehensive study is \cite{3d_keypoint_eval}.
-All these formulas, called sparse feature detectors, resort to selection of maxima in specific state spaces.
-An entirely different scheme is to use a dense feature detector.
-That is, take a uniformly sampled grid of points.
-Dense detectors have an advantage in that they sample slow changing regions in terms of gradient or hessian of an image.
-Examples of such regions would be a clear sky or a calm ocean.
+These include for example SIFT \cite{sift_keypoint}, SUSAN \cite{susan_keypoint} and ISS \cite{iss_keypoint}, with the vast majority implemented for the 2D domain and only a few generalised to 3D.
+A comparative study of detectors available in the PointCloud Library (PCL) can be found in \cite{pcl_keypoint_comparision, 3d_keypoint_eval}.
+All of the above, called sparse feature detectors, resort to selection of maxima in specific state spaces.
+An entirely different scheme is to use a dense feature detector, that is to take a uniformly sampled grid of points.
+Dense detectors are advantageous in that they sample slow changing regions in terms of image derivatives.
+Examples of such regions are a clear sky or a calm ocean.
 Li \emph{et al} showed that dense detectors generally outperform sparse ones \cite{fei2005bayesian}.
@@
   \subsubsection{Feature Extraction}
-    Suppose only coordinates of a keypoint were known.
-In case of even the smallest rotation or translation they would change and the keypoint would be lost.
-Keypoints should be described in a way that makes them invariant to affine transformations, changes in light intensity or colour saturation.
-It is hard to achieve all of these properties simultaneously, but methods that meet some of them exist.
-
+    Suppose only keypoint's coordinates were given.
+The smallest affine transformation applied to the image would render the keypoints useless.
+Feature extraction is about describing a region in a way that is invariant to affine transformations, light intensity changes or colour saturation.
+Achieving all these properties simultaneously can be hard but methods that achieve some of them do exist.
 Keypoint description takes form of coordinates in a high-dimensional space.
@@
   \subsubsection{Vector Quantization}
-    When features are extracted they have to be normalised.
-Vector quantization step have two main phases.
-The first one is a codebook construction from a training dataset.
-The second phase is responsible for parsing (or translation) raw image descriptors into a form compatible with the newly constructed codebook.
-The simplest way of building a dictionary is to find patterns or regions within the descriptors computed on a training dataset.
-Then, the parsing phase is about assigning a descriptor to one of the codebook elements (e.g.
-to one of the regions).
-Suppose we use centroids or medoids of the discovered regions as our codebook's entries.
-Then, we can match a descriptor to one of the centroids performing a nearest neighbour search.
-The descriptor parsed this way is called a \textit{visual word}.
-Finally, we build a histogram of visual word occurrence.
+    Vector quantization comprises of: (1)~codebook construction from a trainset and (2)~descriptor parsing, performed on a test set only on all data, depending on the setting.
+The simplest way of building a dictionary is to find patterns or regions within descriptors computed on a trainset and use their centroids or medoids as the codebook's entries.
+The parsing phase is about assigning a descriptor to one of the codebook elements (e.g.
+1-nearest neighbour matching with a centroid).
+The parsed descriptor is called a \textit{visual word}.
+Finally, a histogram of visual words can be built.
 The histogram have a fixed size equal to the codebook size.
-Each bin of the histogram tells us how many visual words of a particular kind were in the description of the corresponding image.
+Each bin of the histogram tells us how many visual words of a particular kind an image contains.
 
     The kMeans is the single most popular vector quantization algorithm used in the BoW pipelines \cite{tsai2012bag}.
-Developed in 1950's, it is well known and simple to implement.
-kMeans divides all data into a predefined amount of clusters and computes the clusters' centroids.
-Many modifications and alternative versions have emerged \cite{kmeans_jain2010data}.
-Some of them are: faster than the original \emph{approximate kmeans}, \emph{hierarchical kmeans}, which automatically chooses the final number of clusters and a \emph{soft kmeans} --- a variation of the algorithm that allows a fuzzy alignment.
-The fuzzy alignment mean that each point can belong to several clusters with different weights.
-A weight can be proportional for instance to the inverse square of the distance to a centroid.
+Developed in 1950's, it is well known and easy to implement.
+kMeans divides all data into a predefined amount of clusters and computes the their centroids.
+Many modifications and alternative versions emerged \cite{kmeans_jain2010data}.
+Some of them are: faster than the original \emph{approximate kmeans}, \emph{hierarchical kmeans}, which automatically chooses the final number of clusters and a \emph{soft kmeans} --- a variation that allows fuzzy alignment.
+Fuzzy alignment means that each point can belong to several clusters with different weights (e.g.
+proportional to the inverse square of a distance to a centroid).
 
-    If computational cost is of no concern, or if required precision is of the utmost priority, a Gaussian Mixture Model (GMM) can be used.
-The GMM partitions data into a set of clusters, finds their means and covariances.
-In the parsing step we compute a probability distribution of a descriptor over all the clusters.
-We can then build a fuzzy aligned histogram taking the probability distribution as weights.
-The GMM can be thought of as a generalisation of the kMeans algorithm.
-The drawback of the GMM is its massive computational cost in comparison with still expensive kMeans.
-Recently, Perronnin \textit{et al} proposed GMM based fisher-kernel vector quantization step with superior results \cite{fisher1, fisher2}.
+    If computational cost is of no concern or if required precision is of the utmost priority, Gaussian Mixture Model (GMM) can be used.
+GMM partitions data into a set of clusters, finds their means and covariances.
+In the parsing step it computes a probability distribution of a descriptor over all the clusters.
+Fuzzy aligned histogram is built by taking the probability distribution as weights.
+GMM can be thought of as a generalisation of the kMeans algorithm.
+One drawback is massive computational cost in comparison with still expensive kMeans.
+Recently, Perronnin \textit{et al} proposed GMM based fisher-kernel vector quantization step yielding superior results \cite{fisher1, fisher2}.
 
-    After we choose a vector quantization algorithm, we have to decide what size of a dictionary to use.
-In a simplest case, when the kMeans is used, we can treat each clusters' centroid as a visual word.
-Therefore, the dictionary size defines how much information we retain in a BoW histogram.
-A big training set containing many classes with large inter-class and inter-class variance is likely to require a huge codebook.
+    After choosing a vector quantization algorithm a codebook size have to be determined.
+With a standard kMeans implementation the dictionary size defines how much information is retained in a BoW histogram.
+A big trainset containing many classes with large intra-class and inter-class variance is likely to require a huge codebook.
 On the other hand, too big a dictionary might introduce quantization artefacts.
 One has to bear in mind that the vector quantization step is the most time-consuming part of the BoW pipeline.
-The highest computational complexity is associated with the codebook construction step and it is$O(n^3)$, where $n$ is the codebook size.
+The highest computational complexity is associated with the codebook construction step and it is $O(n^3)$, where $n$ is the codebook size.
 
@@
 The Early Fusion concatenates two feature vectors if they have been extracted from the same keypoint.
-The Late Fusion joins histograms, outputted by separate quantization steps.
+The Late Fusion joins histograms that are output of separate quantization steps.
 
@@
 
-\section{Problem of Classification}
+\subsection{Problem of Classification}
 
@@
 
-    \subsubsection{Na\`ive Bayes}
-    Assume that we have a \textit{n}-dimensional feature vector $\mathbf{X}$ such that $\mathbf{X} = \left\{x_1, x_2, ...
-, x_\mathit{n}\right\}$ and an unknown category label \textit{C}.
-The probability of the category \textit{C} given the feature vector \textbf{X} is $P\left(\mathit{C}\middle|\mathbf{X}\right) = P\left(\mathit{C}\middle|\left\{x_1, x_2, ..., x_\mathit{n}\right\}\right)$.
-The strong (or na\`ive) Bayes assumption says that features are independent of each other, that is $P(\mathbf{X}) = P(x_1)*P(x_2)*...*P(x_\mathit{n})$.
-If so, we can compute probability distributions of every class in our training set given every feature.
-Then, for any new feature vector the joint probability distribution over a set of features can be calculated and an appropriate class label can be assigned.
-
-    \subsubsection{k-Nearest Neighbours (kNN)}
-    The nearest neighbours classifier assumes that if there are labelled points in a neighbourhood of a newly added point, then the new point can be classified based on it's neighbours' labels.
-There is an issue of choosing the correct number of nearest neighbours (or k) to consider.
-
-    \subsubsection{Support Vector Machine (SVM)}
-    \begin{figure}[!ht]
-    \centering
-    \includegraphics[width=0.75\textwidth]{../figs/svm}
-    \caption{Classification by a Support Vector Machine. The distance of the separating plane from both datasets is maximal. The figure was originally published in \cite{ponce2011cv}}
-    \label{fig:svm}
-    \end{figure}
-
-    Assume that a set of pairs $\{\{\mathbf{x}_1, y_1\}, \{\mathbf{x}_2, y_2\}, ...\}$ where $x_\mathit{i}$ are features and $y_\mathit{i} \in \{-1, 1\}$ are labels is given.
-Further assume that points with different labels are two linearly-separable datasets as shown in the figure \ref{fig:svm}, where dots and circles are points with different labels.
-Then, parameters \textbf{\textit{w}} and  \textit{b} exist such that
-    \begin{equation}	                        y_\mathit{i}\left(\mathbf{w}*\mathbf{x}_\mathit{i} + b\right) > 0
-    \end{equation}
-    for every $\mathbf{x}_\mathit{i}$ or a data point.
-This equation specifies constraints on a plane (or a hyperplane in general) that separates different classes.
-A Support Vector Machine finds the parameters \textbf{\textit{w}} and  \textit{b} so as to maximise the distance of the plane from members of both classes.
-We can combine several SVM classifiers in a 1-versus-all or an all-versus-all scheme.
-
 \section{ DATASETS }
 
-  Datasets are essential for the following reasons: (1) Supervised learning algorithms have ravenous apetite for labelled data.
-An open database of labelled RGBD images would be of a great help in evaluation of algorithms.
+  Datasets are essential for the following reasons: (1) Supervised learning algorithms have ravenous appetite for labeled data.
+An open database of labeled RGBD images would be of a great help in evaluation of algorithms.
 (2) If any comparison of algorithms is to be meaningful it should be performed on the same data.
@@
 Each annotation states a category of an object as well as it's bounding box location.
-Since neigher image segmentation nor object detection is addressed in this paper we had to extract objects from the images before the dataset could be used.
+Since neither image segmentation nor object detection is addressed in this paper we had to extract objects from the images before the dataset could be used.
 
@@
   There is a plenty of algorithms suitable for any of the four steps of Bag of Words image processing.
-Most of them have multiple tunable parameters and their performance might be interdependant on each other.
+Most of them have multiple tunable parameters and their performance might be interdependent on each other.
 Comprehensive evaluation is inevitable if an optimal combination is to be selected.
@@
   \subsection{Detectors and descriptors}
-    Keypoint detection algorithms were compared with respect to repeatability, invariance in \cite{pcl_keypoint_comparision} and in terms of object retrieval and recognition in \cite{3d_keypoint_eval}.
+    Keypoint detection algorithms were compared with respect to repeatability and invariance in \cite{pcl_keypoint_comparision} as well as in terms of object retrieval and recognition in \cite{3d_keypoint_eval}.
 3D-SIFT and ISS both achieve the highest robustness, while the latter appears to be the best choice for object retrieval.
@@
 Therefore, this paper compares SIFT, ISS and Uniform Sampling keypoint detection techniques.
-Additionaly, PCL descriptors were evaluated in terms of performance in object retrieval in \cite{pcl_features}.
+Additionally, PCL descriptors were evaluated in terms of object retrieval performance in \cite{pcl_features}.
 PFHRGB and SHOTCOLOR delivered the best results, while their simpler counterparts (PFH, FPFH, SHOT) were only a little worse.
@@
 SIFT is in fact the slowest of the three.
-As for the descriptors, FPFH delivered the best performance even though it is an approximate and theoretically the least precise algorithm.
+As for the descriptors, FPFH delivered the best performance, even though it is an approximate and theoretically the least precise algorithm.
 It is also the fastest of the three.
-It appears that the combination of ISS and FPFH is not only surprisingly good in terms of accuracy; it is also the fastest.
-These two algorithms allow near real time point-cloud processing and classification.
+The combination of ISS and FPFH delivers outstanding results at the lowest computational cost.
+It allows near real time point-cloud processing and classification.
 PFHRGB and SIFT are several times slower.
@@
     Extracting objects from the B3DO datasets yielded far too many and unbalanced categories.
-Nnumber of objects in a category varies from 1 (tape) to 299 (table).
+The number of objects in each category varies from 1 (tape) to 299 (table).
 8 categories were picked at random with a restriction that there should be at least 50 object instances in a category.
-Then, the objects were split into train and test set with a proportion of 1:1.
-They were used for estimation and evaluation respectively.
+Then, the objects were split into train and test set with a proportion of 1:1, which were used for estimation and evaluation respectively.
 
@@
 The confusion matrix depicts classification errors.
-Let m\subscript{i, j} be an element of the confusion matrix at the i\superscript{th} row and j\superscript{th} column.
-It shows how many elements from the i\superscript{th} category was assigned to the j\superscript{th} category.
-A high value of m\subscript{i, j} such that $i \neq j$ indicates that the classifier cannot distinguish those two classes.
+Let $m_{i, j}$ be an element of the confusion matrix at the $i^{th}$ row and $j^{th}$ column.
+It shows how many elements from the $i^{th}$ category was assigned to the $j^{th}$ category.
+A high value of $m_{i, j}$ such that $i \neq j$ indicates that the classifier cannot distinguish those two classes.
 
@@
 
-    Every of the 343 images from Tokyo dataset were used.
-Data was split into test and train set in proportions 1:2 in order to provide more training examples due to low number of objects in some classes.
-Even tough the overall accuracy achieved on the Tokyo dataset is similar in value to that of the B3DO, the structure of the result is very different.
+    Everyone of the 343 images from the Tokyo dataset were used.
+Data were split into test and train set in proportions 1:2 in order to provide more training examples due to very limited numbers of objects in some classes.
+Even tough the overall accuracy achieved on the Tokyo dataset is similar in value to that of the B3DO's, the structure of the result is very different as shown in table \ref{tab:tokyo_conf_matrix}.
 It is clearly visible that there is a strong correlation between a per class accuracy and the number of entries in this class.
 The highest performance in the bicycle category is coupled with the largest number of entries.
-On the other end of the scale there are cart and printer categories with only 2 and 4 entries respectively.
-On top of that, differences between some classes are marginal.
+On the other end of the scale there are the printer, scanner and cart categories with 2, 2 and 4 entries respectively and 0\% classification accuracy.
+On top of that, the differences between some classes are marginal.
 The majority of carts and baskets were put into the bucket category.
@@
 
-  In this paper we have tackled the issue of three dimensional point cloud classification with a bag of words-based approach.
+  In this paper the issue of three dimensional point cloud classification with a bag of words-based approach was tackled.
+Two scientific databases suitable for the task of point cloud classification were identified and adapted for the purpose of this work.
+Presence of such datasets is vital --- they act as benchmarks and allow objective comparison of different solutions of the problem.
+The following problems emerged: (1)~Point cloud processing is computationally expensive and inefficient.
+Due to the lack of structure in point clouds (\textit{i.e.} no predefined spatial relationships between points) additional calculations have to be performed (\textit{e.g.} finding nearest neighbours requires at least several distance computations).
+(2)~There are very few and small databases available.
+Machine learning algorithms have ravenous appetite for labelled data.
+As the newest findings in the state-of-the-art 2D object classification suggest, an order of tens of thousands of samples is a prerequisite for any satisfactory results.
+This work had to make do with less than 300 objects in the train sets.
+(3)~There is very little interest in the scientific community for this particular task.
+The majority of research is conducted on retrieval of CAD-like objects from mesh databases.
 
-  The main focus was put on the design and efficient implementation of the pipeline in a way that allows easy addition of algorithms and switching them at run-time.
+  The achieved results the B3DO and Tokyo datasets are respectively $5.21$ and $6.23$ times higher than random rates ($12.5\%$ and $10\%$).
+This shows that classification of point clouds is feasible and can be performed in what is close to real time on a mainstream notebook.
+The accuracy can be further enhanced by generalising 2D algorithms to the 3D domain, while the computational time can be reduced by using a GPU for the most computationally expensive parts of the Bag of Words framework.
+In conclusion, the depth data does not account for a straightforward improvement in classification accuracy.
+In fact, it is easier to obtain better results on 2D RGB images, because the best algorithms are not converted to the 3D domain and there is substantially more data available for the 2D.
 
-  What is more, we have gone to great lengths in order to find scientific databases that are suitable for the task of point cloud classification.
-We believe that the presence of such databases is fundamental, for it allows meaningful comparison with other researchers.
-We have experienced the following problems: Firstly, point cloud processing is computationally expensive and inefficient.
-Due to the lack of structure in point clouds (\textit{i.e.} no predefined relationship between points) additional calculations have to be performed (\textit{e.g.} finding nearest neighbours requires distance comparison for all points in a cloud, whereas for a 2D image one instantly knows where adjacent pixels lie).
-Secondly, there are virtually no databases that would allow extensive training of the bag of words-based pipeline.
-Machine learning algorithms have ravenous appetite for labelled data.
-As the newest findings in the state-of-the-art 2D object classification suggest, an order of tens of thousands of samples is a prerequisite for any satisfactory results We had to make do with as few as 330 objects in our training set.
-Moreover, there is very little interest in the scientific community for this particular task.
-The majority of research is conducted on retrieval of CAD-like objects from mesh databases.
-Last, but not least, there is no 3D detection or description algorithm designed solely for the purpose of bag of words object classification.
-
-  In conclusion I would not recommend any bag-of-words based approach classification of real point clouds registered with a low quality camera such as Microsoft Kinect.
-Being computationally expensive and rather inefficient, it delivers inferior performance in terms of accuracy and speed when compared to 2D RGB image based algorithms.
-To makes matters worse, generalisation of 2D algorithms to the 3D domain can be very involved, causing the cutting-edge inventions of the 2D image processing scientists unavailable for the purpose of 3D point cloud processing.
-
-\subsubsection{\small Mathematical formulae}
-
- The number of a formula has to be written
- in parentheses shifted to the right (see below). Symbols of variables 
- should be written in italic.
- \begin{equation}
-   x = \frac{a^{(1-z)} + b}{10 - d_2}
- \end{equation}
-
- \noindent
- Intervals of values should be written without spaces, e.g.\ 4--45MPa.
-
-\section{FIGURES AND TABLES}
-
-\subsection{Figures and their arrangement}
-
- Figures should be numbered with the Arabic numerals (see fig. 
- \ref{fig-example}).
-
- \begin{figure}[hbtp]
-  \fbox{\rule{0mm}{45mm}\rule{85mm}{0mm}}
-  \caption{The figure caption}
-  \label{fig-example}
- \end{figure}
-
-\subsection{Tables}
-
- Tables have to be formated in the way presented below (see table 
- \ref{tab-example}). The tables have to be numbered  separately from 
- the figures.
-
- \begin{table}[hbtp]
-  \caption{The table caption}
-   \label{tab-example}
-   \begin{tabular}{|c|c|c|c|c|}\hline
-       Column 1 & Column 2 & Column 3 &  Column 4 & Column 5\\ \hline
-       $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$ & $\vdots$\\ \hline
-    \end{tabular}
- \end{table}
-
-\section{CITATIONS}
-
-Citations of papers should be marked  with square brackets, e.g.
-\cite{Ming}. The references have to be arranged in 
-the alphabetic order relative to the authors' surnames (see the example
-below).
-
-\begin{thebibliography}{99}
-\bibitem{Litwiniec}
-    A. Litwin et al. Transport phenomena in InSb doped with various impurities.
-    In: 11 International Conference on the Physics of Semiconductors.
-   {\em Proceedings}. Warszawa -- Poland, July 25--29, 
-    1972. Vol. 2, pp. 952--957.
-
- \bibitem{Lamadrid} 
-  J.~G. de~Lamadrid.
-  \newblock Avoidance of obstacles with unknown trajectories: Locally optimal
-   paths and periodic sensor readings.
-   \newblock {\em The Inter. Journal of Robotics Research}, 13(6):496--507,
-   December 1994.
-
- \bibitem{Ming}
-   A~Ming, K.~Kajihara, M.~Kajitani, and M.~Shimojo.
-   \newblock Development of a rapid obstacle sensing system using sonar 
-   ring for mobile robot.
-   \newblock In {\em Proc. Int. Conf. on Robotics and Automation}, 
-   volume~3, pp. 3068 -- 3073, Washington, D.C., May 2002.
-
- \bibitem{Singh:1987:Convex:Shapes}
-   J.~Sanjiv Singh and Meghanad~D. Wagh.
-   \newblock Robot path planning using intersecting convex shapes: Analysis and
-   simulation.
-   \newblock {\em IEEE Journal of Robotics and Automation}, RA-3(2):101 -- 108,
-   April 1987.
-\end{thebibliography}
+\bibliography{kkr13}
 \end{document}

### 2014-10-12 docs/min/kkr13-eng.tex
min

--- 2014-02-14 docs/kkr13/kkr13-eng.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% This file is delivered as an usage example of the file 'kkr13-eng.sty'.
-% The style file 'kkr13-eng.sty' has been prepared for papers intended 
-% to be presented at the XIII National Conference on Robotics in Poland.
-%
-% The file 'kkr13-eng.sty' contains definitions of macros for English
-% and Polish authors. Thus their names are in English and Polish respectively.
-% They define the same operations. English and Polish names are used
-% only for authors' convenience. 
-% Therefore both types of macros can be used in this type of the document.
-% The same type of macros are defined in the style file defined for papers 
-% written in Polish.
-% Below there is a list of macros names in English and their equivalent forms
-% in Polish.
-%
-%       \articleTitle          =   \tytulArtykulu
-%       \titleFootNote         =   \stopkaPrzypisTytulu
-%       \articleAuthor         =   \autorArtykulu
-%       \affiliation           =   \instytucja
-%       \theSameAffiliationAs  =   \instytucjaTaSamaJak
-%       \articleShortTitle     =   \naglowekTytulSkrocony
-%       \breakAuthorsLine      =   \zlamLinieAutorow
-%       \authorsForHeader      =   \naglowekAutorzyArtykulu
-%       \authorsCustomizedList =   \wlasnaListaAutorow
-%       \abstract              =   \streszczenie
-%       \Equation              =   \wzor
-%       \refeq                 =   \refwzor
-%       \reffig                =   \refrys
-%       \refFig                =   \refRys
-%
-% Author: Bogdan Kreczmer 
-% Last modification:      2013.12.09
-% 
-% In the case of any doubt, please, contact via e-mail.
-% The address of the author is:
-%  bogdan.kreczmer@pwr.wroc.pl
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\documentclass[11pt,twoside]{article}
-\usepackage{kkr13-eng}
-\usepackage{todonotes}
+\documentclass[12pt]{article}
 \usepackage[hidelinks]{hyperref}
@@
 \newcommand{\subscript}[1]{\ensuremath{_{\textrm{#1}}}}
-
-\articleTitle{3D Object Classification \\ Based on RGBD Images}
-
-%
-% For information of a project (if any)
-%
-\titleFootNote{The work described in this paper was conducted within author's Bachelor's dissertation}
-
-%
-% Parameters:
-%   1 - initials of the first and middle name of an author
-%   2 - the first and middle name of an author
-%   3 - the last name of an author
-%
-\articleAuthor{A.}{Adam}{Kosiorek}
-
-\affiliation[institute1]{ Institute of Automation and Robotics, The Faculty of Mechatronics of Warsaw University of\\ Technology, email: iair@mchtr.pw.edu.pl, website: http://iair.mchtr.pw.edu.pl}
+\usepackage{graphicx}
+\usepackage{mathptmx}
 
@@
 
-%\listoftodos
+\title{3D Object Classification Based on RGBD Images}
+\author{Adam Kosiorek}
+\maketitle
+Affiliation: Institute of Automation and Robotics, The Faculty of Mechatronics 
+of Warsaw University of Technology \\
+website: http://iair.mchtr.pw.edu.pl \\
+Supervisor: Prof. dr hab. Barbara Siemiątkowska \\
+Defense date: 11.02.2014
 
@@
 
-  This paper introduces a Bag of Words (BoW) semantic object classification framework based on RGBD data registered by a Microsoft Kinect camera.
-The BoW concept in natural language processing is introduced and a BoW image processing pipeline is described.
-Each part of the pipeline (region detection, feature extraction and vector quantization) is characterized and the most successful algorithms are outlined.
-Applications of BoW in image processing and their results are discussed.
-Additionally, the problem of classification is described.
-Algorithms with high performance potential were identified and evaluated.
+ This paper introduces a Bag of Words (BoW) semantic object classification 
+framework based on RGBD data registered by a Microsoft Kinect camera. We 
+introduce a BoW image processing 
+pipeline, describe it's steps in detail (region detection, feature 
+extraction and vector quantization) and we outline the most successful 
+algorithms. Algorithms with high performance potential were identified and 
+evaluated. 
 Salient region detection is done by SIFT, ISS3D and Uniform Sampling. 
-Description is performed by FPFH, PFH and PFHRGB.
-Vector quantization was carried out by the KMeans algorithm.
-An SVM with the RBF kernel trained with an All-vs-All was used as a classifier.
-We achieved the accuracy of 65.22\% on 8 categories of the Berkely 3D Object Dataset and 62.3\% on a 10 category dataset compiled by Zhang from the Tokyo University.
+Description is performed by FPFH, PFH and PFHRGB. Vector quantization was 
+carried out by KMeans. An SVM with the RBF kernel trained with an 
+All-vs-All method was used as a classifier. We achieved the accuracy of 65.22\% 
+on 8 
+categories of the Berkely 3D Object Dataset and 62.3\% on a 10 category dataset 
+compiled by Zhang.
+
 }
 
-\maketitle
+\section{ Introduction }
 
-\section{ INTRODUCTION }
+  It has never been easier to capture visual information. Popular storage 
+services grow lighting fast due to terabytes of photographs and movies uploaded 
+every day. The growth is so fast that hand-tagging and description, the 
+traditional means of annotation, cease to suffice. They are ambiguous, 
+emotional and rarely optimal. With no better solution at hand databases are 
+becoming increasingly harder to browse. Similar issues occur in mobile 
+robotics, where a robot has to understand it's enviornment if it is to interact 
+with it. Both problems can be cast as a scene or object classification problem, 
+one of the most popular computer vision issues in the last decade.
 
-  It has never been easier to capture visual information.
-Popular storage services grow lighting fast due to terabytes of photographs and movies uploaded every day.
-The growth is so fast that hand-tagging and description, the traditional means of annotation, cease to suffice.
-They are ambiguous, emotional and rarely optimal.
-With no better solution at hand databases are becoming increasingly harder to browse.
-Another, but quite similar setting occurs in the field of mobile robotics.
-A mobile robot is there to interact with its environment.
-If so, it would be desirable for the robot to know what kind of surroundings it is in.
-The problem can be treated as a scene or object classification problem, one of the most popular computer vision issues in the last decade \cite{ponce2011cv}.
-
-  This paper tackles two issues.
-Firstly, the Bag of Words (or BoW for short) approach to image classification is reviewed.
-The Bag of Words method originated from the natural language processing domain \cite{tsai2012bag}.
-It makes a strong assumption that word occurrence in a text document define its meaning.
-It were Csurka \textit{et al} who first used BoW for image classification in 2004 \cite{csurka2004visual}.
-Since images cannot be simply cast into natural language documents a pipeline that help us achieve this goal is needed.
-It usually consist of: keypoint detection, feature extraction, vector quantization together with codebook construction and classification, steps that will be discussed later.
-
-  Being efficient, effective and flexible, a Bag of Words processing pipeline is, however, a blessing in a disguise.
-While in fact it can provide satisfactory results with little effort, it is cumbersome to tune, thus spectacular performance is hard to achieve.
-One reason is the abundance of suitable algorithms available.
-Wide variety of building blocks might make it flexible, but it renders choosing an optimal combination infeasible.
-
-  The rest of this work is organised as follows: Section 2 describes the Bag of Words technique in detail.
-Construction of an image model is discussed and the most popular algorithms are outlined.
-Then, applications of BoW in computer vision are reported and the problem of classification is introduced.
-Section 3 describes two renown RGBD image datasets suitable for evaluation of RGBD data-based object classifiers.
-Section 4 addresses the topics of experimental setup, conducted experiments and provides the results.
+  This paper reviews the Bag of Words (or BoW for short) approach to image 
+classification, evaluates available point cloud databases in terms of usability 
+in scene classification studies and applies BoW model in the 3D domain. The 
+rest of this work is organised as follows: Section 2 describes the Bag of Words 
+technique in detail. Construction of an image model is discussed and the most 
+popular algorithms are outlined and the problem of classification is 
+introduced. Section 3 describes two renown RGBD image datasets suitable for 
+evaluation of RGBD data-based object classifiers. Section 4 addresses the 
+topics of experimental setup, conducted experiments and provides the results. 
 Finally, Section 5 concludes this work.
 
-\section{ BAG OF WORDS }
+\section{ Bag of Words }
 
-  The Bag of Words model is an intermediate representation in a form of a histogram used in natural language processing, information retrieval and data mining.
-It obliterates any grammatical information as well as word order so as to preserve word incidence only.
+  The Bag of Words model originated from the natural language processing domain 
+\cite{tsai2012bag}. It 
+assumes that word occurrence in a text document carries semantic information. 
+It is an intermediate representation (in a form of a hisogram)
+used in natural language processing, information retrieval and general data 
+mining.
 
@@
 
-  \refFig{fig:bow_example} shows a piece of text and its BoW model, with articles and punctuation marks left out.
-In order to compare different documents a global dictionary (codebook) must be built.
-It is constructed by taking every unique word from all available documents.
-One can image that if a dictionary is of any considerable size the resulting representation of especially small documents can be very sparse.
-Classification algorithms can be optimised for sparse data in order to boost performance.
+  Figure \ref{fig:bow_example} shows a piece of text and its BoW model, with 
+articles and punctuation marks left out. To compare different 
+documents we need a global dictionary (or codebook), usually constructed by 
+taking all unique words from available documents (a training set). If 
+a dictionary is of any considerable size the resulting representation of 
+especially small documents can be very sparse.
 
-  In natural language processing BoW is used to infer semantic meaning of documents.
-If we could translate an image into a text document we might be able to employ similar methods.
-A question arises: How does one make a text document from an image?
+  In natural language processing BoW is used to infer semantic meaning of 
+documents. If we could translate an image into a text document we might be able 
+to employ similar methods. How do we do that?
 
-  \subsection{Processing Pipeline}	
-    Tsai describes a well established pipeline that allows translation of images into text documents \cite{tsai2012bag}.
-It consists of the following steps: (1) region detection, (2) feature extraction, (3) vector quantization and (4) BoW histogram formation as can be seen in \refFig{fig:bow_pipeline}.
-The author summarises the most commonly used methods for performing these tasks.
+  \subsection{From Images to Text Documents}	
+The original pipeline consists of the following 
+steps: (1) region detection, (2) feature extraction, (3) vector quantization 
+and (4) BoW histogram formation as in figure \ref{fig:bow_pipeline}. Tsai 
+summarises the most common methods used recently \cite{tsai2012bag}.
 
@@
   \subsubsection{Region Detection}
-    Characteristic region detection is the first step in any Bag of Words framework.
-Numerous detection methods have been developed, which might choosing the right one tricky.
-The most common detectors use a Harris corner detector or 1\textsuperscript{st} or 2\textsuperscript{nd} image derivatives.
-A Harris-Laplace detector is an example of a Harris-based detector.
-The Harris function is scale adapted and its outcome is subjected to a Laplacian-of-Gaussian (LoG) operator, which selects points in scale space.
-2\textsuperscript{nd} image derivatives~---~Hessians can be combined with a LoG operator in order to further select points in the Hessian's determinant space.
+    Characteristic region detection is the first step in any Bag of Words 
+framework. Numerous detection methods have been developed, which makes choosing 
+the right one tricky. The most common detectors use a Harris corner detector or 
+1\textsuperscript{st} or 2\textsuperscript{nd} image derivatives. A 
+Harris-Laplace detector is an example of a Harris-based detector. The Harris 
+function is scale adapted and its outcome is subjected to a 
+Laplacian-of-Gaussian (LoG) operator, which selects points in scale space. 
+2\textsuperscript{nd} image derivatives~---~Hessians can be combined with a LoG 
+operator in order to further select points in the Hessian's determinant space.
 
-    A number of more advanced recipes for salient region localisation have been developed and implemented.
-These include for example SIFT \cite{sift_keypoint}, SUSAN \cite{susan_keypoint} and ISS \cite{iss_keypoint}, with the vast majority implemented for the 2D domain and only a few generalised to 3D.
-A comparative study of detectors available in the PointCloud Library (PCL) can be found in \cite{pcl_keypoint_comparision, 3d_keypoint_eval}.
-All of the above, called sparse feature detectors, resort to selection of maxima in specific state spaces.
-An entirely different scheme is to use a dense feature detector, that is to take a uniformly sampled grid of points.
-Dense detectors are advantageous in that they sample slow changing regions in terms of image derivatives.
-Examples of such regions are a clear sky or a calm ocean.
-Li \emph{et al} showed that dense detectors generally outperform sparse ones \cite{fei2005bayesian}.
+    A number of more advanced recipes for salient region localisation have been 
+developed and implemented. These include for example SIFT
+and ISS, with the vast majority 
+implemented for the 2D domain and only a few generalised to 3D. A comparative 
+study of detectors available in the PointCloud Library (PCL) can be found in 
+\cite{pcl_keypoint_comparision, 3d_keypoint_eval}. All of the above, called 
+sparse feature detectors, resort to selection of maxima in specific state 
+spaces. An entirely different scheme is to use a dense feature detector, that 
+is to take a uniformly sampled grid of points. Dense detectors are advantageous 
+in that they sample slow changing regions in terms of image derivatives. 
+Examples of such regions are a clear sky or a calm ocean. It was
+showed that dense detectors generally outperform sparse ones 
+\cite{tsai2012bag}.
 
   \subsubsection{Feature Extraction}
-    Suppose only keypoint's coordinates were given.
-The smallest affine transformation applied to the image would render the keypoints useless.
-Feature extraction is about describing a region in a way that is invariant to affine transformations, light intensity changes or colour saturation.
-Achieving all these properties simultaneously can be hard but methods that achieve some of them do exist.
-Keypoint description takes form of coordinates in a high-dimensional space.
-One of the most precise and repeatable algorithm is SIFT \cite{sift_features}, which is a 3D histogram of gradients structured as a 128-dimensional vector of floating point values.
-It is the most often extracted descriptor in BoW pipelines.
-Other methods include various colour descriptors, binary descriptors such as 512-dimensional GIST \cite{ponce2011cv}.
-There are techniques designed for 3D exclusively.
-Among them are Persistent Point Feature Histogram (PFH) \cite{pfh_rusu2008}, its faster alternative FPFH \cite{fpfh_rusu2009} and PFHRGB, which takes into account colour information, all implemented in PCL.
+    Suppose only keypoint's coordinates were given. The smallest affine 
+transformation applied to the image would render the keypoints useless. Feature 
+extraction is about describing a region in a way that is invariant to affine 
+transformations, light intensity changes or colour saturation. Achieving all 
+these properties simultaneously can be hard but methods that achieve some of 
+them do exist. Keypoint description takes form of coordinates in a 
+high-dimensional space. One of the most precise and repeatable algorithm is 
+SIFT \cite{sift_features}, which is a 3D histogram of gradients structured as a 
+128-dimensional vector of floating point values. It is the most often extracted 
+descriptor in BoW pipelines. Other methods include various colour descriptors, 
+binary descriptors such as 512-dimensional GIST. There are 
+techniques designed for 3D exclusively. Among them are Persistent Point Feature 
+Histogram (PFH) , its faster alternative FPFH 
+ and PFHRGB, which takes into account colour information, 
+all implemented in PCL.
 
   \subsubsection{Vector Quantization}
-    Vector quantization comprises of: (1)~codebook construction from a trainset and (2)~descriptor parsing, performed on a test set only on all data, depending on the setting.
-The simplest way of building a dictionary is to find patterns or regions within descriptors computed on a trainset and use their centroids or medoids as the codebook's entries.
-The parsing phase is about assigning a descriptor to one of the codebook elements (e.g.
-1-nearest neighbour matching with a centroid).
-The parsed descriptor is called a \textit{visual word}.
-Finally, a histogram of visual words can be built.
-The histogram have a fixed size equal to the codebook size.
-Each bin of the histogram tells us how many visual words of a particular kind an image contains.
+    Vector quantization comprises of: (1)~codebook construction and 
+(2)~descriptor parsing.
 
-    The kMeans is the single most popular vector quantization algorithm used in the BoW pipelines \cite{tsai2012bag}.
-Developed in 1950's, it is well known and easy to implement.
-kMeans divides all data into a predefined amount of clusters and computes the their centroids.
-Many modifications and alternative versions emerged \cite{kmeans_jain2010data}.
-Some of them are: faster than the original \emph{approximate kmeans}, \emph{hierarchical kmeans}, which automatically chooses the final number of clusters and a \emph{soft kmeans} --- a variation that allows fuzzy alignment.
-Fuzzy alignment means that each point can belong to several clusters with different weights (e.g.
-proportional to the inverse square of a distance to a centroid).
+To build a dictionary we have to describe the training set (the previous steps) 
+and find patterns in the descriptor space. A codebook can then contain 
+centroids (means or medoids) of these patterns. The parsing phase is about 
+assigning a descriptor to one of the codebook elements (e.g. 1-nearest 
+neighbour matching with a centroid). A parsed descriptor is called a 
+\textit{visual word}. Finally, we build a histogram by counting how many times 
+each visual word occured for an image. The result is a fixed-size histogram, 
+whose each bin tells us how many times a visual word occured.
 
-    If computational cost is of no concern or if required precision is of the utmost priority, Gaussian Mixture Model (GMM) can be used.
-GMM partitions data into a set of clusters, finds their means and covariances.
-In the parsing step it computes a probability distribution of a descriptor over all the clusters.
-Fuzzy aligned histogram is built by taking the probability distribution as weights.
-GMM can be thought of as a generalisation of the kMeans algorithm.
-One drawback is massive computational cost in comparison with still expensive kMeans.
-Recently, Perronnin \textit{et al} proposed GMM based fisher-kernel vector quantization step yielding superior results \cite{fisher1, fisher2}.
+    The kMeans is the single most popular vector quantization algorithm used in 
+the BoW pipelines \cite{tsai2012bag}. Developed in 1950's, it is well known and 
+easy to implement. kMeans divides all data into a predefined amount of clusters 
+and computes their centroids. Many modifications and alternative versions 
+emerged \cite{kmeans_jain2010data}. Some of them are: faster than the original 
+\emph{approximate kmeans}, \emph{hierarchical kmeans}, which automatically 
+chooses the final number of clusters and a \emph{soft kmeans} --- a variation 
+that allows fuzzy alignment. Fuzzy alignment means that each point can belong 
+to several clusters with different weights (e.g. proportional to the inverse 
+square of a distance to a centroid).
 
-    After choosing a vector quantization algorithm a codebook size have to be determined.
-With a standard kMeans implementation the dictionary size defines how much information is retained in a BoW histogram.
-A big trainset containing many classes with large intra-class and inter-class variance is likely to require a huge codebook.
-On the other hand, too big a dictionary might introduce quantization artefacts.
-One has to bear in mind that the vector quantization step is the most time-consuming part of the BoW pipeline.
-The highest computational complexity is associated with the codebook construction step and it is $O(n^3)$, where $n$ is the codebook size.
+    If computational cost is of no concern or if required precision is of the 
+utmost priority we can use Gaussian Mixture Model (GMM). It partitions data 
+into a set of clusters, finds their means and covariances. In the parsing step 
+it computes a probability distribution of a descriptor over all the clusters. 
+Fuzzy aligned histogram is built by taking the probability distribution as 
+weights. GMM can be thought of as a generalisation of the kMeans algorithm. One 
+drawback is massive computational cost in comparison with still expensive 
+kMeans. Recently, Perronnin \textit{et al} proposed GMM based fisher-kernel 
+vector quantization step yielding superior results \cite{fisher1, fisher2}.
 
-    It is possible to combine several feature extraction algorithms before creating the codebook (Early Fusion) or create many codebooks and concatenate resulting histograms (Late Fusion).
-Both schemes are as simple as vector concatenation.
-The Early Fusion concatenates two feature vectors if they have been extracted from the same keypoint.
-The Late Fusion joins histograms that are output of separate quantization steps.
+    After choosing a vector quantization algorithm a codebook size have to be 
+determined. With a standard kMeans implementation the dictionary size defines 
+how much information is retained in a BoW histogram. A big trainset containing 
+many classes with large intra- and inter-class variance is likely to 
+require a huge codebook. On the other hand, too big a dictionary might 
+introduce quantization artefacts. We have to bear in mind that the vector 
+quantization step is the most time-consuming part of the BoW pipeline. The 
+highest computational complexity is associated with the codebook construction 
+step and it is $O(n^3)$, where $n$ is the codebook size.
 
-  \subsection{Applications in Computer Vision}
-    The Bag of Words approach is a tool than enables us to represent an image by a single feature vector of a chosen size.
-Its most popular applications in computer vision are Content Based Image Retrieval (CBIR) and Scene/Object Classification.
-
-  \subsubsection{Content Based Image Retrieval}
-    CBIR is a computer vision approach to image retrieval from large image databases.
-Tangelder \emph{et al} provides an overview of techniques applicable to 3D objects \cite{tangelder2008survey}.
-The task of image retrieval is to find a database entry that fulfil certain conditions.
-If we wanted to perform the task efficiently, we would have to meet the following criteria \cite{toldo2009bag}: (1) All entries should be indexed in a concise way, (2) a (dis)similarity measure should be provided and (3) an efficient search algorithm should be available.
-
-    Database entries (images) should be indexed beforehand.
-Otherwise we would have to compare all the entries explicitly.
-An index must be compact as well as discriminative.
-Suitable algorithms can be divided into three general categories: (1) feature based methods, (2) graph based methods and (3) other methods.
-
-    Feature based methods can be further divided into global features and local features.
-The global features take form of a single vector (or a point in a \emph{d} dimensional space).
-They are usually associated with object's mass or volume or distributions of these.
-Being easy to compute and straightforward to implement, their discriminative power is rather low --- they cannot be used for partial matching, but are well suited for an early preprocessing.
-
-    Local features, on the other hand, describe object's characteristic regions.
-Their shape is similar to that of the global features, but instead of a single point in space there are multiple ones --- one for each considered region.
-Tangelder argues that local features based approaches are inefficient and lead to a complex indexing problem \cite{tangelder2008survey}.
-At the same time Toldo \emph{et al} and Li \emph{et al} show that Bag of Words local feature based approach has no such drawbacks.
-On the contrary --- it is easy to implement, efficient and provides state-of-the-art results.
-
-    Feature based methods can be either local or global.
-Local features describe characteristic regions of an object, which have to be identified first.
-We have to carry out similar computation for each salient region.
-An outcome is a set of vectors, one vector for each region in \emph{d} dimensional space, where \emph{d} is dimensionality of the descriptor.
-Global features are generally easier (faster) to compute and more compact --- they take form of a single \emph{d} dimensional vector.
-Often global features are more computationally efficient and can be easily used for object indexing .
-Before the advent of BoW it was not clear how to use local features for indexing, nor there was any straight-forward dissimilarity measure available \cite{tangelder2008survey}.
-The Bag of Words approach solved these issues.
-What is more, it is easy to implement, efficient and provides state-of-the-art results \cite{li2010investigating}.
-
-  \subsubsection{Scene and Object Classification}
-    Scene and object classification are among the most popular issues of computer vision nowadays.
-We would like to perform those tasks automatically for the sake of surveillance, navigation or automatic image tagging.
-The very first attempt to use BoW in scene classification was made by Csurka \textit{et al} in 2004 \cite{csurka2004visual}.
-They were inspired by an idea of a ``texton'', a building block of texture introduced earlier in pattern recognition and texture classification.
-The authors suggested a BoW pipeline described above.
-Then, they fed the resulting BoW histograms into two classifiers: Support Vector Machine (SVM) and Na\`ve Bayes (both discussed below).
-Fei-Fei \emph{et al} refined the original approach by examining several keypoint detectors and descriptors \cite{fei2005bayesian}.
-Moreover, they developed a novel probabilistic graphical model for classification.
-They achieved accuracy of 76\% on a large 13 category dataset.
-
-    One of the best entries in an ILSVRC2013\footnote{\url{http://www.image-net.org/challenges/LSVRC/2013/results.php}} challenge, attempting to classify millions of images into 1000 categories, was submitted by a fisher vector based BoW approach as well.
-The top-5\footnote{top-5 --- the classification result is successful if the ground-truth category is in one of the five most probable categories predicted} accuracy rate was close to 85\%.
+    It is possible to combine several feature extraction algorithms before 
+creating the codebook (Early Fusion) or create many codebooks and concatenate 
+resulting histograms (Late Fusion). Both schemes are as simple as vector 
+concatenation. The Early Fusion concatenates two feature vectors if they have 
+been extracted from the same keypoint. The Late Fusion joins histograms that 
+are output of separate quantization steps.
 
@@
 
-    To classify means to, given a set of categories, produce a category label for a given set of features \cite{ponce2011cv}.
-Image classification fits this description perfectly.
-The only difficulty lies in complexity of a raw image.
-Suppose we have a $320$ by $240$ three channel colour image.
-This amounts to a total of $230400$ dimensions, far too many to feed into any classifier directly.
-Fortunately, a Bag of Words histogram is a compact and discriminative intermediate representation that solves this issue.
-It can be used with any classifier.
-Classifiers can be two-class classifiers (e.g.
-binary) or multi-class classifiers.
-The latter are often a combination of several binary classifiers.
-The most popular classifiers are: k-Nearest Neighbours, Logistic Regression, Softmax Regression, Na\`ive Bayes and Support Vector Machine.
+    To classify means to, given a set of categories, produce a category label 
+for a given set of features. Image classification fits this 
+description perfectly. The only difficulty lies in complexity of a raw image. 
+Suppose we have a $320$ by $240$ three channel colour image. This amounts to a 
+total of $230400$ dimensions, far too many to feed into any classifier 
+directly. Fortunately, a Bag of Words histogram is a compact and discriminative 
+intermediate representation that solves this issue. It can be used with any 
+classifier. Classifiers can be two-class classifiers (e.g. binary) or 
+multi-class classifiers. The latter are often a combination of several binary 
+classifiers. The most popular classifiers are: k-Nearest Neighbours, Logistic 
+Regression, Softmax Regression, Na\`ive Bayes and Support Vector Machine.
 
-\section{ DATASETS }
+\section{ Datasets}
 
-  Datasets are essential for the following reasons: (1) Supervised learning algorithms have ravenous appetite for labeled data.
-An open database of labeled RGBD images would be of a great help in evaluation of algorithms.
-(2) If any comparison of algorithms is to be meaningful it should be performed on the same data.
-There is a multitude of RGB datasets available: ImageNet\footnote{\url{http://www.image-net.org/}}, PascalVoc\footnote{\url{http://pascallin.ecs.soton.ac.uk/challenges/VOC/}}, LabelMe\footnote{\url{http://labelme.csail.mit.edu/Release3.0/browserTools/php/dataset.php}} and SUN\footnote{\url{http://groups.csail.mit.edu/vision/SUN/}}, among others.
-Unfortunately, they do not contain any depth information and cannot be used for the purpose of object classification based on RGBD data.
-On the other hand, the vast majority of RGBD datasets are focused on tracking or instance-level recognition, have insufficient number of examples per category or have too few categories.
-Author managed to find only two datasets suited to his needs.
-They are: the Berkeley 3D Object (B3DO) dataset \cite{B3DO} and a dataset compiled by Zhang \emph{et al} at the University of Tokyo\cite{zhangcategory}.
-The latter will be abbreviated Tokyo dataset from now on.
+  Datasets are essential for the following reasons: (1) Supervised learning 
+algorithms have ravenous appetite for labeled data. An open database of labeled 
+RGBD images would be of great help in evaluation of algorithms. (2) If any 
+comparison of algorithms is to be meaningful it should be performed on the same 
+data. There is a multitude of RGB datasets available: 
+ImageNet\footnote{\url{http://www.image-net.org/}}, 
+PascalVoc\footnote{\url{http://pascallin.ecs.soton.ac.uk/challenges/VOC/}}, 
+LabelMe\footnote{\url{
+http://labelme.csail.mit.edu/Release3.0/browserTools/php/dataset.php}} and 
+SUN\footnote{\url{http://groups.csail.mit.edu/vision/SUN/}}, among others. 
+Unfortunately, they do not contain any depth information and cannot be used for 
+the purpose of object classification based on RGBD data. On the other hand, the 
+vast majority of RGBD datasets are focused on tracking or instance-level 
+recognition, have insufficient number of examples per category or have too few 
+categories. Author managed to find only two datasets suited to his needs. They 
+are: the Berkeley 3D Object (B3DO) dataset \cite{B3DO} and a dataset compiled 
+by Zhang \emph{et al} at the University of Tokyo\cite{zhangcategory}. The 
+latter will be abbreviated Tokyo dataset from now on.
 
@@
 
-    The Berkeley 3D Object dataset, shown in \refFig{fig:b3do_objects}, was specifically designed for the purpose of object detection and classification.
-It consists of cluttered images in indoor environment, with many labelled and random objects per image.
-The images are often poorly lit and objects are partially occluded.
-There are around 50 classes with more than 20 examples in each of them.
-RGBD data are provided as pairs of colour images (8 bit RGB jpeg files) and depth maps (16 bit png files).
-Images are densely labelled --- for every pair of images there is an xml file with annotations.
-Each annotation states a category of an object as well as it's bounding box location.
-Since neither image segmentation nor object detection is addressed in this paper we had to extract objects from the images before the dataset could be used.
+    The Berkeley 3D Object dataset, shown in figure \ref{fig:b3do_objects}, was 
+specifically designed for the purpose of object detection and classification. 
+It consists of cluttered images in indoor environment, with many labelled and 
+random objects per image. The images are often poorly lit and objects are 
+partially occluded. There are around 50 classes with more than 20 examples in 
+each of them. RGBD data are provided as pairs of colour images (8 bit RGB jpeg 
+files) and depth maps (16 bit png files). Images are densely labelled --- for 
+every pair of images there is an xml file with annotations. Each annotation 
+states a category of an object as well as it's bounding box location. Since 
+neither image segmentation nor object detection is addressed in this paper we 
+had to extract objects from the images before the dataset could be used.
 
@@
     \includegraphics[width=1\textwidth]{../figs/tokyo_horizontal}
-    \caption{The Tokyo dataset: a) basket b) bicycle c) box d) bucket e) cart f) freezer g) notebook h) printer i) scanner j) scene}
+    \caption{The Tokyo dataset: a) basket b) bicycle c) box d) bucket e) cart 
+f) freezer g) notebook h) printer i) scanner j) scene}
     \label{fig:tokyo}
@@
 
-    The Tokyo dataset, shown in \refFig{fig:tokyo}, is comprised of high quality images of single labelled objects in different settings, with changing viewpoint, object orientation and texture.
-Additional unlabelled object can be present, however, and should not be taken into account.
-No bounding boxes are given, which renders the classification task similar to the scene classification problem.
-The dataset is presented as colour images (8 bit RGB jpeg files) and depth maps (csv files with XYZ coordinates of each pixel).
-This dataset is aimed at the task of object classification in casual images.
+    The Tokyo dataset, shown in figure \ref{fig:tokyo}, is comprised of high 
+quality images of single labelled objects in different settings, with changing 
+viewpoint, object orientation and texture. Additional unlabelled objects can be 
+present, however, and should not be taken into account. No bounding boxes are 
+given, which renders the classification task similar to the scene 
+classification problem. The dataset is presented as colour images (8 bit RGB 
+jpeg files) and depth maps (csv files with XYZ coordinates of each pixel). This 
+dataset is aimed at the task of object classification in casual images.
 
-\section{ EXPERIMENTS }
-  There is a plenty of algorithms suitable for any of the four steps of Bag of Words image processing.
-Most of them have multiple tunable parameters and their performance might be interdependent on each other.
-Comprehensive evaluation is inevitable if an optimal combination is to be selected.
-Considering the PointCloud Library\footnote{\url{http://pointclouds.org/}} (PCL) alone yields far too many options to test, with 12 keypoint detectors and more than 20 feature descriptors.
-A literature review helped to narrow the scope of evaluation considerably.
-All experiments were run on a notebook with Intel Core i7 quad core 2.2 GHz CPU, 8 GB of RAM and a nVidia M540 GPU.
+\section{ Experiments }
+  There is a plenty of algorithms suitable for any of the four steps of Bag of 
+Words image processing. Most of them have multiple tunable parameters and their 
+performance might be interdependent on each other. Comprehensive evaluation is 
+inevitable if an optimal combination is to be selected. Considering the 
+PointCloud Library\footnote{\url{http://pointclouds.org/}} (PCL) alone yields 
+far too many options to test, with 12 keypoint detectors and more than 20 
+feature descriptors. A literature review helped to narrow the scope of 
+evaluation considerably. All experiments were run on a notebook with Intel Core 
+i7 quad core 2.2 GHz CPU, 8 GB of RAM and a nVidia M540 GPU.
 
   \subsection{Detectors and descriptors}
-    Keypoint detection algorithms were compared with respect to repeatability and invariance in \cite{pcl_keypoint_comparision} as well as in terms of object retrieval and recognition in \cite{3d_keypoint_eval}.
-3D-SIFT and ISS both achieve the highest robustness, while the latter appears to be the best choice for object retrieval.
-Dense detector (or uniform sampling) achieves the best performance in 2D image classification \cite{tsai2012bag}.
-Therefore, this paper compares SIFT, ISS and Uniform Sampling keypoint detection techniques.
-Additionally, PCL descriptors were evaluated in terms of object retrieval performance in \cite{pcl_features}.
-PFHRGB and SHOTCOLOR delivered the best results, while their simpler counterparts (PFH, FPFH, SHOT) were only a little worse.
-USC, which is a global descriptor and thus not suitable for the Bag of Words approach, achieved very similar accuracy.
-The family of PFH descriptors is evaluated in this paper.
+    Keypoint detection algorithms were compared with respect to repeatability 
+and invariance in \cite{pcl_keypoint_comparision} as well as in terms of object 
+retrieval and recognition in \cite{3d_keypoint_eval}. 3D-SIFT and ISS both 
+achieve the highest robustness, while the latter appears to be the best choice 
+for object retrieval. Dense detector (or uniform sampling) achieves the best 
+performance in 2D image classification \cite{tsai2012bag}. Therefore, this 
+paper compares SIFT, ISS and Uniform Sampling keypoint detection techniques. 
+Additionally, PCL descriptors were evaluated in terms of object retrieval 
+performance in \cite{pcl_features}. PFHRGB and SHOTCOLOR delivered the best 
+results, while their simpler counterparts (PFH, FPFH, SHOT) were only a little 
+worse. USC, which is a global descriptor and thus not suitable for the Bag of 
+Words approach, achieved very similar accuracy. The family of PFH descriptors 
+is evaluated in this paper.
 
@@
     \centering
-      \caption{Highest accuracy obtained with FPFH, PFH and PFHRGB descriptors on the B3DO dataset}
+      \caption{Highest accuracy obtained with FPFH, PFH and PFHRGB descriptors 
+on the B3DO dataset}
       \label{tab:desc_b3do}
@@
 
-    The best results of each detector/descriptor combination on the B3DO dataset are shown in table \ref{tab:desc_b3do}.
-ISS consistently proved to be the most successful detection algorithm in this setting.
-SIFT and Uniform Sampling scored similar accuracy but the latter is significantly faster.
-SIFT is in fact the slowest of the three.
-As for the descriptors, FPFH delivered the best performance, even though it is an approximate and theoretically the least precise algorithm.
-It is also the fastest of the three.
-The combination of ISS and FPFH delivers outstanding results at the lowest computational cost.
-It allows near real time point-cloud processing and classification.
-PFHRGB and SIFT are several times slower.
+    The best results of each detector/descriptor combination on the B3DO 
+dataset are shown in table \ref{tab:desc_b3do}. ISS consistently proved to be 
+the most successful detection algorithm in this setting. SIFT and Uniform 
+Sampling scored similar accuracy but the latter is significantly faster. SIFT 
+is in fact the slowest of the three. As for the descriptors, FPFH delivered the 
+best performance, even though it is an approximate and theoretically the least 
+precise algorithm. It is also the fastest of the three. The combination of ISS 
+and FPFH delivers outstanding results at the lowest computational cost. It 
+allows near real time point-cloud processing and classification. PFHRGB and 
+SIFT are several times slower.
 
   \subsection{Codebook}
-    KMeans is used in almost every implementation of the Bag of Words image processing pipeline \cite{tsai2012bag, toldo2009bag}.
-Csurka \emph{et al} showed that the number of visual words has a significant impact on the final results \cite{csurka2004visual}.
-A number of tests were run to discover an optimal codebook size for the current setting.
+    KMeans is used in almost every implementation of the Bag of Words image 
+processing pipeline \cite{tsai2012bag}. The number of visual words can have a 
+significant impact on the final results. A number of tests were run to discover 
+an optimal codebook size for the current setting.
 
@@
     \includegraphics[width=.75\textwidth]{../figs/clustering_centroids_b3do}
-    \caption{Influence of dictionary size on the overall accuracy. B3DO dataset with ISS keypoint detector and FPFH feature descriptor}
+    \caption{Influence of dictionary size on the overall accuracy. B3DO dataset 
+with ISS keypoint detector and FPFH feature descriptor}
     \label{fig:cluster_b3do}
@@
 
-    The results from \refFig{fig:cluster_b3do} partially confirm Csurka's findings.
-The performance raises with the increasing number of centroids up to the point of 1500 centroids and 65.22\%.
-The discrepancies might be caused by the following factors: (1) ISS detector finds too many or irrelevant points, thus introducing noise or (2) The FPFH descriptor has too few dimensions (33) to be divided into more than 1500 regions in a meaningful way.
+    The results from figure \ref{fig:cluster_b3do} partially confirm Csurka's 
+findings. The performance raises with the increasing number of centroids up to 
+the point of 1500 centroids and 65.22\%. The discrepancies might be caused by 
+the following factors: (1) ISS detector finds too many or irrelevant points, 
+thus introducing noise or (2) The FPFH descriptor has too few dimensions (33) 
+to be divided into more than 1500 regions in a meaningful way.
 
   \subsection{B3DO}
-    Extracting objects from the B3DO datasets yielded far too many and unbalanced categories.
-The number of objects in each category varies from 1 (tape) to 299 (table).
-8 categories were picked at random with a restriction that there should be at least 50 object instances in a category.
-Then, the objects were split into train and test set with a proportion of 1:1, which were used for estimation and evaluation respectively.
+    Extracting objects from the B3DO datasets yielded far too many and 
+unbalanced categories. The number of objects in each category varies from 1 
+(tape) to 299 (table). 8 categories were picked at random with a restriction 
+that there should be at least 50 object instances in a category. Then, the 
+objects were split into train and test set with a proportion of 1:1, which were 
+used for estimation and evaluation respectively.
 
-    The highest accuracy achieved for this dataset is 65.22\%.
-Table \ref{tab:b3do_conf_matrix} contains a confusion matrix, number of examples per category and accuracy.
-The confusion matrix depicts classification errors.
-Let $m_{i, j}$ be an element of the confusion matrix at the $i^{th}$ row and $j^{th}$ column.
-It shows how many elements from the $i^{th}$ category was assigned to the $j^{th}$ category.
-A high value of $m_{i, j}$ such that $i \neq j$ indicates that the classifier cannot distinguish those two classes.
+    The highest accuracy achieved for this dataset is 65.22\%. Table 
+\ref{tab:b3do_conf_matrix} contains a confusion matrix, number of examples per 
+category and accuracy. The confusion matrix depicts classification errors. Let 
+$m_{i, j}$ be an element of the confusion matrix at the $i^{th}$ row and 
+$j^{th}$ column. It shows how many elements from the $i^{th}$ category was 
+assigned to the $j^{th}$ category. A high value of $m_{i, j}$ such that $i \neq 
+j$ indicates that the classifier cannot distinguish those two classes.
 
@@
     \centering
-    \caption{Results on the B3DO dataset with ISS keypoint detector, FPFH features and a dictionary of 1500 words; \textbf{Average accuracy: 65.22\%}}
+    \caption{Results on the B3DO dataset with ISS keypoint detector, FPFH 
+features and a dictionary of 1500 words; \textbf{Average accuracy: 65.22\%}}
     \includegraphics[width=0.9\textwidth]{../figs/b3do_conf_matrix}	
@@
 
-    More than half of the bottles were assigned to the cup category and keyboards were often mistook for books.
-These two error types are easily explained by a high degree of similarity of objects (bottles and cups are usually round and tall, books and keyboards are flat and rectangular) Surprisingly, however, objects from half of the categories were frequently marked as cups.
-Some of these misclassification errors might be caused by very poor quality of images.
-Many of them are occluded poorly lit low resolution images.
+    More than half of the bottles were assigned to the cup category and 
+keyboards were often mistook for books. These two error types are easily 
+explained by a high degree of similarity of objects (bottles and cups are 
+usually round and tall, books and keyboards are flat and rectangular) 
+Surprisingly, however, objects from half of the categories were frequently 
+marked as cups. Some of these misclassification errors might be caused by very 
+poor quality of images. Many of them are occluded poorly lit low resolution 
+images.
 
@@
     \centering
-    \caption{Results on the Tokyo dataset with ISS keypoint detector, PFH features and a dictionary of 3000 words; \textbf{Average accuracy: 62.30\%}}
+    \caption{Results on the Tokyo dataset with ISS keypoint detector, PFH 
+features and a dictionary of 3000 words; \textbf{Average accuracy: 62.30\%}}
     \includegraphics[width=1\textwidth]{../figs/tokyo_conf_matrix}	
@@
 
-    Everyone of the 343 images from the Tokyo dataset were used.
-Data were split into test and train set in proportions 1:2 in order to provide more training examples due to very limited numbers of objects in some classes.
-Even tough the overall accuracy achieved on the Tokyo dataset is similar in value to that of the B3DO's, the structure of the result is very different as shown in table \ref{tab:tokyo_conf_matrix}.
-It is clearly visible that there is a strong correlation between a per class accuracy and the number of entries in this class.
-The highest performance in the bicycle category is coupled with the largest number of entries.
-On the other end of the scale there are the printer, scanner and cart categories with 2, 2 and 4 entries respectively and 0\% classification accuracy.
-On top of that, the differences between some classes are marginal.
-The majority of carts and baskets were put into the bucket category.
-It does not surprise, for they are simply akin as can be seen in \refFig{fig:tokyo}.
+    Everyone of the 343 images from the Tokyo dataset were used. Data were 
+split into test and train set in proportions 1:2 in order to provide more 
+training examples due to very limited numbers of objects in some classes. Even 
+tough the overall accuracy achieved on the Tokyo dataset is similar in value to 
+that of the B3DO's, the structure of the result is very different as shown in 
+table \ref{tab:tokyo_conf_matrix}. It is clearly visible that there is a strong 
+correlation between a per class accuracy and the number of entries in this 
+class. The highest performance in the bicycle category is coupled with the 
+largest number of entries. On the other end of the scale there are the printer, 
+scanner and cart categories with 2, 2 and 4 entries respectively and 0\% 
+classification accuracy. On top of that, the differences between some classes 
+are marginal. The majority of carts and baskets were put into the bucket 
+category. It does not surprise, for they are simply akin as can be seen in 
+figure \ref{fig:tokyo}.
 
-\section{ CONCLUSION }
+\section{ Conclusion }
 
-  In this paper the issue of three dimensional point cloud classification with a bag of words-based approach was tackled.
-Two scientific databases suitable for the task of point cloud classification were identified and adapted for the purpose of this work.
-Presence of such datasets is vital --- they act as benchmarks and allow objective comparison of different solutions of the problem.
-The following problems emerged: (1)~Point cloud processing is computationally expensive and inefficient.
-Due to the lack of structure in point clouds (\textit{i.e.} no predefined spatial relationships between points) additional calculations have to be performed (\textit{e.g.} finding nearest neighbours requires at least several distance computations).
-(2)~There are very few and small databases available.
-Machine learning algorithms have ravenous appetite for labelled data.
-As the newest findings in the state-of-the-art 2D object classification suggest, an order of tens of thousands of samples is a prerequisite for any satisfactory results.
-This work had to make do with less than 300 objects in the train sets.
-(3)~There is very little interest in the scientific community for this particular task.
-The majority of research is conducted on retrieval of CAD-like objects from mesh databases.
+  In this paper the issue of three dimensional point cloud classification with 
+a bag of words-based approach was tackled. Two scientific databases suitable 
+for the task of point cloud classification were identified and adapted for the 
+purpose of this work. Presence of such datasets is vital --- they act as 
+benchmarks and allow objective comparison of different solutions of the 
+problem. The following problems emerged: (1)~Point cloud processing is 
+computationally expensive and inefficient. Due to the lack of structure in 
+point clouds (\textit{i.e.} no predefined spatial relationships between points) 
+additional calculations have to be performed (\textit{e.g.} finding nearest 
+neighbours requires at least several distance computations). (2)~There are very 
+few and small databases available. Machine learning algorithms have ravenous 
+appetite for labelled data. As the newest findings in the state-of-the-art 2D 
+object classification suggest, an order of tens of thousands of samples is a 
+prerequisite for any satisfactory results. This work had to make do with less 
+than 300 objects in the train sets. (3)~There is very little interest in the 
+scientific community for this particular task. The majority of research is 
+conducted on retrieval of CAD-like objects from mesh databases.
 
-  The achieved results the B3DO and Tokyo datasets are respectively $5.21$ and $6.23$ times higher than random rates ($12.5\%$ and $10\%$).
-This shows that classification of point clouds is feasible and can be performed in what is close to real time on a mainstream notebook.
-The accuracy can be further enhanced by generalising 2D algorithms to the 3D domain, while the computational time can be reduced by using a GPU for the most computationally expensive parts of the Bag of Words framework.
-In conclusion, the depth data does not account for a straightforward improvement in classification accuracy.
-In fact, it is easier to obtain better results on 2D RGB images, because the best algorithms are not converted to the 3D domain and there is substantially more data available for the 2D.
+  The achieved results the B3DO and Tokyo datasets are respectively $5.21$ and 
+$6.23$ times higher than random rates ($12.5\%$ and $10\%$). This shows that 
+classification of point clouds is feasible and can be performed in what is 
+close to real time on a mainstream notebook. The accuracy can be further 
+enhanced by generalising 2D algorithms to the 3D domain, while the 
+computational time can be reduced by using a GPU for the most computationally 
+expensive parts of the Bag of Words framework. In conclusion, the depth data 
+does not account for a straightforward improvement in classification accuracy. 
+In fact, it is easier to obtain better results on 2D RGB images, because the 
+best algorithms are not converted to the 3D domain and there is substantially 
+more data available for the 2D.
 

### 2014-10-14 docs/piap/monografia/kkr13-eng.tex
po polsku

--- 2014-10-12 docs/min/kkr13-eng.tex
@@
 
-\title{3D Object Classification Based on RGBD Images}
+\title{Bag of Words Semantic Object Classification Based on RGBD Images}
 \author{Adam Kosiorek}
 \maketitle
+e-mail: kosiorek.adam@gmail.com
 Affiliation: Institute of Automation and Robotics, The Faculty of Mechatronics 
 of Warsaw University of Technology \\
-website: http://iair.mchtr.pw.edu.pl \\
 Supervisor: Prof. dr hab. Barbara Siemiątkowska \\
-Defense date: 11.02.2014
+Defense date: 11.02.2014 \\
+Keywords: bag-of-visual-words, object-classification, rgbd, point-cloud, datasets
 
@@
 
- This paper introduces a Bag of Words (BoW) semantic object classification 
-framework based on RGBD data registered by a Microsoft Kinect camera. We 
-introduce a BoW image processing 
-pipeline, describe it's steps in detail (region detection, feature 
-extraction and vector quantization) and we outline the most successful 
-algorithms. Algorithms with high performance potential were identified and 
-evaluated. 
-Salient region detection is done by SIFT, ISS3D and Uniform Sampling. 
-Description is performed by FPFH, PFH and PFHRGB. Vector quantization was 
-carried out by KMeans. An SVM with the RBF kernel trained with an 
-All-vs-All method was used as a classifier. We achieved the accuracy of 65.22\% 
-on 8 
-categories of the Berkely 3D Object Dataset and 62.3\% on a 10 category dataset 
-compiled by Zhang.
+This paper reviews a Bag of Words (BoW) semantic object classification framework 
+based on RGBD data registered by the Microsoft Kinect. We describe a BoW 
+processing pipeline (region detection, feature extraction and vector 
+quantization) and evaluate the most popular algorithms in terms of object 
+classification performance. Salient region detection is done by SIFT, ISS3D and 
+Uniform Sampling. Description is performed by FPFH, PFH and PFHRGB. Vector 
+quantization was carried out by KMeans.  All-vs-All-trained SVM with the RBF 
+kernel was used as a classifier. We review available point cloud databases in 
+terms of usability in scene classification studies. We achieved the accuracy of 
+65.22\% on 8 categories of the Berkeley 3D Object Dataset and 62.3\% on a 10 
+category dataset compiled by Zhang.
 
 }
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+%	Po Polsku !!!
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\title{Semantyczna klasyfikacja obiektów na obrazach RGBD metodą Bag of Words}
+Słowa kluczowe: bag-of-visual-words, object-classification, rgbd, chmura-punktów, zbiór-danych
+\abstract{
+
+W pracy przedstawiono metodę klasyfikacji metodą Bag of Words (Bow) obrazów RGBD zarejstrowanych kamerą 
+Microsoft Kinect. Omówiono proces przetwarzania BoW 
+(detekcja i opis punktów, kwantyzacja i klasyfikacja) oraz zbadano 
+najpopularniejsze algorytmy ze względu na efektywność klasyfikacji obiektów. 
+Detekcja odbywa się za pomocą algorytmów SIFT, ISS3D i Uniform Sampling; do 
+opisu punktów wykorzystano FPFH, PFH i PFHRGB; kwantyzację wykonano za pomocą 
+algorytmu KMeans; jako klasyfikator użyto SVM z jądrem RBF trenowany metodą 
+All-vs-All. Dokonano przeględu baz danych chmur punktów pod względem 
+przydatności w badaniach klasyfikacji obiektów. Uzyskano skuteczność 
+klasyfikacji 65.22\% na zbiorze 8 kategorii z Berkely 3D Object Dataset oraz 
+62.3\% na zabiorze 10 kategorii udostępnionych przez Zhanga.
+
+}
+
+Podpisy pod rysunkami w kolejności występowania:
+1. histogram w reprezentacji Bag of Words
+2. Proces przetwarzania Bag of Words. Grafika pochodzi z [9]
+3. obiekty ze zbioru B3D) a) kubki b) butelki c) książki d) klawiatury
+4. Zbiór danych Tokyo a) koszyk b) rower c) pudełko d) koszyk e) wózek f) zamrażarka g) notebook h) drukarka i) skaner j) scena
+5. Wpływ rozmiaru słownika na trafność klasyfikacji. Zbiór B3DO z detektorem ISS i deskryptorem FPFH
+
+Opisy tabel:
+1. Najwyższa trafność klasyfikacji z deskryptorami FPFH, PFH, PFHRGB na zbiorze B3DO
+2. Wyniki na zbiorze B3DO z detektorem ISS, deskryptorem FPFH i słownikiem zawierającym 1500 słów
+3. Wyniki na zbiorze Tokyo z detektorem ISS i deskryptorem PFH i słownikiem zawierającym 3000 słów
+
+%%%%%%%%%%%%%%
+%	Treść
+%%%%%%%%%%%%%%
 
@@
 becoming increasingly harder to browse. Similar issues occur in mobile 
-robotics, where a robot has to understand it's enviornment if it is to interact 
+robotics, where a robot has to understand it's environment if it is to interact 
 with it. Both problems can be cast as a scene or object classification problem, 
@@
 in scene classification studies and applies BoW model in the 3D domain. The 
-rest of this work is organised as follows: Section 2 describes the Bag of Words 
+rest of this work is organized as follows: Section 2 describes the Bag of Words 
 technique in detail. Construction of an image model is discussed and the most 
@@
 assumes that word occurrence in a text document carries semantic information. 
-It is an intermediate representation (in a form of a hisogram)
+It is an intermediate representation (in a form of a histogram)
 used in natural language processing, information retrieval and general data 
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{../figs/bow_example}
+  \includegraphics[width=0.7\textwidth]{figs/bow_example}
   \caption{Bag of Words histogram}
@@
 and (4) BoW histogram formation as in figure \ref{fig:bow_pipeline}. Tsai 
-summarises the most common methods used recently \cite{tsai2012bag}.
+summarizes the most common methods used recently \cite{tsai2012bag}.
 
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{../figs/tsai2012}
+    \includegraphics[width=0.75\textwidth]{figs/tsai2012}
     \caption{Bag of Words pipeline. The figure comes from \cite{tsai2012bag}}
@@
 
-    A number of more advanced recipes for salient region localisation have been 
+    A number of more advanced recipes for salient region localization have been 
 developed and implemented. These include for example SIFT
 and ISS, with the vast majority 
-implemented for the 2D domain and only a few generalised to 3D. A comparative 
+implemented for the 2D domain and only a few generalized to 3D. A comparative 
 study of detectors available in the PointCloud Library (PCL) can be found in 
@@
 extraction is about describing a region in a way that is invariant to affine 
-transformations, light intensity changes or colour saturation. Achieving all 
+transformations, light intensity changes or color saturation. Achieving all 
 these properties simultaneously can be hard but methods that achieve some of 
@@
 128-dimensional vector of floating point values. It is the most often extracted 
-descriptor in BoW pipelines. Other methods include various colour descriptors, 
+descriptor in BoW pipelines. Other methods include various color descriptors, 
 binary descriptors such as 512-dimensional GIST. There are 
@@
 Histogram (PFH) , its faster alternative FPFH 
- and PFHRGB, which takes into account colour information, 
+ and PFHRGB, which takes into account color information, 
 all implemented in PCL.
@@
 assigning a descriptor to one of the codebook elements (e.g. 1-nearest 
-neighbour matching with a centroid). A parsed descriptor is called a 
+neighbor matching with a centroid). A parsed descriptor is called a 
 \textit{visual word}. Finally, we build a histogram by counting how many times 
-each visual word occured for an image. The result is a fixed-size histogram, 
-whose each bin tells us how many times a visual word occured.
+each visual word occurred for an image. The result is a fixed-size histogram, 
+whose each bin tells us how many times a visual word occurred.
 
-    The kMeans is the single most popular vector quantization algorithm used in 
+    The KMeans is the single most popular vector quantization algorithm used in 
 the BoW pipelines \cite{tsai2012bag}. Developed in 1950's, it is well known and 
-easy to implement. kMeans divides all data into a predefined amount of clusters 
+easy to implement. KMeans divides all data into a predefined amount of clusters 
 and computes their centroids. Many modifications and alternative versions 
 emerged \cite{kmeans_jain2010data}. Some of them are: faster than the original 
-\emph{approximate kmeans}, \emph{hierarchical kmeans}, which automatically 
-chooses the final number of clusters and a \emph{soft kmeans} --- a variation 
+\emph{approximate KMeans}, \emph{hierarchical KMeans}, which automatically 
+chooses the final number of clusters and a \emph{soft KMeans} --- a variation 
 that allows fuzzy alignment. Fuzzy alignment means that each point can belong 
@@
 Fuzzy aligned histogram is built by taking the probability distribution as 
-weights. GMM can be thought of as a generalisation of the kMeans algorithm. One 
+weights. GMM can be thought of as a generalization of the KMeans algorithm. One 
 drawback is massive computational cost in comparison with still expensive 
-kMeans. Recently, Perronnin \textit{et al} proposed GMM based fisher-kernel 
+KMeans. Recently, Perronnin \textit{et al} proposed GMM based fisher-kernel 
 vector quantization step yielding superior results \cite{fisher1, fisher2}.
@@
     After choosing a vector quantization algorithm a codebook size have to be 
-determined. With a standard kMeans implementation the dictionary size defines 
+determined. With a standard KMeans implementation the dictionary size defines 
 how much information is retained in a BoW histogram. A big trainset containing 
@@
 description perfectly. The only difficulty lies in complexity of a raw image. 
-Suppose we have a $320$ by $240$ three channel colour image. This amounts to a 
+Suppose we have a $320$ by $240$ three channel color image. This amounts to a 
 total of $230400$ dimensions, far too many to feed into any classifier 
@@
 multi-class classifiers. The latter are often a combination of several binary 
-classifiers. The most popular classifiers are: k-Nearest Neighbours, Logistic 
+classifiers. The most popular classifiers are: k-Nearest Neighbors, Logistic 
 Regression, Softmax Regression, Na\`ive Bayes and Support Vector Machine.
@@
     \centering	
-    \includegraphics[width=.75\textwidth]{../figs/b3do_objects}
+    \includegraphics[width=.75\textwidth]{figs/b3do_objects}
     \caption{B3DO objects: a) cups b) bottles c) books d) keyboards}
@@
 specifically designed for the purpose of object detection and classification. 
-It consists of cluttered images in indoor environment, with many labelled and 
+It consists of cluttered images in indoor environment, with many labeled and 
 random objects per image. The images are often poorly lit and objects are 
 partially occluded. There are around 50 classes with more than 20 examples in 
-each of them. RGBD data are provided as pairs of colour images (8 bit RGB jpeg 
-files) and depth maps (16 bit png files). Images are densely labelled --- for 
+each of them. RGBD data are provided as pairs of color images (8 bit RGB jpeg 
+files) and depth maps (16 bit png files). Images are densely labeled --- for 
 every pair of images there is an xml file with annotations. Each annotation 
@@
     \centering
-    \includegraphics[width=1\textwidth]{../figs/tokyo_horizontal}
+    \includegraphics[width=1\textwidth]{figs/tokyo_horizontal}
     \caption{The Tokyo dataset: a) basket b) bicycle c) box d) bucket e) cart 
@@
     The Tokyo dataset, shown in figure \ref{fig:tokyo}, is comprised of high 
-quality images of single labelled objects in different settings, with changing 
-viewpoint, object orientation and texture. Additional unlabelled objects can be 
+quality images of single labeled objects in different settings, with changing 
+viewpoint, object orientation and texture. Additional unlabeled objects can be 
 present, however, and should not be taken into account. No bounding boxes are 
 given, which renders the classification task similar to the scene 
-classification problem. The dataset is presented as colour images (8 bit RGB 
+classification problem. The dataset is presented as color images (8 bit RGB 
 jpeg files) and depth maps (csv files with XYZ coordinates of each pixel). This 
@@
     \centering	
-    \includegraphics[width=.75\textwidth]{../figs/clustering_centroids_b3do}
+    \includegraphics[width=.75\textwidth]{figs/clustering_centroids_b3do}
     \caption{Influence of dictionary size on the overall accuracy. B3DO dataset 
@@
 features and a dictionary of 1500 words; \textbf{Average accuracy: 65.22\%}}
-    \includegraphics[width=0.9\textwidth]{../figs/b3do_conf_matrix}	
+    \includegraphics[width=0.9\textwidth]{figs/b3do_conf_matrix}	
     \label{tab:b3do_conf_matrix}
@@
 features and a dictionary of 3000 words; \textbf{Average accuracy: 62.30\%}}
-    \includegraphics[width=1\textwidth]{../figs/tokyo_conf_matrix}	
+    \includegraphics[width=1\textwidth]{figs/tokyo_conf_matrix}	
     \label{tab:tokyo_conf_matrix}
@@
 additional calculations have to be performed (\textit{e.g.} finding nearest 
-neighbours requires at least several distance computations). (2)~There are very 
+neighbors requires at least several distance computations). (2)~There are very 
 few and small databases available. Machine learning algorithms have ravenous 
-appetite for labelled data. As the newest findings in the state-of-the-art 2D 
+appetite for labeled data. As the newest findings in the state-of-the-art 2D 
 object classification suggest, an order of tens of thousands of samples is a 
@@
 close to real time on a mainstream notebook. The accuracy can be further 
-enhanced by generalising 2D algorithms to the 3D domain, while the 
+enhanced by generalizing 2D algorithms to the 3D domain, while the 
 computational time can be reduced by using a GPU for the most computationally 
